### 2012-01-21 writeups/proposal/proposal.tex
ported rl_detection writeups in

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\pagestyle{headings}
\usepackage[top=1in, bottom=1in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{subfig}
\usepackage{color}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false,citecolor=red,linkcolor=blue]{hyperref}

%% Command definitions
\def\subsectionautorefname{section}
\newcommand{\note}[1]{\textcolor{red}{\textbf{#1}}}
\definecolor{light-gray}{gray}{0.3}
\newcommand{\aside}[1]{\textcolor{light-gray}{\emph{#1}}}
\newcommand{\comment}[1]{}

\title{Attentional Object Detection: A Proposal}
\author{Sergey Karayev}
\date{updated: 22 April 2011}

\begin{document}
\maketitle

\begin{abstract}
This document tracks the development of ideas for efficient object detection using the idea of attention: a sequential process of looking for something somewhere.
We follow the Deformable Part Model approach to object detection and extend it in several ways, mostly focusing on the role of context, toward the goal of Anytime detection performance.
I expect a submission to NIPS'11 to be whittled down from the text and results here.
\end{abstract}

\tableofcontents
\newpage

\input{introduction.tex}
\input{related_work.tex}
\input{evaluation.tex}
\input{our_approach.tex}
\input{discretization_and_featurization.tex}
\input{ideas.tex}
\input{results.tex}

\bibliographystyle{ieeetr}
\small
\bibliography{../sergeyk-bibtex.bib}
\end{document}

### 2012-01-21 writeups/rl_class/report.tex
ported rl_detection writeups in

--- 2012-01-21 writeups/proposal/proposal.tex
@@
-\documentclass[11pt]{article}
+\documentclass[10pt]{article}
 \usepackage[utf8]{inputenc}
@@
 
-\title{Attentional Object Detection: A Proposal}
+\title{Attentional Object Detection\\
+Report for CS 294-67 Sequential Decisions}
 \author{Sergey Karayev}
-\date{updated: 22 April 2011}
+\date{13 May 2011}
 
@@
 \begin{abstract}
-This document tracks the development of ideas for efficient object detection using the idea of attention: a sequential process of looking for something somewhere.
-We follow the Deformable Part Model approach to object detection and extend it in several ways, mostly focusing on the role of context, toward the goal of Anytime detection performance.
-I expect a submission to NIPS'11 to be whittled down from the text and results here.
+  Multi-class object detection in cluttered natural scenes is a long-standing open problem in computer vision.
+Currently best-performing approaches are computationally expensive.
+We seek to ameliorate this through replacing exhaustive and unprioritized search with a sequential decision process.
 \end{abstract}
-
-\tableofcontents
-\newpage
 
@@
 \input{our_approach.tex}
-\input{discretization_and_featurization.tex}
-\input{ideas.tex}
-\input{results.tex}
+\input{experiments.tex}
 

### 2012-02-04 synthetic/config.py
cleaned up classifier.py by putting file paths in config.py and misc stuff; added empty test file for it

@@ -39,6 +39,7 @@ else:
   raise RuntimeError("Can't set paths correctly")
 
 # repo_dir, data_dir, temp_data_dir
+# temp_data_dir is not propagated between machines!
 paths = {
   'tobi_home':    ['/home/tobibaum/Documents/Vision/timely/',
                    '/home/tobibaum/Documents/Vision/timely/data/',
@@ -78,7 +79,7 @@ config_dir = join(script_dir,'configs')
 
 # Result data
 res_dir = makedirs(join(data_dir, 'results'))
-temp_res_dir = makedirs(join(temp_data_dir, 'results'))
+temp_res_dir = makedirs(join(data_dir, 'temp_results'))
 dets_configs_dir = makedirs(join(res_dir,'det_configs'))
 
 # ./results/sliding_windows_{dataset}
@@ -150,7 +151,9 @@ def get_ext_dets_filename(dataset, suffix):
   dataset_name = dataset.name # NOTE does not depend on # images
   return join(dirname, '%s_%s.npy'%(dataset_name,suffix))
 
-# directory for gist features
+#####
+# GIST
+#####
 gist_dir = makedirs(join(res_dir, 'gist_features'))
 
 def get_gist_dict_filename(dataset_name):
@@ -159,3 +162,25 @@ def get_gist_dict_filename(dataset_name):
 def get_gist_svm_filename(for_cls):
   dirname = makedirs(join(gist_dir,'svm'))
   return join(dirname,for_cls)
+
+#####
+# Classifier
+#####
+# learning
+def get_classifier_learning_dirname(classifier):
+  return makedirs(join(config.temp_res_dir, classifier.name+'_svm_'+classifier.suffix))
+
+def get_classifier_learning_filename(classifier,cls,kernel,intervals,lower,upper,C)
+  dirname = makedirs(join(get_classifier_learning_dirname(classifier), kernel, str(intervals))
+  return join(dirname, "%s_%d_%d_%d"%(cls,lower,upper,C))
+    
+def get_classifier_learning_eval_filename(classifier,cls,kernel,intervals,lower,upper,C)
+  dirname = makedirs(join(get_classifier_learning_dirname(classifier), kernel, str(intervals))
+  return join(dirname, "eval_%d_%d_%d"%(lower,upper,C))
+
+# final
+def get_classifier_dirname(classifier):
+  return makedirs(join(config.res_dir, classifier.name+'_svm_'+classifier.suffix))
+
[…]

### 2012-02-04 synthetic/test/classifier.py

@@ -1,0 +1,6 @@
+from synthetic.classifier import Classifier
+
+class TestClassifier:
+	def test_compute_histogram():
+		# TODO
+		None

### 2012-02-04 synthetic/classifier.py
cleaned up classifier.py by putting file paths in config.py and misc stuff; added empty test file for it

@@ -1,9 +1,3 @@
-'''
-Created on Nov 20, 2011
-
-@author: Tobias Baumgartner
-'''
-
 from abc import abstractmethod
 import fnmatch
 
@@ -18,26 +12,25 @@ class Classifier():
     self.name = ''
     self.suffix = ''
   
-  def compute_histogram(self,arr, intervalls, lower, upper):
+  def compute_histogram(self, arr, intervals, lower, upper):
     band = upper - lower
-    int_width = band/intervalls
-    hist = np.zeros((intervalls,1))
-    # first compute the cumulated  histogram
-    for i in range(int(intervalls)):
+    int_width = band/intervals
+    hist = np.zeros((intervals,1))
+    # first compute the cumulative  histogram
+    for i in range(int(intervals)):
       every = sum(arr < (lower + int_width*(i+1)))
       hist[i] =  every
     # and then uncumulate
-    for j in range(int(intervalls)-1):
-      hist[intervalls-j-1] -= hist[intervalls-j-2]
+    for j in range(int(intervals)-1):
+      hist[intervals-j-1] -= hist[intervals-j-2]
     if sum(hist) > 0:
       hist = np.divide(hist, sum(hist)) 
     return np.transpose(hist)
   
   @abstractmethod
-  def create_vector(self, feats, cls, img, intervalls, lower, upper):
-    """
-    Changes in classifiers. Create the feature vector that is going to be classified 
-    """
+  def create_vector(self, feats, cls, img, intervals, lower, upper):
+    "Create the feature vector."
+    # implement in subclasses
   
   def train(self, pos, neg, kernel, C):    
     y = [1]*pos.shape[0] + [-1]*neg.shape[0]
@@ -58,19 +51,17 @@ class Classifier():
       scores[idx] = 1./(math.exp(-2.*scores[idx]) + 1.)  
     return np.hstack((scores, arr[:,1:3]))
       
-  def train_for_all_cls(self, train_dataset, feats, intervalls, kernel, lower, upper, cls_idx, C):
+  def train_for_all_cls(self, train_dataset, feats, intervals, kernel, lower, upper, cls_idx, C):
     cls = train_dataset.classes[cls_idx]
-    ut.makedirs(config.save_dir + self.name + '_svm_'+self.suffix+'/' + kernel + '/' + str(intervalls))
-    filename = config.save_dir + self.name + '_svm_'+self.suffix+'/'+ kernel + '/' + str(intervalls) + '/'+ \
[…]

### 2012-02-04 synthetic/config.py

@@ -38,6 +38,7 @@ else:
   raise RuntimeError("Can't set paths correctly")
 
 # repo_dir, data_dir, temp_data_dir
+# temp_data_dir is not propagated between machines!
 paths = {
   'tobi_home':    ['/home/tobibaum/Documents/Vision/timely/',
                    '/home/tobibaum/Documents/Vision/timely/data/',
@@ -77,7 +78,7 @@ config_dir = join(script_dir,'configs')
 
 # Result data
 res_dir = makedirs(join(data_dir, 'results'))
-temp_res_dir = makedirs(join(temp_data_dir, 'results'))
+temp_res_dir = makedirs(join(data_dir, 'temp_results'))
 dets_configs_dir = makedirs(join(res_dir,'det_configs'))
 
 # ./results/sliding_windows_{dataset}
@@ -151,7 +152,10 @@ def get_ext_dets_filename(dataset, suffix):
 
 # directory for gist features
 # results/gist_features/
-gist_dir = makedirs(join(res_dir, 'gist_features'))
+=======
+#####
+# GIST
+#####
 
 # results/gist_features/full_pascal_trainval.npy
 def get_gist_dict_filename(dataset_name):
@@ -161,3 +165,25 @@ def get_gist_dict_filename(dataset_name):
 def get_gist_svm_filename(for_cls):
   dirname = makedirs(join(gist_dir,'svm'))
   return join(dirname,for_cls)
+
+#####
+# Classifier
+#####
+# learning
+def get_classifier_learning_dirname(classifier):
+  return makedirs(join(config.temp_res_dir, classifier.name+'_svm_'+classifier.suffix))
+
+def get_classifier_learning_filename(classifier,cls,kernel,intervals,lower,upper,C)
+  dirname = makedirs(join(get_classifier_learning_dirname(classifier), kernel, str(intervals))
+  return join(dirname, "%s_%d_%d_%d"%(cls,lower,upper,C))
+    
+def get_classifier_learning_eval_filename(classifier,cls,kernel,intervals,lower,upper,C)
+  dirname = makedirs(join(get_classifier_learning_dirname(classifier), kernel, str(intervals))
+  return join(dirname, "eval_%d_%d_%d"%(lower,upper,C))
+
+# final
+def get_classifier_dirname(classifier):
+  return makedirs(join(config.res_dir, classifier.name+'_svm_'+classifier.suffix))
+
+def get_classifier_filename(classifier,cls):
+  return join(config.get_classifier_dirname, cls)

### 2012-02-04 synthetic/ext_detector.py

@@ -62,7 +62,7 @@ class ExternalDetector(Detector):
     dets = dets.with_column_omitted('time')
     return (dets.arr, time_passed)
 
-  def compute_posterior(self, image, dets, oracle=True):
+  def compute_posterior(self, image, dets, oracle=False):
     """
     Return the 0/1 decision of whether the cls of this detector is present in
     the image, given the detections table.

### 2012-02-04 writeups/eccv12/eccv12.tex
adding eccv12 writeup support files

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV12SubNumber{***}  % Insert your submission number here

\title{Timely Object Detection}

\titlerunning{ECCV-12 submission ID \ECCV12SubNumber}

\authorrunning{ECCV-12 submission ID \ECCV12SubNumber}

\author{Anonymous ECCV submission}
\institute{Paper ID \ECCV12SubNumber}

\maketitle

\begin{abstract}
\dots
\end{abstract}

\section{Reinforcement Learning}

\bibliographystyle{splncs}
\bibliography{}

\end{document}

### 2012-02-09 writeups/eccv12/eccv12.tex

@@
 \pagestyle{headings}
+
+% Command definitions
+\def\subsectionautorefname{section}
+\definecolor{light-gray}{gray}{0.3}
+\newcommand{\aside}[1]{\textcolor{light-gray}{\emph{#1}}}
+\newcommand{\comment}[1]{}
+
 \mainmatter
@@
 \begin{abstract}
-\dots
 \end{abstract}
 
-\section{Reinforcement Learning}
+\section{Sequential Decision Problem} \label{sec:sdp}
+
+We first describe the requirements for our target system, and set the notation.
+Details of our implementation are then given.
+
+We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains at least one, and often multiple, objects.
+Each object is labeled with exactly one category label $1$ through $K$.
+
+The multi-class, multi-label \emph{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $i$, for each class $i \in \{1,\dots,K\}$.
+The answer for a single label is given with a real-valued confidence by a function $\emph{classify}(I,i)$.
+We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_i$ is a $\{0/1\}$ binary variable set to $1$ if an object of class $i$ is present.
+Henceforth we write $P(C_i)$ to mean $P(C_i=1)$, as shorthand.
+
+The answer is evaluated by plotting precision vs.
+recall across dataset $\mathcal{D}$ (by progressively lowering the confidence threshold for a positive label) and integrating to yield the Average Precision (AP) metric \cite{pascal-voc-2010}.
+
+We can make the classification problem more difficult by posing the \emph{counting} problem, which asks how many objects of class $i$ are present in $\mathcal{I}$, for each $i$.
+This setting is not commonly evaluated; we mention it for its usefulness in later exposition.
+
+Finally, the \emph{detection} problem is to output a list of bounding boxes (sub-images defined by four coordinates), each with a real-valued confidence that it encloses a single instance of an object of class $i$.
+The answer for a single class $i$ is given by an algorithm $\emph{detect}(\mathcal{I},i)$, which outputs a list of bounding boxes $B$ and associated confidences.
+To highlight the hierarchical structure of these problems, we note that the confidences may be given by $\operatorname{classify}(b,i)$ for each sub-image $b \in B$, and that the correct answer to the detection problem also answers the counting and classification problems.
+
+Here we describe the classification problem setup, although we evaluate performance on both classification and detection tasks.
+
+\subsection{Multi-class Classification Policy}
+
+Our goal is a multi-class classification policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(C_1), \dots, \emph{classify}(C_K)\}$, where we omit the obvious dependency on $\mathcal{I}$.
+The policy repeatedly selects an action $a$ from a set of actions $\mathcal{A}$, executes it, potentially receiving a set of observations, and selects the next action.
+A dynamic (or ``closed-loop'') policy bases action selection on observations received from previous actions, allowing context to play a large role.
+This sets our problem formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001}.
+
+The set of actions $\mathcal{A}$ can include per-class classifiers, ``scene context'' functions, and feature computations.
+For simplicity of exposition, let $\mathcal{A}$ consist of $2$ feature computations $F$ and $2K$ per-class classifiers $L$:
+\begin{itemize}
+	\item $L^\text{co}$ are one-vs-all SVMs on a complex featurization of the image (computed by $F^\text{co}$);
+	\item $L^\text{sc}$ are SVMs on a simple scene-level feature (computed by $F^\text{sc}$).
+\end{itemize}
+
+Each classifier $L$ or feature computation $F$ has an expected cost of execution.
+Depending on the setting, the cost can be defined in terms of algorithmic runtime analysis (e.g.
+$O(N^3)$), an idealized property such as number of \emph{flops}, or simply the empirical runtime on specific hardware.
+We take the empirical approach: every executed action advances $t$, the \emph{time into episode}, by its empirical runtime.
+
+The system is given two times: the setup time $T_s$ and deadline $T_d$.
+Between these times, the system must meet the goal of \emph{Anytime} performance and give the best possible answer at any point.
+
+\begin{figure}[h!]
+\center{\includegraphics[width=0.66\linewidth]
+    {figures/evaluation.pdf}}
+  \caption{\label{fig:evaluation}Our objective is to obtain \emph{Anytime} performance within the bounds of the curve.
+That is, the policy should give the best possible answer at any time from start time to deadline.}
+\end{figure}
+
+To meet this goal, the evaluation metric of a policy is defined as the area under the performance vs. time curve between points $T_s$ and $T_d$ (see Figure~\ref{fig:evaluation}).
+We evaluate policies by this more robust metric and not simply by the final performance at deadline time for the same reason---robustness---that Average Precision is used instead of a fixed Precision vs.
+Recall point.
+
+In the language of decision processes, we define the \emph{state} of the decision process by the setting of $\mathbf{C}$ (the $K$ object presence variables $C_i$) and the time into episode $t$.
+When the state has all the necessary information to make optimal action selections, the problem can be formalized as a Markov Decision Process.
+Obviously, the true value of $\mathbf{C}$ is unknown to our system, so we define a \emph{belief state} $b$ as a distribution over states.
+The belief state consists of the distribution $P(\mathbf{C}) = P(C_1, \dots, C_K)$, as well as $t$, and other variables.
+
+A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $(b_1,a_1)$ and so on until $t$ exceeds $T_d$.
+At that point, the policy is terminated and a new episode begins on a new image.
+
+\begin{table}
+\centering
+\caption{Summary of the notation used.}
+\label{tab:notation}
+\begin{tabular}{|l|l|}
+	\hline
+	$C_i$         & presence of at least one object of class $i$  \\ 
+	$K$           & number of object classes                      \\ 
+	$t$           & time into episode                             \\ 
+	$T_s$, $T_d$  & start and deadline times                      \\ 
+	$\mathcal{A}$ & set of actions                                \\ 
+	$b_j$        	& belief state at step $j$                                 \\ 
+	$\pi$         & policy, $\phi(b_s) \mapsto a \in \mathcal{A}$ \\ 
+	\hline
+\end{tabular}\end{table}
+
+\subsection{Reward definition}
+Optimal performance results from becoming maximally certain of the correct values of every $C_i$ as quickly as possible (given the setup time).
+Toward this goal, we formulate a \emph{reward function} that encourages this behavior by assigning a score to an action taken in a belief state.
+Let's say that given deadline $T_d$, the policy had time to take $J$ actions.
+The total expected reward of a policy $\pi$ is then defined as the sum of rewards
+\begin{equation}
+\mathbb{E}_\pi[\sum_{j=0}^J R(b_j, a_j)]
+\end{equation}
+We explore two options for the reward function: the first is derived directly from the evaluation metric; the second cares only about entropy of $P(\mathbf{C})$.
+
+\subsubsection{Slope of performance vs. time}
+Remembering that the final evaluation of a policy consists of the area under the performance vs. time curve, we formulate a per-action reward such that the addition of
+
+\subsubsection{Information gain}
+
+\subsection{Learning the value of an action}
+At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
+
+\section{Evaluation} \label{sec:evaluation}
 
 \bibliographystyle{splncs}
-\bibliography{}
+\bibliography{sergeyk-bibtex}
 

### 2012-02-13 writeups/eccv12/eccv12.tex
meeting with mario

@@
 \usepackage{color}
+\usepackage{subfig}
 \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
+\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
 \begin{document}
@@
 
-% Command definitions
+% Definitions
+\newcommand{\argmax}{\operatornamewithlimits{argmax}}
 \def\subsectionautorefname{section}
@@
 \newcommand{\aside}[1]{\textcolor{light-gray}{\emph{#1}}}
+\newcommand{\todo}[1]{\textcolor{red}{\emph{#1}}}
 \newcommand{\comment}[1]{}
@@
 
+\subsection{Problem Setting} \label{sec:problem_setting}
+
 We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains at least one, and often multiple, objects.
@@
 The multi-class, multi-label \emph{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $i$, for each class $i \in \{1,\dots,K\}$.
-The answer for a single label is given with a real-valued confidence by a function $\emph{classify}(I,i)$.
-We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_i$ is a $\{0/1\}$ binary variable set to $1$ if an object of class $i$ is present.
-Henceforth we write $P(C_i)$ to mean $P(C_i=1)$, as shorthand.
+The answer for a single label is given with a real-valued confidence by a function $\emph{classify}(\mathcal{I},i)$.
+We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_i \in \mathbb{B} = \{0,1\}$ is set to $1$ if an object of class $i$ is present.
 
@@
 
-Our goal is a multi-class classification policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(C_1), \dots, \emph{classify}(C_K)\}$, where we omit the obvious dependency on $\mathcal{I}$.
-The policy repeatedly selects an action $a$ from a set of actions $\mathcal{A}$, executes it, potentially receiving a set of observations, and selects the next action.
-A dynamic (or ``closed-loop'') policy bases action selection on observations received from previous actions, allowing context to play a large role.
-This sets our problem formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001}.
+\begin{figure}[h!]
+\center{\includegraphics[width=0.66\linewidth]
+    {figures/pomdp.pdf}}
+  \caption{Summary of our approach to the problem.
+Our system has two major parts: (1) selecting an action by predicting its value; (2) updating the belief state with observations resulting from the action.}
+  \label{fig:evaluation}
+\end{figure}
+
+Our goal is a multi-class classification policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$.
+The policy repeatedly selects an action $a$ from a set of actions $\mathcal{A}$, executes it, potentially receives a set of observations, and selects the next action.
+A dynamic, or ``closed-loop,'' policy bases action selection on observations received from previous actions, exploiting the signal in inter-object and scene context for a maximally efficient path through the classifiers.
+This is our goal, and what sets our formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001} or \todo{add another one}.
 
 The set of actions $\mathcal{A}$ can include per-class classifiers, ``scene context'' functions, and feature computations.
-For simplicity of exposition, let $\mathcal{A}$ consist of $2$ feature computations $F$ and $2K$ per-class classifiers $L$:
+For simplicity of exposition, let $\mathcal{A}$ consist of $K+1$ feature computations $F$ and $2K$ per-class classifiers $L$:
 \begin{itemize}
-	\item $L^\text{co}$ are one-vs-all SVMs on a complex featurization of the image (computed by $F^\text{co}$);
-	\item $L^\text{sc}$ are SVMs on a simple scene-level feature (computed by $F^\text{sc}$).
+	\item $L^\text{co}_i$ are one-vs-all SVMs on a complex featurization of the image (computed by $F^\text{co}_i$);
+	\item $L^\text{sc}_i$ are SVMs on a simple scene-level feature (computed by $F^\text{sc}$).
 \end{itemize}
+
+\todo{
+Consider revising the above to make a single action compute all the scene classifiers at once.
+}
 
@@
 The system is given two times: the setup time $T_s$ and deadline $T_d$.
-Between these times, the system must meet the goal of \emph{Anytime} performance and give the best possible answer at any point.
+Between these times, the system must meet the goal of \emph{Anytime} performance and give the best possible answer to the classification problem at any point.
 
@@
     {figures/evaluation.pdf}}
-  \caption{\label{fig:evaluation}Our objective is to obtain \emph{Anytime} performance within the bounds of the curve.
-That is, the policy should give the best possible answer at any time from start time to deadline.}
+  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.}
+  \label{fig:evaluation}
 \end{figure}
@@
 
-In the language of decision processes, we define the \emph{state} of the decision process by the setting of $\mathbf{C}$ (the $K$ object presence variables $C_i$) and the time into episode $t$.
-When the state has all the necessary information to make optimal action selections, the problem can be formalized as a Markov Decision Process.
-Obviously, the true value of $\mathbf{C}$ is unknown to our system, so we define a \emph{belief state} $b$ as a distribution over states.
-The belief state consists of the distribution $P(\mathbf{C}) = P(C_1, \dots, C_K)$, as well as $t$, and other variables.
+We define the \emph{belief state} $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$ (writing $P(C_i)$ to mean $P(C_i=1)$), the time into episode $t$, and other variables that will be discussed in \autoref{sec:value}.
+The terminology of ``belief'' comes from reinforcement learning and refers to the distribution $P(\mathbf{C})$.
 
-A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $(b_1,a_1)$ and so on until $t$ exceeds $T_d$.
+An action $a$ can result in a set of observations $o$ that can be used to update the belief state.
+At the very least, the state records the fact that $a$ has been taken.
+A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $(b_1,a_1)$, and so on until $t$ exceeds $T_d$.
 At that point, the policy is terminated and a new episode begins on a new image.
+
+The policy's performance is determined by treating the final values of $P(\mathbf{C})$ as the set of confidence scores $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ for the multi-label classification evaluation (see \autoref{sec:problem_setting}).
 
@@
 
-\subsection{Reward definition}
-Optimal performance results from becoming maximally certain of the correct values of every $C_i$ as quickly as possible (given the setup time).
+\subsection{Reward} \label{sec:reward}
+The goal of our policy is Anytime performance, so it would be limiting to evaluate only at deadline time.
+Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
 Toward this goal, we formulate a \emph{reward function} that encourages this behavior by assigning a score to an action taken in a belief state.
-Let's say that given deadline $T_d$, the policy had time to take $J$ actions.
+
+Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
 The total expected reward of a policy $\pi$ is then defined as the sum of rewards
 \begin{equation}
-\mathbb{E}_\pi[\sum_{j=0}^J R(b_j, a_j)]
+\mathbb{E}_\pi[\sum_{j=0}^J R(b_j)]
 \end{equation}
-We explore two options for the reward function: the first is derived directly from the evaluation metric; the second cares only about entropy of $P(\mathbf{C})$.
+
+The reward function does not necessarily have to be related to the evaluation of the system.
+We explore two options for the reward function: the first is derived directly from the evaluation metric; the second seeks to minimize entropy of $P(\mathbf{C})$.
 
 \subsubsection{Slope of performance vs. time}
-Remembering that the final evaluation of a policy consists of the area under the performance vs. time curve, we formulate a per-action reward such that the addition of
+\begin{figure}[htb]
+  \center{\includegraphics[width=0.66\linewidth]{figures/apvst_expl.pdf}}
+  \caption{\label{fig:rewards}A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action.
+The figure shows this analysis for the action highlighted in orange.}
+\end{figure}
+
+Remembering that the final evaluation of a policy consists of the area under the performance vs.
+time curve, we formulate per-action rewards such that their addition results in precisely this quantity.
+Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
+\begin{equation}\label{eq:advanced}
+\Delta AP (t_T-\Delta t)
+\end{equation}
+where $t_T$ is the time left until deadline, and $\Delta t$ and $\Delta AP$ are the time taken and AP change produced by the action.
+
+The equation breaks down into a term to maximize, $\Delta AP t_T$, and a term to minimize, $\Delta AP \Delta t$.
+This agrees with the intuition that to capture the most area under the curve, the slope needs to be maximized at each point.
+Additionally, the equation shows that if $\Delta t$ exceeds $t_T$, the value of taking the action is negative.
 
 \subsubsection{Information gain}
+A common approach to our kind of problem is to minimize uncertainty as quickly as possible.
+Specifically,
 
-\subsection{Learning the value of an action}
+\todo{What's the difference here between minimizing entropy and maximizing expected information gain over the length of the episode?}
+
+\subsection{The value function} \label{sec:value}
 At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
+We therefore define our policy as
+\begin{equation}
+\argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
+\end{equation}
+
+Learning this accurately is the domain of Reinforcement Learning research, and is generally intractable for large-scale POMDPs.
+We explore three different value functions.
+
+First, we seek to maximize the expected next-stage reward, and manually construct a value function such that picking the action with maximal value achieves this.
+Next, we note that the manually constructed value function can be represented as a scalar product of a parameter vector with a featurization of the belief state; we learn the weights by regression to the actual next-stage reward from running many episodes.
+Lastly, we use a reinforcement learning technique to learn the weights such that the expected rewards over the whole episode are maximized.
+
+\subsubsection{Manually specified greedy value function}
+
+\subsubsection{Learning the greedy policy}
+
+\subsubsection{Learning the proper policy}
+\note{I'm considering two options here: (1) log-linear representation and policy gradient algorithm; (2) least-squares policy iteration.}
+
+\paragraph{Policy gradient algorithm}
+We redefine our policy as picking the mode of a log-linear parametrized distribution:
+\begin{equation}
+P(a|b;\theta) = \frac{\exp(\theta^T \phi(b,a))}{\sum_{a' \in \mathcal{A}} \exp(\theta^T \phi(b,a')}
+\end{equation}
+
+Basically stochastic gradient ascent on the estimate of the reward accrued by an episode.
+
+This approach has been shown to scale to large problems in \cite{Branavan2009,Sutton2000}, although it has been proven to converge only to local maxima and only for MDPs.
+
+\note{Does the constraint that no action is taken more than once affect this algorithm?}
+
+\paragraph{Least-squares Policy Iteration}
+An efficient form of temporal-difference learning used in \cite{Kwok2004}.
+Policy remains parameterized as it was.
+
+\subsection{Updating the belief state}
+While the value function can learn certain dependencies between class occurrences, its job is made easier if the belief state already presents features that clearly present the relevant signals, such as co-occurence.
+Toward this end, we employ an inference model to infer the marginals $P(C_i)$ given the observations.
+It may also be useful to predict the marginals $P(L_i)$, as some formulations of our value function make use of this information.
+
+We explore two alternatives for the inference model: a fully-connected Markov Random Field (MRF) and a locally weighted regression, as shown in Figure~\ref{fig:models}.
+
+\begin{figure}[h!]
+\centering
+\subfloat[MRF]{\includegraphics[width=0.46\linewidth]{figures/inf_model_mrf.pdf}} \hfill
+\subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
+\caption{The models present a point in the middle of the decision process, when some classifiers have already been observed.}
+\label{fig:models}
+\end{figure}
+
+\subsubsection{MRF inference}
+Pros: (probably) more efficient at test time.
+
+Cons: model too restrictive? not exact inference.
+
+\subsubsection{Locally weighted regression}
+Approach of \cite{Gao2011}.
+
+Pros: imposing minimal model constraints (except Gaussian assumptions);
+
+Cons: expensive at test time; data too sparse?
 

### 2012-02-15 writeups/eccv12/eccv12.tex
updated schedule

@@
 Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
-Toward this goal, we formulate a \emph{reward function} that encourages this behavior by assigning a score to an action taken in a belief state.
+Toward this goal, we formulate a \emph{reward function} that encourages this behavior by assigning a score to a belief state.
 
@@
 A common approach to our kind of problem is to minimize uncertainty as quickly as possible.
-Specifically,
+Therefore we define the reward as a function of the negative residual entropy, following \cite{Gao2011}.
 
@@
 \begin{equation}
-\argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
+\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
 \end{equation}
@@
 
-\subsubsection{Manually specified greedy value function}
+\subsubsection{Greedy expected-value}
+We can compute the expected value of the reward function given a distribution over the classifier response.
+If we define the value function by this expectation, we will have constructed a one-step greedy policy.
+
+\note{Discuss submodularity defense of greedy policies here; costs are tricky though.}
 
 \subsubsection{Learning the greedy policy}
+We note that we can represent the one-step greedy policy value function as a scalar product
 
@@
 
-This approach has been shown to scale to large problems in \cite{Branavan2009,Sutton2000}, although it has been proven to converge only to local maxima and only for MDPs.
+This approach has been shown to scale to large problems in \cite{Branavan2009}, although it has been proven to converge only to local maxima and only for MDPs \cite{Sutton2000}.
 

### 2012-02-15 synthetic/config.py
all tests pass

@@ -172,12 +172,12 @@ def get_gist_svm_filename(for_cls):
 def get_classifier_learning_dirname(classifier):
   return makedirs(join(config.temp_res_dir, classifier.name+'_svm_'+classifier.suffix))
 
-def get_classifier_learning_filename(classifier,cls,kernel,intervals,lower,upper,C)
-  dirname = makedirs(join(get_classifier_learning_dirname(classifier), kernel, str(intervals))
+def get_classifier_learning_filename(classifier,cls,kernel,intervals,lower,upper,C):
+  dirname = makedirs(join(get_classifier_learning_dirname(classifier), kernel, str(intervals)))
   return join(dirname, "%s_%d_%d_%d"%(cls,lower,upper,C))
     
-def get_classifier_learning_eval_filename(classifier,cls,kernel,intervals,lower,upper,C)
-  dirname = makedirs(join(get_classifier_learning_dirname(classifier), kernel, str(intervals))
+def get_classifier_learning_eval_filename(classifier,cls,kernel,intervals,lower,upper,C):
+  dirname = makedirs(join(get_classifier_learning_dirname(classifier), kernel, str(intervals)))
   return join(dirname, "eval_%d_%d_%d"%(lower,upper,C))
 
 # final

### 2012-02-15 synthetic/dataset_policy.py

@@ -28,7 +28,7 @@ class DatasetPolicy:
     'suffix': 'jan30', # use this to re-run on same params after changing code
     'detector': 'ext', # perfect,perfect_with_noise,ext
     'class_priors_mode': 'random', # random,oracle,fixed_order,no_smooth,backoff
-    'dets_suffixes': ['csc_default'], # further specifies which detector to use
+    'dets_suffixes': ['dpm'], # further specifies which detector to use (use 'dpm' so tests pass)
     'bounds': None, # start and deadline times for the policy
     'gist': 0, # use the GIST action? 0/1
     'with_entropy': 0, # use the entropy feature in belief state featurization?

### 2012-02-15 synthetic/run_experiment.py

@@ -70,7 +70,7 @@ def main():
     description="Run experiments with the timely detection system.")
 
   parser.add_argument('--test_dataset',
-    choices=['val','test','train','trainval'],
+    choices=['val','test'],
     default='val',
     help="""Dataset to use for testing. Run on val until final runs.
     The training dataset is inferred (val->train; test->trainval).""")
@@ -80,7 +80,7 @@ def main():
 
   parser.add_argument('--config',
     help="""Config file name that specifies the experiments to run.
-    Give name s.t the file is configs/#{name}.json or configs/#{name}/.
+    Give name such that the file is configs/#{name}.json or configs/#{name}/
     In the latter case, all files within the directory will be loaded.""")
 
   parser.add_argument('--force', action='store_true', 
@@ -118,8 +118,7 @@ def main():
   elif args.test_dataset=='val':
     train_dataset = Dataset('full_pascal_train')
   else:
-    print("Impossible, setting train_dataset to dataset")
-    train_dataset = dataset
+    None # impossible by argparse settings
 
   tables = []
   all_bounds = []

### 2012-02-15 synthetic/test/classifier.py

@@ -1,6 +1,6 @@
 from synthetic.classifier import Classifier
 
 class TestClassifier:
-	def test_compute_histogram():
+	def test_compute_histogram(self):
 		# TODO
 		None

### 2012-02-15 synthetic/test/dataset.py

@@ -4,14 +4,16 @@ from synthetic.dataset import Dataset
 import synthetic.config as config
 
 class TestDataset:
+  def setup(self):
+    self.d = Dataset('data1',force=True)
+    self.d2 = Dataset('test_pascal_train',force=True)
+
   def test_load_from_json(self):
-    d = Dataset('data1')
-    assert(d.num_images() == 4)
-    assert(d.classes == ["A","B","C"])
+    assert(self.d.num_images() == 4)
+    assert(self.d.classes == ["A","B","C"])
 
   def test_ground_truth_json(self):
-    d = Dataset('data1')
-    gt = d.get_ground_truth(include_trun=False)
+    gt = self.d.get_ground_truth(include_trun=False)
     arr = np.array(
       [[ 0.,  0.,  0.,  0.,  0.,  0.],
        [ 1.,  1.,  1.,  1.,  1.,  0.],
@@ -24,18 +26,16 @@ class TestDataset:
     assert(gt.cols == cols)
 
   def test_get_cls_counts_json(self):
-    d = Dataset('data1')
     arr = np.array(
       [ [ 1, 1, 1],
         [ 1, 0, 0],
         [ 0, 1, 0],
         [ 0, 0, 1]])
-    print(d.get_cls_counts())
-    assert(np.all(d.get_cls_counts() == arr))
+    print(self.d.get_cls_counts())
+    assert(np.all(self.d.get_cls_counts() == arr))
 
   def test_ground_truth_for_class_json(self):
-    d = Dataset('data1')
-    gt = d.get_ground_truth_for_class("A",include_diff=True,include_trun=True)
+    gt = self.d.get_ground_truth_for_class("A",include_diff=True,include_trun=True)
     arr = np.array(
       [[ 0.,  0.,  0.,  0.,  0., 0., 0, 0.],
        [ 1.,  1.,  1.,  1.,  0., 0., 0., 1.]])
@@ -45,7 +45,7 @@ class TestDataset:
     assert(gt.cols == cols)
 
     # no diff or trun
-    gt = d.get_ground_truth_for_class("A",include_diff=False,include_trun=False)
+    gt = self.d.get_ground_truth_for_class("A",include_diff=False,include_trun=False)
     arr = np.array(
       [[ 0.,  0.,  0.,  0.,  0., 0.],
        [ 1.,  1.,  1.,  1.,  0., 1.]])
@@ -55,36 +55,31 @@ class TestDataset:
[…]

### 2012-02-15 synthetic/test/evaluation.py

@@ -8,20 +8,20 @@ from synthetic.sliding_windows import SlidingWindows
 
 class TestEvaluationPerfect:
   def setup(self):
-    train_dataset = Dataset('test_pascal_train')
-    dataset = Dataset('test_pascal_val')
+    train_dataset = Dataset('test_pascal_train',force=True)
+    dataset = Dataset('test_pascal_val',force=True)
     sw = SlidingWindows(dataset,train_dataset)
     self.dp = DatasetPolicy(dataset,train_dataset,sw, detector='perfect')
     self.evaluation = Evaluation(self.dp)
 
   def test_compute_pr_multiclass(self):
-    cols = ['x','y','w','h','cls_ind','img_ind'] 
+    cols = ['x','y','w','h','diff','cls_ind','img_ind'] 
     dets_cols = ['x', 'y', 'w', 'h', 'score', 'time', 'cls_ind', 'img_ind']
     
     # two objects of different classes in the image, perfect detection
     arr = np.array(
-        [ [0,0,10,10,0,0],
-          [10,10,10,10,1,0] ])
+        [ [0,0,10,10,0,0,0],
+          [10,10,10,10,0,1,0] ])
     gt = ut.Table(arr,cols)
 
     dets_arr = np.array(
@@ -69,10 +69,10 @@ class TestEvaluationPerfect:
 
     # now let's add two objects of a different class to gt to lower recall
     arr = np.array(
-        [ [0,0,10,10,0,0],
-          [10,10,10,10,1,0],
-          [20,20,10,10,2,0],
-          [30,30,10,10,2,0] ])
+        [ [0,0,10,10,0,0,0],
+          [10,10,10,10,0,1,0],
+          [20,20,10,10,0,2,0],
+          [30,30,10,10,0,2,0] ])
     gt = ut.Table(arr,cols)
     ap,rec,prec = self.evaluation.compute_pr(dets, gt)
     correct_rec = np.array([0.25,0.5,0.5,0.5])

### 2012-02-15 synthetic/util.py

@@ -38,6 +38,9 @@ class Table:
   def shape(self):
     return self.arr.shape
 
+  def ind(self,col_name):
+    return self.cols.index(col_name)
+
   ###################
   # Save/Load
   ###################
@@ -115,6 +118,8 @@ class Table:
     Take name of column to index by and value to filter by.
     By providing an operator, more than just equality filtering can be done.
     """
+    if ind_name not in self.cols:
+      return self
     table = Table(cols=self.cols,arr=self.arr)
     table.arr = filter_on_column(table.arr,table.cols.index(ind_name),val,op,omit)
     if omit:

### 2012-02-20 synthetic/config.py
faster cross-valid

@@ -70,6 +70,8 @@ VOC_dir = join(data_dir, 'VOC%(year)s/')%{'year':VOCyear}
 pascal_paths = {
     'test_pascal_train':    join(test_support_dir,'train.txt'),
     'test_pascal_val':      join(test_support_dir,'val.txt'),
+    'test_pascal_train_tobi':    join(test_support_dir,'train_tobi.txt'),
+    'test_pascal_val_tobi':      join(test_support_dir,'val_tobi.txt'),
     'full_pascal_train':    join(VOC_dir,'ImageSets/Main/train.txt'),
     'full_pascal_val':      join(VOC_dir,'ImageSets/Main/val.txt'),
     'full_pascal_trainval': join(VOC_dir,'ImageSets/Main/trainval.txt'),

### 2012-02-20 synthetic/image_classifier.py

@@ -36,6 +36,7 @@ def get_feature_vector(cc, img, quiet=False):
   """
   savefilename = config.get_classifier_featvect_name(cc.d.images[img])  
   if os.path.isfile(savefilename):
+    print 'load feat_vect %s'%(cc.d.images[img].name)
     feat_vect = cPickle.load(open(savefilename,'r'))
   else:
     feat_vect = compute_feature_vector(cc, img, quiet=quiet)
@@ -89,30 +90,32 @@ def compute_feature_vector(cc, img_idx, quiet=False):
 
 def cross_valid_training(cc, Cs, gammas, numfolds=4):
   cc.d.create_folds(numfolds)
-  all_settings = list(itertools.product(Cs, gammas))
+  all_settings = list(itertools.product(Cs, gammas,cc.d.classes))
 
   for set_idx in range(mpi_rank, len(Cs)*len(gammas), mpi_size): # Parallel
     curr_set = all_settings[set_idx]
     C = curr_set[0]
     gamma = curr_set[1]
-    print C, gamma
+    cls = curr_set[2]
     class_corr = 0
     overall = 0
+    
     for _ in range(numfolds):
       cc.d.next_folds()
-      train_image_classifier(cc, C, gamma, force_new=True)
-      val_set = np.where(cc.d.val)[0]
-      print 'val_set', val_set
-      
+      train_image_classify_svm(cc, cls=cls, C=C, gamma=gamma)
+      val_set = np.where(cc.d.val)[0]     
       
       classification = classify_images(cc, val_set, C, gamma)
       overall += classification.size
       class_corr += validate_images(cc, val_set, classification)
-    accuracy = class_corr/float(overall)
+      print 'correct:', class_corr
+      #break
+    accuracy = float(class_corr)/float(overall)
     filename = config.get_classifier_crossval()
     writef = open(filename, 'a')
     writef.write('%f %f - %f\n'%(C, gamma, accuracy))
-    cc.d.create_folds(numfolds)          
+    cc.d.create_folds(numfolds)
+    #return          
       
 
   # determine best one
@@ -125,11 +128,11 @@ def classify_images(cc, images, C, gamma):
       continue
     clf = load_svm(filename, probability=False)
     for idx2, img_idx in enumerate(images):
-      x = compute_feature_vector(cc, img_idx)
+      x = get_feature_vector(cc, img_idx)
       pred = svm_predict(x, clf)
[…]

### 2012-02-20 synthetic/dataset.py
working on classification evaluation

@@ -208,7 +208,7 @@ class Dataset:
   def get_cls_ground_truth(self, include_diff=False,include_trun=True):
     "Return Table containing classification ground truth."
     arr = self.get_cls_counts()>0
-    cols = self.classes + ['img_ind']
+    cols = self.classes
     return ut.Table(arr,cols)
       
   def get_ground_truth(self, include_diff=False, include_trun=True):
@@ -227,6 +227,7 @@ class Dataset:
     """
     Return Table object containing ground truth for the given image indices.
     """
+    img_inds = np.unique(img_inds)
     images = (self.images[int(ind)] for ind in img_inds)
     arr = ut.collect(images, Image.get_gt_arr)
     gt = ut.Table(arr,Image.get_gt_cols())

### 2012-02-20 synthetic/evaluation.py

@@ -102,22 +102,29 @@ class Evaluation:
           gt_for_image = gt_for_image_list[img_ind]
           img_dets = img_dets_list[img_ind]
           dets_to_this_point = img_dets.filter_on_column('time',point,operator.le)
+          # TODO
           #clses_to_this_point = img_clses.filter_on_column('time',point,operator.le)
           num_dets += dets_to_this_point.shape()[0]
           det_ap,rec,prec = self.compute_det_pr(dets_to_this_point, gt_for_image)
-          #cls_ap,rec,prec = self.compute_cls_pr(clses_to_this_point, gt_for_image)
           det_aps.append(det_ap)
+          cls_aps.append(self.compute_cls_map(clses_to_this_point, gt_for_image)
         det_arr[i,:] = [point,np.mean(det_aps),np.std(det_aps)]
+        cls_arr[i,:] = [point,np.mean(cls_aps),np.std(cls_aps)]
         print("Calculating AP (%.3f) of the %d detections up to %.3fs took %.3fs"%(
           np.mean(det_aps),num_dets,point,tt.qtoc()))
       det_arr_all = None
+      cls_arr_all = None
       if comm_rank == 0:
         det_arr_all = np.zeros((num_points,3))
+        cls_arr_all = np.zeros((num_points,3))
       safebarrier(comm)
       comm.Reduce(det_arr,det_arr_all)
+      comm.Reduce(cls_arr,cls_arr_all)
       if comm_rank==0:
-        table = ut.Table(det_arr_all, ['time','ap_mean','ap_std'], self.name)
-        np.save(self.det_apvst_data_fname,table)
+        dets_table = ut.Table(det_arr_all, ['time','ap_mean','ap_std'], self.name)
+        np.save(self.det_apvst_data_fname,dets_table)
+        clses_table = ut.Table(cls_arr_all, ['time','ap_mean','ap_std'], self.name)
+        np.save(self.cls_apvst_data_fname,clses_table)
     # Plot the table
     if plot and comm_rank==0:
       try:
@@ -125,7 +132,58 @@ class Evaluation:
       except:
         print("Could not plot")
     # TODO
-    return (table,table)
+    return (dets_table,clses_table)
+
+  def evaluate_dets_vs_t_whole(self,dets=None,force=False):
+    """
+    Evaluate detections in the AP vs Time regime and write out plots to
+    canonical places.
+    - dets must be on self.dataset
+    This version evaluates on the whole dataset instead of averaging per-image
[…]

### 2012-02-20 synthetic/test/dataset.py

@@ -35,6 +35,17 @@ class TestDataset:
     print(self.d.get_cls_counts())
     assert(np.all(self.d.get_cls_counts() == arr))
 
+  def test_get_cls_ground_truth_json(self):
+    arr = np.array(
+      [ [ True, True, True],
+        [ True, False, False],
+        [ False, True, False],
+        [ False, False, True]])
+    cols = ["A","B","C"]
+    print(self.d.get_cls_ground_truth())
+    assert(np.all(self.d.get_cls_ground_truth().arr == arr))
+    assert(np.all(self.d.get_cls_ground_truth().cols == cols))
+
   def test_ground_truth_for_class_json(self):
     gt = self.d.get_ground_truth_for_class("A",include_diff=True,include_trun=True)
     arr = np.array(

### 2012-02-20 synthetic/test/policy.py
i don't think you need those two sort calls in test/policy.py

@@ -21,8 +21,6 @@ class TestDatasetPolicy:
     dets = dets.subset(['x', 'y', 'w', 'h', 'cls_ind', 'img_ind'])
     gt = self.dataset.get_ground_truth()
     gt = gt.subset(['x', 'y', 'w', 'h', 'cls_ind', 'img_ind'])
-    dets.arr = ut.sort_by_column(dets.arr, 0)
-    gt.arr = ut.sort_by_column(gt.arr, 0)
     assert(dets == gt)
 
   def test_load_dpm_detections(self):

### 2012-02-20 writeups/eccv12/eccv12.tex

@@
 
+\begin{table}
+\centering
+\caption{Summary of the notation used.}
+\label{tab:notation}
+\begin{tabular}{|l|l|}
+	\hline
+	$C_i$         & presence of class $i$ \\ 
+	$K$           & number of object classes \\ 
+	$t$           & time into episode \\ 
+	$T_s$, $T_d$  & start and deadline times \\ 
+	$\mathcal{A}$ & set of actions \\ 
+	$b_j$        	& belief state at step $j$ \\ 
+	$\pi$         & policy, $\pi(b) \mapsto a \in \mathcal{A}$ \\ 
+	\hline
+\end{tabular}\end{table}
+
 \begin{figure}[h!]
@@
 \todo{
-Consider revising the above to make a single action compute all the scene classifiers at once.
+Revise the above to make a single action compute all the scene classifiers at once.
 }
 
-Each classifier $L$ or feature computation $F$ has an expected cost of execution.
-Depending on the setting, the cost can be defined in terms of algorithmic runtime analysis (e.g.
-$O(N^3)$), an idealized property such as number of \emph{flops}, or simply the empirical runtime on specific hardware.
+Each classifier $L$ or feature computation $F$ has an expected cost $c(\cdot)$ of execution.
+Depending on the setting, the cost can be defined in terms of algorithmic runtime analysis, an idealized property such as number of \emph{flops}, or simply the empirical runtime on specific hardware.
 We take the empirical approach: every executed action advances $t$, the \emph{time into episode}, by its empirical runtime.
@@
 
-We define the \emph{belief state} $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$ (writing $P(C_i)$ to mean $P(C_i=1)$), the time into episode $t$, and other variables that will be discussed in \autoref{sec:value}.
-The terminology of ``belief'' comes from reinforcement learning and refers to the distribution $P(\mathbf{C})$.
+We define the \emph{belief state} $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$ (writing $P(C_i)$ to mean $P(C_i=1)$), the time into episode $t$, the set of executed actions $\mathcal{O}$, and other variables that will be discussed in \autoref{sec:value}.
+\comment{The terminology of ``belief'' comes from reinforcement learning and refers to the distribution $P(\mathbf{C})$.}
 
-An action $a$ can result in a set of observations $o$ that can be used to update the belief state.
-At the very least, the state records the fact that $a$ has been taken.
+An action $a$ can result in a set of observations $o$ that are used to update the belief state.
+At the very least, the state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
+
 A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $(b_1,a_1)$, and so on until $t$ exceeds $T_d$.
@@
 
-\begin{table}
+\subsection{The value function} \label{sec:value}
+Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
+As our goal is to pick actions, we want to formulate a function that assigns a value to a potential action, given the current state of the decision process.
+We will then be able to define our policy as simply
+\begin{equation}
+\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} V(b,a)
+\end{equation}
+
+We consider two formulations of the value function: one based on information gain, and one on the classification loss.
+
+\subsubsection{Information gain}
+negative residual entropy, following \cite{Gao2011}.
+
+\todo{Write this out, and mention the greedy submodularity argument, to be made in a later section.}
+
+\subsubsection{Classification loss}
+\todo {Write this out. What to do with the cost here?}
+
+\subsection{Updating the belief state}
+While the value function can learn certain dependencies between class occurrences, its job is made easier if the belief state already presents features that clearly present the relevant signals, such as co-occurence.
+Toward this end, we employ an inference model to infer the marginals $P(C_i)$ given the observations.
+It may also be useful to predict the marginals $P(L_i)$, as some formulations of our value function make use of this information.
+
+We explore two alternatives for the inference model: a fully-connected Markov Random Field (MRF) and a locally weighted regression, as shown in Figure~\ref{fig:models}.
+
+\begin{figure}[h!]
 \centering
-\caption{Summary of the notation used.}
-\label{tab:notation}
-\begin{tabular}{|l|l|}
-	\hline
-	$C_i$         & presence of at least one object of class $i$  \\ 
-	$K$           & number of object classes                      \\ 
-	$t$           & time into episode                             \\ 
-	$T_s$, $T_d$  & start and deadline times                      \\ 
-	$\mathcal{A}$ & set of actions                                \\ 
-	$b_j$        	& belief state at step $j$                                 \\ 
-	$\pi$         & policy, $\phi(b_s) \mapsto a \in \mathcal{A}$ \\ 
-	\hline
-\end{tabular}\end{table}
+\subfloat[MRF]{\includegraphics[width=0.46\linewidth]{figures/inf_model_mrf.pdf}} \hfill
+\subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
+\caption{The models present a point in the middle of the decision process, when some classifiers have already been observed.}
+\label{fig:models}
+\end{figure}
+
+\subsubsection{MRF inference}
+Pros: (probably) more efficient at test time.
+
+Cons: model too restrictive? not exact inference.
+
+\subsubsection{Locally weighted regression}
+Approach of \cite{Gao2011}.
+
+Pros: imposing minimal model constraints (except Gaussian assumptions);
+
+Cons: expensive at test time; data too sparse?
 
 \subsection{Reward} \label{sec:reward}
-The goal of our policy is Anytime performance, so it would be limiting to evaluate only at deadline time.
-Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
-Toward this goal, we formulate a \emph{reward function} that encourages this behavior by assigning a score to a belief state.
-
 Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
@@
 
-\subsubsection{Information gain}
-A common approach to our kind of problem is to minimize uncertainty as quickly as possible.
-Therefore we define the reward as a function of the negative residual entropy, following \cite{Gao2011}.
-
-\todo{What's the difference here between minimizing entropy and maximizing expected information gain over the length of the episode?}
-
-\subsection{The value function} \label{sec:value}
 At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
@@
 
-\subsection{Updating the belief state}
-While the value function can learn certain dependencies between class occurrences, its job is made easier if the belief state already presents features that clearly present the relevant signals, such as co-occurence.
-Toward this end, we employ an inference model to infer the marginals $P(C_i)$ given the observations.
-It may also be useful to predict the marginals $P(L_i)$, as some formulations of our value function make use of this information.
+\section{Evaluation} \label{sec:evaluation}
+- show that the greedy policy works better than random and better than fixed-order
+- show that the reinfrocement learning policy works better than greedy, at least for the non-infogain rewards.
 
-We explore two alternatives for the inference model: a fully-connected Markov Random Field (MRF) and a locally weighted regression, as shown in Figure~\ref{fig:models}.
+\subsection{Classification}
 
-\begin{figure}[h!]
-\centering
-\subfloat[MRF]{\includegraphics[width=0.46\linewidth]{figures/inf_model_mrf.pdf}} \hfill
-\subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
-\caption{The models present a point in the middle of the decision process, when some classifiers have already been observed.}
-\label{fig:models}
-\end{figure}
-
-\subsubsection{MRF inference}
-Pros: (probably) more efficient at test time.
-
-Cons: model too restrictive? not exact inference.
-
-\subsubsection{Locally weighted regression}
-Approach of \cite{Gao2011}.
-
-Pros: imposing minimal model constraints (except Gaussian assumptions);
-
-Cons: expensive at test time; data too sparse?
-
-\section{Evaluation} \label{sec:evaluation}
+\subsection{Detection}
+We also evaluate using the task of detection (see \autoref{sec:problem}).
 

### 2012-02-22 synthetic/image_classifier.py
more parallel

@@ -99,9 +99,8 @@ def compute_feature_vector(cc, img_idx, quiet=False):
 def cross_valid_training(cc, Cs, gammas, kernel='rbf', numfolds=4, train=True):
   cc.d.create_folds(numfolds)
   if train:
-    for cls_idx in range(cc.d.classes):
+    for cls in cc.d.classes:
     #for cls_idx in range(mpi_rank, len(cc.d.classes), mpi_size): # PARALLEL
-      cls = cc.d.classes[cls_idx]
       train_image_classify_svm(cc, cls=cls, Cs=Cs, kernel=kernel, gammas=gammas)
   
   safebarrier(comm)
@@ -186,8 +185,6 @@ def train_image_classify_svm(cc, cls, Cs=[1.0], gammas=[0.0], kernel='rbf', numf
     for current_fold in range(numfolds):
       filename = config.get_classifier_svm_name(cls, C, gamma, current_fold, kernel)
       if not os.path.isfile(filename):
-        # do this! mark it as mine.
-        open(filename, 'w')
         all_exist = False
         break
   if all_exist:
@@ -216,7 +213,7 @@ def train_image_classify_svm(cc, cls, Cs=[1.0], gammas=[0.0], kernel='rbf', numf
   cc.d.create_folds(numfolds)
   
   
-  for _ in range(numfolds):
+  for fold in range(numfolds):
     cc.d.next_folds()
         
     # ======== NEGATIVE IMAGES ===========
@@ -241,11 +238,14 @@ def train_image_classify_svm(cc, cls, Cs=[1.0], gammas=[0.0], kernel='rbf', numf
         
         if os.path.isfile(filename):
           continue
+        write = open(filename, 'w')
+        write.write('')
+        write.close()
         X = np.vstack((pos_pyrs_fold, neg_pyrs_fold))
         Y = [1]*pos_pyrs_fold.shape[0] + [-1]*neg_pyrs_fold.shape[0] 
         
         if X.shape[0] > 0:
-          print 'train svm for class %s, C=%f, gamma=%f, %s on %d'%(cls,C,gamma,kernel, mpi_rank)
+          print 'train svm for class %s, C=%f, gamma=%f, %s, fold %d on %d'%(cls,C,gamma,kernel, fold, mpi_rank)
           cc.tictocer.tic()    
           clf = train_svm(X, Y, kernel=kernel, gamma=gamma, C=C)
           print '\ttrain svm took %f seconds on %d'%(cc.tictocer.toc(quiet=True),mpi_rank)

### 2012-02-22 synthetic/training.py

@@ -122,7 +122,11 @@ def save_svm(model, filename):
 
 
 def load_svm(filename, probability=True):
-  model = cPickle.load(open(filename, 'r'))
+  try:
+    model = cPickle.load(open(filename, 'r'))
+  except:
+    print 'could not load svm %s'%filename
+    return
   if os.path.isfile('%s_0'%filename):
     # We have split data here. load all of it.
     splits = model.support_vectors_[0]

### 2012-02-22 writeups/eccv12/eccv12.tex
writeup

@@
 \def\subsectionautorefname{section}
-\definecolor{light-gray}{gray}{0.3}
+\definecolor{light-gray}{gray}{0.5}
 \newcommand{\aside}[1]{\textcolor{light-gray}{\emph{#1}}}
 \newcommand{\todo}[1]{\textcolor{red}{\emph{#1}}}
+\newcommand{\cut}[1]{\textcolor{light-gray}{#1}}
 \newcommand{\comment}[1]{}
@@
 We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains at least one, and often multiple, objects.
-Each object is labeled with exactly one category label $1$ through $K$.
+Each object is labeled with exactly one category label $k \in \{1, \dots, K\}$.
 
-The multi-class, multi-label \emph{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $i$, for each class $i \in \{1,\dots,K\}$.
-The answer for a single label is given with a real-valued confidence by a function $\emph{classify}(\mathcal{I},i)$.
-We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_i \in \mathbb{B} = \{0,1\}$ is set to $1$ if an object of class $i$ is present.
+The multi-class, multi-label \emph{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $k$.
+The answer for a single label is given with a real-valued confidence by a function $\emph{classify}(\mathcal{I},k)$.
+We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_k \in \mathbb{B} = \{0,1\}$ is set to $1$ if an object of class $k$ is present.
 
@@
 
-We can make the classification problem more difficult by posing the \emph{counting} problem, which asks how many objects of class $i$ are present in $\mathcal{I}$, for each $i$.
+\cut{
+We can make the classification problem more difficult by posing the \emph{counting} problem, which asks how many objects of class $k$ are present in $\mathcal{I}$, for each $k$.
 This setting is not commonly evaluated; we mention it for its usefulness in later exposition.
+}
 
-Finally, the \emph{detection} problem is to output a list of bounding boxes (sub-images defined by four coordinates), each with a real-valued confidence that it encloses a single instance of an object of class $i$.
-The answer for a single class $i$ is given by an algorithm $\emph{detect}(\mathcal{I},i)$, which outputs a list of bounding boxes $B$ and associated confidences.
-To highlight the hierarchical structure of these problems, we note that the confidences may be given by $\operatorname{classify}(b,i)$ for each sub-image $b \in B$, and that the correct answer to the detection problem also answers the counting and classification problems.
+The \emph{detection} problem is to output a list of bounding boxes (sub-images defined by four coordinates), each with a real-valued confidence that it encloses a single instance of an object of class $k$, for each $k$.
+The answer for a single class is given by an algorithm $\emph{detect}(\mathcal{I},k)$, which outputs a list of sub-image bounding boxes $B$ and their associated confidences.
 
-Here we describe the classification problem setup, although we evaluate performance on both classification and detection tasks.
+To highlight the hierarchical structure of these problems, we note that (1) the confidences may be given by $\operatorname{classify}(b,k)$ for each sub-image $b \in B$; (2) the correct answer to the detection problem also answers the counting and classification problems.
+
+The following exposition deals with the classification problem, although we evaluate performance on both the classification and detection tasks.
 
@@
 \centering
-\caption{Summary of the notation used.}
+\caption{Summary of our notation.}
 \label{tab:notation}
@@
 	\hline
-	$C_i$         & presence of class $i$ \\ 
-	$K$           & number of object classes \\ 
+	$\mathcal{I}$	&	image \\
+	$C_k$         & presence of class $k \in \{1,\dots,K\}$ \\ 
 	$t$           & time into episode \\ 
 	$T_s$, $T_d$  & start and deadline times \\ 
-	$\mathcal{A}$ & set of actions \\ 
 	$b_j$        	& belief state at step $j$ \\ 
-	$\pi$         & policy, $\pi(b) \mapsto a \in \mathcal{A}$ \\ 
+	$\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
+	$\mathcal{A}$ & set of actions $a_i \in \{\mathcal{L} \cup \mathcal{F}\}$\\ 
+	$\mathcal{F}$ & set of featurization actions \\
+	$\mathcal{L}$ & set of classification actions\\
+	$o_i$					&	a real-valued observation upon executing $a_i \in \mathcal{L}$\\
+	$\mathcal{O}$	& set of executed actions\\
+	$\mathbf{o}$	& set of observations $\{o_k | a_k \in \mathcal{O}\}$\\
+	$c(a)$				& cost of executing $a$, in units of $t$\\
 	\hline
@@
 Our goal is a multi-class classification policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$.
-The policy repeatedly selects an action $a$ from a set of actions $\mathcal{A}$, executes it, potentially receives a set of observations, and selects the next action.
-A dynamic, or ``closed-loop,'' policy bases action selection on observations received from previous actions, exploiting the signal in inter-object and scene context for a maximally efficient path through the classifiers.
+The policy repeatedly selects an action $a_i$ from a set of actions $\mathcal{A}$, executes it, potentially receives an observation $o_i$, and selects the next action.
+
+A dynamic, or ``closed-loop,'' policy bases action selection on observations received from previous actions, exploiting the signal in inter-object and scene context for a maximally efficient path through the actions.
 This is our goal, and what sets our formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001} or \todo{add another one}.
 
-The set of actions $\mathcal{A}$ can include per-class classifiers, ``scene context'' functions, and feature computations.
-For simplicity of exposition, let $\mathcal{A}$ consist of $K+1$ feature computations $F$ and $2K$ per-class classifiers $L$:
+The set of actions $\mathcal{A}$ can include classifiers and feature computations.
+For simplicity of exposition, let $\mathcal{A}$ consist of $2K+2$ actions:
 \begin{itemize}
-	\item $L^\text{co}_i$ are one-vs-all SVMs on a complex featurization of the image (computed by $F^\text{co}_i$);
-	\item $L^\text{sc}_i$ are SVMs on a simple scene-level feature (computed by $F^\text{sc}$).
+	\item $F^\text{co}$, a complex spatial pyramid (SP) featurization of the image
+	\item $K$ classifiers $L^\text{co}_i$: one-vs-all SVMs trained on the SP feature
+	\item $F^\text{sc}$, a quick GIST featurization of the image
+	\item $K$ classifiers $L^\text{sc}_i$: one-vs-all SVMs on the GIST feature
 \end{itemize}
-
-\todo{
-Revise the above to make a single action compute all the scene classifiers at once.
-}
 
@@
 The system is given two times: the setup time $T_s$ and deadline $T_d$.
-Between these times, the system must meet the goal of \emph{Anytime} performance and give the best possible answer to the classification problem at any point.
+Between these times, the system must strive for the goal of \emph{Anytime} performance and give the best possible answer at any point.
 
@@
 To meet this goal, the evaluation metric of a policy is defined as the area under the performance vs. time curve between points $T_s$ and $T_d$ (see Figure~\ref{fig:evaluation}).
-We evaluate policies by this more robust metric and not simply by the final performance at deadline time for the same reason---robustness---that Average Precision is used instead of a fixed Precision vs.
+We evaluate policies by this more robust metric and not simply by the final performance at deadline time for the same reason that Average Precision is used instead of a fixed Precision vs.
 Recall point.
 
-We define the \emph{belief state} $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$ (writing $P(C_i)$ to mean $P(C_i=1)$), the time into episode $t$, the set of executed actions $\mathcal{O}$, and other variables that will be discussed in \autoref{sec:value}.
-\comment{The terminology of ``belief'' comes from reinforcement learning and refers to the distribution $P(\mathbf{C})$.}
+An action $a$ that consists of running a classifier $L_k$ returns a real-valued observation $o_k \sim P(O_k)$.
+The state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
+We refer to the current set of observations as $\mathbf{o} = \{o_k | L_k \in \mathcal{O}\}$.
 
-An action $a$ can result in a set of observations $o$ that are used to update the belief state.
-At the very least, the state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
+We define the state $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$\footnote{We write $P(C_k)$ to mean $P(C_k=1)$.}, the time into episode $t$, and the set of executed actions $\mathcal{O}$ and corresponding observations $\mathbf{o}$.
 
-A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $(b_1,a_1)$, and so on until $t$ exceeds $T_d$.
+A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $b_1$, and so on until $t$ exceeds $T_d$.
 At that point, the policy is terminated and a new episode begins on a new image.
 
-The policy's performance is determined by treating the final values of $P(\mathbf{C})$ as the set of confidence scores $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ for the multi-label classification evaluation (see \autoref{sec:problem_setting}).
+The policy's performance is determined by treating the final values of $P(\mathbf{C})$ as the set of confidence scores $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ for the multi-label classification evaluation described in \autoref{sec:problem_setting}.
 
-\subsection{The value function} \label{sec:value}
+For ease of reference, our notation is summarized in \autoref{tab:notation}.
+
+\section{Selecting actions} \label{sec:value}
 Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
-As our goal is to pick actions, we want to formulate a function that assigns a value to a potential action, given the current state of the decision process.
-We will then be able to define our policy as simply
-\begin{equation}
+As our goal is to pick actions, we want to formulate a function $V(b,a)$ 	that assigns a value to a potential action, given the current state of the decision process.
+We can then define the policy as simply
+\begin{align}
 \pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} V(b,a)
-\end{equation}
+\end{align}
 
-We consider two formulations of the value function: one based on information gain, and one on the classification loss.
+Our system will be evaluated by some properties of the state $b$, and its performance is time-sensitive.
+Accordingly, the value function should balance two terms: a function of the expected next belief state $b'$ after taking an action $a_i$, and the cost of $a_i$.
+\begin{align}
+V(b,a) = \mathbb{E}_{b' \sim P(b'|b,a)}[R(b')] - \lambda c(a|b)
+\end{align}
 
-\subsubsection{Information gain}
-negative residual entropy, following \cite{Gao2011}.
+We can be more explicit and split $b$ into its constitutents: (1) current set of observations $\mathbf{o}$; (2) posterior distribution $P(\mathbf{C}|\mathbf{o})$.
+Accordingly, we have considerable flexibility in definining the ``reward'' function $R(b)$.
 
-\todo{Write this out, and mention the greedy submodularity argument, to be made in a later section.}
+We consider a formulation of $R(b)$ based on information gain, as is common in problems of this type \todo{cite}.
+The corresponding $R: P \mapsto \mathbb{R}$ is a function on the distribution over $\mathbf{C}$.
+We note that as our goal is to reduce uncertainty of $P(\mathbf{C})$, it is natural to define $R$ as the negative entropy of the distribution given the observations.
+\begin{align}
+V(b,a)
+&= \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[R(P(\mathbf{C}|\mathbf{o} \cup o_i)] - \lambda c(a_i|\mathcal{O}) \\
+&= \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[-H(\mathbf{C}|\mathbf{o} \cup o_i)] - \lambda c(a_i|\mathcal{O})
+\end{align}
 
-\subsubsection{Classification loss}
-\todo {Write this out. What to do with the cost here?}
+Keeping in mind that $ H(\mathbf{C}|\mathcal{O}) = -\sum_{\mathbf{c}} P(\mathbf{c}|\mathcal{O}) \log P(\mathbf{c}|\mathcal{O}) $ is constant w.r.t $a_i$, it is easy to show that the policy consists of picking the action that maximizes information gain of $P(\mathbf{C})$, balanced with the cost of the action:
+\begin{align}
+\pi(b)
+&= \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \, \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[-H(\mathbf{C}|\mathbf{o} \cup o_i)] + H(\mathbf{C}|\mathbf{o}) - H(\mathbf{C}|\mathbf{o}) - \lambda c(a_i|\mathcal{O}) \\
+&= \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \, I(\mathbf{C};O_i|\mathbf{o}) - H(\mathbf{C}|\mathbf{o}) - \lambda c(a_i|\mathcal{O}) \\
+&= \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \, I(\mathbf{C};O_i|\mathbf{o}) - \lambda c(a_i|\mathcal{O})
+\end{align}
 
-\subsection{Updating the belief state}
-While the value function can learn certain dependencies between class occurrences, its job is made easier if the belief state already presents features that clearly present the relevant signals, such as co-occurence.
-Toward this end, we employ an inference model to infer the marginals $P(C_i)$ given the observations.
+\subsection{The model of the belief state}
+\begin{figure}[h!]
+\centering
+\subfloat[MRF]{\includegraphics[width=0.46\linewidth]{figures/inf_model_mrf.pdf}}
+\subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
+\caption{We present a point in the middle of the decision process, when some classifiers have already been observed.}
+\label{fig:model}
+\end{figure}
+
+Evaluation of our policy depends on being able to compute certain marginals for the value function.
+Toward this end, we employ an inference model to infer the marginals $P(C_i)$ given the observations $\mathcal{O}$.
 It may also be useful to predict the marginals $P(L_i)$, as some formulations of our value function make use of this information.
 
-We explore two alternatives for the inference model: a fully-connected Markov Random Field (MRF) and a locally weighted regression, as shown in Figure~\ref{fig:models}.
+We employ a fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
+The parameters are trained on fully-observed data.
+Exact inference is of course intractable in this model; we make use of Loopy Belief Propagation, which provides no general convergence guarantees but has been shown to work well empirically \todo{cite}.
 
-\begin{figure}[h!]
-\centering
-\subfloat[MRF]{\includegraphics[width=0.46\linewidth]{figures/inf_model_mrf.pdf}} \hfill
-\subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
-\caption{The models present a point in the middle of the decision process, when some classifiers have already been observed.}
-\label{fig:models}
-\end{figure}
+\subsection{Submodularity} \label{sec:submodularity}
+A natural question regarding our exposition so far is, why should we assume that a greedy policy would work well at all?
+In fact, the problem as described exhibits interesting properties that here allow us to show that the greedy solution is near-optimal.
 
-\subsubsection{MRF inference}
-Pros: (probably) more efficient at test time.
+We first introduce the notion of submodularity.
 
-Cons: model too restrictive? not exact inference.
+\todo{write this out}
 
-\subsubsection{Locally weighted regression}
-Approach of \cite{Gao2011}.
+\subsection{Policy parametrization and more reward functions}
+\todo{here introduce the view of learning parameters given the observed rewards}
 
-Pros: imposing minimal model constraints (except Gaussian assumptions);
-
-Cons: expensive at test time; data too sparse?
-
-\subsection{Reward} \label{sec:reward}
 Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
@@
 The reward function does not necessarily have to be related to the evaluation of the system.
-We explore two options for the reward function: the first is derived directly from the evaluation metric; the second seeks to minimize entropy of $P(\mathbf{C})$.
 
@@
 \begin{figure}[htb]
-  \center{\includegraphics[width=0.66\linewidth]{figures/apvst_expl.pdf}}
-  \caption{\label{fig:rewards}A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action.
+  \centering
+  \includegraphics[width=0.56\linewidth]{figures/apvst_expl.pdf}
+  \caption{A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action.
 The figure shows this analysis for the action highlighted in orange.}
+  \label{fig:rewards}
 \end{figure}
@@
 Learning this accurately is the domain of Reinforcement Learning research, and is generally intractable for large-scale POMDPs.
-We explore three different value functions.
 
@@
 Lastly, we use a reinforcement learning technique to learn the weights such that the expected rewards over the whole episode are maximized.
-
-\subsubsection{Greedy expected-value}
-We can compute the expected value of the reward function given a distribution over the classifier response.
-If we define the value function by this expectation, we will have constructed a one-step greedy policy.
-
-\note{Discuss submodularity defense of greedy policies here; costs are tricky though.}
 
@@
 
+\section{Implementation Details and Evaluation}
+We use FastInf \cite{Jaimovich2010} for the learning and inference in our MRF model.
+
 \section{Evaluation} \label{sec:evaluation}

### 2012-02-23 fastInf/src/bin/infer.cpp
working on interface to fastinf

@@ -374,6 +374,10 @@ int main(int argc, char* argv[])
       cerr << "The first " << _printMarginals << " marginals after evidence is set: " << endl;
       inf->getInferenceMonitor()->printMarginals(cerr, _printMarginals);
     }
+    if (_printBeliefs > 0) {
+      cerr << endl << endl << "The first " << _printBeliefs << " beliefs after evidence is set: " << endl;
+      inf->getInferenceMonitor()->printBeliefs(cerr, _printBeliefs);
+    }
   }
 
   if (success) {

### 2012-02-23 synthetic/fastinf_gist.py
fastinf-gist-pipe

@@ -7,10 +7,8 @@ from synthetic.gist_detector import GistPriors
 from synthetic.dataset import Dataset
 import cPickle
 
-def create_gist_model_for_dataset(dataset):
-  d = Dataset(dataset)
-  gist = GistPriors(dataset)
-  
+def create_gist_model_for_dataset(gist, d):
+  dataset = d.name  
   images = d.images
   
   table = np.zeros((len(images), len(d.classes)))
@@ -19,7 +17,7 @@ def create_gist_model_for_dataset(dataset):
     t = ut.TicToc()
     t.tic()
   # Some map reduce here!
-  for idx in range(comm_size, len(images), comm_rank):
+  for idx in range(comm_rank, len(images), comm_size):
     img = images[idx]
     print 'classify image %s on %d'%(img.name, comm_rank)
     classif = gist.get_priors(img)
@@ -72,19 +70,35 @@ def create_tables():
     print table
     print table.shape
 
+#def gist_probabilities_for_images(gist, images, num_classes):
+#  table = np.zeros((len(images), num_classes))
+#  for img_idx, img in enumerate(images):
+#    table[img_idx, :] = gist.get_priors(img)
+#  return table
+
 if __name__=='__main__':
   #create_tables()
+  num_bins = 5
+  dataset = 'test_pascal_train_tobi'
   
-  
-  d = Dataset('test_pascal_train_tobi')
+  gist = GistPriors(dataset)
+  d = gist.dataset
   table_gt = d.get_cls_ground_truth().arr.astype(int)
   
-  # replace this
-  table = np.random.random((table_gt.shape[0],20))
-  new_table = discretize_table(table, 5)
+  # replace this with a method to get the probs for each image
+  # ---------------->8-----------------
+  table = create_gist_model_for_dataset(gist, d)
+  #table = plausible_assignments(table_gt)
+  # ----------------8<-----------------
+  discr_table = discretize_table(table, num_bins)  
+  data = np.hstack((table_gt, discr_table))
   
-  print table
-  print new_table
+  filename = config.get_fastinf_mrf_file()
+  data_filename = config.get_fastinf_data_file()
+  write_out_mrf(data, num_bins, filename, data_filename)  
+  result = execute_lbp(filename, data_filename)
+
+  print data
   
   #print table
   

### 2012-02-23 synthetic/gist_detector.py

@@ -180,12 +180,12 @@ def test_gist_one_sample(dataset):
     if vect[idx] > 0.5:
      print config.pascal_classes[idx], vect[idx]
      
-def save_gist_differently():
-  gist_dict = cPickle.load(open(config.res_dir+'gist_features/features','r'))
-  for dataset in ['full_pascal_train','full_pascal_val','full_pascal_test']:
+def save_gist_differently(datasets):
+  gist_dict = cPickle.load(open(join(config.res_dir,'gist_features','features'),'r'))
+  for dataset in datasets:
     d = Dataset(dataset)
     print 'converting set', dataset
-    save_file = config.res_dir+'gist_features/'+dataset
+    save_file = os.path.join(config.res_dir,'gist_features',dataset)
     images = d.images
     gist_tab = np.zeros((len(images), 960))
     for idx in range(len(images)):
@@ -193,8 +193,23 @@ def save_gist_differently():
       print 'on \t', img.name
       gist_tab[idx,:] = gist_dict[img.name[:-3]]
     np.save(save_file, gist_tab)
+    
+def convert_gist_datasets(dataset_origin, datasets_new):
+  data = np.load(config.get_gist_dict_filename(dataset_origin))
+  d_orig = Dataset(dataset_origin)
+  for dataset in datasets_new:
+    savefile = config.get_gist_dict_filename(dataset)
+    d = Dataset(dataset)
+    images = d.images
+    new_data = np.zeros((len(images), data.shape[1]))
+    for img_idx, img in enumerate(images):
+      orig_img = d_orig.get_image_by_filename(img.name)
+      row = d_orig.images.index(orig_img)
+      new_data[img_idx, :] = data[row, :] 
+      
+    np.save(savefile, new_data)
   
-if __name__=='__main__':
+def crossval():
   #save_gist_differently()
   #test_gist_one_sample('full_pascal_test')
   #gist_evaluate_best_svm()
@@ -219,5 +234,7 @@ if __name__=='__main__':
   
   
 if __name__=='__main__':
-  gist = GistPriors()
+  datasets = ['test_pascal_train_tobi','test_pascal_val_tobi']
+  dataset_origin = 'full_pascal_trainval'
+  convert_gist_datasets(dataset_origin, datasets)
   

### 2012-02-23 writeups/eccv12/eccv12.tex
sent draft to stefanie

@@
 	$T_s$, $T_d$  & start and deadline times \\ 
-	$b_j$        	& belief state at step $j$ \\ 
+	$b^j$        	& belief state at step $j$ \\ 
 	$\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
@@
 	$\mathcal{O}$	& set of executed actions\\
-	$\mathbf{o}$	& set of observations $\{o_k | a_k \in \mathcal{O}\}$\\
-	$c(a)$				& cost of executing $a$, in units of $t$\\
+	$\mathbf{o}$	& set of observations $\{o_i | a_i \in \mathcal{O}\}$\\
+	$c(a_i)$				& cost of executing $a_i$, in units of $t$\\
 	\hline
@@
 \begin{figure}[h!]
-\center{\includegraphics[width=0.66\linewidth]
+\center{\includegraphics[width=0.56\linewidth]
     {figures/evaluation.pdf}}
@@
 
-An action $a$ that consists of running a classifier $L_k$ returns a real-valued observation $o_k \sim P(O_k)$.
+An action $a_i$ that consists of running a classifier $L_i$ returns a real-valued observation $o_i \sim P(O_i)$.
 The state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
-We refer to the current set of observations as $\mathbf{o} = \{o_k | L_k \in \mathcal{O}\}$.
+We refer to the current set of observations as $\mathbf{o} = \{o_i | L_i \in \mathcal{O}\}$.
 
-We define the state $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$\footnote{We write $P(C_k)$ to mean $P(C_k=1)$.}, the time into episode $t$, and the set of executed actions $\mathcal{O}$ and corresponding observations $\mathbf{o}$.
+We define the state $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$\footnote{We write $P(C_k)$ to mean $P(C_k=1)$.}, the time into episode $t$, and the set of executed actions $\mathcal{O}$ with corresponding observations $\mathbf{o}$.
 
-A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $b_1$, and so on until $t$ exceeds $T_d$.
+A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b^0$ and action $a^0$ to the next pair $b^1$, and so on until $t$ exceeds $T_d$.
 At that point, the policy is terminated and a new episode begins on a new image.
@@
 \begin{align}
-\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} V(b,a)
+\pi(b) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} V(b,a_i)
 \end{align}
@@
 \begin{align}
-V(b,a) = \mathbb{E}_{b' \sim P(b'|b,a)}[R(b')] - \lambda c(a|b)
+V(b,a_i) = \mathbb{E}_{b' \sim P(b'|b,a_i)}[R(b')] - \lambda c(a_i|b)
 \end{align}
 
-We can be more explicit and split $b$ into its constitutents: (1) current set of observations $\mathbf{o}$; (2) posterior distribution $P(\mathbf{C}|\mathbf{o})$.
+We can be more explicit and split $b$ into its constitutents, such as the current set of observations $\mathbf{o}$ and the posterior distribution $P(\mathbf{C}|\mathbf{o})$.
 Accordingly, we have considerable flexibility in definining the ``reward'' function $R(b)$.
@@
 \begin{align}
-V(b,a)
+V(b,a_i)
 &= \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[R(P(\mathbf{C}|\mathbf{o} \cup o_i)] - \lambda c(a_i|\mathcal{O}) \\
@@
 \centering
-\subfloat[MRF]{\includegraphics[width=0.46\linewidth]{figures/inf_model_mrf.pdf}}
-\subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
+% \subfloat[MRF]{
+\includegraphics[width=0.56\linewidth]{figures/inf_model_mrf.pdf}
+% }
+% \subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
 \caption{We present a point in the middle of the decision process, when some classifiers have already been observed.}
@@
 
-Evaluation of our policy depends on being able to compute certain marginals for the value function.
-Toward this end, we employ an inference model to infer the marginals $P(C_i)$ given the observations $\mathcal{O}$.
-It may also be useful to predict the marginals $P(L_i)$, as some formulations of our value function make use of this information.
-
+Evaluation of our policy depends on being able to efficiently compute the marginals $o_i$ and the expected information gain $I(\mathbf{C};O_i|\mathbf{o})$.
 We employ a fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
 The parameters are trained on fully-observed data.
-Exact inference is of course intractable in this model; we make use of Loopy Belief Propagation, which provides no general convergence guarantees but has been shown to work well empirically \todo{cite}.
+Exact inference is of course intractable in a general model of this type, and quite slow for a model of our size.
+Instead, we use Loopy Belief Propagation, which provides no general convergence guarantees but has been shown to work well empirically \todo{cite}.
+The implementations details are given further in \autoref{sec:implementation}.
 
@@
 A natural question regarding our exposition so far is, why should we assume that a greedy policy would work well at all?
-In fact, the problem as described exhibits interesting properties that here allow us to show that the greedy solution is near-optimal.
+In fact, the problem as described has properties that here allow us to show that the greedy solution is near-optimal.
 
 We first introduce the notion of submodularity.
+A set function $f$ is submodular if, whenever $A \subseteq B \subseteq E$ and $e \in E \setminus B$ it holds that
+\begin{equation}
+f(A \cup {e}) - f(A) \geq f(B \cup {e}) - f(B)
+\end{equation}
 
-\todo{write this out}
+Additionally, $f$ is called monotone if whenever $A \subseteq B$ it holds that $f(A) \leq f(B)$.
+Nemhauser~\cite{Nemhauser1978} famously showed that a greedy algorithm applied to maximizing submodular monotone functions with $f(\emptyset)=0$ will obtain at least a $(1-1/e)$ fraction of the optimal solution.
+
+Krause and Guestrin~\cite{Krause2005a} showed that the result applies to the problem of selecting a set of observations, such as in a sensor network, which maximally reduces uncertainty.
+Specifically, they showed that if the function to be maximized by selecting observations $S$ is information gain of latent variables $U$ in a graphical model such that variables in $S$ are independent given $U$, the greedy selection algorithm gives the same near-optimal bound as  ~\cite{Nemhauser1978}, and that no polynomial-time algorithm can be guaranteed to give a better bound, unless $P \neq NP$.
+
+\todo{adaptive submodularity \cite{Golovin2011}}
 
@@
 
-\section{Implementation Details and Evaluation}
-We use FastInf \cite{Jaimovich2010} for the learning and inference in our MRF model.
+\section{Implementation Details and Evaluation} \label{sec:implementation}
+We use FastInf \cite{Jaimovich2010} for learning and inference in our MRF model.
+The real-valued classifier responses $o_i$ are discretized into data-dependent bins for efficiency.
 
@@
 - show that the greedy policy works better than random and better than fixed-order
-- show that the reinfrocement learning policy works better than greedy, at least for the non-infogain rewards.
+
+- show that the reinforcement learning policy works better than greedy, at least for the non-infogain rewards.
 

### 2012-03-05 synthetic/evaluation.py
read filenames from .txt and plot all with given label,color,line-style

@@ -236,7 +236,7 @@ class Evaluation:
     return auc
 
   @classmethod
-  def plot_ap_vs_t(cls, tables, filename, all_bounds=None, with_legend=True, force=False):
+  def plot_ap_vs_t(cls, tables, filename, all_bounds=None, with_legend=True, force=False, plot_infos=None):
     """
     Take list of Tables containing AP vs. Time information.
     Bounds are given as a list of the same length as tables, or not at all.
@@ -256,6 +256,7 @@ class Evaluation:
     styles = ['-','--','-.','-..']
     prod = [x for x in itertools.product(colors,styles)]
     none_bounds = [None for table in tables]
+    
     # TODO: oooh that's messy
     if np.all(all_bounds==none_bounds):
       None
@@ -269,8 +270,15 @@ class Evaluation:
     for i,table in enumerate(tables):
       print("Plotting %s"%table.name)
       bounds = all_bounds[i]
-      style = prod[i][1]
-      color = prod[i][0]
+      
+      if not plot_infos == None and "line" in plot_infos[i]:
+        style = str(plot_infos[i]["line"])
+      else:
+        style = prod[i][1]
+      if not plot_infos == None and "color" in plot_infos[i]:
+        color = str(plot_infos[i]["color"])
+      else:
+        color = prod[i][0]
       times = table.subset_arr('time')
       if 'ap_mean' in table.cols and 'ap_std' in table.cols:
         vals = table.subset_arr('ap_mean')
@@ -284,8 +292,12 @@ class Evaluation:
       high_bound_val = vals[-1]
       if bounds != None:
         high_bound_val = vals[times.tolist().index(bounds[1])]
-
-      label = "(%.2f, %.2f) %s"%(auc,high_bound_val,table.name)
+      
+      if not plot_infos == None and "label" in plot_infos[i]:
+        label = str(plot_infos[i]["label"])
+      else:
+        label = "(%.2f, %.2f) %s"%(auc,high_bound_val,table.name)
+      
       plt.plot(times, vals, style,
           linewidth=2,color=color,label=label)
 

### 2012-03-05 synthetic/run_experiment.py

@@ -72,13 +72,21 @@ def load_configs(name):
 
   dirname = opjoin(config.config_dir,name)
   filename = opjoin(config.config_dir,name+'.json')
+  collectname = opjoin(config.config_dir,name+'.txt')
+  
   if os.path.isdir(dirname):
     filenames = glob.glob(dirname+'/*.json')
     configs = []
     for filename in filenames:
       configs += load_config_file(filename)
-  else:
+  elif os.path.isfile(filename):
     configs = load_config_file(filename)
+    
+  elif os.path.isfile(collectname):
+    filenames = open(collectname, 'r').readlines()
+    configs = []
+    for filename in filenames:
+      configs += load_config_file(opjoin(config.config_dir,os.path.dirname(name),filename[:-1]+'.json'))
   return configs
 
 def main():
@@ -148,11 +156,12 @@ def main():
   clses_tables_whole = []
   all_bounds = []
 
+  plot_infos = [] 
   for config_f in configs:
     dp = DatasetPolicy(dataset, train_dataset, weights_dataset_name, **config_f)
     ev = Evaluation(dp)
     all_bounds.append(dp.bounds)
-
+    plot_infos.append(dict((k,config_f[k]) for k in ('label','line','color') if k in config_f))
     # output the det configs first
     if args.det_configs:
       dp.output_det_statistics()
@@ -179,20 +188,21 @@ def main():
     # det avg
     ff = opjoin(dirname, '%s_det_avg.png'%filename)
     ff_nl = opjoin(dirname, '%s_det_avg_nl.png'%filename)
-    Evaluation.plot_ap_vs_t(dets_tables, ff, all_bounds, with_legend=True, force=True)
-    Evaluation.plot_ap_vs_t(dets_tables, ff_nl, all_bounds, with_legend=False, force=True)
+    
+    Evaluation.plot_ap_vs_t(dets_tables, ff, all_bounds, with_legend=True, force=True, plot_infos=plot_infos)
+    Evaluation.plot_ap_vs_t(dets_tables, ff_nl, all_bounds, with_legend=False, force=True, plot_infos=plot_infos)
 
     # det whole
     ff = opjoin(dirname, '%s_det_whole.png'%filename)
     ff_nl = opjoin(dirname, '%s_det_whole_nl.png'%filename)
[…]

### 2012-03-05 writeups/eccv12/eccv12.tex
broke paper up into sections, importing some from cvpr12 writeup

--- 2012-02-20 writeups/eccv12/eccv12.tex
@@
 \begin{abstract}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Cras imperdiet, orci sagittis consequat vehicula, metus tellus pulvinar metus, eget cursus tortor quam sit amet ligula.
+Donec vel leo ac sem blandit vulputate.
+Etiam pellentesque, quam non condimentum posuere, dolor augue mollis velit, posuere auctor lectus neque in nulla.
+Aenean in risus sit amet nisl lacinia eleifend et non velit.
+Aliquam mi magna, faucibus sed venenatis vitae, commodo ac nisi.
+Pellentesque tristique dictum mauris, et sollicitudin eros sollicitudin id.
+Cras elit mi, luctus quis vestibulum in, sagittis vel elit.
+Sed ligula dolor, ultrices eget gravida sit amet, dictum vel nisl.
 \end{abstract}
 
-\section{Sequential Decision Problem} \label{sec:sdp}
-
-We first describe the requirements for our target system, and set the notation.
-Details of our implementation are then given.
-
-\subsection{Problem Setting} \label{sec:problem_setting}
-
-We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains at least one, and often multiple, objects.
-Each object is labeled with exactly one category label $1$ through $K$.
-
-The multi-class, multi-label \emph{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $i$, for each class $i \in \{1,\dots,K\}$.
-The answer for a single label is given with a real-valued confidence by a function $\emph{classify}(\mathcal{I},i)$.
-We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_i \in \mathbb{B} = \{0,1\}$ is set to $1$ if an object of class $i$ is present.
-
-The answer is evaluated by plotting precision vs.
-recall across dataset $\mathcal{D}$ (by progressively lowering the confidence threshold for a positive label) and integrating to yield the Average Precision (AP) metric \cite{pascal-voc-2010}.
-
-We can make the classification problem more difficult by posing the \emph{counting} problem, which asks how many objects of class $i$ are present in $\mathcal{I}$, for each $i$.
-This setting is not commonly evaluated; we mention it for its usefulness in later exposition.
-
-Finally, the \emph{detection} problem is to output a list of bounding boxes (sub-images defined by four coordinates), each with a real-valued confidence that it encloses a single instance of an object of class $i$.
-The answer for a single class $i$ is given by an algorithm $\emph{detect}(\mathcal{I},i)$, which outputs a list of bounding boxes $B$ and associated confidences.
-To highlight the hierarchical structure of these problems, we note that the confidences may be given by $\operatorname{classify}(b,i)$ for each sub-image $b \in B$, and that the correct answer to the detection problem also answers the counting and classification problems.
-
-Here we describe the classification problem setup, although we evaluate performance on both classification and detection tasks.
-
-\subsection{Multi-class Classification Policy}
-
-\begin{table}
-\centering
-\caption{Summary of the notation used.}
-\label{tab:notation}
-\begin{tabular}{|l|l|}
-	\hline
-	$C_i$         & presence of class $i$ \\ 
-	$K$           & number of object classes \\ 
-	$t$           & time into episode \\ 
-	$T_s$, $T_d$  & start and deadline times \\ 
-	$\mathcal{A}$ & set of actions \\ 
-	$b_j$        	& belief state at step $j$ \\ 
-	$\pi$         & policy, $\pi(b) \mapsto a \in \mathcal{A}$ \\ 
-	\hline
-\end{tabular}\end{table}
-
-\begin{figure}[h!]
-\center{\includegraphics[width=0.66\linewidth]
-    {figures/pomdp.pdf}}
-  \caption{Summary of our approach to the problem.
-Our system has two major parts: (1) selecting an action by predicting its value; (2) updating the belief state with observations resulting from the action.}
-  \label{fig:evaluation}
-\end{figure}
-
-Our goal is a multi-class classification policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$.
-The policy repeatedly selects an action $a$ from a set of actions $\mathcal{A}$, executes it, potentially receives a set of observations, and selects the next action.
-A dynamic, or ``closed-loop,'' policy bases action selection on observations received from previous actions, exploiting the signal in inter-object and scene context for a maximally efficient path through the classifiers.
-This is our goal, and what sets our formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001} or \todo{add another one}.
-
-The set of actions $\mathcal{A}$ can include per-class classifiers, ``scene context'' functions, and feature computations.
-For simplicity of exposition, let $\mathcal{A}$ consist of $K+1$ feature computations $F$ and $2K$ per-class classifiers $L$:
-\begin{itemize}
-	\item $L^\text{co}_i$ are one-vs-all SVMs on a complex featurization of the image (computed by $F^\text{co}_i$);
-	\item $L^\text{sc}_i$ are SVMs on a simple scene-level feature (computed by $F^\text{sc}$).
-\end{itemize}
-
-\todo{
-Revise the above to make a single action compute all the scene classifiers at once.
-}
-
-Each classifier $L$ or feature computation $F$ has an expected cost $c(\cdot)$ of execution.
-Depending on the setting, the cost can be defined in terms of algorithmic runtime analysis, an idealized property such as number of \emph{flops}, or simply the empirical runtime on specific hardware.
-We take the empirical approach: every executed action advances $t$, the \emph{time into episode}, by its empirical runtime.
-
-The system is given two times: the setup time $T_s$ and deadline $T_d$.
-Between these times, the system must meet the goal of \emph{Anytime} performance and give the best possible answer to the classification problem at any point.
-
-\begin{figure}[h!]
-\center{\includegraphics[width=0.66\linewidth]
-    {figures/evaluation.pdf}}
-  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.}
-  \label{fig:evaluation}
-\end{figure}
-
-To meet this goal, the evaluation metric of a policy is defined as the area under the performance vs. time curve between points $T_s$ and $T_d$ (see Figure~\ref{fig:evaluation}).
-We evaluate policies by this more robust metric and not simply by the final performance at deadline time for the same reason---robustness---that Average Precision is used instead of a fixed Precision vs.
-Recall point.
-
-We define the \emph{belief state} $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$ (writing $P(C_i)$ to mean $P(C_i=1)$), the time into episode $t$, the set of executed actions $\mathcal{O}$, and other variables that will be discussed in \autoref{sec:value}.
-\comment{The terminology of ``belief'' comes from reinforcement learning and refers to the distribution $P(\mathbf{C})$.}
-
-An action $a$ can result in a set of observations $o$ that are used to update the belief state.
-At the very least, the state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
-
-A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $(b_1,a_1)$, and so on until $t$ exceeds $T_d$.
-At that point, the policy is terminated and a new episode begins on a new image.
-
-The policy's performance is determined by treating the final values of $P(\mathbf{C})$ as the set of confidence scores $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ for the multi-label classification evaluation (see \autoref{sec:problem_setting}).
-
-\subsection{The value function} \label{sec:value}
-Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
-As our goal is to pick actions, we want to formulate a function that assigns a value to a potential action, given the current state of the decision process.
-We will then be able to define our policy as simply
-\begin{equation}
-\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} V(b,a)
-\end{equation}
-
-We consider two formulations of the value function: one based on information gain, and one on the classification loss.
-
-\subsubsection{Information gain}
-negative residual entropy, following \cite{Gao2011}.
-
-\todo{Write this out, and mention the greedy submodularity argument, to be made in a later section.}
-
-\subsubsection{Classification loss}
-\todo {Write this out. What to do with the cost here?}
-
-\subsection{Updating the belief state}
-While the value function can learn certain dependencies between class occurrences, its job is made easier if the belief state already presents features that clearly present the relevant signals, such as co-occurence.
-Toward this end, we employ an inference model to infer the marginals $P(C_i)$ given the observations.
-It may also be useful to predict the marginals $P(L_i)$, as some formulations of our value function make use of this information.
-
-We explore two alternatives for the inference model: a fully-connected Markov Random Field (MRF) and a locally weighted regression, as shown in Figure~\ref{fig:models}.
-
-\begin{figure}[h!]
-\centering
-\subfloat[MRF]{\includegraphics[width=0.46\linewidth]{figures/inf_model_mrf.pdf}} \hfill
-\subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
-\caption{The models present a point in the middle of the decision process, when some classifiers have already been observed.}
-\label{fig:models}
-\end{figure}
-
-\subsubsection{MRF inference}
-Pros: (probably) more efficient at test time.
-
-Cons: model too restrictive? not exact inference.
-
-\subsubsection{Locally weighted regression}
-Approach of \cite{Gao2011}.
-
-Pros: imposing minimal model constraints (except Gaussian assumptions);
-
-Cons: expensive at test time; data too sparse?
-
-\subsection{Reward} \label{sec:reward}
-Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
-The total expected reward of a policy $\pi$ is then defined as the sum of rewards
-\begin{equation}
-\mathbb{E}_\pi[\sum_{j=0}^J R(b_j)]
-\end{equation}
-
-The reward function does not necessarily have to be related to the evaluation of the system.
-We explore two options for the reward function: the first is derived directly from the evaluation metric; the second seeks to minimize entropy of $P(\mathbf{C})$.
-
-\subsubsection{Slope of performance vs. time}
-\begin{figure}[htb]
-  \center{\includegraphics[width=0.66\linewidth]{figures/apvst_expl.pdf}}
-  \caption{\label{fig:rewards}A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action.
-The figure shows this analysis for the action highlighted in orange.}
-\end{figure}
-
-Remembering that the final evaluation of a policy consists of the area under the performance vs.
-time curve, we formulate per-action rewards such that their addition results in precisely this quantity.
-Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
-\begin{equation}\label{eq:advanced}
-\Delta AP (t_T-\Delta t)
-\end{equation}
-where $t_T$ is the time left until deadline, and $\Delta t$ and $\Delta AP$ are the time taken and AP change produced by the action.
-
-The equation breaks down into a term to maximize, $\Delta AP t_T$, and a term to minimize, $\Delta AP \Delta t$.
-This agrees with the intuition that to capture the most area under the curve, the slope needs to be maximized at each point.
-Additionally, the equation shows that if $\Delta t$ exceeds $t_T$, the value of taking the action is negative.
-
-At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
-We therefore define our policy as
-\begin{equation}
-\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
-\end{equation}
-
-Learning this accurately is the domain of Reinforcement Learning research, and is generally intractable for large-scale POMDPs.
-We explore three different value functions.
-
-First, we seek to maximize the expected next-stage reward, and manually construct a value function such that picking the action with maximal value achieves this.
-Next, we note that the manually constructed value function can be represented as a scalar product of a parameter vector with a featurization of the belief state; we learn the weights by regression to the actual next-stage reward from running many episodes.
-Lastly, we use a reinforcement learning technique to learn the weights such that the expected rewards over the whole episode are maximized.
-
-\subsubsection{Greedy expected-value}
-We can compute the expected value of the reward function given a distribution over the classifier response.
-If we define the value function by this expectation, we will have constructed a one-step greedy policy.
-
-\note{Discuss submodularity defense of greedy policies here; costs are tricky though.}
-
-\subsubsection{Learning the greedy policy}
-We note that we can represent the one-step greedy policy value function as a scalar product
-
-\subsubsection{Learning the proper policy}
-\note{I'm considering two options here: (1) log-linear representation and policy gradient algorithm; (2) least-squares policy iteration.}
-
-\paragraph{Policy gradient algorithm}
-We redefine our policy as picking the mode of a log-linear parametrized distribution:
-\begin{equation}
-P(a|b;\theta) = \frac{\exp(\theta^T \phi(b,a))}{\sum_{a' \in \mathcal{A}} \exp(\theta^T \phi(b,a')}
-\end{equation}
-
-Basically stochastic gradient ascent on the estimate of the reward accrued by an episode.
-
-This approach has been shown to scale to large problems in \cite{Branavan2009}, although it has been proven to converge only to local maxima and only for MDPs \cite{Sutton2000}.
-
-\note{Does the constraint that no action is taken more than once affect this algorithm?}
-
-\paragraph{Least-squares Policy Iteration}
-An efficient form of temporal-difference learning used in \cite{Kwok2004}.
-Policy remains parameterized as it was.
-
-\section{Evaluation} \label{sec:evaluation}
-- show that the greedy policy works better than random and better than fixed-order
-- show that the reinfrocement learning policy works better than greedy, at least for the non-infogain rewards.
-
-\subsection{Classification}
-
-\subsection{Detection}
-We also evaluate using the task of detection (see \autoref{sec:problem}).
+\input{introduction.tex} % includes Evaluation section
+\input{technical.tex}
+\input{evaluation.tex}
+\input{related.tex}
+\input{future_work.tex}
 

### 2012-03-05 writeups/eccv12/evaluation.tex
broke paper up into sections, importing some from cvpr12 writeup

\section{Evaluation} \label{sec:evaluation}
- show that the greedy policy works better than random and better than fixed-order

- show that the reinforcement learning policy works better than greedy, at least for the non-infogain rewards.

\subsection{Classification}

\subsection{Detection}
We also evaluate using the task of detection (see \autoref{sec:problem}).

### 2012-03-05 writeups/eccv12/introduction.tex
broke paper up into sections, importing some from cvpr12 writeup

\section{Introduction}

In recent years, the computer vision field has converged on a general method for object detection, and a standard evaluation of results.
Most current state-of-the-art object detection systems consist of three tasks: proposing regions of the image, evaluating a given region for presence of an object of a given category, and post-processing the results.
In the evaluation ground truth, each object is most commonly assumed to belong to one of a fixed set of classes; its location is approximated by placing a bounding box around pixels belonging to it.
Large datasets of such human annotations are used for evaluation of detection algorithms~\cite{pascal-voc-2010}.

With few exceptions, current detection systems are not inherently multi-class.
Instead, separate detectors are trained per class, and they are deployed and evaluated independently.
The evaluation of multi-class performance, if at all given, consists of averaging the per-class metrics.
Some notable papers do make multi-class detection a priority, and accordingly evaluate in a multi-class setting, where false positives can be generated both by incorrect localization and incorrect labeling.
State-of-the-art detection systems also do not generally make efficiency a goal.

It is of course important to refrain from locking object recognition research into a single detector architecture with a focus only on increasing efficiency.
That said, there are applications for which performance truly is time-sensitive.
In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
In large-scale detection system deployments, such as for image search, results need to be obtained quickly per image as the number of images to process is large and growing.
When processing large photo collection on end-user machines for immediate consumer navigation, the same is true.

\begin{figure}[ht!]
\center{\includegraphics[width=0.56\linewidth]
    {figures/evaluation.pdf}}
  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.}
  \label{fig:evaluation}
\end{figure}

In all these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.
Furthermore, the value of the answer depends largely on the target application.

A hypothetical recognition system for an advertising deployment presents a great case study.
The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
The most rational detection strategy in such an environment should depend on all of these variables.

We argue that the key to tackling such problems of dynamic recognition resource allocation is to start asking a new question:
\emph{What is the best performance we can get on a budget?}
To answer it, we consider the evaluation metric of performance vs. time, presented in Figure~\ref{fig:evaluation} and discussed further in the text.

Our goal is a dynamic policy for selecting classifiers or detectors to achieve the highest recognition performance under this evaluation.
Without further ado, let us formalize the problem.

### 2012-03-05 writeups/eccv12/related.tex
broke paper up into sections, importing some from cvpr12 writeup

\section{Related Work}
The literature on object detection is vast.
Here we briefly summarize detection work that sufficiently contextualizes our contribution.

An early success in efficient object detection used simple Haar features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime~\cite{Viola2001}.
Although the simple features and classifiers of this method have been surpassed by more complex detectors, the idea of cascading classifier evaluations is still often used.

The best recent performance has come from detectors that use gradient-based features to represent objects as either a collection of local patches or as object-sized windows \cite{Dalal2005,Lowe2004}.
Usually, SVM classifiers are used to learn separating hyperplanes in such feature spaces between objects of a given class and all other possible contents of an image window.

Window proposal is often done exhaustively over the image space, in a ``sliding window'' fashion.
Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Chum2007b,Vedaldi2009,Vijayanarasimhan2011}.
For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008b}---however, the method has not been able to obtain state-of-the-art performance, despite an important recent generalization \cite{Lehmann2011a}.

Although none of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal, some work has been done in the area, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008,Paletta2005}.

Anytime performance in vision systems is a surprisingly little-explored idea.
A pioneering recent paper picks features with maximum value of information in a Hough-voting framework, and explicitly evaluates performance vs. time \cite{Vijayanarasimhan2010}.
A recent detection paper motivated by time constraints concerns real-time person tracking~\cite{Mitzel2011b}.

Inherently multi-class detection has its own line of work, focusing largely on making detection time sublinear in the number of classes through sharing features~\cite{Torralba2007,Fan2005,Razavi2011}.
A recent post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression~\cite{Desai2009}.

Context of course has a long history in vision.
One source of context is the scene or non-detector cues; for the PASCAL VOC, these are quantitatively considered in~\cite{Divvala2009}.
Another source is inter-object context, used for detection in a random field setting in~\cite{Torralba2004}.
A critical summary of the main approaches to using context for object detection is given in \cite{Galleguillos2010}.

### 2012-03-05 writeups/eccv12/technical.tex
broke paper up into sections, importing some from cvpr12 writeup

\section{Recognition Problems}

We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains at least one, and often multiple, objects.
Each object is labeled with exactly one category label $k \in \{1, \dots, K\}$.

The multi-class, multi-label \textbf{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $k$.
The answer for a single label is given with a real-valued confidence by a function $\emph{classify}(\mathcal{I},k)$.
We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_k \in \mathbb{B} = \{0,1\}$ is set to $1$ if an object of class $k$ is present.

The answer is evaluated by plotting precision vs. recall across dataset $\mathcal{D}$ (by progressively lowering the confidence threshold for a positive label) and integrating to yield the Average Precision (AP) metric, which has become the standard evaluation for recognition performance on challenging datasets \cite{pascal-voc-2010}.

\comment{
We can make the classification problem more difficult by posing the \emph{counting} problem, which asks how many objects of class $k$ are present in $\mathcal{I}$, for each $k$.
This setting is not commonly evaluated; we mention it for its usefulness in later exposition.
}

The \textbf{detection} problem is to output a list of bounding boxes (sub-images defined by four coordinates), each with a real-valued confidence that it encloses a single instance of an object of class $k$, for each $k$.
The answer for a single class is given by an algorithm $\emph{detect}(\mathcal{I},k)$, which outputs a list of sub-image bounding boxes $B$ and their associated confidences.

A common measure of a correct detection is the PASCAL overlap: two bounding boxes are considered to match if they have the same label and the ratio of their intersection to their union is at least $\frac{1}{2}$.
Again, Average Precision is the single-number metric for the performance of a detector.

As our task is fundamentally in \emph{multi-class} object detection, we rely on a slightly different evaluation than is commonly used (although it has precedent in \cite{Desai2009}).
Instead of pooling detections across images in the dataset, and considering classes individually, we pool detections across classes, but consider images individually, reporting results averaged across the dataset.

To highlight the hierarchical structure of these problems, we note that (1) the confidences for each sub-image $b \in B$ may be given by $\emph{classify}(b,k)$; (2) the correct answer to the detection problem also answers the classification problem. \comment{the counting and classification problems}

Our goal is a general recognition policy that outputs both classification and detection results; we evaluate on both tasks.

\section{Multi-class Recognition Policy}
\begin{figure}[h!]
\center{\includegraphics[width=0.66\linewidth]
    {figures/pomdp.pdf}}
  \caption{Summary of our approach to the problem. Our system has two major parts: (1) selecting an action by predicting its value; (2) updating the belief state with observations resulting from the action.}
  \label{fig:evaluation}
\end{figure}

Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ and a list of multi-class detection results $\emph{detect}(I)$.

The policy repeatedly selects an action $a_i$ from a set of actions $\mathcal{A}$, executes it, potentially receives an observation $o_i$, and selects the next action.
The set of actions can include classifiers, detectors, or hybrid actions (detector followed by classification of its output).

A dynamic, or ``closed-loop,'' policy bases action selection on observations received from previous actions, exploiting the signal in inter-object and scene context for a maximally efficient path through the actions.
This is our goal, and what sets our formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001} or \todo{add another one}.

For simplicity of exposition, let $\mathcal{A}$ consist of $2K$ actions:
\begin{itemize}
  \item $K$ detectors $L^\text{det}_i$: one-vs-all deformable part-model classifiers on a HOG featurization of the image \cite{Felzenszwalb2010a}, with associated linear classification of the detections.
  \item $K$ classifiers $L^\text{gist}_i$: one-vs-all SVMs on the GIST feature \cite{Torralba2004}.
\end{itemize}

\subsubsection{Time and Evaluation}
Each action $L$ has an expected cost $c(\cdot)$ of execution.
Depending on the setting, the cost can be defined in terms of algorithmic runtime analysis, an idealized property such as number of \emph{flops}, or simply the empirical runtime on specific hardware.
We take the empirical approach: every executed action advances $t$, the \emph{time into episode}, by its empirical runtime.

As shown in Figure~\ref{fig:evaluation}, the system is given two times: the setup time $T_s$ and deadline $T_d$.
From the setup time to the deadline, we want to obtain the best possible answer if stopped at any given time.
This corresponds to the general notion of Anytime algorithms, and is motivated by desired flexibility in the system.

A single-number metric that corresponds to this objective is simply the ratio of the area captured under the curve to the total area between the start and deadline bounds.
\comment{Just like the metric of Average Precision itself was motivated by the inadequacy of any single Precision-Recall operating point to describe the performance of a robust system, our proposed metric is motivated by the inadequacy of any single Performance vs. Time operating point.}
We evaluate policies by this more robust metric and not simply by the final performance at deadline time for the same reason that Average Precision is used instead of a fixed Precision vs. Recall point.

\subsubsection{Sequential Execution}
An action $a_i$ that consists of running a classifier $L_i$ returns a real-valued observation $o_i \sim P(O_i)$.
The state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
We refer to the current set of observations as $\mathbf{o} = \{o_i | L_i \in \mathcal{O}\}$.

We define the belief state $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$, where we write $P(C_k)$ to mean $P(C_k=1)$.
Additionally, $b$ records the time into episode $t$, and the set of executed actions $\mathcal{O}$ with corresponding observations $\mathbf{o}$.

A recognition \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b^0$ and action $a^0$ to the next pair $b^1$, and so on until $t$ exceeds $T_d$.
At that point, the policy is terminated and a new episode begins on a new image.

The policy's performance at time $t$ is determined by the detection and classification observations that have been observed at the last belief state $b^j$ before that point.
For classification of unobserved classes, we treat the corresponding values of $P(\mathbf{C})$ as the set of confidence scores $\{\emph{classify}(k)\}$.
Detection results of unobserved classes are an empty set.

\todo{Is the above sufficiently clear?}

Our notation is summarized in \autoref{tab:notation}.

\begin{table}[h!]
\centering
\caption{Summary of the notation.}
\label{tab:notation}
\begin{tabular}{|l|l|}
  \hline
  $\mathcal{I}$ & image \\
  $C_k$         & presence of class $k \in \{1,\dots,K\}$ \\ 
  $t$           & time into episode \\ 
  $T_s$, $T_d$  & start and deadline times \\ 
  $b^j$         & belief state at step $j$ \\ 
  $\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
  $\mathcal{A}$ & set of actions $a_i \in \{\mathcal{L} \cup \mathcal{F}\}$\\ 
  $\mathcal{F}$ & set of featurization actions \\
  $\mathcal{L}$ & set of classification actions\\
  $o_i$         & a real-valued observation upon executing $a_i \in \mathcal{L}$\\
  $\mathcal{O}$ & set of executed actions\\
  $\mathbf{o}$  & set of observations $\{o_i | a_i \in \mathcal{O}\}$\\
  $c(a_i)$        & cost of executing $a_i$, in units of $t$\\
  \hline
\end{tabular}\end{table}

\section{Selecting actions} \label{sec:value}
Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
As our goal is to pick actions, we want to formulate a function $V(b,a)$  that assigns a value to a potential action, given the current state of the decision process.
We can then define the policy as simply
\begin{align}
\pi(b) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} V(b,a_i)
\end{align}

Our system will be evaluated by some properties of the state $b$, and its performance is time-sensitive.
Accordingly, the value function should balance two terms: a function of the expected next belief state $b'$ after taking an action $a_i$, and the cost of $a_i$.
\begin{align}
V(b,a_i) = \mathbb{E}_{b' \sim P(b'|b,a_i)}[R(b')] - \lambda c(a_i|b)
\end{align}

We can be more explicit and split $b$ into its constitutents, such as the current set of observations $\mathbf{o}$ and the posterior distribution $P(\mathbf{C}|\mathbf{o})$.
Accordingly, we have considerable flexibility in definining the ``reward'' function $R(b)$.

We consider a formulation of $R(b)$ based on information gain, as is common in problems of this type \todo{cite}.
The corresponding $R: P \mapsto \mathbb{R}$ is a function on the distribution over $\mathbf{C}$.
We note that as our goal is to reduce uncertainty of $P(\mathbf{C})$, it is natural to define $R$ as the negative entropy of the distribution given the observations.
\begin{align}
V(b,a_i)
&= \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[R(P(\mathbf{C}|\mathbf{o} \cup o_i)] - \lambda c(a_i|\mathcal{O}) \\
&= \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[-H(\mathbf{C}|\mathbf{o} \cup o_i)] - \lambda c(a_i|\mathcal{O})
\end{align}

Keeping in mind that $ H(\mathbf{C}|\mathcal{O}) = -\sum_{\mathbf{c}} P(\mathbf{c}|\mathcal{O}) \log P(\mathbf{c}|\mathcal{O}) $ is constant w.r.t $a_i$, it is easy to show that the policy consists of picking the action that maximizes information gain of $P(\mathbf{C})$, balanced with the cost of the action:
\begin{align}
\pi(b)
&= \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \, \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[-H(\mathbf{C}|\mathbf{o} \cup o_i)] + H(\mathbf{C}|\mathbf{o}) - H(\mathbf{C}|\mathbf{o}) - \lambda c(a_i|\mathcal{O}) \\
&= \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \, I(\mathbf{C};O_i|\mathbf{o}) - H(\mathbf{C}|\mathbf{o}) - \lambda c(a_i|\mathcal{O}) \\
&= \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \, I(\mathbf{C};O_i|\mathbf{o}) - \lambda c(a_i|\mathcal{O})
\end{align}

\subsection{The model of the belief state}
\begin{figure}[h!]
\centering
% \subfloat[MRF]{
\includegraphics[width=0.56\linewidth]{figures/inf_model_mrf.pdf}
% }
% \subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
\caption{We present a point in the middle of the decision process, when some classifiers have already been observed.}
\label{fig:model}
\end{figure}

Evaluation of our policy depends on being able to efficiently compute the marginals $o_i$ and the expected information gain $I(\mathbf{C};O_i|\mathbf{o})$.
We employ a fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
The parameters are trained on fully-observed data.
Exact inference is of course intractable in a general model of this type, and quite slow for a model of our size.
Instead, we use Loopy Belief Propagation, which provides no general convergence guarantees but has been shown to work well empirically \todo{cite}.
The implementations details are given further in \autoref{sec:implementation}.

\subsection{Submodularity} \label{sec:submodularity}
A natural question regarding our exposition so far is, why should we assume that a greedy policy would work well at all?
In fact, the problem as described has properties that here allow us to show that the greedy solution is near-optimal.

We first introduce the notion of submodularity.
A set function $f$ is submodular if, whenever $A \subseteq B \subseteq E$ and $e \in E \setminus B$ it holds that
\begin{equation}
f(A \cup {e}) - f(A) \geq f(B \cup {e}) - f(B)
\end{equation}

Additionally, $f$ is called monotone if whenever $A \subseteq B$ it holds that $f(A) \leq f(B)$.
Nemhauser~\cite{Nemhauser1978} famously showed that a greedy algorithm applied to maximizing submodular monotone functions with $f(\emptyset)=0$ will obtain at least a $(1-1/e)$ fraction of the optimal solution.

Krause and Guestrin~\cite{Krause2005a} showed that the result applies to the problem of selecting a set of observations, such as in a sensor network, which maximally reduces uncertainty.
Specifically, they showed that if the function to be maximized by selecting observations $S$ is information gain of latent variables $U$ in a graphical model such that variables in $S$ are independent given $U$, the greedy selection algorithm gives the same near-optimal bound as  ~\cite{Nemhauser1978}, and that no polynomial-time algorithm can be guaranteed to give a better bound, unless $P \neq NP$.

\todo{adaptive submodularity \cite{Golovin2011}}

\subsection{Policy parametrization and more reward functions}
\todo{here introduce the view of learning parameters given the observed rewards}

Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
The total expected reward of a policy $\pi$ is then defined as the sum of rewards
\begin{equation}
\mathbb{E}_\pi[\sum_{j=0}^J R(b_j)]
\end{equation}

The reward function does not necessarily have to be related to the evaluation of the system.

\subsubsection{Slope of performance vs. time}
\begin{figure}[htb]
  \centering
  \includegraphics[width=0.56\linewidth]{figures/apvst_expl.pdf}
  \caption{A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action. The figure shows this analysis for the action highlighted in orange.}
  \label{fig:rewards}
\end{figure}

Remembering that the final evaluation of a policy consists of the area under the performance vs. time curve, we formulate per-action rewards such that their addition results in precisely this quantity.
Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
\begin{equation}\label{eq:advanced}
\Delta AP (t_T-\Delta t)
\end{equation}
where $t_T$ is the time left until deadline, and $\Delta t$ and $\Delta AP$ are the time taken and AP change produced by the action.

The equation breaks down into a term to maximize, $\Delta AP t_T$, and a term to minimize, $\Delta AP \Delta t$.
This agrees with the intuition that to capture the most area under the curve, the slope needs to be maximized at each point.
Additionally, the equation shows that if $\Delta t$ exceeds $t_T$, the value of taking the action is negative.

At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
We therefore define our policy as
\begin{equation}
\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
\end{equation}

Learning this accurately is the domain of Reinforcement Learning research, and is generally intractable for large-scale POMDPs.

First, we seek to maximize the expected next-stage reward, and manually construct a value function such that picking the action with maximal value achieves this.
Next, we note that the manually constructed value function can be represented as a scalar product of a parameter vector with a featurization of the belief state; we learn the weights by regression to the actual next-stage reward from running many episodes.
Lastly, we use a reinforcement learning technique to learn the weights such that the expected rewards over the whole episode are maximized.

\subsubsection{Learning the greedy policy}
We note that we can represent the one-step greedy policy value function as a scalar product

\subsubsection{Learning the proper policy}
\note{I'm considering two options here: (1) log-linear representation and policy gradient algorithm; (2) least-squares policy iteration.}

\paragraph{Policy gradient algorithm}
We redefine our policy as picking the mode of a log-linear parametrized distribution:
\begin{equation}
P(a|b;\theta) = \frac{\exp(\theta^T \phi(b,a))}{\sum_{a' \in \mathcal{A}} \exp(\theta^T \phi(b,a')}
\end{equation}

Basically stochastic gradient ascent on the estimate of the reward accrued by an episode.

This approach has been shown to scale to large problems in \cite{Branavan2009}, although it has been proven to converge only to local maxima and only for MDPs \cite{Sutton2000}.

\note{Does the constraint that no action is taken more than once affect this algorithm?}

\paragraph{Least-squares Policy Iteration}
An efficient form of temporal-difference learning used in \cite{Kwok2004}.
Policy remains parameterized as it was.

\section{Implementation Details and Evaluation} \label{sec:implementation}
We use FastInf \cite{Jaimovich2010} for learning and inference in our MRF model.
The real-valued classifier responses $o_i$ are discretized into data-dependent bins for efficiency.

### 2012-03-05 synthetic/evaluation.py
fixed bugs for csc AND gist runs

@@ -82,7 +82,7 @@ class Evaluation:
       for img_ind,image in enumerate(self.dataset.images):
         gt_for_image_list.append(gt.filter_on_column('img_ind',img_ind))
         if dets.arr == None:
-          detections = ut.Table(arr=np.arange([]),cols=[]) 
+          detections = ut.Table() 
         else:
           detections = dets.filter_on_column('img_ind',img_ind)
         img_dets_list.append(detections)
@@ -104,9 +104,13 @@ class Evaluation:
         for img_ind,image in enumerate(self.dataset.images):
           gt_for_image = gt_for_image_list[img_ind]
           img_dets = img_dets_list[img_ind] 
-          dets_to_this_point = img_dets.filter_on_column('time',point,operator.le)          
-          num_dets += dets_to_this_point.shape()[0]
-          det_ap,rec,prec = self.compute_det_pr(dets_to_this_point, gt_for_image)
+          if img_dets.cols == None:
+            dets_to_this_point= img_dets
+            det_ap = 0
+          else:
+            dets_to_this_point = img_dets.filter_on_column('time',point,operator.le)          
+            num_dets += dets_to_this_point.shape()[0]
+            det_ap,_,_ = self.compute_det_pr(dets_to_this_point, gt_for_image)
           det_aps.append(det_ap)
         det_arr[i,:] = [point,np.mean(det_aps),np.std(det_aps)]
         print("Calculating AP (%.3f) of the %d detections up to %.3fs took %.3fs"%(
@@ -175,11 +179,15 @@ class Evaluation:
       for i in range(comm_rank,num_points,comm_size):
         tt = ut.TicToc().tic()
         point = points[i]
-        dets_to_this_point = dets.filter_on_column('time',point,operator.le)
+        if not dets.cols == None:
+          dets_to_this_point = dets
+          ap = 0
+        else:
+          dets_to_this_point = dets.filter_on_column('time',point,operator.le)
 
-        img_inds = np.unique(dets_to_this_point.subset_arr('img_ind'))
-        gt = self.dataset.get_ground_truth_for_img_inds(img_inds, include_diff=True)
-        ap,rec,prec = self.compute_det_pr(dets_to_this_point,gt)
+          img_inds = np.unique(dets_to_this_point.subset_arr('img_ind'))
+          gt = self.dataset.get_ground_truth_for_img_inds(img_inds, include_diff=True)
[…]

### 2012-03-05 writeups/eccv12/technical.tex
tech

@@
 
-We consider a formulation of $R(b)$ based on information gain, as is common in problems of this type \todo{cite}.
-The corresponding $R: P \mapsto \mathbb{R}$ is a function on the distribution over $\mathbf{C}$.
-We note that as our goal is to reduce uncertainty of $P(\mathbf{C})$, it is natural to define $R$ as the negative entropy of the distribution given the observations.
-\begin{align}
-V(b,a_i)
-&= \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[R(P(\mathbf{C}|\mathbf{o} \cup o_i)] - \lambda c(a_i|\mathcal{O}) \\
-&= \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[-H(\mathbf{C}|\mathbf{o} \cup o_i)] - \lambda c(a_i|\mathcal{O})
-\end{align}
-
-Keeping in mind that $ H(\mathbf{C}|\mathcal{O}) = -\sum_{\mathbf{c}} P(\mathbf{c}|\mathcal{O}) \log P(\mathbf{c}|\mathcal{O}) $ is constant w.r.t $a_i$, it is easy to show that the policy consists of picking the action that maximizes information gain of $P(\mathbf{C})$, balanced with the cost of the action:
-\begin{align}
-\pi(b)
-&= \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \, \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[-H(\mathbf{C}|\mathbf{o} \cup o_i)] + H(\mathbf{C}|\mathbf{o}) - H(\mathbf{C}|\mathbf{o}) - \lambda c(a_i|\mathcal{O}) \\
-&= \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \, I(\mathbf{C};O_i|\mathbf{o}) - H(\mathbf{C}|\mathbf{o}) - \lambda c(a_i|\mathcal{O}) \\
-&= \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \, I(\mathbf{C};O_i|\mathbf{o}) - \lambda c(a_i|\mathcal{O})
-\end{align}
-
 \subsection{The model of the belief state}
@@
 \centering
-% \subfloat[MRF]{
 \includegraphics[width=0.56\linewidth]{figures/inf_model_mrf.pdf}
-% }
-% \subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
-\caption{We present a point in the middle of the decision process, when some classifiers have already been observed.}
+\caption{
+We present a point in the middle of the decision process for 3 classes.
+Some classifiers have already been observed.
+}
 \label{fig:model}
@@
 The implementations details are given further in \autoref{sec:implementation}.
-
-\subsection{Submodularity} \label{sec:submodularity}
-A natural question regarding our exposition so far is, why should we assume that a greedy policy would work well at all?
-In fact, the problem as described has properties that here allow us to show that the greedy solution is near-optimal.
-
-We first introduce the notion of submodularity.
-A set function $f$ is submodular if, whenever $A \subseteq B \subseteq E$ and $e \in E \setminus B$ it holds that
-\begin{equation}
-f(A \cup {e}) - f(A) \geq f(B \cup {e}) - f(B)
-\end{equation}
-
-Additionally, $f$ is called monotone if whenever $A \subseteq B$ it holds that $f(A) \leq f(B)$.
-Nemhauser~\cite{Nemhauser1978} famously showed that a greedy algorithm applied to maximizing submodular monotone functions with $f(\emptyset)=0$ will obtain at least a $(1-1/e)$ fraction of the optimal solution.
-
-Krause and Guestrin~\cite{Krause2005a} showed that the result applies to the problem of selecting a set of observations, such as in a sensor network, which maximally reduces uncertainty.
-Specifically, they showed that if the function to be maximized by selecting observations $S$ is information gain of latent variables $U$ in a graphical model such that variables in $S$ are independent given $U$, the greedy selection algorithm gives the same near-optimal bound as  ~\cite{Nemhauser1978}, and that no polynomial-time algorithm can be guaranteed to give a better bound, unless $P \neq NP$.
-
-\todo{adaptive submodularity \cite{Golovin2011}}
 

### 2012-03-05 synthetic/evaluation.py
not computing wholeset AP for dets cause WHY?

@@ -187,7 +187,9 @@ class Evaluation:
 
           img_inds = np.unique(dets_to_this_point.subset_arr('img_ind'))
           gt = self.dataset.get_ground_truth_for_img_inds(img_inds, include_diff=True)
-          ap,_,_ = self.compute_det_pr(dets_to_this_point,gt)
+          # TODO: fuck it!
+          #ap,_,_ = self.compute_det_pr(dets_to_this_point,gt)
+          ap = 0
         det_arr[i,:] = [point,ap]
 
         # go through the per-image classifications and only keep the latest time

### 2012-03-05 synthetic/dataset_policy.py
lowering discount

@@ -361,8 +361,8 @@ class DatasetPolicy:
     dets,clses,all_samples = self.run_on_dataset(False,num_samples)
     
     # Loop until max_iterations or the error is below threshold
-    error = threshold = 0.001
-    max_iterations = 12
+    error = threshold = 0.002
+    max_iterations = 8
     for i in range(0,max_iterations):
       # do regression with cross-validated parameters (parallelized)
       weights = None
@@ -404,7 +404,7 @@ class DatasetPolicy:
   the error and ap are %.3f and %.3f:"""%(i,len(all_samples),error,ap))
 
         # after the first iteration, check if the error is small
-        if i>0 and error<threshold:
+        if i>0 and error<=threshold:
           break
 
         print("Now collecting more samples with the updated weights...")
@@ -448,7 +448,7 @@ class DatasetPolicy:
     return np.array(feats)
 
   def compute_reward_from_samples(self, samples, mode='greedy',
-    discount=0.8, attr=None):
+    discount=0.4, attr=None):
     """
     Return vector of rewards for the given samples.
     - mode=='greedy' just uses the actual_ap of the taken action

### 2012-03-05 synthetic/dataset_policy.py
blacklist bugs, nicer labels

@@ -357,7 +357,7 @@ class DatasetPolicy:
       print self.get_reshaped_weights()
 
     # Collect samples (parallelized)
-    num_samples = 300 # actually this refers to images
+    num_samples = 350 # actually this refers to images
     dets,clses,all_samples = self.run_on_dataset(False,num_samples)
     
     # Loop until max_iterations or the error is below threshold
@@ -386,22 +386,12 @@ class DatasetPolicy:
         except:
           print("Couldn't plot, no big deal.")
 
-        # Compute the det AP of stuff so far
-        img_inds = np.unique(dets.subset_arr('img_ind'))
-        gt = self.dataset.get_ground_truth_for_img_inds(img_inds, include_diff=True)
-        ap,rec,prec = self.ev.compute_det_pr(dets, gt)
-
-        log_filename = opjoin(
-            config.get_dp_weights_images_dirname(self),'iter_%d.txt'%i)
         print("""
   After iteration %d, we've trained on %d samples and
-  the error and ap %.3f and %.3f:"""%(i,len(all_samples),error,ap))
+  the weights and error are:"""%(i,len(all_samples)))
         np.set_printoptions(precision=2,suppress=True,linewidth=160)
         print self.get_reshaped_weights()
-        with open(log_filename,'w') as f:
-          f.write("""
-  After iteration %d, we've trained on %d samples and
-  the error and ap are %.3f and %.3f:"""%(i,len(all_samples),error,ap))
+        print error
 
         # after the first iteration, check if the error is small
         if i>0 and error<threshold:
@@ -413,7 +403,7 @@ class DatasetPolicy:
       safebarrier(comm)
       weights = comm.bcast(weights,root=0)
       self.weights = weights
-      dets,clses,new_samples = self.run_on_dataset(False,num_samples)
+      new_dets,new_clses,new_samples = self.run_on_dataset(False,num_samples)
 
       if comm_rank==0:
         # We either collect only unique samples or all samples
@@ -448,7 +438,7 @@ class DatasetPolicy:
     return np.array(feats)
 
   def compute_reward_from_samples(self, samples, mode='greedy',
-    discount=0.8, attr=None):
+    discount=0.9, attr=None):
     """
     Return vector of rewards for the given samples.
     - mode=='greedy' just uses the actual_ap of the taken action
@@ -506,7 +496,7 @@ class DatasetPolicy:
     best_alpha = alphas[best_ind]
[…]

### 2012-03-05 synthetic/evaluation.py

@@ -78,9 +78,9 @@ class Evaluation:
       gt_for_image_list = []
       img_dets_list = []
       gt = self.dataset.get_ground_truth(include_diff=True)
+      
       for black in blacklist:
-        gt = gt.filter_on_column('cls_ind', black, op=operator.ne)
-      # TODO: SOMETHING IS PROBABLY WRONG HERE
+        gt = gt.filter_on_column('cls_ind', black, op=operator.ne)   
 
       for img_ind,image in enumerate(self.dataset.images):
         gt_for_image_list.append(gt.filter_on_column('img_ind',img_ind))
@@ -179,9 +179,10 @@ class Evaluation:
       cls_gt = self.dataset.get_cls_ground_truth(include_diff=False)
       
       # TODO: WRONG, REMOVE COLS INSTEAD
+      cls_gt_classes = list(cls_gt.cols)
       for black in blacklist:
-        cls_gt = cls_gt.filter_on_column('cls_ind', black, op=operator.ne)
-        
+        cls_gt = cls_gt.with_column_omitted(cls_gt_classes[black])
+
       det_arr = np.zeros((num_points,2))
       cls_arr = np.zeros((num_points,2))
       for i in range(comm_rank,num_points,comm_size):
@@ -308,14 +309,14 @@ class Evaluation:
           plt.fill_between(times,vals-stdevs,vals+stdevs,color='#4084ff',alpha=0.3)
       else:
         vals = table.subset_arr('ap')
-      auc = Evaluation.compute_auc(times,vals,bounds)
+      auc = Evaluation.compute_auc(times,vals,bounds)/float(bounds[1]-bounds[0])
 
       high_bound_val = vals[-1]
       if bounds != None:
         high_bound_val = vals[times.tolist().index(bounds[1])]
       
       if not plot_infos == None and "label" in plot_infos[i]:
-        label = str(plot_infos[i]["label"])
+        label = '%s: %.2f'%(str(plot_infos[i]["label"]), auc)
       else:
         label = "(%.2f, %.2f) %s"%(auc,high_bound_val,table.name)
       
@@ -355,8 +356,9 @@ class Evaluation:
       cls = self.dataset.classes[cls_ind] 
       cls_dets = dets.filter_on_column('cls_ind',cls_ind)
       cls_gt = self.dataset.get_ground_truth_for_class(cls,include_diff=True)
+      cls_gt_classes = list(cls_gt.cols)
[…]

### 2012-03-05 writeups/eccv12/technical.tex
stuff

@@
 Our system has two major parts: (1) selecting an action by predicting its value; (2) updating the belief state with observations resulting from the action.}
-  \label{fig:evaluation}
+  \label{fig:pomdp}
 \end{figure}
@@
 
-For simplicity of exposition, let $\mathcal{A}$ consist of $2K$ actions:
+Let $\mathcal{A}$ consist of $K$ detectors $L^\text{det}_i$.
+We use one-vs-all deformable part-model classifiers on a HOG featurization of the image \cite{Felzenszwalb2010a}, with associated linear classification of the detections.
+
+\comment{Let $\mathcal{A}$ consist of $K$ actions:
 \begin{itemize}
@@
   \item $K$ classifiers $L^\text{gist}_i$: one-vs-all SVMs on the GIST feature \cite{Torralba2004}.
-\end{itemize}
+\end{itemize}}
 
@@
 \section{Selecting actions} \label{sec:value}
-Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
-As our goal is to pick actions, we want to formulate a function $V(b,a)$  that assigns a value to a potential action, given the current state of the decision process.
-We can then define the policy as simply
+\comment{Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).}
+As our goal is to pick actions dynamically, we want to formulate a function $V(b,a)$  that assigns a value to a potential action, given the current state of the decision process.
+We can then define the policy as simply the untaken action with the maximum value:
 \begin{align}
@@
 
-Our system will be evaluated by some properties of the state $b$, and its performance is time-sensitive.
-Accordingly, the value function should balance two terms: a function of the expected next belief state $b'$ after taking an action $a_i$, and the cost of $a_i$.
-\begin{align}
-V(b,a_i) = \mathbb{E}_{b' \sim P(b'|b,a_i)}[R(b')] - \lambda c(a_i|b)
-\end{align}
+For this policy to be \emph{closed-loop}, the observations $o_i$ generated by taking an action $a_i$ need to update $b$ and thus influence the selection of the next action.
+Figure~\ref{fig:pomdp} visualizes such an execution process.
 
-We can be more explicit and split $b$ into its constitutents, such as the current set of observations $\mathbf{o}$ and the posterior distribution $P(\mathbf{C}|\mathbf{o})$.
-Accordingly, we have considerable flexibility in definining the ``reward'' function $R(b)$.
+Before we discuss how to set $V(b,a_i)$ such that our policy obtains best performance under our evaluation, we present our model for updating the belief state with observations.
 
@@
 
-Evaluation of our policy depends on being able to efficiently compute the marginals $o_i$ and the expected information gain $I(\mathbf{C};O_i|\mathbf{o})$.
+The quantities that may be useful to us for selecting which actions to deploy are the probabilities and entropies of the class presence variables $C_k$.
+These allow us to look for the most probable classes given the observations.
+When the policy starts, the model should present the prior distributions $P(C_k)$; as observations are accrued, the model should present the updated conditionals $P(C_k|\mathbf{o})$.
+
 We employ a fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
@@
 \subsection{Policy parametrization and more reward functions}
+
+At each time step, our system is evaluated by properties of the state $b$ (the list of detections and the classification outputs).
+The final evaluation metric is a function of the history of execution $h^0=b^0,b^1,\dots,b^J$, with $J$ being the last step of the process with $t \le T_d$.
+
+Ideally, the value function for a point in the decision process $b^j$ should give the expected value of the final evaluation metric, over all possible histories starting at point $j$:
+\begin{align}
+V(b^j,a_i) = \mathbb{E}_{h^j \sim P(h^j|b,a_i)}[R(h^j)]
+\end{align}
+
+The reward function $R(h^j)$ assigns a real-valued score to a history.
+We have considerable flexibility in defining $R$; it does not necessarily have to be directly tied to the final evaluation.
+
 \todo{here introduce the view of learning parameters given the observed rewards}

### 2012-03-05 writeups/eccv12/technical.tex
mrf section done

@@
 
-\section{Multi-class Recognition Policy}
+\section{Multi-class Recognition Policy} \label{sec:tech}
 \begin{figure}[h!]
@@
 \centering
-\includegraphics[width=0.56\linewidth]{figures/inf_model_mrf.pdf}
+\includegraphics[width=0.56\linewidth]{figures/inf_model_mrf_1.pdf}
 \caption{
-We present a point in the middle of the decision process for 3 classes.
-Some classifiers have already been observed.
+We present a point in the middle of the decision process for 3 classes; one action has already been taken.
+\comment{Some classifiers have already been observed.}
 }
@@
 We employ a fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
-The parameters are trained on fully-observed data.
-Exact inference is of course intractable in a general model of this type, and quite slow for a model of our size.
-Instead, we use Loopy Belief Propagation, which provides no general convergence guarantees but has been shown to work well empirically \todo{cite}.
-The implementations details are given further in \autoref{sec:implementation}.
+The $L_i$ variables are discretized from real-valued responses of a classifier on the detections output by the deformable part-model detector we employ (see Section~\ref{sec:tech}).
+
+The classifier is a linear kernel SVM on the top two max detection scores in the list of detections.
+The responses are discretized per variable based on the distribution of the scores on the training dataset.
+
+The MRF is implemented with an open-source graphical model package \cite{Jaimovich2010}.
+The parameters of the model are trained on fully-observed data.
+Exact inference is generally intractable in this model.
+Instead, we use Loopy Belief Propagation, which does not provide general convergence guarantees but has been shown to work well empirically on similar tasks \todo{cite}.
+
+\todo{what to say about cost of inference? realistically it's 0.5 seconds while the detection action + classification is about 2 seconds.}
 
@@
 
-\subsubsection{Learning the greedy policy}
+\subsubsection{Learning the weights}
 We note that we can represent the one-step greedy policy value function as a scalar product
-
-\subsubsection{Learning the proper policy}
-\note{I'm considering two options here: (1) log-linear representation and policy gradient algorithm; (2) least-squares policy iteration.}
-
-\paragraph{Policy gradient algorithm}
-We redefine our policy as picking the mode of a log-linear parametrized distribution:
-\begin{equation}
-P(a|b;\theta) = \frac{\exp(\theta^T \phi(b,a))}{\sum_{a' \in \mathcal{A}} \exp(\theta^T \phi(b,a')}
-\end{equation}
-
-Basically stochastic gradient ascent on the estimate of the reward accrued by an episode.
-
-This approach has been shown to scale to large problems in \cite{Branavan2009}, although it has been proven to converge only to local maxima and only for MDPs \cite{Sutton2000}.
-
-\note{Does the constraint that no action is taken more than once affect this algorithm?}
-
-\paragraph{Least-squares Policy Iteration}
-An efficient form of temporal-difference learning used in \cite{Kwok2004}.
-Policy remains parameterized as it was.
-
-\section{Implementation Details and Evaluation} \label{sec:implementation}
-We use FastInf \cite{Jaimovich2010} for learning and inference in our MRF model.
-The real-valued classifier responses $o_i$ are discretized into data-dependent bins for efficiency.

### 2012-03-05 synthetic/evaluation.py
plotting

@@ -335,7 +335,7 @@ class Evaluation:
       plt.setp(ltext, fontsize='small')
     plt.xlabel('Time',size=14)
     plt.ylabel('AP',size=14)
-    plt.ylim(0,1)
+    plt.ylim(0,.8)
     plt.grid(True)
     plt.savefig(filename)
 

### 2012-03-05 writeups/eccv12/technical.tex
almost done with technical

@@
 
+One simple heuristic value function that we can try is simply picking the action corresponding to the class presence variable $C_k$ with the highest probability.
+Of course, we'd like to learn the value function from the data, but the above heuristic will be used as a baseline in the evaluation to follow.
+
 Before we discuss how to set $V(b,a_i)$ such that our policy obtains best performance under our evaluation, we present our model for updating the belief state with observations.
@@
 \caption{
-We present a point in the middle of the decision process for 3 classes; one action has already been taken.
+The MRF inference model used in our system.
+We show a point in the middle of the decision process for 3 classes; one action has already been taken.
 \comment{Some classifiers have already been observed.}
@@
 
-\subsection{Policy parametrization and more reward functions}
+\subsection{Learning the Value Function}
+
+Remember that our heuristic value function consisted of picking the action corresponding to the class presence variable with the highest probability $P(C_k)$.
+We can formulate such a policy as a scalar product:
+\begin{align}
+\pi(b) = \argmax_{a_i \in \mathcal{A}} \theta^\top \phi(b,a_i)
+\end{align}
+where $\phi(b,a_i)$ is a feature vector representation of the belief state.
+This approach is known as function approximation in reinforcement learning \cite{Sutton1998}.
+
+Let us take take the feature representation for an action $a_i$ to be $[P(C_k), \, 1]$, where $C_k$ corresponds to the action.
+This corresponds to our heuristic value function, with a bias variable.
+The feature representation $\phi(b,a_i)$ then is a vector of size $F|\mathcal{A}|$, with $F=2$ for this feature, where all values are $0$ except those corresponding to $a_i$.
+
+This representation allows us to use a single vector of weights $\theta$ as a compact representation of our policy.
 
@@
 
-\todo{here introduce the view of learning parameters given the observed rewards}
-
+One feature we want the reward function to have is additivity.
 Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
-The total expected reward of a policy $\pi$ is then defined as the sum of rewards
+The total reward of a policy $\pi$ starting at state $b^j$ is then defined as the sum of rewards
 \begin{equation}
-\mathbb{E}_\pi[\sum_{j=0}^J R(b_j)]
+R(h^j) = \sum_{j'=j}^J R(b_j')
 \end{equation}
 
-The reward function does not necessarily have to be related to the evaluation of the system.
+We formulate two reward definitions: one strives to match the final AP evaluation of the detections, and one is motivated by lowering uncertainty of $P(\mathbf{C})$.
 
-\subsubsection{Slope of performance vs. time}
+\subsubsection{Reward: area under the AP vs. Time curve}
 \begin{figure}[htb]
@@
 
-Remembering that the final evaluation of a policy consists of the area under the performance vs.
-time curve, we formulate per-action rewards such that their addition results in precisely this quantity.
+The final evaluation of a policy consists of the area under the performance vs. time curve.
+Accordingly, we formulate per-action rewards such that their addition results in precisely this quantity.
 Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
 \begin{equation}\label{eq:advanced}
-\Delta AP (t_T-\Delta t)
+R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}_i)t_T^j}
 \end{equation}
-where $t_T$ is the time left until deadline, and $\Delta t$ and $\Delta AP$ are the time taken and AP change produced by the action.
+where $t_T^j$ is the time left until deadline at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.
 
-The equation breaks down into a term to maximize, $\Delta AP t_T$, and a term to minimize, $\Delta AP \Delta t$.
-This agrees with the intuition that to capture the most area under the curve, the slope needs to be maximized at each point.
-Additionally, the equation shows that if $\Delta t$ exceeds $t_T$, the value of taking the action is negative.
+\subsubsection{Reward: decrease in mean entropy}
+We also consider a similar additive reward function based on the mean entropy of the variables $P(C_k)$.
+As with the above policy, the decrease in entropy is considered with regard to the time of the action.
 
-At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
-We therefore define our policy as
-\begin{equation}
-\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
-\end{equation}
+The goal of a policy that maximizes these rewards is to take actions that reduce uncertainty of the most uncertain variables most quickly.
 
-Learning this accurately is the domain of Reinforcement Learning research, and is generally intractable for large-scale POMDPs.
+\subsection{Learning the weights}
 
-First, we seek to maximize the expected next-stage reward, and manually construct a value function such that picking the action with maximal value achieves this.
-Next, we note that the manually constructed value function can be represented as a scalar product of a parameter vector with a featurization of the belief state; we learn the weights by regression to the actual next-stage reward from running many episodes.
-Lastly, we use a reinforcement learning technique to learn the weights such that the expected rewards over the whole episode are maximized.
-
-\subsubsection{Learning the weights}
-We note that we can represent the one-step greedy policy value function as a scalar product
+\todo{Describe the greedy thing and the generalized policy iteration that we do.}

### 2012-03-05 writeups/eccv12/eccv12.tex
almost there

@@
 \mainmatter
-\def\ECCV12SubNumber{***}  % Insert your submission number here
+\def\ECCV12SubNumber{1617}  % Insert your submission number here
 
@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Cras imperdiet, orci sagittis consequat vehicula, metus tellus pulvinar metus, eget cursus tortor quam sit amet ligula.
-Donec vel leo ac sem blandit vulputate.
-Etiam pellentesque, quam non condimentum posuere, dolor augue mollis velit, posuere auctor lectus neque in nulla.
-Aenean in risus sit amet nisl lacinia eleifend et non velit.
-Aliquam mi magna, faucibus sed venenatis vitae, commodo ac nisi.
-Pellentesque tristique dictum mauris, et sollicitudin eros sollicitudin id.
-Cras elit mi, luctus quis vestibulum in, sagittis vel elit.
-Sed ligula dolor, ultrices eget gravida sit amet, dictum vel nisl.
+In a large, multi-class detection system, the problem of timeliness of results is crucial.
+We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
+Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
+Toward this goal, we formulate a dynamic policy to decide which detector to deploy next.
+The policy is guided by an estimate of the contents of the image, and is sensitive to the time deadline and the ``value'' of different classes.
+We evaluate parametrizations of the policy with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC dataset.
 \end{abstract}

### 2012-03-05 writeups/eccv12/technical.tex
almost there

@@
 Accordingly, we formulate per-action rewards such that their addition results in precisely this quantity.
+
 Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
@@
 
+\todo{explain the behavior}
+
 \subsubsection{Reward: decrease in mean entropy}
-We also consider a similar additive reward function based on the mean entropy of the variables $P(C_k)$.
-As with the above policy, the decrease in entropy is considered with regard to the time of the action.
+We also consider a similar additive reward function based on the mean entropy of the variables $P(C_k)$: $\frac{1}{K}\sum_{k=1}^K H(C_k)$, where $H(C_k) = - \sum_{c_k \in {0,1}} P(c_k) \log P(c_k)$.
+We follow the same setup as above, but strive to maximize the area \emph{above} the curve of mean entropy vs. time.
 
@@
 
-\todo{Describe the greedy thing and the generalized policy iteration that we do.}
+The feature representation of the belief state for a given action $a_i$ that corresponds to class $k$ is defined to be $[P(C_k), \, H(C_k), \, 1]$.
+
+Our procedure for learning the weights is standard generalized policy iteration \cite{Sutton1998}.
+We first initialize the weights $\theta$ to the heuristic value function of simply picking the maximum $P(C_k)$: $\theta_i = [1, \,0, \,0]$.
+
+With this policy, we gather $N$ recognition episodes.
+We formulate a matrix $\Phi$ from the featurizations $\phi(b^j,a_i)$ that were seen in the gathered episodes, and a vector $y$ consisting of the individual rewards.
+We then solve the system $\Phi \theta = y$.
+
+\todo{more}

### 2012-03-05 writeups/eccv12/evaluation.tex
draft

@@
 \section{Evaluation} \label{sec:evaluation}
-- show that the greedy policy works better than random and better than fixed-order
 
-- show that the reinforcement learning policy works better than greedy, at least for the non-infogain rewards.
+\todo{Describe random, oracle, and then go through our experimental settings.}
 
-\subsection{Classification}
+\begin{figure}[h!]
+\centering
+\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
+    {figures/manual_plots_det_avg.png}} \\
+\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
+    {figures/manual_plots_cls_whole.png}}
+  \caption{Heuristic value function.}
+  \label{fig:results_manual}
+\end{figure}
 
-\subsection{Detection}
-We also evaluate using the task of detection (see \autoref{sec:problem}).
+\todo{How do the different reward functions affect performance?}
+
+\begin{figure}[h!]
+\centering
+\subfloat[Detection]{\includegraphics[width=0.48\linewidth]
+    {figures/entropy_plots_det_avg.png}} \hfill
+\subfloat[Classification]{\includegraphics[width=0.48\linewidth]
+    {figures/entropy_plots_cls_whole.png}}
+  \caption{Entropy reward function.}
+  \label{fig:results_entropy}
+\end{figure}
+
+\todo{Mention how fixedorder and fastinf learn totally different weights.}

### 2012-03-05 writeups/eccv12/eccv12.tex
draft
people's ocmment

@@
 
-\title{Timely Object Detection}
+\title{Timely Object Recognition}
 
@@
 \begin{abstract}
+\todo{put the word visual somewhere}
 In a large, multi-class detection system, the problem of timeliness of results is crucial.
-We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
+We are motivated by situations where running all detectors would take an unacceptably long time, and that the best answer must be given by some deadline.
 Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
@@
 \bibliographystyle{splncs}
-\bibliography{sergeyk-bibtex}
+\bibliography{sergeyk-bibtex,misc}
 

### 2012-03-05 writeups/eccv12/technical.tex
people's ocmment

@@
 
-Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ and a list of multi-class detection results $\emph{detect}(I)$.
+As presented in Figure~\ref{fig:pomdp}, our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ and a list of multi-class detection results $\emph{detect}(I)$.
 
@@
 A dynamic, or ``closed-loop,'' policy bases action selection on observations received from previous actions, exploiting the signal in inter-object and scene context for a maximally efficient path through the actions.
-This is our goal, and what sets our formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001} or \todo{add another one}.
+This is our goal, and what sets our formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001} or decision trees.
 
@@
 From the setup time to the deadline, we want to obtain the best possible answer if stopped at any given time.
-This corresponds to the general notion of Anytime algorithms, and is motivated by desired flexibility in the system.
+This corresponds to the general notion of \emph{Anytime} algorithms, and is motivated by desired flexibility in the system.
 
@@
   $\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
-  $\mathcal{A}$ & set of actions $a_i \in \{\mathcal{L} \cup \mathcal{F}\}$\\ 
-  $\mathcal{F}$ & set of featurization actions \\
-  $\mathcal{L}$ & set of classification actions\\
-  $o_i$         & a real-valued observation upon executing $a_i \in \mathcal{L}$\\
+  $\mathcal{A}$ & set of actions $a$\\ 
+  \comment{$\mathcal{F}$ & set of featurization actions \\}
+  \comment{$\mathcal{L}$ & set of classification actions\\}
+  $o_i$         & a real-valued observation upon executing $a_i \in \mathcal{A}$\\
   $\mathcal{O}$ & set of executed actions\\
@@
 \begin{equation}\label{eq:advanced}
-R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}_i)t_T^j}
+R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}^j)t_T^j}
 \end{equation}

### 2012-03-05 writeups/eccv12/evaluation.tex

@@
 \centering
-\subfloat[Detection]{\includegraphics[width=0.48\linewidth]
-    {figures/entropy_plots_det_avg.png}} \hfill
-\subfloat[Classification]{\includegraphics[width=0.48\linewidth]
+\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
+    {figures/entropy_plots_det_avg.png}} \\
+\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
     {figures/entropy_plots_cls_whole.png}}

### 2012-03-05 writeups/eccv12/technical.tex
yo

@@
 
-The final evaluation of a policy consists of the area under the performance vs. time curve.
-Accordingly, we formulate per-action rewards such that their addition results in precisely this quantity.
+The final evaluation of a policy consists of the area under the performance vs. time curve (normalized by the total area).
+Accordingly, we formulate per-action rewards such that their addition results in this quantity.
 
@@
 \end{equation}
-where $t_T^j$ is the time left until deadline at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.
+where $t_T^j$ and $\text{ap}^j$ are the time left until deadline and the AP at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.
 
-\todo{explain the behavior}
+The reward is $1$ if the policy takes an action that obtains the maximum possible area under the curve at that point, and $0$ if no area under the curve is captured.
 
@@
 
-The feature representation of the belief state for a given action $a_i$ that corresponds to class $k$ is defined to be $[P(C_k), \, H(C_k), \, 1]$.
+The feature representation of the belief state for a given action $a_i$ that corresponds to class $k$ is defined to be
+\begin{align}
+[P(C_k), \, H(C_k), \, 1]
+\end{align}
 
@@
 
-With this policy, we gather $N$ recognition episodes.
-We formulate a matrix $\Phi$ from the featurizations $\phi(b^j,a_i)$ that were seen in the gathered episodes, and a vector $y$ consisting of the individual rewards.
+With this policy, we run $N$ recognition episodes.
+From the state-action samples gathered in running the episodes, we formulate a matrix $\Phi$ from the featurizations $\phi(b^j,a_i)$, and a vector $y$ consisting of the individual rewards $R(b^j,a_i)$.
 We then solve the system $\Phi \theta = y$.

### 2012-03-05 writeups/eccv12/introduction.tex

@@
 In the evaluation ground truth, each object is most commonly assumed to belong to one of a fixed set of classes; its location is approximated by placing a bounding box around pixels belonging to it.
-Large datasets of such human annotations are used for evaluation of detection algorithms~\cite{pascal-voc-2010}.
+Large datasets of such human annotations are used for evaluation of detection algorithms~\cite{pascal-voc-2010,imagenet_cvpr09}.
 
@@
 
+\begin{figure}[ht!]
+\center{\includegraphics[width=0.56\linewidth]
+    {figures/evaluation.pdf}}
+  \caption{We aim for \emph{Anytime} performance within the bounds of the curve.
+That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.
+\todo{CAN WE PUT PICTURES OF DETECTORS IN HERE?}}
+  \label{fig:evaluation}
+\end{figure}
+
 It is of course important to refrain from locking object recognition research into a single detector architecture with a focus only on increasing efficiency.
@@
 
-\begin{figure}[ht!]
-\center{\includegraphics[width=0.56\linewidth]
-    {figures/evaluation.pdf}}
-  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.}
-  \label{fig:evaluation}
-\end{figure}
-
 In all these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.
@@
 
-A hypothetical recognition system for an advertising deployment presents a great case study.
+A hypothetical recognition system for a vision-based advertising deployment presents a case study.
 The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
@@
 Our goal is a dynamic policy for selecting classifiers or detectors to achieve the highest recognition performance under this evaluation.
-Without further ado, let us formalize the problem.

### 2012-03-05 writeups/eccv12/technical.tex

@@
 
-As presented in Figure~\ref{fig:pomdp}, our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ and a list of multi-class detection results $\emph{detect}(I)$.
+As presented in Figure~\ref{fig:pomdp}, our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and then outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ and a list of multi-class detection results $\emph{detect}(I)$.
 
@@
 \begin{align}
-\pi(b) = \argmax_{a_i \in \mathcal{A}} \theta^\top \phi(b,a_i)
+\pi(b) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a_i)
 \end{align}
@@
 \begin{equation}
-R(h^j) = \sum_{j'=j}^J R(b_j')
+R(h^j) = \sum_{j'=j}^J R(b_j',a^{j'})
 \end{equation}
@@
 \begin{align}
-[P(C_k), \, H(C_k), \, 1]
+\phi_k(b) = [P(C_k), \, H(C_k), \, 1]
 \end{align}
@@
 From the state-action samples gathered in running the episodes, we formulate a matrix $\Phi$ from the featurizations $\phi(b^j,a_i)$, and a vector $y$ consisting of the individual rewards $R(b^j,a_i)$.
-We then solve the system $\Phi \theta = y$.
 
-\todo{more}
+The rewards are computed as the sum of discounted rewards to the end of the episode:
+\begin{align}
+R(b^j,a_i) = \sum_{i=0}^{J-j} \lambda^i R(b_{j+i},a^{j+i})
+\end{align}
+Note that with $\lambda=0$, the reward is determined entirely by the actual action taken; with $\lambda=1$, the reward is the sum of all rewards until the end of the episode.
+
+We then solve the system $\Phi \theta = y$ for $\theta$ with Lasso regression.
+With the updated weights $\theta$, we run $N$ more episodes and repeat the procedure until convergence.
+
+The parameters of this training procedure are the $\alpha$ weight on the regularization term in the regression and the $\lambda$ discount weight.
+We cross-validate for both values.

### 2012-03-05 writeups/eccv12/evaluation.tex

@@
-\section{Evaluation} \label{sec:evaluation}
-
-\todo{Describe random, oracle, and then go through our experimental settings.}
-
 \begin{figure}[h!]
 \centering
-\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
+\subfloat[Detection]{\includegraphics[width=0.68\linewidth]
     {figures/manual_plots_det_avg.png}} \\
-\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
+\subfloat[Classification]{\includegraphics[width=0.68\linewidth]
     {figures/manual_plots_cls_whole.png}}
@@
 \end{figure}
+
+\section{Evaluation} \label{sec:evaluation}
+
+To summarize, we evaluate our system in the multi-class, multi-label detection and classification regime.
+We evaluate on the PASCAL VOC 2007 dataset: training on the training and validation data and testing on the test set.
+We run our policies on all images in the test set, cutting off execution at $T_d$.
+
+To evaluate performance at a given time, we gather all detections and the classification answers found to this point in all the recognition episodes.
+As described before, we evaluate detection performance by averaging per-image performance in the multi-class regime.
+We evaluate classification performance by pooling the ground truth across the dataset, in standard procedure.
+
+We establish the baseline performance of our system by selecting actions randomly at each step.
+The time setting for our evaluation is $T_s=0$, $T_d=20$ (in seconds).
+As shown in Figure~\ref{fig:results_manual}, the random policy results in a roughly linear gain of performance vs. time.
+
+To establish an upper bound on performance, we also plot the Oracle curve, obtained by re-ordering the actions with the hindsight of the results they produced.
+Note that the curves turn downward in this setting: this is due to the different performance levels of the detectors: as the weaker detectors are inevitably run, they introduce more false positives and false negatives than true positives.
 

### 2012-03-05 writeups/eccv12/eccv12.tex
final

@@
 \begin{abstract}
-\todo{put the word visual somewhere}
-In a large, multi-class detection system, the problem of timeliness of results is crucial.
+In a large visual multi-class detection system, the problem of timeliness of results is crucial.
 We are motivated by situations where running all detectors would take an unacceptably long time, and that the best answer must be given by some deadline.
 Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
-Toward this goal, we formulate a dynamic policy to decide which detector to deploy next.
-The policy is guided by an estimate of the contents of the image, and is sensitive to the time deadline and the ``value'' of different classes.
+Toward this goal, we formulate a dynamic policy, guided by inference of the contents of the image, to decide which detector to deploy next.
 We evaluate parametrizations of the policy with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC dataset.

### 2012-03-05 writeups/eccv12/evaluation.tex
final

@@
 \centering
-\subfloat[Detection]{\includegraphics[width=0.68\linewidth]
+\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
     {figures/manual_plots_det_avg.png}} \\
-\subfloat[Classification]{\includegraphics[width=0.68\linewidth]
+\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
     {figures/manual_plots_cls_whole.png}}
@@
 
-\todo{How do the different reward functions affect performance?}
+Figure~\ref{fig:results_manual} also shows the performance of our policy with the heuristic value function and two inference models: the MRF model and a simple fixed-order model that follows the priors.
 
@@
 
-\todo{Mention how fixedorder and fastinf learn totally different weights.}
+Figure~\ref{fig:results_entropy} shows the performance of the polices with learned weights.
+A notable difference between the MRF inference model and the fixed-order model was in the weights learned: while the fixed-order model learned weights onto the bias feature only, the MRF inference model learned weights onto a mix of the entropy and probability features.

### 2012-03-05 writeups/eccv12/technical.tex
final

@@
 
-\todo{Is the above sufficiently clear?}
-
 Our notation is summarized in \autoref{tab:notation}.
@@
 Exact inference is generally intractable in this model.
-Instead, we use Loopy Belief Propagation, which does not provide general convergence guarantees but has been shown to work well empirically on similar tasks \todo{cite}.
-
-\todo{what to say about cost of inference? realistically it's 0.5 seconds while the detection action + classification is about 2 seconds.}
+Instead, we use Loopy Belief Propagation, which does not provide general convergence guarantees but has been shown to work well empirically on similar tasks \cite{Desai2009}.
 

### 2012-03-06 writeups/eccv12/evaluation.tex
post-final i think

@@
 Figure~\ref{fig:results_manual} also shows the performance of our policy with the heuristic value function and two inference models: the MRF model and a simple fixed-order model that follows the priors.
+We can see that due to the dataset bias, the fixed-order policy performs well at first (the person class is disproportionately likely to be in the image), but is overtaken by the proper inference model as execution goes on.
 
@@
 
-Figure~\ref{fig:results_entropy} shows the performance of the polices with learned weights.
+Figure~\ref{fig:results_entropy} shows the performance of the polices with learned weights, comparing our two reward functions.
+We found the entropy-based reward to work better than the AP-based reward.
+
 A notable difference between the MRF inference model and the fixed-order model was in the weights learned: while the fixed-order model learned weights onto the bias feature only, the MRF inference model learned weights onto a mix of the entropy and probability features.

### 2012-04-15 synthetic/common_imports.py
in the middle of simplifying a bunch of code

@@ -15,6 +15,7 @@ import json
 import itertools
 import cPickle
 import pickle
+from pandas import *
 
 import numpy as np
 import scipy.stats as st

### 2012-04-15 synthetic/config.py

@@ -1,12 +1,13 @@
-"Set up paths to files and other one-time or platform-dependent settings."
-
 from os.path import join,exists
 import getpass
+from IPython import embed
 
 from synthetic.util import makedirs
 
+"Set up paths to files and other one-time or platform-dependent settings."
+
 ##################
-# VARIABLES
+# CONSTANTS 
 ##################
 VOCyear = '2007'
 kernels = ['linear', 'rbf']
@@ -24,10 +25,11 @@ dpm_may25_dirname = '/tscratch/tmp/sergeyk/object_detection/dets_may25_DP/'
 # - temp_data_dir is for large files and can be on temp filespace
 ##################
 # Determine environment
-if exists('/home/tobibaum'):
-  env = 'tobi_home'
-elif exists('/Users/sergeyk'):
+if exists('/Users/sergeyk'):
   env = 'sergeyk_home'
+elif exists('/home/tobibaum'):
+  # NOTE (sergeyk): there's a strange bug where this *does* exist on my laptop
+  env = 'tobi_home'
 elif exists('/u/vis/'):
   user = getpass.getuser()
   if user=='tobibaum':
@@ -37,7 +39,7 @@ elif exists('/u/vis/'):
 else:
   raise RuntimeError("Can't set paths correctly")
 
-# repo_dir, data_dir, temp_data_dir
+# Set [repo_dir, data_dir, temp_data_dir]
 # temp_data_dir is not propagated between machines!
 paths = {
   'tobi_home':    ['/home/tobibaum/Documents/Vision/timely/',
@@ -46,11 +48,11 @@ paths = {
   'tobi_icsi':    ['/u/tobibaum/timely/',
                    '/u/vis/x1/tobibaum/data/',
                    '/tscratch/tmp/tobibaum/timely/'],
-  'sergeyk_home': ['/Users/sergeyk/research/timely/',
-                   '/Users/sergeyk/research/timely/data/',
-                   '/Users/sergeyk/research/timely/data/temp/'],
-  'sergeyk_icsi': ['/u/sergeyk/research/timely/',
-                   '/u/sergeyk/research/timely/data',
+  'sergeyk_home': ['/Users/sergeyk/work/timely/',
+                   '/Users/sergeyk/work/timely/data/',
+                   '/Users/sergeyk/work/timely/data/temp/'],
+  'sergeyk_icsi': ['/u/sergeyk/work/timely/',
[…]

### 2012-04-15 synthetic/dataset.py

@@ -7,58 +7,12 @@ import synthetic.config as config
 
 from synthetic.image import *
 from synthetic.sliding_windows import SlidingWindows
-from synthetic import config
 
 class Dataset:
   """
   Methods for constructing, accessing, and evaluating detection performance
   on a dataset.
   """
-
-  # Convenience methods
-  def num_classes(self):
-    return len(self.classes)
-  
-  def num_images(self):
-    return len(self.images)
-
-  def get_ind(self,cls):
-    """
-    Return the index of the given cls. If cls is 'all', returns an extra
-    index.
-    """
-    if cls=='all':
-      return len(self.classes)
-    assert(cls in self.classes)
-    return self.classes.index(cls)
-
-  def get_img_ind(self,image):
-    """Return the index of the given image."""
-    assert(image in self.images)
-    return self.images.index(image)
-
-  def get_name(self):
-    return "%s_%s"%(self.name,len(self.images))
-
-  def see_image(self,img_ind):
-    """Convenience method to display the image at given ind in self.images."""
-    # TODO: use scikits-image to load as numpy matrix (matplotlib.imread loads
-    # inverted for some reason)
-    im = PILImage.open(self.get_image_filename(img_ind))
-    im.show()
-
-  def get_image_by_filename(self, filename):
-    for img in self.images:
-      if img.name == filename:
-        return img
-    return None
-
-  def get_image_filename(self,img_ind):
-    return opjoin(config.VOC_dir, 'JPEGImages', self.images[img_ind].name)
-
-  def __repr__(self):
-    return self.get_name()
-  
   def __init__(self, name=None, force=False):
     self.classes = []
     self.images = []
@@ -66,18 +20,31 @@ class Dataset:
     self.current_fold = -1
     if re.search('pascal', name):
       self.load_from_pascal(name,force)
-    elif name == 'data1':
-      self.load_from_json(config.data1)
+    elif name == 'test_data1':
+      self.load_from_json(config.test_data1)
     else:
       print("WARNING: Unknown dataset initialization string, not loading images.")
+
+  def get_name(self):
+    return "%s_%s"%(self.name,self.df.shape[0])
+
+  ###
+  # Loaders
+  ###
+  def load_from_json(self, filename):
+    "Load all parameters of the dataset from a JSON file."
+    with open(filename) as f:
+      config = json.load(f)
+    self.classes = config['classes']
[…]

### 2012-04-15 synthetic/image.py

@@ -1,64 +1,58 @@
-from xml.dom.minidom import parseString
-
+import xml.dom.minidom as minidom
 from common_imports import *
-
 from synthetic.bounding_box import BoundingBox
 
 class Image:
-  """An image has a size and a list of objects."""
+  "An image has a size and a list of objects."
   
-  def __init__(self,name=None,size=None,objects=None,dataset=None):
+  def __init__(self,name=None,size=None,classes=None):
     self.name = name          # just a string identifier 
     self.size = size          # (width,height)
-    if not objects:
-      self.objects = []
-    self.dataset = dataset
+    self.classes = classes
+    self.objects = []
 
   def get_whole_image_bbox(self):
-    """Returns a BoundingBox with (0,0,width,height) of the image."""
+    "Return a BoundingBox with (0,0,width,height) of the image."
     return BoundingBox((0,0,self.size[0],self.size[1]))
       
   @classmethod
-  def from_json(cls, dataset, data):
-    """Instantiate an Image from a JSON representation."""
-    img = Image(size=data['size'])
-    img.dataset = dataset
+  def load_from_json(cls, classes, data):
+    "Return an Image instantiated from a JSON representation."
+    img = Image(size=data['size'],classes=classes)
     for obj in data['objects']:
       bbox = BoundingBox(obj['bbox'])
       cls = obj['class']
       cls_ind = dataset.get_ind(cls)
-      diff = 0 # just dummy variable, as this data is not in JSON
-      trun = 0 # same
+      trun = diff = 0 # just dummy variable, as this data is not in JSON
       img.objects.append(Object(bbox, cls_ind, diff, trun))
     return img
   
   @classmethod
-  def get_data_from_tag(cls, node, tag):
-    """Read the entries for a specific tag"""
-    if tag is "bndbox":
-      x1 = int(node.getElementsByTagName(tag)[0].childNodes[1].childNodes[0].data)
-      y1 = int(node.getElementsByTagName(tag)[0].childNodes[3].childNodes[0].data)
-      x2 = int(node.getElementsByTagName(tag)[0].childNodes[5].childNodes[0].data)
-      y2 = int(node.getElementsByTagName(tag)[0].childNodes[7].childNodes[0].data)
-      return (x1, y1, x2, y2)
-    else:
-      return node.getElementsByTagName(tag)[0].childNodes[0].data
[…]

### 2012-04-15 synthetic/test/dataset.py

@@ -1,11 +1,10 @@
-import numpy as np
+from synthetic.common_imports import *
 
 from synthetic.dataset import Dataset
 
-class TestDataset:
+class TestDatasetJson:
   def setup(self):
-    self.d = Dataset('data1',force=True)
-    self.d2 = Dataset('test_pascal_train',force=True)
+    self.d = Dataset('test_data1',force=True)
 
   def test_load_from_json(self):
     assert(self.d.num_images() == 4)
@@ -13,17 +12,16 @@ class TestDataset:
 
   def test_ground_truth_json(self):
     gt = self.d.get_ground_truth(include_trun=False)
-    arr = np.array(
+    df = DataFrame(
       [[ 0.,  0.,  0.,  0.,  0.,  0.],
        [ 1.,  1.,  1.,  1.,  1.,  0.],
        [ 2.,  2.,  2.,  2.,  2.,  0.],
        [ 1.,  1.,  1.,  1.,  0.,  1.],
        [ 0.,  0.,  0.,  0.,  1.,  2.],
        [ 0.,  0.,  0.,  0.,  2.,  3.],
-       [ 1.,  1.,  1.,  1.,  2.,  3.]])
-    cols = ['x','y','w','h','cls_ind','img_ind']
-    assert(np.all(gt.arr == arr))
-    assert(gt.cols == cols)
+       [ 1.,  1.,  1.,  1.,  2.,  3.]],
+       columns=['x','y','w','h','cls_ind','img_ind'])
+    assert(gt == df)
 
   def test_get_cls_counts_json(self):
     arr = np.array(
@@ -35,15 +33,13 @@ class TestDataset:
     assert(np.all(self.d.get_cls_counts() == arr))
 
   def test_get_cls_ground_truth_json(self):
-    arr = np.array(
+    df = DataFrame(
       [ [ True, True, True],
         [ True, False, False],
         [ False, True, False],
-        [ False, False, True]])
-    cols = ["A","B","C"]
+        [ False, False, True] ], columns = ["A","B","C"])
     print(self.d.get_cls_ground_truth())
-    assert(np.all(self.d.get_cls_ground_truth().arr == arr))
-    assert(np.all(self.d.get_cls_ground_truth().cols == cols))
+    assert(self.d.get_cls_ground_truth()==df)
 
   def test_ground_truth_for_class_json(self):
     gt = self.d.get_ground_truth_for_class("A",include_diff=True,include_trun=True)
[…]

### 2012-05-02 synthetic/common_imports.py
plotting sweet correlation figure for dataset

@@ -1,6 +1,4 @@
-import os
-import sys
-import time
+import os,sys,time
 import copy
 import types
 import math
@@ -18,12 +16,12 @@ from IPython import embed
 from os.path import join as opjoin
 from os.path import exists as opexists
 from pprint import pprint
+from sklearn.cross_validation import KFold
+from pandas import Series,DataFrame
 
 import numpy as np
 import scipy.stats as st
-from sklearn.cross_validation import KFold
 import matplotlib.pyplot as plt
-
-from pandas import *
-
 import synthetic.util as ut
+
+from synthetic.common_mpi import *

### 2012-05-02 synthetic/dataset.py

@@ -1,8 +1,6 @@
-from synthetic.common_mpi import *
 from synthetic.common_imports import *
 import synthetic.config as config
 
-from PIL import Image as PILImage
 from synthetic.image import Image
 from synthetic.sliding_windows import SlidingWindows
 
@@ -22,11 +20,12 @@ from synthetic.sliding_windows import SlidingWindows
     self.cls_ground_truth = np.array(choices[choice])
 """
 
-class Dataset:
+class Dataset(object):
   """
-  Methods for constructing, accessing, and evaluating detection performance
-  on a dataset.
+  Representation of a dataset, with methods to construct from different sources
+  of data, get ground truth, and construct sets of train/test data.
   """
+
   def __init__(self, name=None, force=False):
     self.classes = []
     self.images = []
@@ -41,7 +40,7 @@ class Dataset:
       self.classes = ['A','B','C']
       num_images = 1000
       for i in range(0,num_images):
-        self.images.append(Image(name="whatever",size=(100,100),classes=self.classes)
+        self.images.append(Image(name="whatever",size=(100,100),classes=self.classes))
     else:
       print("WARNING: Unknown dataset initialization string, not loading images.")
     self.image_names = [image.name for image in self.images]
@@ -94,7 +93,7 @@ class Dataset:
         tt.tic('2')
       if len(img)>0:
         xml_filename = opjoin(config.VOC_dir,'Annotations',img+'.xml')
-        self.images.append(Image.load_from_xml_filename(self.classes,xml_filename))
+        self.images.append(Image.load_from_pascal_xml_filename(self.classes,xml_filename))
     filename = config.get_cached_dataset_filename(name)
     print("  ...saving to cache file")
     with open(filename, 'w') as f:
@@ -177,46 +176,63 @@ class Dataset:
     return all_windows[:num,:]
 
   ###
-  # Assemble ground truth
+  # Ground truth
   ###
+  def get_cls_counts(self, with_diff=True, with_trun=True):
+    """
+    Return DataFrame of class presence counts.
+      Index: image.name
+      Columns: self.classes
+    """
+    data = {}
+    for image in self.images:
+      data[image.name] = image.get_cls_counts()
+    return DataFrame(data).T
+
   def get_cls_ground_truth(self,with_diff=True,with_trun=True):
     "Return DataFrame of classification (0/1) ground truth."
     return self.get_cls_counts(with_diff,with_trun)>0
 
[…]

### 2012-05-02 synthetic/image.py

@@ -1,11 +1,13 @@
 from synthetic.common_imports import *
 import synthetic.config as config
 
+from skimage.io import imread,imsave,imshow
 import xml.dom.minidom as minidom
+
 from synthetic.bounding_box import BoundingBox
 from synthetic.sliding_windows import SlidingWindows
 
-class Image:
+class Image(object):
   "An image has a name, size and a DataFrame of objects."
 
   columns = BoundingBox.columns + ['cls_ind', 'diff', 'trun']
@@ -17,29 +19,32 @@ class Image:
     self.name = name
     self.filename = None
     self.objects_df = None
-    # the above DataFrame is constructed by loader
+    # the above DataFrame is constructed by the loader class
 
   def __repr__(self):
     return "Image (%(name)s)\n  W x H: %(width)d x %(height)d\n  Objects:\n %(objects_df)s" % self.__dict__
 
   def display_image(self):
-    "Convenience method to display the Image."
-    # TODO: use scikits-image to load as numpy matrix (matplotlib.imread loads
-    # inverted for some reason)
+    "Display the image using skimage."
+    imshow(self.load_image())
+
+  def load_image(self):
+    "Return the image loaded using skimage."
     if not self.filename:
-      print("Image: Cannot display, no associated filename")
-      return
-    im = PILImage.open(self.filename)
-    im.show()
+      print("Image: Cannot load, no associated filename")
+      return None
+    return imread(self.filename)
+
+  def compute_sift(self):
+    "Return SIFT features on the image."
+    # TODO
+    None
 
   def get_objects_df(self,with_diff=False,with_trun=True):
     "Return objects_df filtered with the parameters."
     df = self.objects_df
-    ind = []
-    if not with_diff:
-      df = df[df['diff']==0]
-    if not with_trun:
-      df = df[df['trun']==0]
+    df = df if with_diff else df[df['diff']==0] 
+    df = df if with_trun else df[df['trun']==0]
     return df
 
   def get_det_gt(self, with_diff=False, with_trun=True, cls_name=None):
@@ -117,7 +122,7 @@ class Image:
   def load_from_pascal_xml_filename(cls, classes, filename):
     "Load image info from a file in the PASCAL VOC XML format."
 
-    def get_data_from_tag(cls, node, tag):
+    def get_data_from_tag(node, tag):
       if tag is "bndbox":
[…]

### 2012-05-02 writeups/nips12/nips2012.tex
nips writeup started and looks good

--- 2012-03-05 writeups/eccv12/eccv12.tex
@@
-\documentclass[runningheads]{llncs}
+\documentclass{article} % For LaTeX2e
+\usepackage{nips12submit_e,times}
 \usepackage{graphicx}
 \usepackage{amsmath,amssymb} % define this before the line numbering.
-\usepackage{ruler}
 \usepackage{color}
 \usepackage{subfig}
-\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
+\usepackage{natbib}
 \usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
-\begin{document}
-% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
-% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
-% \linenumbers
-\pagestyle{headings}
 
-% Definitions
 \newcommand{\argmax}{\operatornamewithlimits{argmax}}
@@
 
-\mainmatter
-\def\ECCV12SubNumber{1617}  % Insert your submission number here
-
 \title{Timely Object Recognition}
 
-\titlerunning{ECCV-12 submission ID \ECCV12SubNumber}
+\author{
+Sergey Karayev \And
+Tobias Baumgartner \And
+Mario Fritz \And
+Trevor Darrell
+}
 
-\authorrunning{ECCV-12 submission ID \ECCV12SubNumber}
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
 
-\author{Anonymous ECCV submission}
-\institute{Paper ID \ECCV12SubNumber}
+%\nipsfinalcopy % Uncomment for camera-ready version
 
+\begin{document}
 \maketitle
@@
 
-\input{introduction.tex} % includes Evaluation section
-\input{technical.tex}
-\input{evaluation.tex}
-\input{related.tex}
-\input{future_work.tex}
+\input{../eccv12/introduction.tex} % includes Evaluation section
+\input{../eccv12/technical.tex}
+\input{../eccv12/evaluation.tex}
+\input{../eccv12/related.tex}
 
-\bibliographystyle{splncs}
-\bibliography{sergeyk-bibtex,misc}
+\subsubsection*{Acknowledgments}
+
+Use unnumbered third level headings for the acknowledgments. All
+acknowledgments go at the end of the paper. Do not include 
+acknowledgments in the anonymized submission, only in the 
+final paper.
+
+\renewcommand\bibsection{\subsubsection*{\refname}}
+\bibliographystyle{unsrt}
+\small{
+  \bibliography{../sergeyk_Timely}
+}
 

### 2012-05-02 synthetic/config.py
plotting co-occurence to results/dataset_stats

@@ -88,6 +88,9 @@ eval_template_filename = join(eval_support_dir, 'dashboard_template.html')
 res_dir = makedirs(join(data_dir, 'results'))
 temp_res_dir = makedirs(join(data_dir, 'temp_results'))
 
+def get_dataset_stats_dir(dataset):
+  return makedirs(join(res_dir,'dataset_stats',dataset.name))
+
 # ./results/det_configs/{dataset}
 def get_dets_configs_dir(dataset):
   return makedirs(join(res_dir,'det_configs',dataset.name))

### 2012-05-02 synthetic/dataset.py

@@ -213,7 +213,7 @@ class Dataset(object):
   ###
   # Statistics
   ###
-  def plot_cooccurence(self,with_diff=True,with_trun=False,second_order=False):
+  def plot_cooccurence(self,with_diff=True,with_trun=True,second_order=False):
     """
     Plot the correlation matrix of class occurence.
       second_order: plot co-occurence of two-class pairs with third class.
@@ -223,7 +223,10 @@ class Dataset(object):
     df = self.get_cls_ground_truth(with_diff,with_trun)
     f = drawmatrix_channels(df.corr().as_matrix(),df.columns,
       size=(10,10),color_anchor=(-1,1))
-    f.savefig(config.get_cooccurence_plot_filename(with_diff,with_trun,second_order)
+    dirname = config.get_dataset_stats_dir(self)
+    filename = opjoin(dirname,'cooccur_diff_%s_trun_%s_second_order_%s.png'%(
+      with_diff,with_trun,second_order))
+    f.savefig(filename)
 
   ###
   # K-Folds

### 2012-05-28 synthetic/evaluation.py
mean det ap now in final vs. t evaluation, and some minor changes

@@ -58,7 +58,6 @@ class Evaluation:
     We evaluate on the whole dataset instead of averaging per-image,
     and so get rid of error bars.
     Return two tables: one for detection and one for classification evals.
-    This version average per-image results.
     """
     bounds = self.dp.bounds if self.dp and self.dp.bounds else None
 
@@ -108,7 +107,8 @@ class Evaluation:
           else:
             dets_to_this_point = img_dets.filter_on_column('time',point,operator.le)          
             num_dets += dets_to_this_point.shape[0]
-            det_ap,_,_ = self.compute_det_pr(dets_to_this_point, gt_for_image)
+            #det_ap,_,_ = self.compute_det_pr(dets_to_this_point, gt_for_image)
+            det_ap = self.compute_det_map(dets_to_this_point, gt_for_image)
           det_aps.append(det_ap)
         det_arr[i,:] = [point,np.mean(det_aps),np.std(det_aps)]
         print("Calculating AP (%.3f) of the %d detections up to %.3fs took %.3fs"%(

### 2012-05-28 writeups/nips12/technical.tex
now mentioning L1 regularization

--- 2012-03-05 writeups/eccv12/technical.tex
@@
 \center{\includegraphics[width=0.66\linewidth]
-    {figures/pomdp.pdf}}
+    {../figures/pomdp.png}}
   \caption{Summary of our approach to the problem.
@@
 \centering
-\includegraphics[width=0.56\linewidth]{figures/inf_model_mrf_1.pdf}
+\includegraphics[width=0.56\linewidth]{../figures/inf_model_mrf_1.pdf}
 \caption{
@@
 
-We employ a fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
+We employ a pairwise fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
+All parameters of the model are trained on fully-observed data.
+Exact inference is generally intractable in this model.
+Instead, we use Loopy Belief Propagation, which does not provide general convergence guarantees but has been shown to work well empirically on similar tasks \cite{Desai2009}.
+
 The $L_i$ variables are discretized from real-valued responses of a classifier on the detections output by the deformable part-model detector we employ (see Section~\ref{sec:tech}).
-
-The classifier is a linear kernel SVM on the top two max detection scores in the list of detections.
+The classifier is a linear SVM on the top two max detection scores in the list of detections.
 The responses are discretized per variable based on the distribution of the scores on the training dataset.
 
-The MRF is implemented with an open-source graphical model package \cite{Jaimovich2010}.
-The parameters of the model are trained on fully-observed data.
-Exact inference is generally intractable in this model.
-Instead, we use Loopy Belief Propagation, which does not provide general convergence guarantees but has been shown to work well empirically on similar tasks \cite{Desai2009}.
+The graphical model structure is set as fully-connected, but as shown in \autoref{fig:dataset_stats}, some classes are overwhelmingly unlikely to co-occurr.
+Accordingly, the graph edge weights are learned with L1 regularization, which obtains the desired sparse structure \cite{Lee2006}.
+ is implemented with an open-source graphical model package \cite{Jaimovich2010}.
+
+ \todo{section on a ``fast approximation'' to this based on the n-gram counts we had before?}
 
@@
   \centering
-  \includegraphics[width=0.56\linewidth]{figures/apvst_expl.pdf}
+  \includegraphics[width=0.56\linewidth]{../figures/apvst_expl.pdf}
   \caption{A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action.

### 2012-05-28 writeups/nips12/evaluation.tex

--- 2012-03-06 writeups/eccv12/evaluation.tex
@@
+\section{Evaluation} \label{sec:evaluation}
+
 \begin{figure}[h!]
 \centering
-\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
-    {figures/manual_plots_det_avg.png}} \\
-\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
-    {figures/manual_plots_cls_whole.png}}
-  \caption{Heuristic value function.}
-  \label{fig:results_manual}
+\subfloat[Occurence of a class with another]{\includegraphics[]
+    {../figures/full_pascal_trainval_stats/cooccur_trim.png}} \hfill
+\subfloat[Occurence of a class with two others]{\includegraphics[]
+    {../figures/full_pascal_trainval_stats/cooccur_second_order_trim.png}}
+  \caption{
+  Co-occurrence statistics on the training portion of the PASCAL VOC 2007 dataset.
+  In the first plot, a (row,column) cell shows the probability that an image that contains an object of the row class also contains an object of the column class.
+  Accordingly, in the second plot, the probability that an image containing objects of the two classes listed in the row also contains an object of the column class.
+  }
+  \label{fig:dataset_stats}
 \end{figure}
 
-\section{Evaluation} \label{sec:evaluation}
+To summarize \autoref{sec:}, we evaluate our system in the multi-class, multi-label detection regime.
+We evaluate on a popular detection challenge task: the PASCAL VOC dataset \cite{pascal-voc-2010}.
+As shown in \autoref{fig:dataset_stats}, the dataset exhibits a rather modest amount of class co-occurrence, which puts our model in a disadvantaged setting.
+$60\%$ of the images in the training set have only one class; $30\%$ have two classes, $7\%$ have three classes, and almost none have more.
 
-To summarize, we evaluate our system in the multi-class, multi-label detection and classification regime.
-We evaluate on the PASCAL VOC 2007 dataset: training on the training and validation data and testing on the test set.
+Using the 2007 version of the dataset, we train on the training and validation data and test on the test set.
 We run our policies on all images in the test set, cutting off execution at $T_d$.
@@
 
+\begin{figure}[h!]
+\centering
+\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
+    {../figures/manual_plots_det_avg.png}} \\
+\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
+    {../figures/manual_plots_cls_whole.png}}
+  \caption{Heuristic value function.}
+  \label{fig:results_manual}
+\end{figure}
+
 Figure~\ref{fig:results_manual} also shows the performance of our policy with the heuristic value function and two inference models: the MRF model and a simple fixed-order model that follows the priors.
@@
 \subfloat[Detection]{\includegraphics[width=0.78\linewidth]
-    {figures/entropy_plots_det_avg.png}} \\
+    {../figures/entropy_plots_det_avg.png}} \\
 \subfloat[Classification]{\includegraphics[width=0.78\linewidth]
-    {figures/entropy_plots_cls_whole.png}}
+    {../figures/entropy_plots_cls_whole.png}}
   \caption{Entropy reward function.}

### 2012-05-28 synthetic/test/ext_detector_regions.py
ext_regions test doesnt pass due to some classifier thing but merging anyway

@@ -1,4 +1,4 @@
-from common_imports import *
+from synthetic.common_imports import *
 import synthetic.config as config
 
 from synthetic.ext_detector_regions import *

### 2012-05-29 writeups/nips12/related.tex
started working on related work

\section{Related Work}

under construction

The literature on object detection is vast.
Here we briefly summarize detection work that sufficiently contextualizes our contribution in the areas of object classification and detection in context, saliency, multi-class prediction, steering of computation (such as in cascades, any time algorithm) and active classification.

\paragraph{Contect}
Context of course has a long history in vision.
One source of context is the scene or non-detector cues; for the PASCAL VOC, these are quantitatively considered in~\cite{Divvala2009}. 
Another source is inter-object context, used for detection in a random field setting in~\cite{Torralba2004}. These  statistics interlink individual object detection tasks as well as image classification. Exploiting this information has shown to improve classification as well as detection tasks (e.g. \cite{Torralba, visual phrases}).
A critical summary of the main approaches to using context for object detection is given in \cite{Galleguillos2010}.

\paragraph{Multi-Class Detection}
Inherently multi-class detection has its own line of work, focusing largely on making detection time sublinear in the number of classes through sharing features~\cite{Torralba2007,Fan2005,Razavi2011}.
A recent post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression~\cite{Desai2009}. Most critically, theses methods don't use intermediate results in order to maximize the joint detection performance.

\paragraph{Attention and Steering of Computation}
An early success in efficient object detection used simple Haar features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime~\cite{Viola2001}.
Although the simple features and classifiers of this method have been surpassed by more complex detectors, the idea of cascading classifier evaluations is still often used.

The best recent performance has come from detectors that use gradient-based features to represent objects as either a collection of local patches or as object-sized windows \cite{Dalal2005,Lowe2004}.
Usually, SVM classifiers are used to learn separating hyperplanes in such feature spaces between objects of a given class and all other possible contents of an image window. One of the state of the art classifiers available to us today builds upon a linear classifier on gradient representation which is sped up with a cascaded evaluation scheme \cite{DPM-cascade}[

Window proposal is often done exhaustively over the image space, in a ``sliding window'' fashion.
Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Chum2007b,Vedaldi2009,Vijayanarasimhan2011}.
For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008b}---however, the method has not been able to obtain state-of-the-art performance.

Although none of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal, some work has been done in the area, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008,Paletta2005}.

\paragraph{Anytime Algorithms}
Although an important concept, anytime performance in vision systems is a surprisingly little-explored idea \cite{Shlomo Zilberstein}.
A recent application to the problem of visual detection picks features with maximum value of information in a Hough-voting framework, and explicitly evaluates performance vs. time \cite{Vijayanarasimhan2010}. 
Also recent work on greedy methods and submodular formulations propose strategies for classifier/sensor evaluations in order to maximize information gain. Due to the aforementioned interlink between image classification and detection problems, anytime algorithms and greedy strategies seem counter intuitive and we therefore seek a "detection on a budget" formulation. In this fashion we can explore policies that don't yield any immediate reward.

\paragraph{Active Classification}
While most of the referenced work followed a rigid classification strategy at test time, there has been work on active classification \cite{Active Classification based on Value of Classifier}
 and active sensing  \cite{active sensing} which considers intermediate results in order to schedule the execution of further classification step. We provide a treatment of this topic for object detection that can be simply learned from traces of the system and can therefore also be easily be adapted to different loss functions.

### 2012-05-30 synthetic/dataset_policy.py
not collecting samples if not in sample collecting mode. should alleviate memory issues

@@ -305,7 +305,8 @@ class DatasetPolicy:
       dets,clses,samples = self.run_on_image(images[i],dataset,epsilon=epsilon)
       all_dets.append(dets)
       all_clses.append(clses)
-      all_samples += samples
+      if sample_size>0:
+        all_samples += samples
     safebarrier(comm)
 
     # Aggregate the results
@@ -317,6 +318,7 @@ class DatasetPolicy:
     final_samples = comm.reduce(all_samples, op=MPI.SUM, root=0)
     #if self.inference_mode=='fastinf':
       # all_fm_cache_items = comm.reduce(self.inf_model.cache.items(), op=MPI.SUM, root=0)
+    
     # Save if root
     if comm_rank==0:
       dets_table = Table(cols=self.det_columns)

### 2012-05-30 writeups/nips12/introduction.tex
working on writeup

--- 2012-03-05 writeups/eccv12/introduction.tex
@@
 \center{\includegraphics[width=0.56\linewidth]
-    {figures/evaluation.pdf}}
-  \caption{We aim for \emph{Anytime} performance within the bounds of the curve.
-That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.
-\todo{CAN WE PUT PICTURES OF DETECTORS IN HERE?}}
+    {../figures/evaluation_thumbs.png}}
+  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.}
   \label{fig:evaluation}
@@
 \emph{What is the best performance we can get on a budget?}
-To answer it, we consider the evaluation metric of performance vs. time, presented in Figure~\ref{fig:evaluation} and discussed further in the text.
-
+To answer it, we consider the evaluation metric of performance vs. time, shown in Figure~\ref{fig:evaluation} and discussed further in the text.
 Our goal is a dynamic policy for selecting classifiers or detectors to achieve the highest recognition performance under this evaluation.

### 2012-05-30 writeups/nips12/nips2012.tex
mean det ap now in final vs. t evaluation, and some minor changes
working on writeup

@@
 Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
-Toward this goal, we formulate a dynamic policy, guided by inference of the contents of the image, to decide which detector to deploy next.
-We evaluate parametrizations of the policy with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC dataset.
+Toward this goal, we formulate a dynamic policy guided by inference of the contents of the image to decide which detector to deploy next.
+We evaluate with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC object detection dataset.
 \end{abstract}
 
-\input{../eccv12/introduction.tex} % includes Evaluation section
-\input{../eccv12/technical.tex}
-\input{../eccv12/evaluation.tex}
-\input{../eccv12/related.tex}
+\input{introduction.tex} % includes Evaluation section
+\input{related.tex}
+\input{technical.tex}
+\input{evaluation.tex}
 
-\subsubsection*{Acknowledgments}
-
-Use unnumbered third level headings for the acknowledgments. All
-acknowledgments go at the end of the paper. Do not include 
-acknowledgments in the anonymized submission, only in the 
-final paper.
+% \subsubsection*{Acknowledgments}
+% Use unnumbered third level headings for the acknowledgments. All
+% acknowledgments go at the end of the paper. Do not include 
+% acknowledgments in the anonymized submission, only in the 
+% final paper.
 

### 2012-05-30 writeups/nips12/related.tex
started working on related work
working on writeup

@@
-\section{Related Work}
+\section{Recognition Problems and Related Work}
 
-under construction
+We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains at least one, and often multiple, objects.
+Each object is labeled with exactly one category label $k \in \{1, \dots, K\}$.
 
+The multi-class, multi-label \textbf{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $k$.
+We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_k \in \mathbb{B} = \{0,1\}$ is set to $1$ if an object of class $k$ is present.
+
+The \textbf{detection} problem is to output a list of bounding boxes (sub-images defined by four coordinates), each with a real-valued confidence that it encloses a single instance of an object of class $k$, for each $k$.
+The answer for a single class is given by an algorithm $\emph{detect}(\mathcal{I},k)$, which outputs a list of sub-image bounding boxes $B$ and their associated confidences.
+
+The answer is evaluated by plotting precision vs. recall across dataset $\mathcal{D}$ (by progressively lowering the confidence threshold for a positive detection).
+The area under the curve yields the Average Precision (AP) metric, which has become the standard evaluation for recognition performance on challenging datasets in vision \cite{pascal-voc-2010}.
+A common measure of a correct detection is the PASCAL overlap: two bounding boxes are considered to match if they have the same label and the ratio of their intersection to their union is at least $\frac{1}{2}$.
+
+To highlight the hierarchical structure of these problems, we note that (1) the confidences for each sub-image $b \in B$ may be given by $\emph{classify}(b,k)$; (2) correct answer to the detection problem also answers the classification problem.
+
+\subsection{Related Work}
 The literature on object detection is vast.

### 2012-05-30 writeups/nips12/technical.tex
working on writeup

@@
-\section{Recognition Problems}
-
-We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains at least one, and often multiple, objects.
-Each object is labeled with exactly one category label $k \in \{1, \dots, K\}$.
-
-The multi-class, multi-label \textbf{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $k$.
-The answer for a single label is given with a real-valued confidence by a function $\emph{classify}(\mathcal{I},k)$.
-We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_k \in \mathbb{B} = \{0,1\}$ is set to $1$ if an object of class $k$ is present.
-
-The answer is evaluated by plotting precision vs.
-recall across dataset $\mathcal{D}$ (by progressively lowering the confidence threshold for a positive label) and integrating to yield the Average Precision (AP) metric, which has become the standard evaluation for recognition performance on challenging datasets \cite{pascal-voc-2010}.
-
-\comment{
-We can make the classification problem more difficult by posing the \emph{counting} problem, which asks how many objects of class $k$ are present in $\mathcal{I}$, for each $k$.
-This setting is not commonly evaluated; we mention it for its usefulness in later exposition.
-}
-
-The \textbf{detection} problem is to output a list of bounding boxes (sub-images defined by four coordinates), each with a real-valued confidence that it encloses a single instance of an object of class $k$, for each $k$.
-The answer for a single class is given by an algorithm $\emph{detect}(\mathcal{I},k)$, which outputs a list of sub-image bounding boxes $B$ and their associated confidences.
-
-A common measure of a correct detection is the PASCAL overlap: two bounding boxes are considered to match if they have the same label and the ratio of their intersection to their union is at least $\frac{1}{2}$.
-Again, Average Precision is the single-number metric for the performance of a detector.
-
-As our task is fundamentally in \emph{multi-class} object detection, we rely on a slightly different evaluation than is commonly used (although it has precedent in \cite{Desai2009}).
-Instead of pooling detections across images in the dataset, and considering classes individually, we pool detections across classes, but consider images individually, reporting results averaged across the dataset.
-
-To highlight the hierarchical structure of these problems, we note that (1) the confidences for each sub-image $b \in B$ may be given by $\emph{classify}(b,k)$; (2) the correct answer to the detection problem also answers the classification problem.
-\comment{the counting and classification problems}
-
-Our goal is a general recognition policy that outputs both classification and detection results; we evaluate on both tasks.
-
 \section{Multi-class Recognition Policy} \label{sec:tech}
@@
 
-As presented in Figure~\ref{fig:pomdp}, our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and then outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ and a list of multi-class detection results $\emph{detect}(I)$.
+Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs a list of multi-class detection results $\emph{detect}(I)$ by running detector and other \emph{actions} sequentially.
 
-The policy repeatedly selects an action $a_i$ from a set of actions $\mathcal{A}$, executes it, potentially receives an observation $o_i$, and selects the next action.
-The set of actions can include classifiers, detectors, or hybrid actions (detector followed by classification of its output).
+The policy repeatedly selects an action $a_i$ from a set of actions $\mathcal{A}$, executes it, receiving observations $o_i$, and then selects the next action.
+The set of actions can include both classifiers and detectors: anything that would be useful for inferring the contents of the image.
 
-A dynamic, or ``closed-loop,'' policy bases action selection on observations received from previous actions, exploiting the signal in inter-object and scene context for a maximally efficient path through the actions.
-This is our goal, and what sets our formulation apart from multi-class systems that evaluate in a fixed order, such as simple cascades \cite{Viola2001} or decision trees.
-
-Let $\mathcal{A}$ consist of $K$ detectors $L^\text{det}_i$.
-We use one-vs-all deformable part-model classifiers on a HOG featurization of the image \cite{Felzenszwalb2010a}, with associated linear classification of the detections.
-
-\comment{Let $\mathcal{A}$ consist of $K$ actions:
-\begin{itemize}
-  \item $K$ detectors $L^\text{det}_i$: one-vs-all deformable part-model classifiers on a HOG featurization of the image \cite{Felzenszwalb2010a}, with associated linear classification of the detections.
-  \item $K$ classifiers $L^\text{gist}_i$: one-vs-all SVMs on the GIST feature \cite{Torralba2004}.
-\end{itemize}}
-
-\subsubsection{Time and Evaluation}
-Each action $L$ has an expected cost $c(\cdot)$ of execution.
+Each action $a_i$ has an expected cost $c(a_i)$ of execution.
 Depending on the setting, the cost can be defined in terms of algorithmic runtime analysis, an idealized property such as number of \emph{flops}, or simply the empirical runtime on specific hardware.
@@
 A single-number metric that corresponds to this objective is simply the ratio of the area captured under the curve to the total area between the start and deadline bounds.
-\comment{Just like the metric of Average Precision itself was motivated by the inadequacy of any single Precision-Recall operating point to describe the performance of a robust system, our proposed metric is motivated by the inadequacy of any single Performance vs.
-Time operating point.}
 We evaluate policies by this more robust metric and not simply by the final performance at deadline time for the same reason that Average Precision is used instead of a fixed Precision vs.
@@
 \subsubsection{Sequential Execution}
+An ``open-loop'' policy takes actions in a sequence that does not depend on observations received from previous actions.
+The common classifier cascade \cite{Viola2001} is an example.
+In contrast, our goal is to learn a dynamic, or ``closed-loop,'' policy, which would exploit the signal in inter-object and scene context for a maximally efficient path through the actions.
+
 An action $a_i$ that consists of running a classifier $L_i$ returns a real-valued observation $o_i \sim P(O_i)$.

### 2012-05-30 writeups/nips12/evaluation.tex
working on writeup
reworked paper quite a bit, but not done

@@
 \section{Evaluation} \label{sec:evaluation}
+
+\todo{completely rework when settled on results story}
+
+One simple heuristic value function that we can try is simply picking the action corresponding to the class presence variable $C_k$ with the highest probability.
+
+We use one-vs-all deformable part-model classifiers on a HOG featurization of the image \cite{Felzenszwalb2010a}, with associated linear classification of the detections.
 

### 2012-05-30 writeups/nips12/related.tex
reworked paper quite a bit, but not done

@@
 
+Multi-class performance is evaluated by averaging the individual per-class AP values.
+Since our use case is motivated by a potential advertising system, we generalize this metric to a weighted average, with the weights set by the \emph{values} of the classes.
+
 \subsection{Related Work}
@@
 
-\paragraph{Contect}
+\paragraph{Context}
 Context of course has a long history in vision.

### 2012-05-30 writeups/nips12/technical.tex
reworked paper quite a bit, but not done

@@
 
-Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs a list of multi-class detection results $\emph{detect}(I)$ by running detector and other \emph{actions} sequentially.
+Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs a list of multi-class detection results by running detector and other \emph{actions} sequentially.
 
-The policy repeatedly selects an action $a_i$ from a set of actions $\mathcal{A}$, executes it, receiving observations $o_i$, and then selects the next action.
-The set of actions can include both classifiers and detectors: anything that would be useful for inferring the contents of the image.
+The policy repeatedly selects an action $a_i \in \mathcal{A}$, executes it, receiving observations $o_i$, and then selects the next action.
+The set of actions $\mathcal{A}$ can include both classifiers and detectors: anything that would be useful for inferring the contents of the image.
 
@@
 
-\subsubsection{Sequential Execution}
+\subsection{Sequential Execution}
 An ``open-loop'' policy takes actions in a sequence that does not depend on observations received from previous actions.
@@
 
-An action $a_i$ that consists of running a classifier $L_i$ returns a real-valued observation $o_i \sim P(O_i)$.
-The state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
-We refer to the current set of observations as $\mathbf{o} = \{o_i | L_i \in \mathcal{O}\}$.
+The basis for the decisions made by the decision process is called the \emph{state}.
+The state, $b$, includes the currently believed distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$, where we write $P(C_k)$ to mean $P(C_k=1)$
 
-We define the belief state $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$, where we write $P(C_k)$ to mean $P(C_k=1)$.
-Additionally, $b$ records the time into episode $t$, and the set of executed actions $\mathcal{O}$ with corresponding observations $\mathbf{o}$.
+Additionally, the state records the fact that an action $a_i$ has been taken by adding it to the initially empty set $\mathcal{O}$ and recording the resulting observations $o_i$.
+We refer to the current set of observations as $\mathbf{o} = \{o_i | a_i \in \mathcal{O}\}$.
+The state also includes the time into episode $t$, and the setup and deadline times $T_s,T_d$.
 
-A recognition \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b^0$ and action $a^0$ to the next pair $b^1$, and so on until $t$ exceeds $T_d$.
+A recognition \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial state $b^0$ and action $a^0$ to the next pair $(b^1,a^1)$, and so on until $t$ exceeds $T_d$.
 At that point, the policy is terminated and a new episode begins on a new image.
 
-The policy's performance at time $t$ is determined by the detection and classification observations that have been observed at the last belief state $b^j$ before that point.
-For classification of unobserved classes, we treat the corresponding values of $P(\mathbf{C})$ as the set of confidence scores $\{\emph{classify}(k)\}$.
+The policy's performance at time $t$ is determined by the detections that are part of the set of observations $\mathbf{o}$ at the last state $b^j$ before $t$.
 Detection results of unobserved classes are an empty set.
-
-Our notation is summarized in \autoref{tab:notation}.
 
@@
 
-\section{Selecting actions} \label{sec:value}
-\comment{Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).}
-As our goal is to pick actions dynamically, we want to formulate a function $V(b,a)$  that assigns a value to a potential action, given the current state of the decision process.
-We can then define the policy as simply the untaken action with the maximum value:
+\subsection{Selecting actions based on expected reward} \label{sec:value}
+As our goal is to pick actions dynamically, we want a function $V(b,a): B \times \mathcal{A} \mapsto \mathbb{R}$, where $B$ is the space of all possible states, to assign a value to a potential action, given the current state of the decision process.
+We can then define the desired policy $\pi$ as simply taking the (untaken) action with the maximum value:
 \begin{align}
@@
 
-For this policy to be \emph{closed-loop}, the observations $o_i$ generated by taking an action $a_i$ need to update $b$ and thus influence the selection of the next action.
-Figure~\ref{fig:pomdp} visualizes such an execution process.
+This formulation can represent a closed-loop policy if the observations $\mathbf{o}$ (part of the state $b$) play a role in determining the value of a potential action.
 
-One simple heuristic value function that we can try is simply picking the action corresponding to the class presence variable $C_k$ with the highest probability.
-Of course, we'd like to learn the value function from the data, but the above heuristic will be used as a baseline in the evaluation to follow.
+Before proceeding, we note that that although the action space $\mathcal{A}$ is quite manageable, consisting of the detectors and classifier we would like to run on the image, the space of possible states $B$ is infinite.
+Therefore we cannot learn a tabular representation of $V(b,a)$, and so use function approximation to represent it \cite{Sutton1998}.
+We featurize the state-action pair and assume linear structure: $V^\pi(b,a) = \theta_\pi^\top  \phi(b,a_i)$.
 
-Before we discuss how to set $V(b,a_i)$ such that our policy obtains best performance under our evaluation, we present our model for updating the belief state with observations.
-
-\subsection{The model of the belief state}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.56\linewidth]{../figures/inf_model_mrf_1.pdf}
-\caption{
-The MRF inference model used in our system.
-We show a point in the middle of the decision process for 3 classes; one action has already been taken.
-\comment{Some classifiers have already been observed.}
-}
-\label{fig:model}
-\end{figure}
-
-The quantities that may be useful to us for selecting which actions to deploy are the probabilities and entropies of the class presence variables $C_k$.
-These allow us to look for the most probable classes given the observations.
-When the policy starts, the model should present the prior distributions $P(C_k)$; as observations are accrued, the model should present the updated conditionals $P(C_k|\mathbf{o})$.
-
-We employ a pairwise fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
-All parameters of the model are trained on fully-observed data.
-Exact inference is generally intractable in this model.
-Instead, we use Loopy Belief Propagation, which does not provide general convergence guarantees but has been shown to work well empirically on similar tasks \cite{Desai2009}.
-
-The $L_i$ variables are discretized from real-valued responses of a classifier on the detections output by the deformable part-model detector we employ (see Section~\ref{sec:tech}).
-The classifier is a linear SVM on the top two max detection scores in the list of detections.
-The responses are discretized per variable based on the distribution of the scores on the training dataset.
-
-The graphical model structure is set as fully-connected, but as shown in \autoref{fig:dataset_stats}, some classes are overwhelmingly unlikely to co-occurr.
-Accordingly, the graph edge weights are learned with L1 regularization, which obtains the desired sparse structure \cite{Lee2006}.
- is implemented with an open-source graphical model package \cite{Jaimovich2010}.
-
- \todo{section on a ``fast approximation'' to this based on the n-gram counts we had before?}
-
-\subsection{Learning the Value Function}
-
-Remember that our heuristic value function consisted of picking the action corresponding to the class presence variable with the highest probability $P(C_k)$.
-We can formulate such a policy as a scalar product:
-\begin{align}
-\pi(b) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a_i)
-\end{align}
-where $\phi(b,a_i)$ is a feature vector representation of the belief state.
-This approach is known as function approximation in reinforcement learning \cite{Sutton1998}.
-
-Let us take take the feature representation for an action $a_i$ to be $[P(C_k), \, 1]$, where $C_k$ corresponds to the action.
-This corresponds to our heuristic value function, with a bias variable.
-The feature representation $\phi(b,a_i)$ then is a vector of size $F|\mathcal{A}|$, with $F=2$ for this feature, where all values are $0$ except those corresponding to $a_i$.
-
-This representation allows us to use a single vector of weights $\theta$ as a compact representation of our policy.
-
-At each time step, our system is evaluated by properties of the state $b$ (the list of detections and the classification outputs).
+Rembmer that at each time step, our system is evaluated by properties of the state $b$ (the list of detections and the classification outputs).
 The final evaluation metric is a function of the history of execution $h^0=b^0,b^1,\dots,b^J$, with $J$ being the last step of the process with $t \le T_d$.
 
+\todo{rework the below from the persepctive of individual action rewards, not reward of whole history}
 Ideally, the value function for a point in the decision process $b^j$ should give the expected value of the final evaluation metric, over all possible histories starting at point $j$:
@@
 \end{equation}
-
-We formulate two reward definitions: one strives to match the final AP evaluation of the detections, and one is motivated by lowering uncertainty of $P(\mathbf{C})$.
 
@@
 
-\subsubsection{Reward: decrease in mean entropy}
-We also consider a similar additive reward function based on the mean entropy of the variables $P(C_k)$: $\frac{1}{K}\sum_{k=1}^K H(C_k)$, where $H(C_k) = - \sum_{c_k \in {0,1}} P(c_k) \log P(c_k)$.
-We follow the same setup as above, but strive to maximize the area \emph{above} the curve of mean entropy vs. time.
+\todo{discuss the raw vs. the normalized area, saying we'll try both}
 
-The goal of a policy that maximizes these rewards is to take actions that reduce uncertainty of the most uncertain variables most quickly.
+\subsection{Feature representation and learning the policy}
+\todo{write out current approach}
 
-\subsection{Learning the weights}
+Let us take take the feature representation for an action $a_i$ to be $[P(C_k), \, 1]$, where $C_k$ corresponds to the action.
+This corresponds to our heuristic value function, with a bias variable.
+The feature representation $\phi(b,a_i)$ then is a vector of size $F|\mathcal{A}|$, with $F=2$ for this feature, where all values are $0$ except those corresponding to $a_i$.
 
@@
 We cross-validate for both values.
+
+\subsection{Updating probabilities}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.56\linewidth]{../figures/inf_model_mrf_1.pdf}
+\caption{
+The MRF inference model used in our system.
+We show a point in the middle of the decision process for 3 classes; one action has already been taken.
+\comment{Some classifiers have already been observed.}
+}
+\label{fig:model}
+\end{figure}
+
+\todo{Rework from the persepctive of two potential ways of updating the beliefs with observations: just putting them in directly vs.
+going through MRF.
+De-emphasize the need for the model, treat it as an extra oomph.}
+
+The quantities that may be useful to us for selecting which actions to deploy are the probabilities and entropies of the class presence variables $C_k$.
+These allow us to look for the most probable classes given the observations.
+When the policy starts, the model should present the prior distributions $P(C_k)$; as observations are accrued, the model should present the updated conditionals $P(C_k|\mathbf{o})$.
+
+We employ a pairwise fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
+All parameters of the model are trained on fully-observed data.
+Exact inference is generally intractable in this model.
+Instead, we use Loopy Belief Propagation, which does not provide general convergence guarantees but has been shown to work well empirically on similar tasks \cite{Desai2009}.
+
+The $L_i$ variables are discretized from real-valued responses of a classifier on the detections output by the deformable part-model detector we employ (see Section~\ref{sec:tech}).
+The classifier is a linear SVM on the top two max detection scores in the list of detections.
+The responses are discretized per variable based on the distribution of the scores on the training dataset.
+
+The graphical model structure is set as fully-connected, but as shown in \autoref{fig:dataset_stats}, some classes are overwhelmingly unlikely to co-occurr.
+Accordingly, the graph edge weights are learned with L1 regularization, which obtains the desired sparse structure \cite{Lee2006}.
+ is implemented with an open-source graphical model package \cite{Jaimovich2010}.

### 2012-05-30 writeups/nips12/evaluation.tex
fixing gist oracle

@@
 
-\begin{figure}[h!]
-\centering
-\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
-    {../figures/entropy_plots_det_avg.png}} \\
-\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
-    {../figures/entropy_plots_cls_whole.png}}
-  \caption{Entropy reward function.}
-  \label{fig:results_entropy}
-\end{figure}
-
-Figure~\ref{fig:results_entropy} shows the performance of the polices with learned weights, comparing our two reward functions.
-We found the entropy-based reward to work better than the AP-based reward.
-
-A notable difference between the MRF inference model and the fixed-order model was in the weights learned: while the fixed-order model learned weights onto the bias feature only, the MRF inference model learned weights onto a mix of the entropy and probability features.
+A notable difference between the MRF inference model and the fixed-order model was in the weights learned: while the fixed-order model learned weights onto the bias feature only, the MRF inference model learned weights onto a mix of the entropy and probability features

### 2012-05-30 synthetic/dataset_policy.py

@@ -683,7 +683,9 @@ class DatasetPolicy:
       # stuff for the sample collection
       sample.det_naive_ap = 0
       sample.det_actual_ap = 0
-      if 'dets' in obs:
+      if not 'dets' in obs:
+        all_detections.append(np.array([]))
+      else:
         det = action.obj
         dets = obs['dets']
         cls_ind = dataset.classes.index(det.cls)
@@ -795,7 +797,10 @@ class DatasetPolicy:
         action = self.actions[action_ind]
         obs = action.obj.get_observations(image)
         b.t += obs['dt']
-        b.update_with_score(action_ind, obs['score'])
+        if action.name=='gist':
+          b.update_with_gist(action_ind, obs['scores'])
+        else:
+          b.update_with_score(action_ind, obs['score'])
         clses = b.get_p_c().tolist() + [img_ind,b.t]
         all_clses.append(clses)
 

### 2012-05-31 writeups/nips12/evaluation.tex
paper stuff

@@
 \centering
-\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
-    {../figures/manual_plots_det_avg.png}} \\
-\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
-    {../figures/manual_plots_cls_whole.png}}
-  \caption{Heuristic value function.}
-  \label{fig:results_manual}
+\subfloat[AP vs. Time curves]{\includegraphics[width=0.47\linewidth]
+    {../figures/final1.png}} \hfill
+\subfloat[Execution traces of different policies]{\includegraphics[draft,width=0.47\linewidth]
+    {../figures/final1.png}}
+  \label{fig:results1}
 \end{figure}
 
-Figure~\ref{fig:results_manual} also shows the performance of our policy with the heuristic value function and two inference models: the MRF model and a simple fixed-order model that follows the priors.
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.87\linewidth]
+    {../figures/weights.pdf}
+\caption{Weights}
+\label{fig:weights}
+\end{figure}
+
+\begin{table}[t]
+\caption{Results}
+\label{tab:results}
+\begin{center}
+\begin{tabular}{|l|l|l|l|l|l|}
+\\ \hline \\
+Bounds & Random & Fixed Order & RL w/ MRF & w/ GIST   & Oracle \\ \hline
+(0,10) & 0.1191 & 0.2404      & 0.2664    & 0.2665    & 0.4638 \\ 
+(0,20) & 0.2497 & 0.3421      & 0.3781    & 0.3824    & 0.4878 \\ 
+(5,15) & 0      & 0           & 0         & 0         & 0      \\
+\end{tabular}
+\end{center}
+\end{table}
+
+Figure~\ref{fig:results1} also shows the performance of our policy with the heuristic value function and two inference models: the MRF model and a simple fixed-order model that follows the priors.
 We can see that due to the dataset bias, the fixed-order policy performs well at first (the person class is disproportionately likely to be in the image), but is overtaken by the proper inference model as execution goes on.

### 2012-05-31 writeups/nips12/technical.tex
paper stuff

@@
 
-The basis for the decisions made by the decision process is called the \emph{state}.
-The state, $b$, includes the currently believed distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$, where we write $P(C_k)$ to mean $P(C_k=1)$
+We refer to the basis for the decisions made by the decision process as the \emph{state} $b$.
+The state includes the currently believed distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$, where we write $P(C_k)$ to mean $P(C_k=1)$
 
@@
 We refer to the current set of observations as $\mathbf{o} = \{o_i | a_i \in \mathcal{O}\}$.
-The state also includes the time into episode $t$, and the setup and deadline times $T_s,T_d$.
+The state also keeps track of the time into episode $t$, and the setup and deadline times $T_s,T_d$.
 
 A recognition \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial state $b^0$ and action $a^0$ to the next pair $(b^1,a^1)$, and so on until $t$ exceeds $T_d$.
-At that point, the policy is terminated and a new episode begins on a new image.
-
-The policy's performance at time $t$ is determined by the detections that are part of the set of observations $\mathbf{o}$ at the last state $b^j$ before $t$.
-Detection results of unobserved classes are an empty set.
+At that point, the policy is terminated, and a new episode can begin on a new image.
 
@@
 Therefore we cannot learn a tabular representation of $V(b,a)$, and so use function approximation to represent it \cite{Sutton1998}.
-We featurize the state-action pair and assume linear structure: $V^\pi(b,a) = \theta_\pi^\top  \phi(b,a_i)$.
-
-Rembmer that at each time step, our system is evaluated by properties of the state $b$ (the list of detections and the classification outputs).
-The final evaluation metric is a function of the history of execution $h^0=b^0,b^1,\dots,b^J$, with $J$ being the last step of the process with $t \le T_d$.
-
-\todo{rework the below from the persepctive of individual action rewards, not reward of whole history}
-Ideally, the value function for a point in the decision process $b^j$ should give the expected value of the final evaluation metric, over all possible histories starting at point $j$:
+We featurize the state-action pair and assume linear structure:
 \begin{align}
-V(b^j,a_i) = \mathbb{E}_{h^j \sim P(h^j|b,a_i)}[R(h^j)]
+V^\pi(b,a_i) = \theta_\pi^\top  \phi(b,a_i)
 \end{align}
 
-The reward function $R(h^j)$ assigns a real-valued score to a history.
-We have considerable flexibility in defining $R$; it does not necessarily have to be directly tied to the final evaluation.
+The policy's performance at time $t$ is determined by the detections that are part of the set of observations $\mathbf{o}$ at the last state $b^j$ before $t$.
+Detection results of unobserved classes are an empty set.
+Therefore, the final AP vs. Time evaluation of the episode is a function of the history of execution $h^0=b^0,b^1,\dots,b^J$, where $J$ is the last step of the process with $t \le T_d$.
+We call the final evaluation function $eval(h^0,T_s,T_d)$, and it is precisely the area under the AP vs.
+Time curve (normalized by total possible area) between $T_s$ and $T_d$, as determined by the detections in $\mathbf{o^j}$ for all steps $j$ in the episode $h$.
 
-One feature we want the reward function to have is additivity.
-Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
-The total reward of a policy $\pi$ starting at state $b^j$ is then defined as the sum of rewards
-\begin{equation}
-R(h^j) = \sum_{j'=j}^J R(b_j',a^{j'})
-\end{equation}
-
-\subsubsection{Reward: area under the AP vs. Time curve}
-\begin{figure}[htb]
+\begin{figure}[h!]
   \centering
@@
 
-The final evaluation of a policy consists of the area under the performance vs. time curve (normalized by the total area).
-Accordingly, we formulate per-action rewards such that their addition results in this quantity.
+As shown in \autoref{fig:rewards}, the evaluation function is additive per action, as each action can generate detections that either raise or lower the AP of all detections so far: ($\Delta ap$), and takes a certain time: $t$.
+From these, we can find the area under the curve that was contributed by the action.
 
-Specifically, as shown in Figure~\ref{fig:rewards}, we define the reward of an action as
-\begin{equation}\label{eq:advanced}
+Specifically, as shown in Figure~\ref{fig:rewards}, we define the \emph{reward} of an action as
+\begin{align}\label{eq:advanced}
 R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}^j)t_T^j}
-\end{equation}
+\end{align}
 where $t_T^j$ and $\text{ap}^j$ are the time left until deadline and the AP at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.
 
-The reward is $1$ if the policy takes an action that obtains the maximum possible area under the curve at that point, and $0$ if no area under the curve is captured.
+\todo{discuss the raw vs. the normalized area, saying we'll try both}
 
-\todo{discuss the raw vs. the normalized area, saying we'll try both}
+We can then represent the final evaluation in terms of individual rewards:
+\begin{align}
+eval(h^0) = \sum_{j=0}^J R(b_j,a^{j})
+\end{align}
+
+And we can represent the expected value of the final evaluation recursively in terms of the value function:
+\begin{align} \label{eq:recursive_value}
+V(b^j,a_i) = \mathbb{E}_{b^{j+1}} [R(b^j,a_i) + \gamma V(b^{j+1},\pi(b^{j+1}))]
+\end{align}
+where $\gamma \in [0,1]$ is a \emph{discount} value that can mitigate the effects of increasing state-transition uncertainty over long episodes.
 
@@
 \centering
-\includegraphics[width=0.56\linewidth]{../figures/inf_model_mrf_1.pdf}
+\includegraphics[width=0.56\linewidth]{../figures/mrf_w_gist.pdf}
 \caption{
-The MRF inference model used in our system.
-We show a point in the middle of the decision process for 3 classes; one action has already been taken.
-\comment{Some classifiers have already been observed.}
+The MRF inference model used in our system. The shaded nodes represent two actions that have already been taken; their observations have been recorded.
 }

### 2012-05-31 synthetic/evaluation.py

@@ -316,7 +316,7 @@ class Evaluation:
       
       labels.append(label)
       plt.plot(times, vals, style,
-          linewidth=2,color=color,label=label)
+          linewidth=3,color=color,label=label)
 
       # draw vertical lines at bounds, if given
       if bounds:
@@ -330,9 +330,10 @@ class Evaluation:
       plt.setp(ltext, fontsize='small')
     plt.xlabel('Time',size=14)
     plt.ylabel('AP',size=14)
-    plt.ylim(0,1)
+    plt.ylim(0,0.8)
     plt.xlim(0,20)
-    plt.grid(True)
+    plt.grid(True,'major')
+    plt.grid(True,'minor')
 
     # save text file with the label information and save the figure
     txt_filename = os.path.splitext(filename)[0]+'.txt'

### 2012-05-31 synthetic/run_experiment.py

@@ -221,6 +221,9 @@ def main():
     # det avg
     ff = opjoin(dirname, '%s_det_avg.png'%filename)
     ff_nl = opjoin(dirname, '%s_det_avg_nl.png'%filename)
+
+    # make sure directory exists
+    ut.makedirs(os.path.dirname(ff))
     
     Evaluation.plot_ap_vs_t(dets_tables, ff, all_bounds, with_legend=True, force=True, plot_infos=plot_infos)
     Evaluation.plot_ap_vs_t(dets_tables, ff_nl, all_bounds, with_legend=False, force=True, plot_infos=plot_infos)

### 2012-05-31 writeups/nips12/technical.tex
paper

@@
 \section{Multi-class Recognition Policy} \label{sec:tech}
-\begin{figure}[h!]
-\center{\includegraphics[width=0.66\linewidth]
-    {../figures/pomdp.png}}
-  \caption{Summary of our approach to the problem.
-Our system has two major parts: (1) selecting an action by predicting its value; (2) updating the belief state with observations resulting from the action.}
-  \label{fig:pomdp}
-\end{figure}
-
 Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs a list of multi-class detection results by running detector and other \emph{actions} sequentially.
@@
 
-We refer to the basis for the decisions made by the decision process as the \emph{state} $b$.
+We refer to the basis for the decisions made by the decision process as the \emph{state} $s$.
 The state includes the currently believed distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$, where we write $P(C_k)$ to mean $P(C_k=1)$
@@
 
-A recognition \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial state $b^0$ and action $a^0$ to the next pair $(b^1,a^1)$, and so on until $t$ exceeds $T_d$.
+A recognition \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial state $s^0$ and action $a^0$ to the next pair $(s^1,a^1)$, and so on until $t$ exceeds $T_d$.
 At that point, the policy is terminated, and a new episode can begin on a new image.
@@
   $T_s$, $T_d$  & start and deadline times \\ 
-  $b^j$         & belief state at step $j$ \\ 
+  $s^j$         & belief state at step $j$ \\ 
   $\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
@@
 \subsection{Selecting actions based on expected reward} \label{sec:value}
-As our goal is to pick actions dynamically, we want a function $V(b,a): B \times \mathcal{A} \mapsto \mathbb{R}$, where $B$ is the space of all possible states, to assign a value to a potential action, given the current state of the decision process.
+As our goal is to pick actions dynamically, we want a function $Q(s,a): S \times \mathcal{A} \mapsto \mathbb{R}$, where $S$ is the space of all possible states, to assign a value to a potential action, given the current state of the decision process.
 We can then define the desired policy $\pi$ as simply taking the (untaken) action with the maximum value:
 \begin{align}
-\pi(b) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} V(b,a_i)
+\pi(s) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} Q(s,a_i)
 \end{align}
 
-This formulation can represent a closed-loop policy if the observations $\mathbf{o}$ (part of the state $b$) play a role in determining the value of a potential action.
-
-Before proceeding, we note that that although the action space $\mathcal{A}$ is quite manageable, consisting of the detectors and classifier we would like to run on the image, the space of possible states $B$ is infinite.
-Therefore we cannot learn a tabular representation of $V(b,a)$, and so use function approximation to represent it \cite{Sutton1998}.
+Although the action space $\mathcal{A}$ is quite manageable, consisting of the detectors and classifier we would like to run on the image, the space of possible states $B$ is infinite.
+Therefore we cannot learn a tabular representation of $Q(s,a)$, and so use function approximation to represent it \cite{Sutton1998}.
 We featurize the state-action pair and assume linear structure:
 \begin{align}
-V^\pi(b,a_i) = \theta_\pi^\top  \phi(b,a_i)
+Q^\pi(s,a_i) = \theta_\pi^\top  \phi(s,a_i)
 \end{align}
 
-The policy's performance at time $t$ is determined by the detections that are part of the set of observations $\mathbf{o}$ at the last state $b^j$ before $t$.
+The policy's performance at time $t$ is determined by the detections that are part of the set of observations $\mathbf{o}$ at the last state $s^j$ before $t$.
 Detection results of unobserved classes are an empty set.
-Therefore, the final AP vs. Time evaluation of the episode is a function of the history of execution $h^0=b^0,b^1,\dots,b^J$, where $J$ is the last step of the process with $t \le T_d$.
+Therefore, the final AP vs. Time evaluation of the episode is a function of the history of execution $h^0=s^0,s^1,\dots,s^J$, where $J$ is the last step of the process with $t \le T_d$.
 We call the final evaluation function $eval(h^0,T_s,T_d)$, and it is precisely the area under the AP vs.
@@
 \begin{align}\label{eq:advanced}
-R(b^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}^j)t_T^j}
+R(s^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}^j)t_T^j}
 \end{align}
-where $t_T^j$ and $\text{ap}^j$ are the time left until deadline and the AP at state $b^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.
+where $t_T^j$ and $\text{ap}^j$ are the time left until deadline and the AP at state $s^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.
 
@@
 \begin{align}
-eval(h^0) = \sum_{j=0}^J R(b_j,a^{j})
+eval(h^0) = \sum_{j=0}^J R(s_j,a^{j})
 \end{align}
@@
 \begin{align} \label{eq:recursive_value}
-V(b^j,a_i) = \mathbb{E}_{b^{j+1}} [R(b^j,a_i) + \gamma V(b^{j+1},\pi(b^{j+1}))]
+Q(s^j,a_i) = \mathbb{E}_{s^{j+1}} [R(s^j,a_i) + \gamma Q(s^{j+1},\pi(s^{j+1}))]
 \end{align}
@@
 
-\subsection{Feature representation and learning the policy}
-\todo{write out current approach}
+\subsection{Learning the policy}
+While we can't directly compute the expectation in \eqref{eq:recursive_value}, we can sample it by running actual episodes to gather $<s,a,r,s'>$ samples, where $r$ is the reward obtained by taking action $a$ in state $s$, and $s'$ is the following state.
 
-Let us take take the feature representation for an action $a_i$ to be $[P(C_k), \, 1]$, where $C_k$ corresponds to the action.
-This corresponds to our heuristic value function, with a bias variable.
-The feature representation $\phi(b,a_i)$ then is a vector of size $F|\mathcal{A}|$, with $F=2$ for this feature, where all values are $0$ except those corresponding to $a_i$.
+\comment{
+Specifically, we collect such samples to the end of the episode, and are thus able to compute the actual discounted sum of rewards for $Q(s^j,a_i)$:
+\begin{align}
+Q(s^j,a_i) = \theta_\pi^\top \phi(s,a_i) = \sum_{i=0}^{J-j} \lambda^i R(b_{j+i},a^{j+i})
+\end{align}
+}
 
-The feature representation of the belief state for a given action $a_i$ that corresponds to class $k$ is defined to be
-\begin{align}
-\phi_k(b) = [P(C_k), \, H(C_k), \, 1]
-\end{align}
+Learning the policy is then a problem of repeatedly gathering samples with the current policy, minimizing the error between the discounted reward to the end of the episode as predicted by our current $Q(s^j,a_i)$ and the actual values gathered, and updating the policy with the resulting weights.
+This is standard generalized policy iteration, or more specifically fitted Q-iteration \cite{Sutton1998,Ernst2005}.
 
-Our procedure for learning the weights is standard generalized policy iteration \cite{Sutton1998}.
-We first initialize the weights $\theta$ to the heuristic value function of simply picking the maximum $P(C_k)$: $\theta_i = [1, \,0, \,0]$.
+We use $L_2$-regularized regression to minimize the error.
+We run $15$ iterations of accumulating samples by running $350$ episodes, starting with a baseline policy which will be described in \autoref{sec:evaluation}, and cross-validating the regularization parameter at each iteration; samples are not thrown away between iterations.
 
-With this policy, we run $N$ recognition episodes.
-From the state-action samples gathered in running the episodes, we formulate a matrix $\Phi$ from the featurizations $\phi(b^j,a_i)$, and a vector $y$ consisting of the individual rewards $R(b^j,a_i)$.
+One meta-parameter of the approach is the discount $\gamma$.
+With $\gamma=0$, the value function is determined entirely by the immediate reward; learning in this case can only result in completely greedy policies.
+With $\gamma=1$, the value function is determined by the expected rewards to the end of the episode, which is an approximation to the final evaluation metric.
+However, the highest value for $\gamma$ is not necessarily best, due to the interplay between the expressive power of the value function and the actual state transition behavior of the world.
+We experiment with several values of $\gamma$, and find a mid-level value of $0.4$ to work best.
 
-The rewards are computed as the sum of discounted rewards to the end of the episode:
-\begin{align}
-R(b^j,a_i) = \sum_{i=0}^{J-j} \lambda^i R(b_{j+i},a^{j+i})
-\end{align}
-Note that with $\lambda=0$, the reward is determined entirely by the actual action taken; with $\lambda=1$, the reward is the sum of all rewards until the end of the episode.
+\subsection{Feature representation}
+Our policy is at its base determined by a linear function of the features of the state: $\pi(s) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \theta_\pi^\top \phi(s,a_i)$.
+Since we want to be able to learn a dynamic policy, the observations $\mathbf{o}$ that are part of the state $s$ should play a role in determining the value of a potential action.
+We include the following quantities as features $\phi(s,a)$:
+\begin{description}
+\item[$P(C_a)$] The prior probability of the class that corresponds to the detector of action $a$
+\item[$P(C_0|\mathbf{o}) \ldots P(C_1|\mathbf{o})$] The probabilities of all classes, conditioned on the current set of observations.
+\item[$H(C_0|\mathbf{o}) \ldots H(C_1|\mathbf{o})$] The entropies of all classes, conditioned on the current set of observations.
+\end{description}
 
-We then solve the system $\Phi \theta = y$ for $\theta$ with Lasso regression.
-With the updated weights $\theta$, we run $N$ more episodes and repeat the procedure until convergence.
+Additionally, we include the mean and maximum entropies of all classes, and time features that represent the times until start and deadline.
+To formulate learning the policy as a single regression problem, we represent the features in block form, where $\phi(s,a_i)$ is a vector of size $F|\mathcal{A}|$, with $F=47$ for $20$ classes and the features as described, with all values set to $0$ except for the block corresponding to $a_i$.
 
-The parameters of this training procedure are the $\alpha$ weight on the regularization term in the regression and the $\lambda$ discount weight.
-We cross-validate for both values.
+Jumping ahead, we visualize the learned weights on these features in \autoref{fig:weights}, reshaped to a matrix of size $|\mathcal{A}| \times F$.
 
-\subsection{Updating probabilities}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.87\linewidth]
+    {../figures/weights.pdf}
+\caption{Weights \todo{describe}}
+\label{fig:weights}
+\end{figure}
+
+\subsection{Updating with observations}
 \begin{figure}[h!]

### 2012-05-31 writeups/nips12/technical.tex
printing out and reading, still need to rework evaluation

@@
 
-\subsection{Updating with observations}
+\subsection{Updating with observations} \label{sec:updating}
 \begin{figure}[h!]
@@
 \caption{
+\todo{get rid of this figure?}
 The MRF inference model used in our system. The shaded nodes represent two actions that have already been taken; their observations have been recorded.
@@
 
-\todo{Rework from the persepctive of two potential ways of updating the beliefs with observations: just putting them in directly vs.
-going through MRF.
-De-emphasize the need for the model, treat it as an extra oomph.}
+The bulk of our feature representation is formed by probability of individual class occurrence, conditioned on the observations so far: $P(C_0|\mathbf{o}) \ldots P(C_1|\mathbf{o})$.
+This allows the action-value function to learn correlations between presence of different classes, and so the policy can look for the most probable classes given the observations.
 
-The quantities that may be useful to us for selecting which actions to deploy are the probabilities and entropies of the class presence variables $C_k$.
-These allow us to look for the most probable classes given the observations.
-When the policy starts, the model should present the prior distributions $P(C_k)$; as observations are accrued, the model should present the updated conditionals $P(C_k|\mathbf{o})$.
+However, higher-order co-occurrences are not well represented in this form.
+Additionally, updating $P(C_i|\mathbf{o})$ presents choices regarding independence assumptions between the classes.
 
-We employ a pairwise fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
-All parameters of the model are trained on fully-observed data.
-Exact inference is generally intractable in this model.
-Instead, we use Loopy Belief Propagation, which does not provide general convergence guarantees but has been shown to work well empirically on similar tasks \cite{Desai2009}.
+We evaluate two ways of updating probabilities: \emph{direct} and \emph{MRF}.
+In the \emph{direct} way, $P(C_i|\mathbf{o}) = score(C_i)$ if $\mathbf{o}$ includes the observations for class $C_i$ and $P(C_i|\mathbf{o}) = P(C_i)$ otherwise.
 
+In the \emph{MRF} way, we employ a pairwise fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}, with the observation nodes set to $score(C_i)$ appropriately, or considered unobserved.
+
+The graphical model structure is set as fully-connected, but as shown in \autoref{fig:dataset_stats}, some classes are overwhelmingly unlikely to co-occurr.
+Accordingly, the graph edge weights are learned with $L_1$ regularization, which obtains the desired sparse structure \cite{Lee2006}.
+All parameters of the model are trained on fully-observed data, and inference is implemented with an open-source graphical model package \cite{Jaimovich2010}.
+As exact inference is generally intractable in this model, we use Loopy Belief Propagation; although it does not provide general convergence guarantees, it has been shown to work well empirically on similar tasks \cite{Desai2009}.
+
+\todo{rework the below, and also explain how GIST works}
 The $L_i$ variables are discretized from real-valued responses of a classifier on the detections output by the deformable part-model detector we employ (see Section~\ref{sec:tech}).
@@
 The responses are discretized per variable based on the distribution of the scores on the training dataset.
-
-The graphical model structure is set as fully-connected, but as shown in \autoref{fig:dataset_stats}, some classes are overwhelmingly unlikely to co-occurr.
-Accordingly, the graph edge weights are learned with L1 regularization, which obtains the desired sparse structure \cite{Lee2006}.
- is implemented with an open-source graphical model package \cite{Jaimovich2010}.

### 2012-05-31 writeups/nips12/introduction.tex
reword intro and related work

@@
 In recent years, the computer vision field has converged on a general method for object detection, and a standard evaluation of results.
-Most current state-of-the-art object detection systems consist of three tasks: proposing regions of the image, evaluating a given region for presence of an object of a given category, and post-processing the results.
-In the evaluation ground truth, each object is most commonly assumed to belong to one of a fixed set of classes; its location is approximated by placing a bounding box around pixels belonging to it.
+In the evaluation ground truth, each object is assumed to belong to one of a fixed set of classes; its location is approximated by placing a bounding box around pixels belonging to it.
 Large datasets of such human annotations are used for evaluation of detection algorithms~\cite{pascal-voc-2010,imagenet_cvpr09}.
@@
 Instead, separate detectors are trained per class, and they are deployed and evaluated independently.
-The evaluation of multi-class performance, if at all given, consists of averaging the per-class metrics.
-Some notable papers do make multi-class detection a priority, and accordingly evaluate in a multi-class setting, where false positives can be generated both by incorrect localization and incorrect labeling.
+The evaluation of multi-class performance consists of averaging the per-class metrics.
 State-of-the-art detection systems also do not generally make efficiency a goal.
@@
 
-It is of course important to refrain from locking object recognition research into a single detector architecture with a focus only on increasing efficiency.
-That said, there are applications for which performance truly is time-sensitive.
+There are of course many applications of object recogniition for which performance truly is time-sensitive.
 In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
@@
 To answer it, we consider the evaluation metric of performance vs. time, shown in Figure~\ref{fig:evaluation} and discussed further in the text.
-Our goal is a dynamic policy for selecting classifiers or detectors to achieve the highest recognition performance under this evaluation.
+
+Our system takes various detectors and classifiers as black boxes, and derives a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.

### 2012-05-31 writeups/nips12/related.tex
reword intro and related work

@@
 \subsection{Related Work}
-The literature on object detection is vast.
-Here we briefly summarize detection work that sufficiently contextualizes our contribution in the areas of object classification and detection in context, saliency, multi-class prediction, steering of computation (such as in cascades, any time algorithm) and active classification.
+The literature on object recognition is vast.
+Here we briefly summarize work that sufficiently contextualizes our contribution.
+
+\paragraph{Single-class detection}
+The best recent performance has come from detectors that use gradient-based features to represent objects as either a collection of local patches or as object-sized windows \cite{Dalal2005,Lowe2004}.
+Classifiers are then used to distinguish between featurizations of a given class and all other possible contents of an image window.
+
+Window proposal is often done exhaustively over the image space, as a ``sliding window''.
+Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Vedaldi2009,Vijayanarasimhan2011}.
+For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008b}.
+
+None of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal.
+Some work has been done on this topic, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008,Paletta2005}.
+
+A state-of-the-art detector builds upon a linear classifier on a gradient-based image representation, sped up with cascaded evaluation (see relevant paragraph further down) \cite{Felzenszwalb2010b}.
+Our system employs these detectors.
 
 \paragraph{Context}
-Context of course has a long history in vision.
-One source of context is the scene or non-detector cues; for the PASCAL VOC, these are quantitatively considered in~\cite{Divvala2009}. 
+Context has a long history in vision.
+One source of context is the scene or other non-detector cues; for the commonly used PASCAL dataset, these are quantitatively explored in~\cite{Divvala2009}. 
+The most common scene-level feature is the GIST \cite{Oliva2001a} of the image; it provides reasonable information for scene classification \cite{Xiao2010a}.
+
 Another source is inter-object context, used for detection in a random field setting in~\cite{Torralba2004}.
-These  statistics interlink individual object detection tasks as well as image classification.
-Exploiting this information has shown to improve classification as well as detection tasks (e.g.
-\cite{Torralba, visual phrases}).
-A critical summary of the main approaches to using context for object detection is given in \cite{Galleguillos2010}.
+Exploiting this information has shown to improve classification as well as detection tasks.
+A critical summary of the main approaches to using context for object and scene recognition is given in \cite{Galleguillos2010}.
 
 \paragraph{Multi-Class Detection}
-Inherently multi-class detection has its own line of work, focusing largely on making detection time sublinear in the number of classes through sharing features~\cite{Torralba2007,Fan2005,Razavi2011}.
-A recent post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression~\cite{Desai2009}.
-Most critically, theses methods don't use intermediate results in order to maximize the joint detection performance.
+Inherently multi-class detection has its own line of work, which focuses largely on making detection time sublinear in the number of classes, through sharing features~\cite{Torralba2007,Fan2005,Razavi2011}.
+A proposed post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression~\cite{Desai2009}.
 
-\paragraph{Attention and Steering of Computation}
-An early success in efficient object detection used simple Haar features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime~\cite{Viola2001}.
+\paragraph{Cascades}
+An early success in efficient object detection used simple, fast features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime~\cite{Viola2001}.
 Although the simple features and classifiers of this method have been surpassed by more complex detectors, the idea of cascading classifier evaluations is still often used.
+Most recently, cyclic optimization has been applied to optimize cascades with respect to feature computation cost as well as classifier performance \cite{Chen2012}.
 
-The best recent performance has come from detectors that use gradient-based features to represent objects as either a collection of local patches or as object-sized windows \cite{Dalal2005,Lowe2004}.
-Usually, SVM classifiers are used to learn separating hyperplanes in such feature spaces between objects of a given class and all other possible contents of an image window.
-One of the state of the art classifiers available to us today builds upon a linear classifier on gradient representation which is sped up with a cascaded evaluation scheme \cite{DPM-cascade}[
+However, cascades are not dynamic policies---they cannot change the order of execution based on observations obtained during execution, which is our goal.
 
-Window proposal is often done exhaustively over the image space, in a ``sliding window'' fashion.
-Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Chum2007b,Vedaldi2009,Vijayanarasimhan2011}.
-For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008b}---however, the method has not been able to obtain state-of-the-art performance.
-
-Although none of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal, some work has been done in the area, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008,Paletta2005}.
-
-\paragraph{Anytime Algorithms}
+\paragraph{Anytime Algorithms and Active Classification}
 Although an important concept, anytime performance in vision systems is a surprisingly little-explored idea \cite{Shlomo Zilberstein}.
@@
 time \cite{Vijayanarasimhan2010}.
-Also recent work on greedy methods and submodular formulations propose strategies for classifier/sensor evaluations in order to maximize information gain.
-Due to the aforementioned interlink between image classification and detection problems, anytime algorithms and greedy strategies seem counter intuitive and we therefore seek a "detection on a budget" formulation.
-In this fashion we can explore policies that don't yield any immediate reward.
 
-\paragraph{Active Classification}
-While most of the referenced work followed a rigid classification strategy at test time, there has been work on active classification \cite{Active Classification based on Value of Classifier}
- and active sensing  \cite{active sensing} which considers intermediate results in order to schedule the execution of further classification step.
-We provide a treatment of this topic for object detection that can be simply learned from traces of the system and can therefore also be easily be adapted to different loss functions.
+There has also been work on active classification \cite{Gao2011} and active sensing \cite{Yu2009}, in which intermediate results are considered in order to decide on the next classification step.
+This line of work is closest to our approach.
+Most commonly, the scheduling is greedy with respect to some quantity such as expected information gain.
+
+In contrast, we are able to learn policies that take actions without any immediate such reward.
+We aim for a general system that can take black-box detectors and classifiers, and learn its policy from its own trial execution traces, and can be adapted to different loss functions.

### 2012-06-01 writeups/nips12/evaluation.tex
paper
draft for mario

@@
 
-\todo{completely rework when settled on results story}
+We evaluate our system on the multi-class, multi-label detection task as previously described.
+Each detection episode takes an image and outputs detections with associated times, based on the order of actions taken.
+We evaluate on a popular detection challenge task: the PASCAL VOC 2007 dataset \cite{pascal-voc-2010}.
+As shown in \autoref{fig:dataset_stats}, the dataset exhibits a rather modest amount of class co-occurrence.
 
-One simple heuristic value function that we can try is simply picking the action corresponding to the class presence variable $C_k$ with the highest probability.
+We learn weights on the training and validation sets, and run our policy on all images in the testing set.
+The final evaluation pools all detections up to a certain time, and computes their multi-class AP per image, then averaging over all images.
+This is done for different times to plot the AP vs. Time curve over the whole dataset.
+The evaluation is slightly different that what is usually done (all detections for a class are pooled across the dataset), but has been used before \cite{Desai2009}.
 
-We use one-vs-all deformable part-model classifiers on a HOG featurization of the image \cite{Felzenszwalb2010a}, with associated linear classification of the detections.
+For the detector actions, we use one-vs-all cascaded deformable part-model detectors on a HOG featurization of the image \cite{Felzenszwalb2010b}, with associated linear classification of the detections.
+There are $20$ classes in the PASCAL challenge task, so there are $20$ detector actions.
+Running a detector on a PASCAL image takes about $1$ second.
+Additionally, we use a classifier from the scene-level GIST feature to class presence, for each class.
+This is considered one action, and takes about $0.3$ seconds.
+
+We test three different settings of the start and deadline times.
+In the first one, the start time is immediate and execution is cut off at 20 seconds, which is enough time to run basically all actions.
+In the second one, execution is cut off after only 10 seconds.
+Lastly, we measure performance between 5 seconds and 15 seconds.
+These operating points show how our method would behave when deployed in different conditions.
 
@@
 
-To summarize \autoref{sec:}, we evaluate our system in the multi-class, multi-label detection regime.
-We evaluate on a popular detection challenge task: the PASCAL VOC dataset \cite{pascal-voc-2010}.
-As shown in \autoref{fig:dataset_stats}, the dataset exhibits a rather modest amount of class co-occurrence, which puts our model in a disadvantaged setting.
-$60\%$ of the images in the training set have only one class; $30\%$ have two classes, $7\%$ have three classes, and almost none have more.
-
-Using the 2007 version of the dataset, we train on the training and validation data and test on the test set.
-We run our policies on all images in the test set, cutting off execution at $T_d$.
-
-To evaluate performance at a given time, we gather all detections and the classification answers found to this point in all the recognition episodes.
-As described before, we evaluate detection performance by averaging per-image performance in the multi-class regime.
-We evaluate classification performance by pooling the ground truth across the dataset, in standard procedure.
-
-We establish the baseline performance of our system by selecting actions randomly at each step.
-The time setting for our evaluation is $T_s=0$, $T_d=20$ (in seconds).
-As shown in Figure~\ref{fig:results_manual}, the random policy results in a roughly linear gain of performance vs. time.
-
-To establish an upper bound on performance, we also plot the Oracle curve, obtained by re-ordering the actions with the hindsight of the results they produced.
-Note that the curves turn downward in this setting: this is due to the different performance levels of the detectors: as the weaker detectors are inevitably run, they introduce more false positives and false negatives than true positives.
-
 \begin{figure}[h!]
 \centering
-\subfloat[AP vs. Time curves]{\includegraphics[width=0.47\linewidth]
-    {../figures/final1.png}} \hfill
+\subfloat[AP vs.
+Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy, with start time of 5 seconds and deadline of 15 seconds.]{\includegraphics[width=0.47\linewidth]
+    {../figures/final1_515.png}} \hfill
 \subfloat[Execution traces of different policies]{\includegraphics[draft,width=0.47\linewidth]
@@
 
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.87\linewidth]
-    {../figures/weights.pdf}
-\caption{Weights}
-\label{fig:weights}
-\end{figure}
+We establish the first baseline for our system by selecting actions randomly at each step.
+As shown in Figure~\ref{fig:results1}, this \textbf{Random} policy results in a roughly linear gain of AP vs. time.
+This is expected: the detectors are capable of obtaining a certain level of performance; if half the detectors are run, the expected performance level is half of the maximum level.
+
+To establish an upper bound on performance, we plot the \textbf{Oracle} policy, obtained by re-ordering the actions with the hindsight of the results they produced.
+
+We consider another baseline: selecting actions in a fixed order based on the value they bring to the AP vs. Time evaluation, which is roughly proportional to their occurrence probability.
+We refer to this as \textbf{Fixed Order}.
+
+Then there are our proposed systems, which the previous section thoroughly described: \textbf{RL w/ Direct} and \textbf{RL w/ MRF}.
+In experiments, the two were not exceedingly different in performance, with the MRF model consistently performing slightly better.
+
+In \autoref{fig:results1}, we can see that due to the dataset bias, the fixed-order policy performs well at first (as can be seen in \autoref{fig:dataset_stats}, the person class is disproportionately likely to be in the image), but is significantly overtaken by our model as execution goes on.
+
+Lastly, we also evaluate the system that includes a GIST action; this always uses the MRF model to properly update the class probabilities with GIST observations.
+This brings another boost in performance.
+All results are shown in \autoref{tab:results}.
+
+Additionally, we evaluated different settings of the discount parameter $\gamma$, and found that a mid-range value works best.
+We only report results for that value on the test set.
+\autoref{fig:weights} shows how changing $\gamma$ affects the learned weights: the GIST action is learned to never be taken in the greedy setting, because it does not nring any immediate detections results.
+In the reinforcement learning setting, however (higher $\gamma$), GIST is learned to be taken for its value in quickly refining the class presence probabilities.
 
@@
 Bounds & Random & Fixed Order & RL w/ MRF & w/ GIST  & Oracle \\ \hline
-(0,10) & 0.1191 & 0.2404      & 0.2664    & 0.2665    & 0.4638 \\ 
-(0,20) & 0.2497 & 0.3421      & 0.3781    & 0.3824    & 0.4878 \\ 
-(5,15) & 0      & 0           & 0         & 0         & 0      \\
+(0,10) & 0.119  & 0.240       & 0.266     & \textbf{0.267}    & 0.464 \\ 
+(0,20) & 0.250  & 0.342       & 0.378     & 0.382    & 0.488 \\ 
+(5,15) & 0.257  & 0.362       & 0.418     & 0.420    & 0.530 \\
 \end{tabular}
@@
 
-Figure~\ref{fig:results1} also shows the performance of our policy with the heuristic value function and two inference models: the MRF model and a simple fixed-order model that follows the priors.
-We can see that due to the dataset bias, the fixed-order policy performs well at first (the person class is disproportionately likely to be in the image), but is overtaken by the proper inference model as execution goes on.
-
-A notable difference between the MRF inference model and the fixed-order model was in the weights learned: while the fixed-order model learned weights onto the bias feature only, the MRF inference model learned weights onto a mix of the entropy and probability features
+\todo{something about setting values?}

### 2012-06-01 writeups/nips12/introduction.tex
draft for mario

@@
 
-In recent years, the computer vision field has converged on a general method for object detection, and a standard evaluation of results.
-In the evaluation ground truth, each object is assumed to belong to one of a fixed set of classes; its location is approximated by placing a bounding box around pixels belonging to it.
-Large datasets of such human annotations are used for evaluation of detection algorithms~\cite{pascal-voc-2010,imagenet_cvpr09}.
+The computer vision field has converged on a general method for object detection, and a standard evaluation of results.
+Efficiency is not a concern of the evaluation metrics, and the methods are not evaluated in an inherently multi-class setting.
+However, in most real-world applications of object recogniition, performance is time-sensitive and inherently tied to the many-class nature of the world.
 
-With few exceptions, current detection systems are not inherently multi-class.
-Instead, separate detectors are trained per class, and they are deployed and evaluated independently.
-The evaluation of multi-class performance consists of averaging the per-class metrics.
-State-of-the-art detection systems also do not generally make efficiency a goal.
+In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
+In large-scale detection system deployments, such as for image search, results need to be obtained quickly per image as the number of images to process is large and growing.
+
+In these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.
+Furthermore, the value of the answer depends on the target application.
 
 \begin{figure}[ht!]
-\center{\includegraphics[width=0.56\linewidth]
-    {../figures/evaluation_thumbs.png}}
-  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.}
-  \label{fig:evaluation}
+\center{\includegraphics[width=0.86\linewidth]
+    {../figures/figure1.pdf}}
+  \caption{
+A sample trace of our method.
+At each time step beginning at $t=0$, potential actions are considered according to their \emph{value}, and the one with the highest value is picked.
+The selected action is performed and returns observations, which influence the selection of the next action.
+The final evaluation of a detection episode is the area of the AP vs. Time curve between the start and end times.
+The value of an action is the expected value of the final evaluation if the action is taken and the policy continues to be followed, which allows actions without an immediate benefit to be scheduled.
+}
+  \label{fig:figure1}
 \end{figure}
-
-There are of course many applications of object recogniition for which performance truly is time-sensitive.
-In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
-In large-scale detection system deployments, such as for image search, results need to be obtained quickly per image as the number of images to process is large and growing.
-When processing large photo collection on end-user machines for immediate consumer navigation, the same is true.
-
-In all these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.
-Furthermore, the value of the answer depends largely on the target application.
 
@@
 The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
-The most rational detection strategy in such an environment should depend on all of these variables.
+The detection strategy to maximize profit in such an environment should depend on all of these variables.
 
@@
 \emph{What is the best performance we can get on a budget?}
-To answer it, we consider the evaluation metric of performance vs. time, shown in Figure~\ref{fig:evaluation} and discussed further in the text.
+To answer it, we consider the evaluation metric of performance vs. time, shown in Figure~\ref{fig:figure1} and discussed further in the text.
 
-Our system takes various detectors and classifiers as black boxes, and derives a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
+We present a method that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
+We are able to obtain better performance than baselines when there is less time available than is needed to run all detectors.

### 2012-06-01 writeups/nips12/nips2012.tex
draft for mario

@@
 \begin{abstract}
-In a large visual multi-class detection system, the problem of timeliness of results is crucial.
-We are motivated by situations where running all detectors would take an unacceptably long time, and that the best answer must be given by some deadline.
-Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
-Toward this goal, we formulate a dynamic policy guided by inference of the contents of the image to decide which detector to deploy next.
-We evaluate with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC object detection dataset.
+In a large visual multi-class detection framework, the problem of timeliness of results is crucial.
+We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
+Our method for multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
+Toward this goal, we formulate a dynamic, \emph{closed-loop} policy guided by inference of the contents of the image in order to decide which detector to deploy next.
+We evaluate our method with respect to performance in the novel Average Precision (AP) vs. Time evaluation on the widely used PASCAL VOC object detection dataset.
+With our method, if execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
+Overall, our method obtains at least $11\%$ better performance on the AP vs. Time evaluation.
 \end{abstract}
@@
 \input{evaluation.tex}
+
+\section{Conclusion}
+We presented a method for learning ``closed-loop'' policies for multi-class object recognition, given existing object detectors and classifiers and a metric to optimize.
+The method learns the optimal policy using reinforcement learning, by observing execution traces in training.
+If detection on an image is cut off after only half the detectors have been run, our method does $66\%$ better than random, and $14\%$ better than an intelligent baseline.
+
+As always with reinforcement learning problems, the setting of the reward function requires some manual work.
+Here, we derive it for the novel detection AP vs. Time evaluation that we suggest is most useful for evaluating efficiency in recognition.
+Although computation devoted to scheduling actions is much less significant than the computation due to running the actions, an interesting future research direction is to explicitly consider this decision-making cost.
 

### 2012-06-01 writeups/nips12/related.tex
draft for mario

@@
 
-We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains at least one, and often multiple, objects.
+We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains zero or more objects.
 Each object is labeled with exactly one category label $k \in \{1, \dots, K\}$.
@@
 Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Vedaldi2009,Vijayanarasimhan2011}.
-For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008b}.
+For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008a}.
 
@@
 
-A state-of-the-art detector builds upon a linear classifier on a gradient-based image representation, sped up with cascaded evaluation (see relevant paragraph further down) \cite{Felzenszwalb2010b}.
-Our system employs these detectors.
+\paragraph{Context}
+Context has a foundational role in vision.
+One source of context is the scene or other non-detector cues; the most common scene-level feature is the GIST \cite{Oliva2001a} of the image.
+For the commonly used PASCAL VOC dataset \cite{pascal-voc-2010}, GIST and other sources of context are quantitatively explored in~\cite{Divvala2009}.
 
-\paragraph{Context}
-Context has a long history in vision.
-One source of context is the scene or other non-detector cues; for the commonly used PASCAL dataset, these are quantitatively explored in~\cite{Divvala2009}. 
-The most common scene-level feature is the GIST \cite{Oliva2001a} of the image; it provides reasonable information for scene classification \cite{Xiao2010a}.
-
-Another source is inter-object context, used for detection in a random field setting in~\cite{Torralba2004}.
-Exploiting this information has shown to improve classification as well as detection tasks.
+Another source is inter-object context, shown to be useful for improving detection \cite{Torralba2004}.
 A critical summary of the main approaches to using context for object and scene recognition is given in \cite{Galleguillos2010}.
@@
 \paragraph{Multi-Class Detection}
-Inherently multi-class detection has its own line of work, which focuses largely on making detection time sublinear in the number of classes, through sharing features~\cite{Torralba2007,Fan2005,Razavi2011}.
-A proposed post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression~\cite{Desai2009}.
+Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005,Razavi2011}.
+A proposed post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression \cite{Desai2009}.
 
 \paragraph{Cascades}
-An early success in efficient object detection used simple, fast features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime~\cite{Viola2001}.
+An early success in efficient object detection used simple, fast features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime \cite{Viola2001}.
 Although the simple features and classifiers of this method have been surpassed by more complex detectors, the idea of cascading classifier evaluations is still often used.
@@
 \paragraph{Anytime Algorithms and Active Classification}
-Although an important concept, anytime performance in vision systems is a surprisingly little-explored idea \cite{Shlomo Zilberstein}.
+Anytime performance in vision systems is a surprisingly little-explored idea.
 A recent application to the problem of visual detection picks features with maximum value of information in a Hough-voting framework, and explicitly evaluates performance vs.
@@
 This line of work is closest to our approach.
-Most commonly, the scheduling is greedy with respect to some quantity such as expected information gain.
+Most commonly, the scheduling in these approaches is greedy with respect to some quantity such as expected information gain.
 
-In contrast, we are able to learn policies that take actions without any immediate such reward.
-We aim for a general system that can take black-box detectors and classifiers, and learn its policy from its own trial execution traces, and can be adapted to different loss functions.
+In contrast, we are able to learn policies that take actions without any immediate reward.

### 2012-06-01 writeups/nips12/technical.tex
draft for mario

@@
 \section{Multi-class Recognition Policy} \label{sec:tech}
+
 Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs a list of multi-class detection results by running detector and other \emph{actions} sequentially.
@@
 
-As shown in Figure~\ref{fig:evaluation}, the system is given two times: the setup time $T_s$ and deadline $T_d$.
+As shown in Figure~\ref{fig:figure1}, the system is given two times: the setup time $T_s$ and deadline $T_d$.
 From the setup time to the deadline, we want to obtain the best possible answer if stopped at any given time.
-This corresponds to the general notion of \emph{Anytime} algorithms, and is motivated by desired flexibility in the system.
-
-A single-number metric that corresponds to this objective is simply the ratio of the area captured under the curve to the total area between the start and deadline bounds.
+A single-number metric that corresponds to this objective is the area captured under the curve between the start and deadline bounds, normalized by the total area possible.
 We evaluate policies by this more robust metric and not simply by the final performance at deadline time for the same reason that Average Precision is used instead of a fixed Precision vs.
-Recall point.
+Recall point in the conventional evaluations.
 
 \subsection{Sequential Execution}
-An ``open-loop'' policy takes actions in a sequence that does not depend on observations received from previous actions.
-The common classifier cascade \cite{Viola2001} is an example.
-In contrast, our goal is to learn a dynamic, or ``closed-loop,'' policy, which would exploit the signal in inter-object and scene context for a maximally efficient path through the actions.
+An \emph{open-loop} policy takes actions in a sequence that does not depend on observations received from previous actions.
+The common classifier cascade is an example \cite{Viola2001}.
+In contrast, our goal is to learn a dynamic, or \emph{closed-loop}, policy, which would exploit the signal in scene and inter-object context for a maximally efficient path through the actions.
 
@@
 
-A recognition \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial state $s^0$ and action $a^0$ to the next pair $(s^1,a^1)$, and so on until $t$ exceeds $T_d$.
+A recognition \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial state $s^0$ and action $a^0$ to the next pair $(s^1,a^1)$, and so on until $(s^J,a^J)$, where $J$ is the last step of the process with $t \le T_d$.
 At that point, the policy is terminated, and a new episode can begin on a new image.
 
-\begin{table}[h!]
-\centering
-\caption{Summary of the notation.}
-\label{tab:notation}
-\begin{tabular}{|l|l|}
-  \hline
-  $\mathcal{I}$ & image \\
-  $C_k$         & presence of class $k \in \{1,\dots,K\}$ \\ 
-  $t$           & time into episode \\ 
-  $T_s$, $T_d$  & start and deadline times \\ 
-  $s^j$         & belief state at step $j$ \\ 
-  $\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
-  $\mathcal{A}$ & set of actions $a$\\ 
-  \comment{$\mathcal{F}$ & set of featurization actions \\}
-  \comment{$\mathcal{L}$ & set of classification actions\\}
-  $o_i$         & a real-valued observation upon executing $a_i \in \mathcal{A}$\\
-  $\mathcal{O}$ & set of executed actions\\
-  $\mathbf{o}$  & set of observations $\{o_i | a_i \in \mathcal{O}\}$\\
-  $c(a_i)$        & cost of executing $a_i$, in units of $t$\\
-  \hline
-\end{tabular}\end{table}
+The specific actions we consider in the following exposition are detector actions $a_{{det}_i}$, where ${det}_i$ is a detector class $C_i$, and a scene-level context action $a_{gist}$, which updates the probabilities of all classes.
 
-\subsection{Selecting actions based on expected reward} \label{sec:value}
+% \begin{table}[h!]
+% \centering
+% \caption{Summary of the notation.}
+% \label{tab:notation}
+% \begin{tabular}{|l|l|}
+%   \hline
+%   $\mathcal{I}$ & image \\
+%   $C_k$         & presence of class $k \in \{1,\dots,K\}$ \\ 
+%   $t$           & time into episode \\ 
+%   $T_s$, $T_d$  & start and deadline times \\ 
+%   $s^j$         & belief state at step $j$ \\ 
+%   $\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
+%   $\mathcal{A}$ & set of actions $a$\\ 
+%   \comment{$\mathcal{F}$ & set of featurization actions \\}
+%   \comment{$\mathcal{L}$ & set of classification actions\\}
+%   $o_i$         & a real-valued observation upon executing $a_i \in \mathcal{A}$\\
+%   $\mathcal{O}$ & set of executed actions\\
+%   $\mathbf{o}$  & set of observations $\{o_i | a_i \in \mathcal{O}\}$\\
+%   $c(a_i)$        & cost of executing $a_i$, in units of $t$\\
+%   \hline
+% \end{tabular}\end{table}
+
+\subsection{Selecting actions} \label{sec:value}
 As our goal is to pick actions dynamically, we want a function $Q(s,a): S \times \mathcal{A} \mapsto \mathbb{R}$, where $S$ is the space of all possible states, to assign a value to a potential action, given the current state of the decision process.
@@
 
-Although the action space $\mathcal{A}$ is quite manageable, consisting of the detectors and classifier we would like to run on the image, the space of possible states $B$ is infinite.
-Therefore we cannot learn a tabular representation of $Q(s,a)$, and so use function approximation to represent it \cite{Sutton1998}.
+Although the action space $\mathcal{A}$ is quite manageable, consisting of the detectors and classifier we would like to run on the image, the space of possible states $S$ is infinite.
+Therefore we cannot learn a tabular representation of $Q(s,a)$, and must use function approximation to represent it \cite{Sutton1998}.
 We featurize the state-action pair and assume linear structure:
@@
 
-The policy's performance at time $t$ is determined by the detections that are part of the set of observations $\mathbf{o}$ at the last state $s^j$ before $t$.
-Detection results of unobserved classes are an empty set.
-Therefore, the final AP vs. Time evaluation of the episode is a function of the history of execution $h^0=s^0,s^1,\dots,s^J$, where $J$ is the last step of the process with $t \le T_d$.
-We call the final evaluation function $eval(h^0,T_s,T_d)$, and it is precisely the area under the AP vs.
-Time curve (normalized by total possible area) between $T_s$ and $T_d$, as determined by the detections in $\mathbf{o^j}$ for all steps $j$ in the episode $h$.
+The policy's performance at time $t$ is determined by the detections that are part of the set of observations $\mathbf{o}^j$ at the last state $s^j$ before $t$.
+Therefore, the final AP vs. Time evaluation of an episode is a function of the history of execution $h=s^0,s^1,\dots,s^J$.
+
+We refer to the final evaluation function as $eval(h,T_s,T_d)$, and it is precisely the area under the AP vs.
+Time curve between $T_s$ and $T_d$ (normalized by total possible area), as determined by the detections in $\mathbf{o}^j$ for all steps $j$ in the episode.
 
@@
   \includegraphics[width=0.56\linewidth]{../figures/apvst_expl.pdf}
-  \caption{A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action.
+  \caption{\todo{what text here?} A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action.
 The figure shows this analysis for the action highlighted in orange.}
@@
 
-As shown in \autoref{fig:rewards}, the evaluation function is additive per action, as each action can generate detections that either raise or lower the AP of all detections so far: ($\Delta ap$), and takes a certain time: $t$.
-From these, we can find the area under the curve that was contributed by the action.
+As shown in \autoref{fig:rewards}, this evaluation function is additive per action, as each action can generate detections that either raise or lower the AP of all detections so far ($\Delta ap$) and takes a certain time ($\Delta t$).
+From these and $T_s$ and $T_d$, we can find the area under the curve that was contributed by the action.
 
@@
 \begin{align}\label{eq:advanced}
-R(s^j,a_i) = \frac{\Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)}{(1-\text{ap}^j)t_T^j}
+R(s^j,a_i) = \Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)
 \end{align}
 where $t_T^j$ and $\text{ap}^j$ are the time left until deadline and the AP at state $s^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.
-
-\todo{discuss the raw vs. the normalized area, saying we'll try both}
+(For clarity of exposition, we do not account for $T_s$ here.)
 
@@
 \begin{align}
-eval(h^0) = \sum_{j=0}^J R(s_j,a^{j})
+eval(h) = \sum_{j=0}^J R(s^j,a^j)
 \end{align}
@@
 \begin{align} \label{eq:recursive_value}
-Q(s^j,a_i) = \mathbb{E}_{s^{j+1}} [R(s^j,a_i) + \gamma Q(s^{j+1},\pi(s^{j+1}))]
+Q^\pi(s^j,a_i) = \mathbb{E}_{s^{j+1}} [R(s^j,a_i) + \gamma Q\pi(s^{j+1},\pi(s^{j+1}))]
 \end{align}
@@
 
-\comment{
-Specifically, we collect such samples to the end of the episode, and are thus able to compute the actual discounted sum of rewards for $Q(s^j,a_i)$:
-\begin{align}
-Q(s^j,a_i) = \theta_\pi^\top \phi(s,a_i) = \sum_{i=0}^{J-j} \lambda^i R(b_{j+i},a^{j+i})
-\end{align}
-}
-
 Learning the policy is then a problem of repeatedly gathering samples with the current policy, minimizing the error between the discounted reward to the end of the episode as predicted by our current $Q(s^j,a_i)$ and the actual values gathered, and updating the policy with the resulting weights.
-This is standard generalized policy iteration, or more specifically fitted Q-iteration \cite{Sutton1998,Ernst2005}.
+This is fitted Q-iteration, a variant of generalized policy iteration \cite{Ernst2005,Sutton1998}.
 
@@
 
-One meta-parameter of the approach is the discount $\gamma$.
-With $\gamma=0$, the value function is determined entirely by the immediate reward; learning in this case can only result in completely greedy policies.
-With $\gamma=1$, the value function is determined by the expected rewards to the end of the episode, which is an approximation to the final evaluation metric.
-However, the highest value for $\gamma$ is not necessarily best, due to the interplay between the expressive power of the value function and the actual state transition behavior of the world.
-We experiment with several values of $\gamma$, and find a mid-level value of $0.4$ to work best.
+A meta-parameter of the approach is the discount $\gamma$.
+With $\gamma=0$, the value function is determined entirely by the immediate reward.
+Learning in this case can only result in completely greedy policies.
+
+With $\gamma=1$, the value function is determined by the expected rewards to the end of the episode, and so should be a close approximation to the final evaluation metric.
+However, the highest value for $\gamma$ is not necessarily best if the action-value function is not expressive enough to represent the actual state transition behavior of the world.
+We experiment with several values of $\gamma$, and find a mid-level value ($0.4$) to work best.
 
@@
 Since we want to be able to learn a dynamic policy, the observations $\mathbf{o}$ that are part of the state $s$ should play a role in determining the value of a potential action.
+
 We include the following quantities as features $\phi(s,a)$:
@@
 
-Additionally, we include the mean and maximum entropies of all classes, and time features that represent the times until start and deadline.
-To formulate learning the policy as a single regression problem, we represent the features in block form, where $\phi(s,a_i)$ is a vector of size $F|\mathcal{A}|$, with $F=47$ for $20$ classes and the features as described, with all values set to $0$ except for the block corresponding to $a_i$.
+Additionally, we include the mean and maximum entropies of all classes, time features that represent the times until start and deadline, and the expected time (cost) of the action, for a total of $F$ features.
 
-Jumping ahead, we visualize the learned weights on these features in \autoref{fig:weights}, reshaped to a matrix of size $|\mathcal{A}| \times F$.
+We note that this setup is commonly used to solve Markov Decision Processes \cite{Sutton1998}.
+There are two related limitations of MDPs when it comes to most systems of interesting complexity, however: the state has to be functionally approximated instead of exhaustively enumerated; and some aspects of the state are not observed, making the problem a Partially Observed MDP (POMDP), for which exact solution methods are intractable for all but rather small problems \cite{Roy2002}.
+
+There isn't much to do about the necessity of approximating the state but design good features.
+Our initial solution to the partial observability problem is to include uncertainty features into the feature representation to \emph{augment} the MDP \cite{Kwok2004}.
+
+To formulate learning the policy as a single regression problem, we represent the features in block form, where $\phi(s,a_i)$ is a vector of size $F|\mathcal{A}|$, with all values set to $0$ except for the block corresponding to $a_i$.
+
+As an illustration, we visualize the learned weights on these features in \autoref{fig:weights}, reshaped such that each row shows the weights learned for an action, in order.
+The featurization for the $a_{gist}$ scene-context action, which concerns all classes, omits the first $P(C_a)$ feature.
 
@@
 \centering
-\includegraphics[width=0.87\linewidth]
-    {../figures/weights.pdf}
-\caption{Weights \todo{describe}}
+\includegraphics[width=0.87\linewidth]{../figures/weights.pdf}
+\caption{Weights \todo{describe. can talk about the person-class weights, the role of the time weights. how you can see the co-occurrence matrix in the weights}}
 \label{fig:weights}
@@
 
-\subsection{Updating with observations} \label{sec:updating}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.56\linewidth]{../figures/mrf_w_gist.pdf}
-\caption{
-\todo{get rid of this figure?}
-The MRF inference model used in our system. The shaded nodes represent two actions that have already been taken; their observations have been recorded.
-}
-\label{fig:model}
-\end{figure}
+% \subsection{Updating with observations} \label{sec:updating}
+% \begin{figure}[h!]
+% \centering
+% \includegraphics[width=0.56\linewidth]{../figures/mrf_w_gist.pdf}
+% \caption{
+% \todo{get rid of this figure?}
+% The MRF inference model used in our system. The shaded nodes represent two actions that have already been taken; their observations have been recorded.
+% }
+% \label{fig:model}
+% \end{figure}
 
@@
 In the \emph{direct} way, $P(C_i|\mathbf{o}) = score(C_i)$ if $\mathbf{o}$ includes the observations for class $C_i$ and $P(C_i|\mathbf{o}) = P(C_i)$ otherwise.
+This means that an observation of class $i$ does not influence the estimated probability of any class but $C_i$.
+$score(C_i)$ for $a_{{det}_i}$ is obtained by training a probabilistic classifier on the detections output.
+$score(C_i)$ for $a_{gist}$ is obtained by training probabilistic classifiers on the GIST feature, for all classes.
 
-In the \emph{MRF} way, we employ a pairwise fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}, with the observation nodes set to $score(C_i)$ appropriately, or considered unobserved.
+In the \emph{MRF} way, we employ a pairwise fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:figure1}, with the observation nodes set to $score(C_i)$ appropriately, or considered unobserved.
 
@@
 As exact inference is generally intractable in this model, we use Loopy Belief Propagation; although it does not provide general convergence guarantees, it has been shown to work well empirically on similar tasks \cite{Desai2009}.
-
-\todo{rework the below, and also explain how GIST works}
-The $L_i$ variables are discretized from real-valued responses of a classifier on the detections output by the deformable part-model detector we employ (see Section~\ref{sec:tech}).
-The classifier is a linear SVM on the top two max detection scores in the list of detections.
-The responses are discretized per variable based on the distribution of the scores on the training dataset.

### 2012-06-01 writeups/nips12/introduction.tex
edits of abstract, intro, related work
some squeezing

new "myparagraph" environment which is more space economic

@@
 Efficiency is not a concern of the evaluation metrics, and the methods are not evaluated in an inherently multi-class setting.
-However, in most real-world applications of object recogniition, performance is time-sensitive and inherently tied to the many-class nature of the world.
+However, in most real-world applications of object recognition, performance is time-sensitive and inherently tied to the many-class nature of the world.
 

### 2012-06-01 writeups/nips12/nips2012.tex
edits of abstract, intro, related work
some squeezing

new "myparagraph" environment which is more space economic

@@
 \newcommand{\comment}[1]{}
+
+\newcommand{\myparagraph}[1]{\vspace{-0.1cm}{\bf #1}}
 
@@
 Toward this goal, we formulate a dynamic, \emph{closed-loop} policy guided by inference of the contents of the image in order to decide which detector to deploy next.
+In contrast to previous work, our method significantly diverts from the predominant greedy strategies and therefore learns to employ actions without any immediate reward for the goal of detection.
 We evaluate our method with respect to performance in the novel Average Precision (AP) vs. Time evaluation on the widely used PASCAL VOC object detection dataset.
 With our method, if execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
-Overall, our method obtains at least $11\%$ better performance on the AP vs. Time evaluation.
+Overall, our method obtains at least $11\%$ better performance on the AP vs.
+Time evaluation.
+At time of publication we will make our code available, which is easily extendible to new detectors, classifiers, tasks and reward functions due to the modular nature of our formulation.
 \end{abstract}

### 2012-06-01 writeups/nips12/related.tex
edits of abstract, intro, related work
some squeezing

new "myparagraph" environment which is more space economic

@@
 
-\paragraph{Single-class detection}
+\myparagraph{Single-class detection}
 The best recent performance has come from detectors that use gradient-based features to represent objects as either a collection of local patches or as object-sized windows \cite{Dalal2005,Lowe2004}.
 Classifiers are then used to distinguish between featurizations of a given class and all other possible contents of an image window.
-
+%
 Window proposal is often done exhaustively over the image space, as a ``sliding window''.
@@
 For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008a}.
-
+%
 None of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal.
@@
 
-\paragraph{Context}
+\myparagraph{Context}
 Context has a foundational role in vision.
@@
 
-\paragraph{Multi-Class Detection}
+\myparagraph{Multi-Class Detection}
 Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005,Razavi2011}.
@@
 
-\paragraph{Cascades}
+\myparagraph{Cascades}
 An early success in efficient object detection used simple, fast features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime \cite{Viola2001}.
@@
 Most recently, cyclic optimization has been applied to optimize cascades with respect to feature computation cost as well as classifier performance \cite{Chen2012}.
-
 However, cascades are not dynamic policies---they cannot change the order of execution based on observations obtained during execution, which is our goal.
 
-\paragraph{Anytime Algorithms and Active Classification}
+\myparagraph{Anytime Algorithms and Active Classification}
 Anytime performance in vision systems is a surprisingly little-explored idea.
@@
 time \cite{Vijayanarasimhan2010}.
-
 There has also been work on active classification \cite{Gao2011} and active sensing \cite{Yu2009}, in which intermediate results are considered in order to decide on the next classification step.
@@
 Most commonly, the scheduling in these approaches is greedy with respect to some quantity such as expected information gain.
-
 In contrast, we are able to learn policies that take actions without any immediate reward.

### 2012-06-01 writeups/nips12/evaluation.tex
oops littel fix
changes and squeezing … also squeeze images

@@
 We establish the first baseline for our system by selecting actions randomly at each step.
-As shown in Figure~\ref{fig:results1}, this \textbf{Random} policy results in a roughly linear gain of AP vs. time.
+As shown in Figure \autoref{fig:results1}, this \textbf{Random} policy results in a roughly linear gain of AP vs. time.
 This is expected: the detectors are capable of obtaining a certain level of performance; if half the detectors are run, the expected performance level is half of the maximum level.
@@
 
-In \autoref{fig:results1}, we can see that due to the dataset bias, the fixed-order policy performs well at first (as can be seen in \autoref{fig:dataset_stats}, the person class is disproportionately likely to be in the image), but is significantly overtaken by our model as execution goes on.
+In Figure \autoref{fig:results1}, we can see that due to the dataset bias, the fixed-order policy performs well at first (as can be seen in \autoref{fig:dataset_stats}, the person class is disproportionately likely to be in the image), but is significantly overtaken by our model as execution goes on.
 
@@
 We only report results for that value on the test set.
-\autoref{fig:weights} shows how changing $\gamma$ affects the learned weights: the GIST action is learned to never be taken in the greedy setting, because it does not nring any immediate detections results.
+\autoref{fig:weights} shows how changing $\gamma$ affects the learned weights: the GIST action is learned to never be taken in the greedy setting, because it does not bring any immediate detections results.
 In the reinforcement learning setting, however (higher $\gamma$), GIST is learned to be taken for its value in quickly refining the class presence probabilities.
@@
 \begin{tabular}{|l|l|l|l|l|l|}
-\\ \hline \\
+%\\ \hline \\
+\hline
 Bounds & Random & Fixed Order & RL w/ MRF & w/ GIST  & Oracle \\ \hline
@@
 (0,20) & 0.250  & 0.342       & 0.378     & 0.382    & 0.488 \\ 
-(5,15) & 0.257  & 0.362       & 0.418     & 0.420    & 0.530 \\
+(5,15) & 0.257  & 0.362       & 0.418     & 0.420    & 0.530 \\ \hline
 \end{tabular}

### 2012-06-01 writeups/nips12/nips2012.tex
changes and squeezing … also squeeze images

@@
 \usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage{subfigure}
 
@@
 If detection on an image is cut off after only half the detectors have been run, our method does $66\%$ better than random, and $14\%$ better than an intelligent baseline.
+In particular, our method learns to take action with no intermediate reward in order to improve the overall performance of the system.
 
-As always with reinforcement learning problems, the setting of the reward function requires some manual work.
+As always with reinforcement learning problems, the defining the reward function requires some manual work.
 Here, we derive it for the novel detection AP vs. Time evaluation that we suggest is most useful for evaluating efficiency in recognition.
 Although computation devoted to scheduling actions is much less significant than the computation due to running the actions, an interesting future research direction is to explicitly consider this decision-making cost.
+
+At time of publication, we will release the code of our modular framework, that allows for easy incorporation of other classifiers and detectors on different tasks and rewards.
 

### 2012-06-01 synthetic/dataset_policy.py
before pumping up actions to 60

@@ -16,6 +16,7 @@ from synthetic.bounding_box import BoundingBox
 from synthetic.belief_state import BeliefState
 from synthetic.fastinf_model import FastinfModel
 import matplotlib.pyplot as plt
+from synthetic.ext_detector_regions import ExternalDetectorRegions
 
 class ImageAction:
   def __init__(self, name, obj):
@@ -119,7 +120,7 @@ class DatasetPolicy:
         self.fastinf_model_name='GIST'
       elif self.detectors == ['gist','csc_default']:
         self.fastinf_model_name='GIST_CSC'
-      elif self.detectos == ['csc_regions']:
+      elif self.detectors == ['csc_regions']:
         self.fastinf_model_name='CSC_regions'
       else:
         raise RuntimeError("""
@@ -167,6 +168,14 @@ class DatasetPolicy:
           all_dets_for_cls = all_dets.filter_on_column('cls_ind',cls_ind,omit=True)
           det = ExternalDetector(
             dataset, self.train_dataset, cls, all_dets_for_cls, detector)
+          actions.append(ImageAction('%s_%s'%(detector,cls), det))
+      elif detector == 'csc_regions':
+        all_dets = self.load_ext_detections(dataset, detector)
+        for cls in dataset.classes:
+          cls_ind = dataset.get_ind(cls)
+          all_dets_for_cls = all_dets.filter_on_column('cls_ind',cls_ind,omit=True)
+          det = ExternalDetectorRegions(
+            dataset, self.train_dataset, cls, all_dets_for_cls, detector, '1big_2small', 0.5)
           actions.append(ImageAction('%s_%s'%(detector,cls), det))
 
       else:

### 2012-06-01 synthetic/detector.py

@@ -46,14 +46,14 @@ class Detector(object):
     if detector_config:
       self.config.update(detector_config)
 
-  def get_observations(self,image):
+  def get_observations(self,image, *args):
     """
     Return a dict of
     - dets
     - score
     """
-    dets, dt_dets = self.detect(image)
-    score, dt_score = self.compute_score(image)
+    dets, dt_dets = self.detect(image, *args)
+    score, dt_score = self.compute_score(image, *args)
     dt = dt_dets+dt_score
     return {'dets': dets, 'dt_dets': dt_dets,
             'score': score, 'dt_score': dt_score,

### 2012-06-01 synthetic/ext_detector_regions.py

@@ -94,6 +94,8 @@ class ExternalDetectorRegions(ExternalDetector):
     '''
     ExternalDetector.__init__(self, dataset, train_dataset, cls, dets, detname)
     self.region_model = RegionModel(rtype, args)
+    if self.classif.svm == None:
+      raise RuntimeError('SVM in External Detector Regions is None')
     
   def convert_wh2scale(self, img, x, y, w, h):
     W, _ = img.size    
@@ -132,7 +134,7 @@ class ExternalDetectorRegions(ExternalDetector):
     img_ind = self.dataset.get_img_ind(image)
     dets = self.dets.filter_on_column('img_ind',img_ind,omit=True) # This function already creates a copy
     self.filter_dets_for_reg_id(image, dets, region_id) # At this position choose only the detections that fall into the desired region
-    return ExternalDetector.detect(self, image, astable, dets) # Now call the regular external detector with just those detections
+    return super(ExternalDetectorRegions, self).detect(image, astable, dets) # Now call the regular external detector with just those detections
   
   def compute_score(self, image, region_id, oracle=False):
     """
@@ -142,8 +144,8 @@ class ExternalDetectorRegions(ExternalDetector):
     """
     img_ind = self.dataset.get_img_ind(image)
     dets = self.dets.filter_on_column('img_ind',img_ind,omit=True)
-    self.filter_dets_for_reg_id(image, dets, region_id) # At this position choose only the detections that fall into the desired region    
-    return ExternalDetector.compute_score(self, image, oracle, dets) # Now call the regular external detector with just those detections 
+    self.filter_dets_for_reg_id(image, dets, region_id) # At this position choose only the detections that fall into the desired region
+    return super(ExternalDetectorRegions, self).compute_score(image, oracle, dets) # Now call the regular external detector with just those detections 
   
   def get_number_regions(self):
     return self.region_model.get_number_regions()
@@ -162,6 +164,7 @@ def run():
   dets = all_dets.filter_on_column('cls_ind',cls_ind,omit=True)  
   ext_det = ExternalDetectorRegions(dataset, train_dataset, cls, dets, detector, rtype, args)
   img = dataset.images[13]  # Just some random image...where did the get_image_by_name go?
+  embed()
   print img.size
   print ext_det.detect(img, 0)
   print ext_det.detect(img, 1)

### 2012-06-01 writeups/nips12/technical.tex
oops littel fix
changes and squeezing … also squeeze images
fixed figure1 and little mistake in technical

@@
 The specific actions we consider in the following exposition are detector actions $a_{{det}_i}$, where ${det}_i$ is a detector class $C_i$, and a scene-level context action $a_{gist}$, which updates the probabilities of all classes.
-
-% \begin{table}[h!]
-% \centering
-% \caption{Summary of the notation.}
-% \label{tab:notation}
-% \begin{tabular}{|l|l|}
-%   \hline
-%   $\mathcal{I}$ & image \\
-%   $C_k$         & presence of class $k \in \{1,\dots,K\}$ \\ 
-%   $t$           & time into episode \\ 
-%   $T_s$, $T_d$  & start and deadline times \\ 
-%   $s^j$         & belief state at step $j$ \\ 
-%   $\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
-%   $\mathcal{A}$ & set of actions $a$\\ 
-%   \comment{$\mathcal{F}$ & set of featurization actions \\}
-%   \comment{$\mathcal{L}$ & set of classification actions\\}
-%   $o_i$         & a real-valued observation upon executing $a_i \in \mathcal{A}$\\
-%   $\mathcal{O}$ & set of executed actions\\
-%   $\mathbf{o}$  & set of observations $\{o_i | a_i \in \mathcal{O}\}$\\
-%   $c(a_i)$        & cost of executing $a_i$, in units of $t$\\
-%   \hline
-% \end{tabular}\end{table}
 
@@
 \item[$P(C_a)$] The prior probability of the class that corresponds to the detector of action $a$
-\item[$P(C_0|\mathbf{o}) \ldots P(C_1|\mathbf{o})$] The probabilities of all classes, conditioned on the current set of observations.
-\item[$H(C_0|\mathbf{o}) \ldots H(C_1|\mathbf{o})$] The entropies of all classes, conditioned on the current set of observations.
+\item[$P(C_0|\mathbf{o}) \ldots P(C_K|\mathbf{o})$] The probabilities of all classes, conditioned on the current set of observations.
+\item[$H(C_0|\mathbf{o}) \ldots H(C_K|\mathbf{o})$] The entropies of all classes, conditioned on the current set of observations.
 \end{description}
@@
 \centering
-\includegraphics[width=0.87\linewidth]{../figures/weights.pdf}
+\subfigure[Greedy]{\includegraphics[width=0.49\linewidth]{../figures/weights_greedy}}
+\subfigure[RL]{\includegraphics[width=0.49\linewidth]{../figures/weights_rl}}
+% \includegraphics[width=0.87\linewidth]{../figures/weights.pdf}
 \caption{Weights \todo{describe. can talk about the person-class weights, the role of the time weights. how you can see the co-occurrence matrix in the weights}}
@@
 
-% \subsection{Updating with observations} \label{sec:updating}
+\subsection{Updating with observations} \label{sec:updating}
 % \begin{figure}[h!]
@@
 
-The bulk of our feature representation is formed by probability of individual class occurrence, conditioned on the observations so far: $P(C_0|\mathbf{o}) \ldots P(C_1|\mathbf{o})$.
+The bulk of our feature representation is formed by probability of individual class occurrence, conditioned on the observations so far: $P(C_0|\mathbf{o}) \ldots P(C_K|\mathbf{o})$.
 This allows the action-value function to learn correlations between presence of different classes, and so the policy can look for the most probable classes given the observations.

### 2012-06-01 synthetic/dataset_policy.py
temp couple of lines of code to generate samples to plot execution traces

@@ -315,8 +315,10 @@ class DatasetPolicy:
       dets,clses,samples = self.run_on_image(images[i],dataset,epsilon=epsilon)
       all_dets.append(dets)
       all_clses.append(clses)
-      if sample_size>0:
-        all_samples += samples
+      #if sample_size>0:
+      #  all_samples += samples
+      # TODO: TEMP
+      all_samples += samples
     safebarrier(comm)
 
     # Aggregate the results
@@ -346,6 +348,8 @@ class DatasetPolicy:
       if not sample_size > 0:
         np.save(det_filename,dets_table)
         np.save(cls_filename,clses_table)
+        # TODO: TEMP
+        np.save(det_filename+'_samples.npy',all_samples)
 
       # Save the fastinf cache
       # TODO: turning this off for now

### 2012-06-01 synthetic/dataset_policy.py
oops mpi bug

@@ -349,7 +349,7 @@ class DatasetPolicy:
         np.save(det_filename,dets_table)
         np.save(cls_filename,clses_table)
         # TODO: TEMP
-        np.save(det_filename+'_samples.npy',all_samples)
+        np.save(det_filename+'_samples.npy',final_samples)
 
       # Save the fastinf cache
       # TODO: turning this off for now

### 2012-06-01 synthetic/tasks/plot_trajectories.py

@@ -1,0 +1,33 @@
+from pandas import DataFrame
+from pylab import *
+
+def plot_order(samples,name,filename):
+  df = DataFrame({
+    'img': [s.img_ind for s in samples],
+    'action': [s.action_ind for s in samples],
+    't': [s.t+s.dt for s in samples]
+    })
+  print(name)
+  print("Num samples: %d"%df.shape[0])
+  fixed_order = [14,  6,  8, 11, 17,  7,  2, 12, 19, 15, 10, 18,  4,  1, 13,  0,  5,  3,  9, 16]
+  fig = plt.figure()
+  ax = fig.add_subplot(111)
+  for img in df.img.unique():
+    a = (df[df.img==img].action)
+    # change to linear for the fixed order
+    a = [fixed_order.index(a) for a in a]
+    t = (df[df.img==img].t)
+    ax.plot(t,a,'s-',alpha=0.2)
+    ax.set_yticklabels([str(d) for d in fixed_order])
+    ax.set_ylabel('Action Index')
+    ax.set_xlabel('Time (s)')
+    title(name)
+  plt.show(fig)
+  fig.savefig(filename)
+
+dirname = '/Users/sergeyk/work/timely/data/results/evals/full_pascal_test_120/'
+samples = np.load(dirname+'fixed_order_csc_default_0-20_manual_1_det_actual_ap_may29/cached_dets.npy_samples.npy')
+plot_order(samples,'Fixed Order','./tasks/trajectories_fixed_order.png')
+
+samples = np.load(dirname+'fastinf_csc_default_0-20_rl_half_auc_ap_raw_may29/cached_dets.npy_samples.npy')
+plot_order(samples,'RL w/ MRF','./tasks/trajectories_rl_mrf.png')

### 2012-06-01 synthetic/belief_state.py
regions policies run through, just the region MRFs seems to be wrong :/

@@ -15,7 +15,7 @@ class BeliefState(object):
   ngram_modes = ['no_smooth','backoff']
   accepted_modes = ngram_modes+['random','fixed_order','fastinf']
 
-  def __init__(self,dataset,actions,mode='fixed_order',bounds=None,model=None,fastinf_model_name='perfect'):
+  def __init__(self,dataset,actions,mode='fixed_order',bounds=None,model=None,fastinf_model_name='perfect',num_regions=1):
     assert(mode in self.accepted_modes)
     self.mode = mode
     self.dataset = dataset
@@ -53,9 +53,12 @@ class BeliefState(object):
         assert(isinstance(model,FastinfModel))
         self.model = model
       else:
-        self.model = FastinfModel(dataset, self.fastinf_model_name, self.num_obs_vars)
+        self.model = FastinfModel(dataset, self.fastinf_model_name, self.num_obs_vars, num_regions=num_regions)
     else:
       raise RuntimeError("Unknown mode")
+    if not self.model.num_regions == 3:
+      raise RuntimeError('region number isnt correct')
+    
     self.reset()
     self.orig_p_c = self.get_p_c()
 
@@ -115,7 +118,7 @@ class BeliefState(object):
     #self.full_feature = self.compute_full_feature()
 
   num_time_blocks = 1
-  num_features = num_time_blocks * 47
+  num_features = num_time_blocks * 127
   # [P(C) [P(C_i|O) for all i] [H(C_i|O) for all i] mean_entropy max_entropy t/S (1-t/S) t/T (1-t/T)]
   def compute_full_feature(self):
     """
@@ -153,7 +156,6 @@ class BeliefState(object):
         time_ratio*np.ones(len(self.actions)),
         1.-time_ratio*np.ones(len(self.actions))
       )).T
-
     feat = np.hstack((
         np.atleast_2d(orig_p_c).T, p_c, h_c, rest))
 
@@ -162,6 +164,7 @@ class BeliefState(object):
     # all the time, without worrying about actions that have been taken:
     # the best it will be able to do for those is 0
     feat[np.flatnonzero(self.taken),:] = 0
+    self.num_features = feat.shape[1]
     return feat
 
   def block_out_action(self, full_feature, action_ind=-1):

### 2012-06-01 synthetic/dataset_policy.py

@@ -172,11 +172,12 @@ class DatasetPolicy:
       elif detector == 'csc_regions':
         all_dets = self.load_ext_detections(dataset, detector)
         for cls in dataset.classes:
-          cls_ind = dataset.get_ind(cls)
-          all_dets_for_cls = all_dets.filter_on_column('cls_ind',cls_ind,omit=True)
-          det = ExternalDetectorRegions(
-            dataset, self.train_dataset, cls, all_dets_for_cls, detector, '1big_2small', 0.5)
-          actions.append(ImageAction('%s_%s'%(detector,cls), det))
+          for region in range(3):
+            cls_ind = dataset.get_ind(cls)
+            all_dets_for_cls = all_dets.filter_on_column('cls_ind',cls_ind,omit=True)
+            det = ExternalDetectorRegions(
+              dataset, self.train_dataset, cls, all_dets_for_cls, detector, region, '1big_2small', 0.5)
+            actions.append(ImageAction('%s_%s_%d'%(detector,cls, region), det))
 
       else:
         raise RuntimeError("Unknown mode in detectors: %s"%self.detectors)
@@ -652,12 +653,15 @@ class DatasetPolicy:
 
     # If we have previously run_on_image(), then we already have a reference to an inf_model
     # Otherwise, we make a new one and store a reference to it, to keep it alive
+    regions = 1
+    if self.fastinf_model_name == 'CSC_regions': 
+      regions = self.actions[0].obj.get_number_regions()
     if hasattr(self,'inf_model'):
       b = BeliefState(self.train_dataset, self.actions, self.inference_mode,
         self.bounds, self.inf_model, self.fastinf_model_name)
     else:
       b = BeliefState(self.train_dataset, self.actions, self.inference_mode,
-        self.bounds, fastinf_model_name=self.fastinf_model_name)
+        self.bounds, fastinf_model_name=self.fastinf_model_name, num_regions=regions)
       self.b = b
       self.inf_model = b.model
 

### 2012-06-01 synthetic/ext_detector_regions.py

@@ -88,7 +88,7 @@ class ExternalDetectorRegions(ExternalDetector):
   '''
   External Detector that also tests for specific regions.
   '''
-  def __init__(self, dataset, train_dataset, cls, dets, detname, rtype, args):
+  def __init__(self, dataset, train_dataset, cls, dets, detname, region_id, rtype, args):
     '''
     Also pass in the region-type as rtype and the according arguments as args
     '''
@@ -96,6 +96,7 @@ class ExternalDetectorRegions(ExternalDetector):
     self.region_model = RegionModel(rtype, args)
     if self.classif.svm == None:
       raise RuntimeError('SVM in External Detector Regions is None')
+    self.region_id = region_id
     
   def convert_wh2scale(self, img, x, y, w, h):
     W, _ = img.size    
@@ -124,7 +125,7 @@ class ExternalDetectorRegions(ExternalDetector):
       new_dets_arr = np.vstack(new_dets_arr)
     dets.arr = new_dets_arr     
   
-  def detect(self, image, region_id, astable=False):
+  def detect(self, image, astable=False):
     """
     Return the detections that match that image index in cached dets for a 
     specific region in the image that is determined by the region_id.
@@ -133,10 +134,10 @@ class ExternalDetectorRegions(ExternalDetector):
     """
     img_ind = self.dataset.get_img_ind(image)
     dets = self.dets.filter_on_column('img_ind',img_ind,omit=True) # This function already creates a copy
-    self.filter_dets_for_reg_id(image, dets, region_id) # At this position choose only the detections that fall into the desired region
+    self.filter_dets_for_reg_id(image, dets, self.region_id) # At this position choose only the detections that fall into the desired region
     return super(ExternalDetectorRegions, self).detect(image, astable, dets) # Now call the regular external detector with just those detections
   
-  def compute_score(self, image, region_id, oracle=False):
+  def compute_score(self, image, oracle=False):
     """
     Return the 0/1 decision of whether the cls of this detector is present in
     the image, given the detections table for a given region id.
@@ -144,7 +145,7 @@ class ExternalDetectorRegions(ExternalDetector):
     """
     img_ind = self.dataset.get_img_ind(image)
     dets = self.dets.filter_on_column('img_ind',img_ind,omit=True)
-    self.filter_dets_for_reg_id(image, dets, region_id) # At this position choose only the detections that fall into the desired region
[…]

### 2012-06-01 synthetic/fastInf.py

@@ -336,6 +336,7 @@ def run_fastinf_different_settings(d, ms, rs, suffixs, num_bins = 5):
       
       bounds, discr_table_region = discretize_table(orig_table_region, num_bins)
       table = np.hstack((table_gt_region, discr_table_region))
+      embed()
       
     elif suffix == 'GIST_CSC':
       filename_csc = os.path.join(config.get_ext_dets_foldname(d),'table')

### 2012-06-01 synthetic/fastinf_model.py

@@ -8,7 +8,7 @@ from synthetic.ngram_model import InferenceModel
 from synthetic.fastInf import FastinfDiscretizer
 
 class FastinfModel(InferenceModel):
-  def __init__(self,dataset,model_name,num_obs_vars,m='0',r1='1', lbp_iters=3000):
+  def __init__(self,dataset,model_name,num_obs_vars,m='0',r1='1', lbp_iters=3000, num_regions=1):
     # TODO: experiment with different values of fastinf
 
     self.dataset = dataset
@@ -31,6 +31,7 @@ class FastinfModel(InferenceModel):
     self.tt = ut.TicToc().tic()
     self.process = pexpect.spawn(self.cmd)
     self.blacklist = []
+    self.num_regions = num_regions
   
     marginals = self.get_marginals()
     print("FastinfModel: Computed initial marginals in %.3f sec"%self.tt.qtoc())
@@ -51,21 +52,21 @@ class FastinfModel(InferenceModel):
       print("comm_rank %d: Skipping blacklisted evidence!"%comm_rank)
       # don't do anything, we don't want to get stuck with another timeout
       return
-    try:
-      marginals = self.get_marginals(evidence)
-    except Exception as e:
-      print("comm_rank %d: something went wrong in fastinf:get_marginals!!!"%
-        comm_rank)
-      print evidence
-      print e
-      # blacklist this evidence and restart process
-      self.blacklist.append(evidence)
-      try:
-        self.process.close(force=True)
-      except Exception as e2:
-        print("comm_rank %d: can't close process!"%comm_rank)
-      self.process = pexpect.spawn(self.cmd)
-      self.get_marginals()
+#    try:
+    marginals = self.get_marginals(evidence)
+#    except Exception as e:
+#      print("comm_rank %d: something went wrong in fastinf:get_marginals!!!"%
+#        comm_rank)
+#      print evidence
+#      print e
+#      # blacklist this evidence and restart process
+#      self.blacklist.append(evidence)
+#      try:
+#        self.process.close(force=True)
+#      except Exception as e2:
+#        print("comm_rank %d: can't close process!"%comm_rank)
+#      self.process = pexpect.spawn(self.cmd)
+#      self.get_marginals()
     
     # TODO: hack to set the actual classifier score here!
     # GIST is hard-coded as second half of observations!
@@ -96,7 +97,7 @@ class FastinfModel(InferenceModel):
       if evidence in self.cache:
[…]

### 2012-06-01 synthetic/util.py

@@ -146,6 +146,7 @@ def log2(x):
   "Base-2 log that returns 0 if x==0."
   y = np.atleast_1d(np.copy(x))
   y[y==0]=1
+  print y
   return np.log2(y)
 
 def mean_squared_error(y_true,y_pred):

### 2012-06-01 synthetic/tasks/plot_trajectories.py
trajectories figure

@@ -1,27 +1,39 @@
 from pandas import DataFrame
 from pylab import *
+import synthetic.config as config
 
 def plot_order(samples,name,filename):
   df = DataFrame({
     'img': [s.img_ind for s in samples],
     'action': [s.action_ind for s in samples],
-    't': [s.t+s.dt for s in samples]
+    't': [s.t+s.dt for s in samples],
+    'ap': [s.det_naive_ap for s in samples]
     })
   print(name)
   print("Num samples: %d"%df.shape[0])
   fixed_order = [14,  6,  8, 11, 17,  7,  2, 12, 19, 15, 10, 18,  4,  1, 13,  0,  5,  3,  9, 16]
   fig = plt.figure()
   ax = fig.add_subplot(111)
+  ax.set_yticks(arange(-1,21))
+  ax.set_yticklabels(['']+[str(d) for d in fixed_order]+[''])
+  ax.set_yticklabels(['']+[config.pascal_classes[d] for d in fixed_order]+[''])
+  ax.set_ylabel('Action Index')
+  ax.set_xticks(arange(-1,22))
+  ax.set_xlabel('Time (s)')
+  title(name)
   for img in df.img.unique():
     a = (df[df.img==img].action)
     # change to linear for the fixed order
     a = [fixed_order.index(a) for a in a]
-    t = (df[df.img==img].t)
-    ax.plot(t,a,'s-',alpha=0.2)
-    ax.set_yticklabels([str(d) for d in fixed_order])
-    ax.set_ylabel('Action Index')
-    ax.set_xlabel('Time (s)')
-    title(name)
+    t = df[df.img==img].t
+    ap = df[df.img==img].ap
+    if name =='Oracle':
+      # we don't actually update the samples in oracle mode: only the dets
+      # so these have to be sorted, as they are for oracle in dataset_policy
+      ap = np.array(sorted(ap,reverse=True))
+    size = 0+200*ap
+    ax.plot(t,a,'.-',alpha=0.05,color='orange')
+    ax.scatter(t,a,size,alpha=0.2)
   plt.show(fig)
   fig.savefig(filename)
 
@@ -31,3 +43,9 @@ plot_order(samples,'Fixed Order','./tasks/trajectories_fixed_order.png')
 
 samples = np.load(dirname+'fastinf_csc_default_0-20_rl_half_auc_ap_raw_may29/cached_dets.npy_samples.npy')
[…]

### 2012-06-01 writeups/nips12/technical.tex

@@
 
-We evaluate two ways of updating probabilities: \emph{direct} and \emph{MRF}.
-In the \emph{direct} way, $P(C_i|\mathbf{o}) = score(C_i)$ if $\mathbf{o}$ includes the observations for class $C_i$ and $P(C_i|\mathbf{o}) = P(C_i)$ otherwise.
+We evaluate two approaches of updating probabilities: \emph{direct} and \emph{MRF}.
+In the \emph{direct} method, $P(C_i|\mathbf{o}) = score(C_i)$ if $\mathbf{o}$ includes the observations for class $C_i$ and $P(C_i|\mathbf{o}) = P(C_i)$ otherwise.
 This means that an observation of class $i$ does not influence the estimated probability of any class but $C_i$.
@@
 
-In the \emph{MRF} way, we employ a pairwise fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:figure1}, with the observation nodes set to $score(C_i)$ appropriately, or considered unobserved.
+The \emph{MRF} approach employs a pairwise fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:figure1}, with the observation nodes set to $score(C_i)$ appropriately, or considered unobserved.
 

### 2012-06-01 writeups/nips12/evaluation.tex
trajectories figure in

@@
 \centering
-\subfloat[Occurence of a class with another]{\includegraphics[]
-    {../figures/full_pascal_trainval_stats/cooccur_trim.png}} \hfill
-\subfloat[Occurence of a class with two others]{\includegraphics[]
-    {../figures/full_pascal_trainval_stats/cooccur_second_order_trim.png}}
-  \caption{
-  Co-occurrence statistics on the training portion of the PASCAL VOC 2007 dataset.
-  In the first plot, a (row,column) cell shows the probability that an image that contains an object of the row class also contains an object of the column class.
-  Accordingly, in the second plot, the probability that an image containing objects of the two classes listed in the row also contains an object of the column class.
-  }
-  \label{fig:dataset_stats}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\subfloat[AP vs.
-Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy, with start time of 5 seconds and deadline of 15 seconds.]{\includegraphics[width=0.47\linewidth]
-    {../figures/final1_515.png}} \hfill
-\subfloat[Execution traces of different policies]{\includegraphics[draft,width=0.47\linewidth]
-    {../figures/final1.png}}
- \label{fig:results1}
+\subfloat[AP vs. Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy, with start time of 5 seconds and deadline of 15 seconds.]{
+\includegraphics[width=0.47\linewidth]
+    {../figures/final1_515.png}\label{fig:results1}} \hfill
+\subfloat[Reward function explanation]{
+\includegraphics[width=0.47\linewidth]
+    {../figures/apvst_expl.pdf}\label{fig:rewards}}
 \end{figure}
@@
 All results are shown in \autoref{tab:results}.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.86\linewidth]{../figures/trajectories.pdf}
+  \caption{\todo{trajectories}}
+  \label{fig:trajectories}
+\end{figure}
 

### 2012-06-01 writeups/nips12/technical.tex
trajectories figure in

@@
 Time curve between $T_s$ and $T_d$ (normalized by total possible area), as determined by the detections in $\mathbf{o}^j$ for all steps $j$ in the episode.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.56\linewidth]{../figures/apvst_expl.pdf}
-  \caption{\todo{what text here?} A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action.
-The figure shows this analysis for the action highlighted in orange.}
-  \label{fig:rewards}
-\end{figure}
 
@@
 \centering
-\subfigure[Greedy]{\includegraphics[width=0.49\linewidth]{../figures/weights_greedy}}
-\subfigure[RL]{\includegraphics[width=0.49\linewidth]{../figures/weights_rl}}
+\subfloat[Greedy]{\includegraphics[width=0.49\linewidth]{../figures/weights_greedy}}
+\subfloat[RL]{\includegraphics[width=0.49\linewidth]{../figures/weights_rl}}
 % \includegraphics[width=0.87\linewidth]{../figures/weights.pdf}
@@
 \subsection{Updating with observations} \label{sec:updating}
-% \begin{figure}[h!]
-% \centering
-% \includegraphics[width=0.56\linewidth]{../figures/mrf_w_gist.pdf}
-% \caption{
-% \todo{get rid of this figure?}
-% The MRF inference model used in our system. The shaded nodes represent two actions that have already been taken; their observations have been recorded.
-% }
-% \label{fig:model}
-% \end{figure}
 
@@
 
-We evaluate two approaches of updating probabilities: \emph{direct} and \emph{MRF}.
+We evaluate two approaches for updating probabilities: \emph{direct} and \emph{MRF}.
 In the \emph{direct} method, $P(C_i|\mathbf{o}) = score(C_i)$ if $\mathbf{o}$ includes the observations for class $C_i$ and $P(C_i|\mathbf{o}) = P(C_i)$ otherwise.

### 2012-06-01 synthetic/tasks/plot_trajectories.py

@@ -35,7 +35,7 @@ def plot_order(samples,name,filename):
     ax.plot(t,a,'.-',alpha=0.05,color='orange')
     ax.scatter(t,a,size,alpha=0.2)
   plt.show(fig)
-  fig.savefig(filename)
+  fig.savefig(filename,dpi=300)
 
 dirname = '/Users/sergeyk/work/timely/data/results/evals/full_pascal_test_120/'
 samples = np.load(dirname+'fixed_order_csc_default_0-20_manual_1_det_actual_ap_may29/cached_dets.npy_samples.npy')

### 2012-06-01 writeups/nips12/introduction.tex
trevor's edits incorporated

@@
 
-The computer vision field has converged on a general method for object detection, and a standard evaluation of results.
-Efficiency is not a concern of the evaluation metrics, and the methods are not evaluated in an inherently multi-class setting.
-However, in most real-world applications of object recognition, performance is time-sensitive and inherently tied to the many-class nature of the world.
-
+In most real-world applications of object recognition, performance is time-sensitive and inherently tied to the many-class nature of the world.
 In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
 In large-scale detection system deployments, such as for image search, results need to be obtained quickly per image as the number of images to process is large and growing.
-
 In these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.
-Furthermore, the value of the answer depends on the target application.
 
@@
 
-A hypothetical recognition system for a vision-based advertising deployment presents a case study.
+The conventional approach to evaluation of results on visual category
+recognition does not consider efficiency and evaluates performance
+indepednently across classes.  
+We argue that the key to tackling such problems of dynamic recognition resource allocation is to start asking a new question:
+\emph{What is the best performance we can get on a budget?}
+We propose a new \emph{timeliness} measure of performance vs. time (shown in Figure~\ref{fig:figure1}), which evalutes the time efficiency of multi-class detection.
+
+We present a method based on reinforcement learning that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
+We are able to obtain better performance than baselines when there is less time available than is needed to run all detectors.
+
+A hypothetical recognition system for a vision-based advertising deployment presents a motivational case study.
 The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
 The detection strategy to maximize profit in such an environment should depend on all of these variables.
-
-We argue that the key to tackling such problems of dynamic recognition resource allocation is to start asking a new question:
-\emph{What is the best performance we can get on a budget?}
-To answer it, we consider the evaluation metric of performance vs. time, shown in Figure~\ref{fig:figure1} and discussed further in the text.
-
-We present a method that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
-We are able to obtain better performance than baselines when there is less time available than is needed to run all detectors.
+We explore this scenario using the PASCAL VOC datasets and evaluation regimes, and show that our learned dynamic policy offers a better strategy than a random or optimal static ordering of detectors.

### 2012-06-01 writeups/nips12/nips2012.tex
trajectories figure in
trevor's edits incorporated

@@
 \usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
-\usepackage{subfigure}
 
@@
 \begin{abstract}
-In a large visual multi-class detection framework, the problem of timeliness of results is crucial.
+In a large visual multi-class detection framework, the timeliness of results can be crucial.
 We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
-Our method for multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
+Our method for \emph{timely multi-class detection} aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
 Toward this goal, we formulate a dynamic, \emph{closed-loop} policy guided by inference of the contents of the image in order to decide which detector to deploy next.
-In contrast to previous work, our method significantly diverts from the predominant greedy strategies and therefore learns to employ actions without any immediate reward for the goal of detection.
-We evaluate our method with respect to performance in the novel Average Precision (AP) vs. Time evaluation on the widely used PASCAL VOC object detection dataset.
+In contrast to previous work, our method significantly diverts from the predominant greedy strategies, and is able to learn to employ actions with deferred value.
+We evaluate our method with respect to performance on a novel \emph{timeliness} measure, computed as the area under an Average Precision (AP) vs. Time
+curve.
+We conduct experiments on the widely used PASCAL VOC object detection dataset.
 With our method, if execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
-Overall, our method obtains at least $11\%$ better performance on the AP vs.
-Time evaluation.
-At time of publication we will make our code available, which is easily extendible to new detectors, classifiers, tasks and reward functions due to the modular nature of our formulation.
+Overall, our method obtains at least $11\%$ better performance on the AP vs. Time evaluation on PASCAL VOC.
+% At time of publication we will make our code available, which is easily extendible to new detectors, classifiers, tasks and reward functions due to the modular nature of our formulation.
 \end{abstract}

### 2012-06-01 writeups/nips12/evaluation.tex
printed

@@
 Each detection episode takes an image and outputs detections with associated times, based on the order of actions taken.
-We evaluate on a popular detection challenge task: the PASCAL VOC 2007 dataset \cite{pascal-voc-2010}.
-As shown in \autoref{fig:dataset_stats}, the dataset exhibits a rather modest amount of class co-occurrence.
+We evaluate on a popular detection challenge task: the PASCAL VOC 2007 dataset \cite{pascal-voc-2010}, which exhibits only a rather modest amount of class co-occurrence: the ``person'' class is highly likely to occur, and less than $10\%$ of the images have more than two classes.
 
@@
 We test three different settings of the start and deadline times.
-In the first one, the start time is immediate and execution is cut off at 20 seconds, which is enough time to run basically all actions.
-In the second one, execution is cut off after only 10 seconds.
-Lastly, we measure performance between 5 seconds and 15 seconds.
-These operating points show how our method would behave when deployed in different conditions.
+In the first one, the start time is immediate and execution is cut off at $20$ seconds, which is enough time to run basically all actions.
+In the second one, execution is cut off after only $10$ seconds.
+Lastly, we measure performance between $5$ seconds and $15$ seconds.
+These operating points show how our method behaves when deployed in different conditions.
+The results are given in rows of \autoref{tab:results}.
 
@@
     {../figures/apvst_expl.pdf}\label{fig:rewards}}
+\caption{}
 \end{figure}
@@
 
-In Figure \autoref{fig:results1}, we can see that due to the dataset bias, the fixed-order policy performs well at first (as can be seen in \autoref{fig:dataset_stats}, the person class is disproportionately likely to be in the image), but is significantly overtaken by our model as execution goes on.
+In Figure~\autoref{fig:results1}, we can see that due to the dataset bias, the fixed-order policy performs well at first, as the person class is disproportionately likely to be in the image, but is significantly overtaken by our model as execution goes on and more rare classes have to be detected.
 
@@
   \includegraphics[width=0.86\linewidth]{../figures/trajectories.pdf}
-  \caption{\todo{trajectories}}
+  \caption{
+Visualizing the action trajectories of different policies.
+The orange lines show the action selections over many episodes; the size of the blue circles correspond to the $\Delta ap$ obtained by the action.
+We see that the \textbf{Random} policy selects actions and obtains rewards randomly, while the \textbf{Oracle} policy obtains all rewards in the first few actions.
+The \textbf{Fixed Order} policy selects actions in a static optimal order.
+Our policy does not stick a static order but selects actions dynamically to maximize the rewards obtained early on.
+}
   \label{fig:trajectories}
@@
 \begin{tabular}{|l|l|l|l|l|l|}
-%\\ \hline \\
 \hline
 Bounds & Random & Fixed Order & RL w/ MRF & w/ GIST         & Oracle \\ \hline
+(0,20) & 0.250  & 0.342       & 0.378     & \textbf{0.382}  & 0.488 \\ 
 (0,10) & 0.119  & 0.240       & 0.266     & \textbf{0.267}  & 0.464 \\ 
-(0,20) & 0.250  & 0.342       & 0.378     & 0.382    & 0.488 \\ 
-(5,15) & 0.257  & 0.362       & 0.418     & 0.420    & 0.530 \\ \hline
+(5,15) & 0.257  & 0.362       & 0.418     & \textbf{0.420}  & 0.530 \\ \hline
 \end{tabular}
@@
 
-\todo{something about setting values?}
+%\todo{something about setting values?}

### 2012-06-01 writeups/nips12/technical.tex
printed

@@
 Therefore we cannot learn a tabular representation of $Q(s,a)$, and must use function approximation to represent it \cite{Sutton1998}.
-We featurize the state-action pair and assume linear structure:
-\begin{align}
-Q^\pi(s,a_i) = \theta_\pi^\top  \phi(s,a_i)
-\end{align}
+We featurize the state-action pair and assume linear structure: $Q^\pi(s,a_i) = \theta_\pi^\top  \phi(s,a_i)$.
 
@@
 
-We can then represent the final evaluation in terms of individual rewards:
-\begin{align}
-eval(h) = \sum_{j=0}^J R(s^j,a^j)
-\end{align}
+We can then represent the final evaluation $eval(h,T_s,T_d)$ in terms of individual rewards: $\sum_{j=0}^J R(s^j,a^j)$.
 
@@
 
-Additionally, we include the mean and maximum entropies of all classes, time features that represent the times until start and deadline, and the expected time (cost) of the action, for a total of $F$ features.
+Additionally, we include the mean and maximum entropies of all classes, the expected time (cost) of the action, and time features that represent the times until start and deadline, for a total of $F$ features.
 
@@
 % \includegraphics[width=0.87\linewidth]{../figures/weights.pdf}
-\caption{Weights \todo{describe. can talk about the person-class weights, the role of the time weights. how you can see the co-occurrence matrix in the weights}}
+\caption{
+Learned policy weights $\theta_\pi$ (best viewed in color: red corresponds to positive, blue to negative values).
+The first row corresponds to the scene-level action, which does not generate detections itself but only helps reduce uncertainty about the contents of the image.
+Note that in the greedy learning case, this action is learned to never be taken---whereas it is shown to be useful in the reinforcement learning case.
+}
 \label{fig:weights}
@@
 
-The graphical model structure is set as fully-connected, but as shown in \autoref{fig:dataset_stats}, some classes are overwhelmingly unlikely to co-occurr.
+The graphical model structure is set as fully-connected, but some classes are overwhelmingly unlikely to co-occurr in our dataset.
 Accordingly, the graph edge weights are learned with $L_1$ regularization, which obtains the desired sparse structure \cite{Lee2006}.
-All parameters of the model are trained on fully-observed data, and inference is implemented with an open-source graphical model package \cite{Jaimovich2010}.
-As exact inference is generally intractable in this model, we use Loopy Belief Propagation; although it does not provide general convergence guarantees, it has been shown to work well empirically on similar tasks \cite{Desai2009}.
+All parameters of the model are trained on fully-observed data, and Loopy Belief Propagation inference is implemented with an open-source graphical model package \cite{Jaimovich2010}.
+% As exact inference is generally intractable in this model, we use Loopy Belief Propagation; although it does not provide general convergence guarantees, it has been shown to work well empirically on similar tasks \cite{Desai2009}.

### 2012-06-01 writeups/nips12/introduction.tex
exactly 8+1 pages

@@
 In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
-In large-scale detection system deployments, such as for image search, results need to be obtained quickly per image as the number of images to process is large and growing.
+In large-scale detection systems (e.g. image search), results need to be obtained quickly per image as the number of items to process is constantly growing.
 In these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.
@@
 
-The conventional approach to evaluation of results on visual category
-recognition does not consider efficiency and evaluates performance
-indepednently across classes.  
-We argue that the key to tackling such problems of dynamic recognition resource allocation is to start asking a new question:
+The conventional approach to evaluation of visual category recognition does not consider efficiency and evaluates performance independently across classes.
+We argue that the key to tackling problems of dynamic recognition resource allocation is to start asking a new question:
 \emph{What is the best performance we can get on a budget?}
-We propose a new \emph{timeliness} measure of performance vs. time (shown in Figure~\ref{fig:figure1}), which evalutes the time efficiency of multi-class detection.
 
-We present a method based on reinforcement learning that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
+We propose a new \emph{timeliness} measure of performance vs.
+time (shown in Figure~\ref{fig:figure1}), and present a method based on reinforcement learning that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
 We are able to obtain better performance than baselines when there is less time available than is needed to run all detectors.
 
-A hypothetical recognition system for a vision-based advertising deployment presents a motivational case study.
-The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
-The detection strategy to maximize profit in such an environment should depend on all of these variables.
+A hypothetical system for vision-based advertising presents a case study.
+The system will have different values and accuracies for objects of different classes, and the queue of unprocessed images will vary in size.
+The detection strategy to maximize profit in such an environment has to be dynamic.
 We explore this scenario using the PASCAL VOC datasets and evaluation regimes, and show that our learned dynamic policy offers a better strategy than a random or optimal static ordering of detectors.

### 2012-06-01 writeups/nips12/nips2012.tex
printed
exactly 8+1 pages

@@
 In a large visual multi-class detection framework, the timeliness of results can be crucial.
-We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
-Our method for \emph{timely multi-class detection} aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
-Toward this goal, we formulate a dynamic, \emph{closed-loop} policy guided by inference of the contents of the image in order to decide which detector to deploy next.
-In contrast to previous work, our method significantly diverts from the predominant greedy strategies, and is able to learn to employ actions with deferred value.
-We evaluate our method with respect to performance on a novel \emph{timeliness} measure, computed as the area under an Average Precision (AP) vs. Time
-curve.
-We conduct experiments on the widely used PASCAL VOC object detection dataset.
-With our method, if execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
-Overall, our method obtains at least $11\%$ better performance on the AP vs. Time evaluation on PASCAL VOC.
-% At time of publication we will make our code available, which is easily extendible to new detectors, classifiers, tasks and reward functions due to the modular nature of our formulation.
+%We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
+Our method for \emph{timely} multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
+Toward this goal, we formulate a dynamic, \emph{closed-loop} policy that infers the contents of the image in order to decide which detector to deploy next.
+In contrast to previous work, our method significantly diverts from the predominant greedy strategies, and is able to learn to take actions with deferred values.
+We evaluate our method with a novel \emph{timeliness} measure, computed as the area under an Average Precision (AP) vs. Time curve.
+Experiments are conducted on the eminent PASCAL VOC object detection dataset.
+If execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
+On the timeliness measure, our method obtains at least $11\%$ better performance.
+Our code, to be made available upon publication, is easily extensible as it treats detectors and classifiers as black boxes and learns from execution traces using reinforcement learning.
 \end{abstract}
 
-\input{introduction.tex} % includes Evaluation section
+\input{introduction.tex}
 \input{related.tex}

### 2012-06-01 writeups/nips12/related.tex
more minor squeezing
exactly 8+1 pages

@@
 
-\subsection{Related Work}
+%\subsection{Related Work}
 The literature on object recognition is vast.
-Here we briefly summarize work that sufficiently contextualizes our contribution.
+Here we briefly summarize work that sufficiently contextualizes our contribution:
 
@@
 None of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal.
-Some work has been done on this topic, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008,Paletta2005}.
+Some work has been done on this topic, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008}.
 
@@
 For the commonly used PASCAL VOC dataset \cite{pascal-voc-2010}, GIST and other sources of context are quantitatively explored in~\cite{Divvala2009}. 
-
+%
 Another source is inter-object context, shown to be useful for improving detection \cite{Torralba2004}.
@@
 \myparagraph{Multi-Class Detection}
-Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005,Razavi2011}.
+Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005}.
 A proposed post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression \cite{Desai2009}.

### 2012-06-01 writeups/nips12/evaluation.tex
figure 3 captions more compact
final polish

@@
 We learn weights on the training and validation sets, and run our policy on all images in the testing set.
-The final evaluation pools all detections up to a certain time, and computes their multi-class AP per image, then averaging over all images.
+The final evaluation pools all detections up to a certain time, and computes their multi-class AP per image, averaging over all images.
 This is done for different times to plot the AP vs. Time curve over the whole dataset.
-The evaluation is slightly different that what is usually done (all detections for a class are pooled across the dataset), but has been used before \cite{Desai2009}.
+Our method of averaging per-image performance follows \cite{Desai2009}.
 
@@
 Running a detector on a PASCAL image takes about $1$ second.
-Additionally, we use a classifier from the scene-level GIST feature to class presence, for each class.
-This is considered one action, and takes about $0.3$ seconds.
 
@@
 
-Then there are our proposed systems, which the previous section thoroughly described: \textbf{RL w/ Direct} and \textbf{RL w/ MRF}.
+Then there are our proposed systems, described in the previous section : \textbf{RL w/ Direct} and \textbf{RL w/ MRF}.
 In experiments, the two were not exceedingly different in performance, with the MRF model consistently performing slightly better.
@@
 
-Lastly, we also evaluate the system that includes a GIST action; this always uses the MRF model to properly update the class probabilities with GIST observations.
+Lastly, we include an additional scene-level GIST feature that updates the posterior probabilities of all classes.
+This is considered one action, and takes about $0.3$ seconds.
+This setting always uses the MRF model to properly update the class probabilities with GIST observations.
 This brings another boost in performance.
@@
 
+\autoref{fig:trajectories} illustrates the action trajectories of different policies.
+
 \begin{table}[t]
-\caption{Results}
+\caption{
+The areas under the AP vs. Time curve for different experimental conditions.
+Our method reliably beats the intelligent static baseline; including the GIST action further boosts performance.}
 \label{tab:results}
@@
 \end{table}
-
-%\todo{something about setting values?}

### 2012-06-01 writeups/nips12/related.tex
final polish

@@
 Multi-class performance is evaluated by averaging the individual per-class AP values.
-Since our use case is motivated by a potential advertising system, we generalize this metric to a weighted average, with the weights set by the \emph{values} of the classes.
+We generalize this metric to a weighted average, with the weights set by the \emph{values} of the classes.
 
-%\subsection{Related Work}
+\subsection{Related Work}
 The literature on object recognition is vast.
-Here we briefly summarize work that sufficiently contextualizes our contribution:
+Here we briefly summarize work that sufficiently contextualizes our contribution.
 
@@
 Classifiers are then used to distinguish between featurizations of a given class and all other possible contents of an image window.
-%
-Window proposal is often done exhaustively over the image space, as a ``sliding window''.
-Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Vedaldi2009,Vijayanarasimhan2011}.
-For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008a}.
-%
+Window proposal is most often done exhaustively over the image space, as a ``sliding window''.
+Some approaches use ``jump windows'' (hypotheses voted on by local features) \cite{Vedaldi2009,Vijayanarasimhan2011}, or a bounded search over the space of all possible windows \cite{Lampert2008a}.
+
 None of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal.
@@
 For the commonly used PASCAL VOC dataset \cite{pascal-voc-2010}, GIST and other sources of context are quantitatively explored in~\cite{Divvala2009}. 
-%
-Another source is inter-object context, shown to be useful for improving detection \cite{Torralba2004}.
+Inter-object context has also been shown to be useful for improving detection \cite{Torralba2004}.
 A critical summary of the main approaches to using context for object and scene recognition is given in \cite{Galleguillos2010}.
@@
 Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005}.
-A proposed post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression \cite{Desai2009}.
+A post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for non-maximum suppression \cite{Desai2009}.
 
@@
 An early success in efficient object detection used simple, fast features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime \cite{Viola2001}.
-Although the simple features and classifiers of this method have been surpassed by more complex detectors, the idea of cascading classifier evaluations is still often used.
 Most recently, cyclic optimization has been applied to optimize cascades with respect to feature computation cost as well as classifier performance \cite{Chen2012}.
@@
 \myparagraph{Anytime Algorithms and Active Classification}
-Anytime performance in vision systems is a surprisingly little-explored idea.
-A recent application to the problem of visual detection picks features with maximum value of information in a Hough-voting framework, and explicitly evaluates performance vs.
-time \cite{Vijayanarasimhan2010}.
+This surprisingly little-explored line of work in vision is closest to our approach.
+A recent application to the problem of visual detection picks features with maximum value of information in a Hough-voting framework \cite{Vijayanarasimhan2010}. 
 There has also been work on active classification \cite{Gao2011} and active sensing \cite{Yu2009}, in which intermediate results are considered in order to decide on the next classification step.
-This line of work is closest to our approach.
-Most commonly, the scheduling in these approaches is greedy with respect to some quantity such as expected information gain.
-In contrast, we are able to learn policies that take actions without any immediate reward.
+Most commonly, the scheduling in these approaches is greedy with respect to some manual quantity such as expected information gain.
+In contrast, we learn policies that take actions without any immediate reward.

### 2012-06-01 writeups/nips12/technical.tex
final polish

@@
 From the setup time to the deadline, we want to obtain the best possible answer if stopped at any given time.
-A single-number metric that corresponds to this objective is the area captured under the curve between the start and deadline bounds, normalized by the total area possible.
+A single-number metric that corresponds to this objective is the area captured under the curve between the start and deadline bounds, normalized by the total area.
 We evaluate policies by this more robust metric and not simply by the final performance at deadline time for the same reason that Average Precision is used instead of a fixed Precision vs.
@@
 We refer to the basis for the decisions made by the decision process as the \emph{state} $s$.
-The state includes the currently believed distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$, where we write $P(C_k)$ to mean $P(C_k=1)$
+The state includes the currently believed distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$, where we write $P(C_k)$ to mean $P(C_k=1)$.
 
-Additionally, the state records the fact that an action $a_i$ has been taken by adding it to the initially empty set $\mathcal{O}$ and recording the resulting observations $o_i$.
+Additionally, the state records that an action $a_i$ has been taken by adding it to the initially empty set $\mathcal{O}$ and recording the resulting observations $o_i$.
 We refer to the current set of observations as $\mathbf{o} = \{o_i | a_i \in \mathcal{O}\}$.
@@
 \subsection{Selecting actions} \label{sec:value}
-As our goal is to pick actions dynamically, we want a function $Q(s,a): S \times \mathcal{A} \mapsto \mathbb{R}$, where $S$ is the space of all possible states, to assign a value to a potential action, given the current state of the decision process.
+As our goal is to pick actions dynamically, we want a function $Q(s,a): S \times \mathcal{A} \mapsto \mathbb{R}$, where $S$ is the space of all possible states, to assign a value to a potential action given the current state of the decision process.
 We can then define the desired policy $\pi$ as simply taking the (untaken) action with the maximum value:
@@
 The policy's performance at time $t$ is determined by the detections that are part of the set of observations $\mathbf{o}^j$ at the last state $s^j$ before $t$.
-Therefore, the final AP vs. Time evaluation of an episode is a function of the history of execution $h=s^0,s^1,\dots,s^J$.
-
-We refer to the final evaluation function as $eval(h,T_s,T_d)$, and it is precisely the area under the AP vs.
-Time curve between $T_s$ and $T_d$ (normalized by total possible area), as determined by the detections in $\mathbf{o}^j$ for all steps $j$ in the episode.
+Therefore, the final AP vs. Time evaluation of an episode is a function $eval(h,T_s,T_d)$ of the history of execution $h=s^0,s^1,\dots,s^J$.
+It is precisely the normalized area under the AP vs. Time curve between $T_s$ and $T_d$, as determined by the detections in $\mathbf{o}^j$ for all steps $j$ in the episode.
 
@@
 From these and $T_s$ and $T_d$, we can find the area under the curve that was contributed by the action.
+So, we can then represent the final evaluation $eval(h,T_s,T_d)$ in terms of individual rewards: $\sum_{j=0}^J R(s^j,a^j)$.
 
@@
 
-We can then represent the final evaluation $eval(h,T_s,T_d)$ in terms of individual rewards: $\sum_{j=0}^J R(s^j,a^j)$.
-
-And we can represent the expected value of the final evaluation recursively in terms of the value function:
+\subsection{Learning the policy}
+The expected value of the final evaluation can be written recursively in terms of the value function:
 \begin{align} \label{eq:recursive_value}
@@
 
-\subsection{Learning the policy}
 While we can't directly compute the expectation in \eqref{eq:recursive_value}, we can sample it by running actual episodes to gather $<s,a,r,s'>$ samples, where $r$ is the reward obtained by taking action $a$ in state $s$, and $s'$ is the following state.
@@
 
-Additionally, we include the mean and maximum entropies of all classes, the expected time (cost) of the action, and time features that represent the times until start and deadline, for a total of $F$ features.
+Additionally, we include the mean and maximum entropies of all classes, the expected time of the action $c(a)$, and time features that represent the times until start and deadline, for a total of $F$ features.
 

### 2012-06-01 writeups/nips12/nips2012.tex
final polish
final

@@
 In a large visual multi-class detection framework, the timeliness of results can be crucial.
-%We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
 Our method for \emph{timely} multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
 Toward this goal, we formulate a dynamic, \emph{closed-loop} policy that infers the contents of the image in order to decide which detector to deploy next.
-In contrast to previous work, our method significantly diverts from the predominant greedy strategies, and is able to learn to take actions with deferred values.
-We evaluate our method with a novel \emph{timeliness} measure, computed as the area under an Average Precision (AP) vs. Time curve.
+In contrast to previous work, our method significantly diverges from the predominant greedy strategies, and is able to learn to take actions with deferred values.
+We evaluate our method with a novel \emph{timeliness} measure, computed as the area under an Average Precision vs. Time curve.
 Experiments are conducted on the eminent PASCAL VOC object detection dataset.
@@
 
-As always with reinforcement learning problems, the defining the reward function requires some manual work.
+As always with reinforcement learning problems, defining the reward function requires some manual work.
 Here, we derive it for the novel detection AP vs. Time evaluation that we suggest is most useful for evaluating efficiency in recognition.
 Although computation devoted to scheduling actions is much less significant than the computation due to running the actions, an interesting future research direction is to explicitly consider this decision-making cost.
-
 At time of publication, we will release the code of our modular framework, that allows for easy incorporation of other classifiers and detectors on different tasks and rewards.

### 2012-06-01 writeups/nips12/technical.tex
final

@@
 
-Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs a list of multi-class detection results by running detector and other \emph{actions} sequentially.
+Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs a list of multi-class detection results by running detector and global scene \emph{actions} sequentially.
 
@@
 
-We refer to the basis for the decisions made by the decision process as the \emph{state} $s$.
-The state includes the currently believed distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$, where we write $P(C_k)$ to mean $P(C_k=1)$.
+We refer to the information available to the decision process as the \emph{state} $s$.
+The state includes the currently believed distribution over class presence variables $P(\mathbf{C}) = \{P(C_0), \ldots, P(C_K)\}$, where we write $P(C_k)$ to mean $P(C_k=1)$.
 
@@
 \subsection{Selecting actions} \label{sec:value}
-As our goal is to pick actions dynamically, we want a function $Q(s,a): S \times \mathcal{A} \mapsto \mathbb{R}$, where $S$ is the space of all possible states, to assign a value to a potential action given the current state of the decision process.
+As our goal is to pick actions dynamically, we want a function $Q(s,a): S \times \mathcal{A} \mapsto \mathbb{R}$, where $S$ is the space of all possible states, to assign a value to a potential action $a \in \mathcal{A}$ given the current state $s$ of the decision process.
 We can then define the desired policy $\pi$ as simply taking the (untaken) action with the maximum value:
@@
 
-Although the action space $\mathcal{A}$ is quite manageable, consisting of the detectors and classifier we would like to run on the image, the space of possible states $S$ is infinite.
+Although the action space $\mathcal{A}$ is quite manageable, consisting of the detectors and global classifier we would like to run on the image, the space of possible states $S$ is intractable.
 Therefore we cannot learn a tabular representation of $Q(s,a)$, and must use function approximation to represent it \cite{Sutton1998}.
@@
 
-As shown in \autoref{fig:rewards}, this evaluation function is additive per action, as each action can generate detections that either raise or lower the AP of all detections so far ($\Delta ap$) and takes a certain time ($\Delta t$).
+As shown in \autoref{fig:rewards}, this evaluation function is additive per action, as each action can generate detections that either raise or lower the mean AP of the results so far ($\Delta ap$) and takes a certain time ($\Delta t$).
 From these and $T_s$ and $T_d$, we can find the area under the curve that was contributed by the action.
@@
 \end{align}
-where $t_T^j$ and $\text{ap}^j$ are the time left until deadline and the AP at state $s^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.
+where $t_T^j$ and $\text{ap}^j$ are the time left until the deadline and the AP at state $s^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.
 (For clarity of exposition, we do not account for $T_s$ here.)
@@
 \begin{align} \label{eq:recursive_value}
-Q^\pi(s^j,a_i) = \mathbb{E}_{s^{j+1}} [R(s^j,a_i) + \gamma Q\pi(s^{j+1},\pi(s^{j+1}))]
+Q^\pi(s^j,a_i) = \mathbb{E}_{s^{j+1}} [R(s^j,a_i) + \gamma Q^\pi(s^{j+1},\pi(s^{j+1}))]
 \end{align}

### 2012-06-01 writeups/nips12/evaluation.tex
final

@@
 \centering
-\subfloat[AP vs. Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy, with start time of 5 seconds and deadline of 15 seconds.]{
+\subfloat[]{
 \includegraphics[width=0.47\linewidth]
     {../figures/final1_515.png}\label{fig:results1}} \hfill
-\subfloat[Reward function explanation]{
+\subfloat[]{
 \includegraphics[width=0.47\linewidth]
     {../figures/apvst_expl.pdf}\label{fig:rewards}}
-\caption{}
+\caption{(a) AP vs. Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy, with start time of 5 seconds and deadline of 15 seconds. (b) Reward function explanation.}
 \end{figure}
@@
 Visualizing the action trajectories of different policies.
-The orange lines show the action selections over many episodes; the size of the blue circles correspond to the $\Delta ap$ obtained by the action.
+Action selection traces are plotted in orange over many episodes; the size of the blue circles correspond to the $\Delta ap$ obtained by the action.
 We see that the \textbf{Random} policy selects actions and obtains rewards randomly, while the \textbf{Oracle} policy obtains all rewards in the first few actions.

### 2012-08-03 writeups/nips12/rebuttal.txt
nips reviews and rebuttal

All reviewers noted the significance of our "refreshingly new" view on performing and evaluating object detection, and recognized that we open interesting research avenues with convincing results.
As Reviewer 6 writes, we introduce a new ``timeliness'' AP vs. Time measure of detection performance, and use a reinforcement learning approach to optimize it.

The reviewer's main uncertainties about our method concern the reward function:
1) that it assumes that the measure is non-decreasing;
2) that it depends on a deadline time.

The first concern is not valid, as the definition of the reward can absolutely handle decreasing AP vs. Time: it simply produces negative rewards, which pose no problem to our learning approach.

Regarding the second concern, we note in the abstract that our goal is Anytime performance **between a start time and a deadline**.
Figure 3b illustrates a situation in which the deadline plays an important role: the very last possible action is illustrated as a choice between a solid green line and a dashed red line.
The green line is for an action that obtains a lower AP but finishes prior to deadline; the red line is for an action that obtains a higher AP but finishes after deadline.
The system should be able to learn to take the ``green'' action; this is why our reward function depends on a deadline time.

We appreciate the reviewer's valuable suggestion for a modification to the reward function, and agree that it would be helpful to provide more exposition here.

Regarding the reviewer's additional comments:
- Entropy: that is correct;
- Class correlations: that is correct, which is why we use an MRF model for inference: it is able to learn additional correlations;
- Actions: as we write, we report runtimes for a specific combination of software implementation and hardware; the details are not as important as the general approach used, as our learning is agnostic to the performances of the system components
We use the original MATLAB implementation of GIST by Torralba, which takes about a quarter of the time of the cascaded DPM implementation by Felzenswalb.

Reviewer 8 considers our approach to be interesting and new, but believes that the work of [18] is a close analog.
We disagree; while [18] uses a similar evaluation, they formulate a very specific system for object categorization using local features.
In contrast, we develop a general framework for optimizing object detection, using different detectors and classifiers.
The closest work to ours is [19], but it deals with classification and not detection, and does not learn non-greedy policies.

In fact, the reviewer's questions regarding the basics of Figures 1 and 2 raise concerns about their understanding of our approach.
Figure 1 shows the execution of our system over time, as different actions (classification and detection) are performed in sequence, results are obtained, and inference is performed in the MRF.
Figure 2 shows the weights learned by greedy learning and reinforcement learning on the features that represent the state of the system; the differences are illustrative of the desired properties of the reinforecement learning approach.
Regarding fairness, we note that we report multiple time bounds exactly for that reason.

Reviewer 5 provides helpful comments that we appreciate and would love to further discuss in another venue due to space constraints of this rebuttal.
We sincerely appreciate all the reviewers' effort in providing very helpful comments on our paper!

### 2012-11-02 writeups/nips12/introduction.tex
final polish
final
working on nips final and reorganizing slides into deadline folders

@@
 
-In most real-world applications of object recognition, performance is time-sensitive and inherently tied to the many-class nature of the world.
-In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection if the robot is to usefully interact with humans.
+In real-world applications of visual object recognition, performance is time-sensitive.% and inherently tied to the many-class nature of the world.
+In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection, if the robot is to usefully interact with humans.
 In large-scale detection systems (e.g. image search), results need to be obtained quickly per image as the number of items to process is constantly growing.
@@
 time (shown in Figure~\ref{fig:figure1}), and present a method based on reinforcement learning that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
-We are able to obtain better performance than baselines when there is less time available than is needed to run all detectors.
+We are able to obtain better performance than all baselines when there is less time available than is needed to exhaustively run all detectors.
 

### 2012-11-02 writeups/nips12/introduction.tex
edited introduction

@@
 In robotics, a small finite amount of processing power per unit time is all that is available for robust object detection, if the robot is to usefully interact with humans.
-In large-scale detection systems (e.g. image search), results need to be obtained quickly per image as the number of items to process is constantly growing.
-In these cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.
+In large-scale detection systems, such as image search, results need to be obtained quickly per image as the number of items to process is constantly growing.
+In such cases, an acceptable answer at a reasonable time may be more valuable than the best answer given too late.
 
@@
 A sample trace of our method.
-At each time step beginning at $t=0$, potential actions are considered according to their \emph{value}, and the one with the highest value is picked.
-The selected action is performed and returns observations, which influence the selection of the next action.
-The final evaluation of a detection episode is the area of the AP vs. Time curve between the start and end times.
-The value of an action is the expected value of the final evaluation if the action is taken and the policy continues to be followed, which allows actions without an immediate benefit to be scheduled.
+At each time step beginning at $t=0$, potential actions are considered according to their \emph{value}, and the $\arg\max$ action is picked.
+
+The selected action is performed and returns \emph{observations}.
+Different actions return different observations: a detector returns a list of detections, while a scene context action simply returns its cmoputed feature. 
+The \emph{belief model} of our system is updated with the observations, which influences the selection of the next action.
+
+The final evaluation of a detection episode is the area of the \emph{AP vs. Time curve} between given start and end times.
+The value of an action is the expected result of final evaluation if the action is taken and the policy continues to be followed, which allows actions without an immediate benefit to be scheduled.
 }
@@
 
-The conventional approach to evaluation of visual category recognition does not consider efficiency and evaluates performance independently across classes.
+% TODO: more fully explain that this is a detection system
+A hypothetical system for vision-based advertising presents a case study: companies pay money to have their products detected in images on the internet.
+The system has different values (e.g. in terms of cost-per-click) and accuracies for different classes of objects, and the queue of unprocessed images varies in size.
+The detection strategy to maximize profit in such an environment has to exploit every inter-object context signal available to it, because there is not enough time to run detection for all classes.
+
+What matters in the real world is timeliness, and either not all images can be processed or not all classes can be evaluated in a detection task.
+Yet the conventional approach to evaluating visual recognition does not consider efficiency, and evaluates performance independently across classes.
 We argue that the key to tackling problems of dynamic recognition resource allocation is to start asking a new question:
@@
 
-We propose a new \emph{timeliness} measure of performance vs.
-time (shown in Figure~\ref{fig:figure1}), and present a method based on reinforcement learning that takes various detectors and classifiers as black boxes, and learns a dynamic policy for selecting detector and other actions to achieve the highest performance under this evaluation.
-We are able to obtain better performance than all baselines when there is less time available than is needed to exhaustively run all detectors.
-
-A hypothetical system for vision-based advertising presents a case study.
-The system will have different values and accuracies for objects of different classes, and the queue of unprocessed images will vary in size.
-The detection strategy to maximize profit in such an environment has to be dynamic.
-We explore this scenario using the PASCAL VOC datasets and evaluation regimes, and show that our learned dynamic policy offers a better strategy than a random or optimal static ordering of detectors.
+Taking the task of object detection, we propose a new \emph{timeliness} measure of performance vs. time (shown in Figure~\ref{fig:figure1}).
+We present a method that treats different detectors and classifiers as black boxes, and uses reinforcement learning to learn a dynamic policy for selecting actions to achieve the highest performance under this evaluation.
+Evaluating on the PASCAL VOC dataset and evaluation regime, we are able to obtain better performance than all baselines when there is less time available than is needed to exhaustively run all detectors.

### 2012-11-02 writeups/nips12/related.tex
edited introduction
went through related work

@@
 
-We deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains zero or more objects.
+Formally, we deal with a dataset of images $\mathcal{D}$, where each image $\mathcal{I}$ contains zero or more objects.
 Each object is labeled with exactly one category label $k \in \{1, \dots, K\}$.
@@
 The multi-class, multi-label \textbf{classification} problem asks whether $\mathcal{I}$ contains at least one object of class $k$.
-We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_k \in \mathbb{B} = \{0,1\}$ is set to $1$ if an object of class $k$ is present.
+We write the ground truth for an image as $\mathbf{C}=\{C_1,\dots,C_K\}$, where $C_k \in \{0,1\}$ is set to $1$ if an object of class $k$ is present.
 
 The \textbf{detection} problem is to output a list of bounding boxes (sub-images defined by four coordinates), each with a real-valued confidence that it encloses a single instance of an object of class $k$, for each $k$.
-The answer for a single class is given by an algorithm $\emph{detect}(\mathcal{I},k)$, which outputs a list of sub-image bounding boxes $B$ and their associated confidences.
+The answer for a single class $k$ is given by an algorithm $\emph{detect}(\mathcal{I},k)$, which outputs a list of sub-image bounding boxes $B$ and their associated confidences.
 
-The answer is evaluated by plotting precision vs. recall across dataset $\mathcal{D}$ (by progressively lowering the confidence threshold for a positive detection).
+Performance is evaluated by plotting precision vs. recall across dataset $\mathcal{D}$ (by progressively lowering the confidence threshold for a positive detection).
 The area under the curve yields the Average Precision (AP) metric, which has become the standard evaluation for recognition performance on challenging datasets in vision \cite{pascal-voc-2010}.
-A common measure of a correct detection is the PASCAL overlap: two bounding boxes are considered to match if they have the same label and the ratio of their intersection to their union is at least $\frac{1}{2}$.
+A common measure of a correct detection is the PASCAL overlap: two bounding boxes are considered to match if they have the same class label and the ratio of their intersection to their union is at least $\frac{1}{2}$.
 
-To highlight the hierarchical structure of these problems, we note that (1) the confidences for each sub-image $b \in B$ may be given by $\emph{classify}(b,k)$; (2) correct answer to the detection problem also answers the classification problem.
+To highlight the hierarchical structure of these problems, we note that the confidences for each sub-image $b \in B$ may be given by $\emph{classify}(b,k)$, and, more saliently for our setup, correct answer to the detection problem also answers the classification problem.
 
 Multi-class performance is evaluated by averaging the individual per-class AP values.
-We generalize this metric to a weighted average, with the weights set by the \emph{values} of the classes.
+In a specialized system such as the advertising case study from~\autoref{sec:introduction}, the metric generalizes to a weighted average, with the weights set by the \emph{values} of the classes.
 
 \subsection{Related Work}
-The literature on object recognition is vast.
-Here we briefly summarize work that sufficiently contextualizes our contribution.
+To situate our contribution, let us briefly review approaches to object detection.
 
-\myparagraph{Single-class detection}
+\myparagraph{Object detection}
 The best recent performance has come from detectors that use gradient-based features to represent objects as either a collection of local patches or as object-sized windows \cite{Dalal2005,Lowe2004}.
@@
 Window proposal is most often done exhaustively over the image space, as a ``sliding window''.
-Some approaches use ``jump windows'' (hypotheses voted on by local features) \cite{Vedaldi2009,Vijayanarasimhan2011}, or a bounded search over the space of all possible windows \cite{Lampert2008a}.
+For state-of-the-art performance, the object-sized window models are augmented with parts \cite{Felzenszwalb2010a}, and the bag-of-visual-words models employ non-linear classifiers \cite{Vedaldi2009}.
+%Some approaches use ``jump windows'' (hypotheses voted on by local features) \cite{Vedaldi2009,Vijayanarasimhan2011}, or a bounded search over the space of all possible windows \cite{Lampert2008a}.
 
-None of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal.
-Some work has been done on this topic, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008}.
+%None of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal.
+%Some work has been done on this topic, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008}.
 
-\myparagraph{Context}
-Context has a foundational role in vision.
-One source of context is the scene or other non-detector cues; the most common scene-level feature is the GIST \cite{Oliva2001a} of the image.
+Most methods train individual models for each class.
+Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005}.
+
+% A post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for non-maximum suppression \cite{Desai2009}.
+
+\myparagraph{Using context}
+Leveraging \emph{context} for detection has a long-studied role in vision.
+The most common source of context is the \emph{scene} or other non-detector cues; the most common scene-level feature is the GIST \cite{Oliva2001a} of the image.
 For the commonly used PASCAL VOC dataset \cite{pascal-voc-2010}, GIST and other sources of context are quantitatively explored in~\cite{Divvala2009}.
-Inter-object context has also been shown to be useful for improving detection \cite{Torralba2004}.
+
+Inter-object context has also been shown to improve detection \cite{Torralba2004}.
+In a standard evaluation setup, inter-object context plays a role only in post-filtering, once all detectors have been run.
+In contrast, our work leverages inter-object context in the action-planning loop.
+
 A critical summary of the main approaches to using context for object and scene recognition is given in \cite{Galleguillos2010}.
 
-\myparagraph{Multi-Class Detection}
-Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005}.
-A post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for non-maximum suppression \cite{Desai2009}.
+\myparagraph{Efficiency through cascades}
+An early success in efficient object detection of a single class uses simple, fast features to build up a \emph{cascade} of classifiers, which then considers image regions in a sliding window regime \cite{Viola2001}.
+Most recently, cyclic optimization has been applied to optimize cascades with respect to feature computation cost as well as classifier performance \cite{Chen2012}.
 
-\myparagraph{Cascades}
-An early success in efficient object detection used simple, fast features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime \cite{Viola2001}.
-Most recently, cyclic optimization has been applied to optimize cascades with respect to feature computation cost as well as classifier performance \cite{Chen2012}.
-However, cascades are not dynamic policies---they cannot change the order of execution based on observations obtained during execution, which is our goal.
+To our knowledge, cascades have not been applied to multi-class detection, \todo{is this true?} and they are not dynamic policies.
+They cannot change the order of execution based on observations obtained during execution, which is our goal.
 
-\myparagraph{Anytime Algorithms and Active Classification}
+\myparagraph{Anytime and active classification}
 This surprisingly little-explored line of work in vision is closest to our approach.

### 2012-11-02 writeups/nips12/technical.tex
final
went through related work

@@
 Depending on the setting, the cost can be defined in terms of algorithmic runtime analysis, an idealized property such as number of \emph{flops}, or simply the empirical runtime on specific hardware.
-We take the empirical approach: every executed action advances $t$, the \emph{time into episode}, by its empirical runtime.
+We take the empirical approach: every executed action advances $t$, the \emph{time into episode}, by its runtime.
 
@@
 This is fitted Q-iteration, a variant of generalized policy iteration \cite{Ernst2005,Sutton1998}.
+
+To ensure sufficient exploration of the state space, we implement $\epsilon$-greedy action selection during training: with a probability that decreases with each training iteration, a random action is selected instead of following the policy.
+During test time, $\epsilon$ is set to $0.05$.
 

### 2012-11-03 writeups/nips12/evaluation.tex
camera-ready draft sent to collaborators

@@
 
-We evaluate our system on the multi-class, multi-label detection task as previously described.
-Each detection episode takes an image and outputs detections with associated times, based on the order of actions taken.
-We evaluate on a popular detection challenge task: the PASCAL VOC 2007 dataset \cite{pascal-voc-2010}, which exhibits only a rather modest amount of class co-occurrence: the ``person'' class is highly likely to occur, and less than $10\%$ of the images have more than two classes.
+We evaluate our system on the multi-class, multi-label detection task, as previously described.
+%Each detection episode takes an image and outputs detections with associated times, based on the order of actions taken.
+We evaluate on a popular detection challenge task: the PASCAL VOC 2007 dataset \cite{pascal-voc-2010}.
+This datasets exhibits a rather modest amount of class co-occurrence: the ``person'' class is highly likely to occur, and less than $10\%$ of the images have more than two classes.
 
@@
 
-For the detector actions, we use one-vs-all cascaded deformable part-model detectors on a HOG featurization of the image \cite{Felzenszwalb2010b}, with associated linear classification of the detections.
+For the detector actions, we use one-vs-all cascaded deformable part-model detectors on a HOG featurization of the image \cite{Felzenszwalb2010b}, with linear classification of the list of detections as described in the previous section.
 There are $20$ classes in the PASCAL challenge task, so there are $20$ detector actions.
@@
 We test three different settings of the start and deadline times.
-In the first one, the start time is immediate and execution is cut off at $20$ seconds, which is enough time to run basically all actions.
+In the first one, the start time is immediate and execution is cut off at $20$ seconds, which is enough time to run all actions.
 In the second one, execution is cut off after only $10$ seconds.
@@
 \subfloat[]{
-\includegraphics[width=0.47\linewidth]
+\includegraphics[width=0.53\linewidth]
     {../figures/final1_515.png}\label{fig:results1}} \hfill
 \subfloat[]{
-\includegraphics[width=0.47\linewidth]
+\includegraphics[width=0.44\linewidth]
     {../figures/apvst_expl.pdf}\label{fig:rewards}}
-\caption{(a) AP vs. Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy, with start time of 5 seconds and deadline of 15 seconds. (b) Reward function explanation.}
+\caption{
+(a) AP vs. Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy. (b) Graphically representing our reward function, as described in~\autoref{sec:value}.
+}
 \end{figure}
@@
 We establish the first baseline for our system by selecting actions randomly at each step.
-As shown in Figure \autoref{fig:results1}, this \textbf{Random} policy results in a roughly linear gain of AP vs. time.
+As shown in Figure~\autoref{fig:results1}, the \textbf{Random} policy results in a roughly linear gain of AP vs. time.
 This is expected: the detectors are capable of obtaining a certain level of performance; if half the detectors are run, the expected performance level is half of the maximum level.
 
-To establish an upper bound on performance, we plot the \textbf{Oracle} policy, obtained by re-ordering the actions with the hindsight of the results they produced.
+To establish an upper bound on performance, we plot the \textbf{Oracle} policy, obtained by re-ordering the actions at the end of each detection episode in the order of AP gains they produced.
 
@@
 
-Then there are our proposed systems, described in the previous section : \textbf{RL w/ Direct} and \textbf{RL w/ MRF}.
-In experiments, the two were not exceedingly different in performance, with the MRF model consistently performing slightly better.
+Then there are instantiations of our method, as described in the previous section : \textbf{RL w/ Direct} inference and \textbf{RL w/ MRF} inference.
+In experiments, the two were not exceedingly different in performance, with the \textbf{MRF} model consistently outperforming \textbf{Direct}.
 
@@
 This setting always uses the MRF model to properly update the class probabilities with GIST observations.
-This brings another boost in performance.
-All results are shown in \autoref{tab:results}.
+This brings another small boost in performance.
+The results are shown in \autoref{tab:results}.
+
+Visualizing the learned weights in~\autoref{fig:weights}, we note that the GIST action is learned to never be taken in the greedy ($\gamma=0$) setting, but is learned to be taken with a higher value of $\gamma$.
+It is additionally informative to consider the action trajectories of different policies in~\autoref{fig:trajectories}.
 
@@
   \centering
-  \includegraphics[width=0.86\linewidth]{../figures/trajectories.pdf}
+  \includegraphics[width=0.9\linewidth]{../figures/trajectories.pdf}
   \caption{
@@
 
-Additionally, we evaluated different settings of the discount parameter $\gamma$, and found that a mid-range value works best.
-We only report results for that value on the test set.
-\autoref{fig:weights} shows how changing $\gamma$ affects the learned weights: the GIST action is learned to never be taken in the greedy setting, because it does not bring any immediate detections results.
-In the reinforcement learning setting, however (higher $\gamma$), GIST is learned to be taken for its value in quickly refining the class presence probabilities.
-
-\autoref{fig:trajectories} illustrates the action trajectories of different policies.
-
 \begin{table}[t]
-\caption{
-The areas under the AP vs. Time curve for different experimental conditions.
-Our method reliably beats the intelligent static baseline; including the GIST action further boosts performance.}
+\caption{The areas under the AP vs. Time curve for different experimental conditions.}
 \label{tab:results}

### 2012-11-03 writeups/nips12/introduction.tex
went through related work
camera-ready draft sent to collaborators

@@
-\section{Introduction}
+\section{Introduction} \label{sec:introduction}
 
@@
 At each time step beginning at $t=0$, potential actions are considered according to their \emph{value}, and the $\arg\max$ action is picked.
-
 The selected action is performed and returns \emph{observations}.
@@
 The \emph{belief model} of our system is updated with the observations, which influences the selection of the next action.
-
 The final evaluation of a detection episode is the area of the \emph{AP vs. Time curve} between given start and end times.
@@
 
-% TODO: more fully explain that this is a detection system
 A hypothetical system for vision-based advertising presents a case study: companies pay money to have their products detected in images on the internet.
-The system has different values (e.g. in terms of cost-per-click) and accuracies for different classes of objects, and the queue of unprocessed images varies in size.
+The system has different values (in terms of cost per click) and accuracies for different classes of objects, and the queue of unprocessed images varies in size.
 The detection strategy to maximize profit in such an environment has to exploit every inter-object context signal available to it, because there is not enough time to run detection for all classes.
@@
 We present a method that treats different detectors and classifiers as black boxes, and uses reinforcement learning to learn a dynamic policy for selecting actions to achieve the highest performance under this evaluation.
+
+Specifically, we run scene context and object class detectors over the whole image sequentially, using the results of detection obtained so far to select the next actions.
 Evaluating on the PASCAL VOC dataset and evaluation regime, we are able to obtain better performance than all baselines when there is less time available than is needed to exhaustively run all detectors.

### 2012-11-03 writeups/nips12/nips2012.tex
working on nips final and reorganizing slides into deadline folders
camera-ready draft sent to collaborators

@@
 \usepackage{natbib}
+\usepackage{array}
+\usepackage{tabularx}
 \usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
@@
 \author{
-Sergey Karayev \And
-Tobias Baumgartner \And
-Mario Fritz \And
-Trevor Darrell
+Sergey Karayev \\
+UC Berkeley
+\And
+Tobias Baumgartner \\
+Affiliation
+\And
+Mario Fritz \\
+MPI Saarbr\"{u}cken
+\And
+Trevor Darrell \\
+UC Berkeley
 }
@@
 
-%\nipsfinalcopy % Uncomment for camera-ready version
+\nipsfinalcopy % Uncomment for camera-ready version
 
@@
 On the timeliness measure, our method obtains at least $11\%$ better performance.
-Our code, to be made available upon publication, is easily extensible as it treats detectors and classifiers as black boxes and learns from execution traces using reinforcement learning.
+Our method is easily extensible, as it treats detectors and classifiers as black boxes and learns from execution traces using reinforcement learning.
 \end{abstract}
@@
 The method learns the optimal policy using reinforcement learning, by observing execution traces in training.
-If detection on an image is cut off after only half the detectors have been run, our method does $66\%$ better than random, and $14\%$ better than an intelligent baseline.
+If detection on an image is cut off after only half the detectors have been run, our method does $66\%$ better than a random ordering, and $14\%$ better than an intelligent baseline.
 In particular, our method learns to take action with no intermediate reward in order to improve the overall performance of the system.
@@
 As always with reinforcement learning problems, defining the reward function requires some manual work.
-Here, we derive it for the novel detection AP vs. Time evaluation that we suggest is most useful for evaluating efficiency in recognition.
-Although computation devoted to scheduling actions is much less significant than the computation due to running the actions, an interesting future research direction is to explicitly consider this decision-making cost.
-At time of publication, we will release the code of our modular framework, that allows for easy incorporation of other classifiers and detectors on different tasks and rewards.
+Here, we derive it for the novel detection AP vs. Time evaluation that we suggest is useful for evaluating efficiency in recognition.
+Although computation devoted to scheduling actions is less significant than the computation due to running the actions, an interesting future research direction is to explicitly consider this decision-making cost; the same goes for feature computation costs.
+The code for our method is available\footnote{\url{http://sergeykarayev.com/work/timely/}}.
 
-% \subsubsection*{Acknowledgments}
-% Use unnumbered third level headings for the acknowledgments. All
-% acknowledgments go at the end of the paper. Do not include 
-% acknowledgments in the anonymized submission, only in the 
-% final paper.
+\subsubsection*{Acknowledgments}
+This research was made with Government support under and awarded by DoD, Air Force Office of Scientific Research, National Defense Science and Engineering Graduate (NDSEG) Fellowship, 32 CFR 168a.
 

### 2012-11-03 writeups/nips12/related.tex
camera-ready draft sent to collaborators

@@
 \subsection{Related Work}
-To situate our contribution, let us briefly review approaches to object detection.
 
@@
 Window proposal is most often done exhaustively over the image space, as a ``sliding window''.
+
 For state-of-the-art performance, the object-sized window models are augmented with parts \cite{Felzenszwalb2010a}, and the bag-of-visual-words models employ non-linear classifiers \cite{Vedaldi2009}.
+We employ the former detector in our evaluation.
 %Some approaches use ``jump windows'' (hypotheses voted on by local features) \cite{Vedaldi2009,Vijayanarasimhan2011}, or a bounded search over the space of all possible windows \cite{Lampert2008a}.
@@
 
-Most methods train individual models for each class.
-Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005}.
+% Most detection methods train individual models for each class.
+% Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005}.
 
@@
 \myparagraph{Using context}
-Leveraging \emph{context} for detection has a long-studied role in vision.
-The most common source of context is the \emph{scene} or other non-detector cues; the most common scene-level feature is the GIST \cite{Oliva2001a} of the image.
-For the commonly used PASCAL VOC dataset \cite{pascal-voc-2010}, GIST and other sources of context are quantitatively explored in~\cite{Divvala2009}.
+The most common source of context for detection is the \emph{scene} or other non-detector cues; the most common scene-level feature is the GIST \cite{Oliva2001a} of the image.
+We use this source of scene context in our evaluation.
 
@@
 A critical summary of the main approaches to using context for object and scene recognition is given in \cite{Galleguillos2010}.
+For the commonly used PASCAL VOC dataset \cite{pascal-voc-2010}, GIST and other sources of context are quantitatively explored in~\cite{Divvala2009}.
 
@@
 
-To our knowledge, cascades have not been applied to multi-class detection, \todo{is this true?} and they are not dynamic policies.
+To our knowledge, cascades have not been applied to multi-class detection, and they are not dynamic policies.
 They cannot change the order of execution based on observations obtained during execution, which is our goal.

### 2012-11-03 writeups/nips12/technical.tex
camera-ready draft sent to collaborators

@@
 As shown in Figure~\ref{fig:figure1}, the system is given two times: the setup time $T_s$ and deadline $T_d$.
-From the setup time to the deadline, we want to obtain the best possible answer if stopped at any given time.
+We want to obtain the best possible answer if stopped at any given time between the setup time and the deadline.
 A single-number metric that corresponds to this objective is the area captured under the curve between the start and deadline bounds, normalized by the total area.
@@
 \subsection{Sequential Execution}
-An \emph{open-loop} policy takes actions in a sequence that does not depend on observations received from previous actions.
-The common classifier cascade is an example \cite{Viola2001}.
+An \emph{open-loop} policy, such as the common classifier cascade \cite{Viola2001}, takes actions in a sequence that does not depend on observations received from previous actions.
 In contrast, our goal is to learn a dynamic, or \emph{closed-loop}, policy, which would exploit the signal in scene and inter-object context for a maximally efficient path through the actions.
@@
 We refer to the information available to the decision process as the \emph{state} $s$.
-The state includes the currently believed distribution over class presence variables $P(\mathbf{C}) = \{P(C_0), \ldots, P(C_K)\}$, where we write $P(C_k)$ to mean $P(C_k=1)$.
+The state includes the current estimate of the distribution over class presence variables $P(\mathbf{C}) = \{P(C_0), \ldots, P(C_K)\}$, where we write $P(C_k)$ to mean $P(C_k=1)$ (class $k$ is present in the image).
 
@@
 The specific actions we consider in the following exposition are detector actions $a_{{det}_i}$, where ${det}_i$ is a detector class $C_i$, and a scene-level context action $a_{gist}$, which updates the probabilities of all classes.
+Although we avoid this in the exposition, note that our system easily handles multiple detector actions per class.
 
@@
 As our goal is to pick actions dynamically, we want a function $Q(s,a): S \times \mathcal{A} \mapsto \mathbb{R}$, where $S$ is the space of all possible states, to assign a value to a potential action $a \in \mathcal{A}$ given the current state $s$ of the decision process.
-We can then define the desired policy $\pi$ as simply taking the (untaken) action with the maximum value:
+We can then define the policy $\pi$ as simply taking the action with the maximum value:
 \begin{align}
@@
 
-Although the action space $\mathcal{A}$ is quite manageable, consisting of the detectors and global classifier we would like to run on the image, the space of possible states $S$ is intractable.
-Therefore we cannot learn a tabular representation of $Q(s,a)$, and must use function approximation to represent it \cite{Sutton1998}.
-We featurize the state-action pair and assume linear structure: $Q^\pi(s,a_i) = \theta_\pi^\top  \phi(s,a_i)$.
+Although the action space $\mathcal{A}$ is manageable, the space of possible states $S$ is intractable, and we must use function approximation to represent $Q(s,a)$: a common technique in reinforcement learning \cite{Sutton1998}.
+We featurize the state-action pair and assume linear structure:
+\begin{align}
+Q^\pi(s,a) = \theta_\pi^\top \phi(s,a)
+\end{align}
 
-The policy's performance at time $t$ is determined by the detections that are part of the set of observations $\mathbf{o}^j$ at the last state $s^j$ before $t$.
+The policy's performance at time $t$ is determined by all detections that are part of the set of observations $\mathbf{o}^j$ at the last state $s^j$ before $t$.
+Recall that detector actions returns lists of detection hypotheses.
 Therefore, the final AP vs. Time evaluation of an episode is a function $eval(h,T_s,T_d)$ of the history of execution $h=s^0,s^1,\dots,s^J$.
@@
 
-As shown in \autoref{fig:rewards}, this evaluation function is additive per action, as each action can generate detections that either raise or lower the mean AP of the results so far ($\Delta ap$) and takes a certain time ($\Delta t$).
-From these and $T_s$ and $T_d$, we can find the area under the curve that was contributed by the action.
-So, we can then represent the final evaluation $eval(h,T_s,T_d)$ in terms of individual rewards: $\sum_{j=0}^J R(s^j,a^j)$.
+Note from~\autoref{fig:rewards} that this evaluation function is additive per action, as each action $a$ generates observations that may raise or lower the mean AP of the results so far ($\Delta ap$) and takes a certain time ($\Delta t$).
+We can accordingly represent the final evaluation $eval(h,T_s,T_d)$ in terms of individual action rewards: $\sum_{j=0}^J R(s^j,a^j)$.
 
-Specifically, as shown in Figure~\ref{fig:rewards}, we define the \emph{reward} of an action as
+Specifically, as shown in Figure~\ref{fig:rewards}, we define the \emph{reward} of an action $a$ as
 \begin{align}\label{eq:advanced}
-R(s^j,a_i) = \Delta \text{ap}_i (t_T^j-\frac{1}{2}\Delta t_i)
+R(s^j,a) = \Delta \text{ap} (t_T^j-\frac{1}{2}\Delta t)
 \end{align}
-where $t_T^j$ and $\text{ap}^j$ are the time left until the deadline and the AP at state $s^j$, and $\Delta t_i$ and $\Delta \text{ap}_i$ are the time taken and AP change produced by the action $a_i$.
-(For clarity of exposition, we do not account for $T_s$ here.)
+where $t_T^j$ is the time left until $T_d$ at state $s^j$, and $\Delta t$ and $\Delta \text{ap}$ are the time taken and AP change produced by the action $a$.
+(We do not account for $T_s$ here for clarity of exposition.)
 
@@
 \begin{align} \label{eq:recursive_value}
-Q^\pi(s^j,a_i) = \mathbb{E}_{s^{j+1}} [R(s^j,a_i) + \gamma Q^\pi(s^{j+1},\pi(s^{j+1}))]
+Q^\pi(s^j,a) = \mathbb{E}_{s^{j+1}} [R(s^j,a) + \gamma Q^\pi(s^{j+1},\pi(s^{j+1}))]
 \end{align}
-where $\gamma \in [0,1]$ is a \emph{discount} value that can mitigate the effects of increasing state-transition uncertainty over long episodes.
+where $\gamma \in [0,1]$ is the \emph{discount} value.
+
+With $\gamma=0$, the value function is determined entirely by the immediate reward, and so only completely greedy policies can be learned.
+With $\gamma=1$, the value function is determined by the correct expected rewards to the end of the episode.
+However, a lower value of $\gamma$ mitigates the effects of increasing uncertainty regarding the state transitions over long episodes. %, and so the highest value is not necessarily best.
+We set this meta-parameter of our approach through cross-validation, and find that a mid-level value ($0.4$) works best.
 
@@
 
-Learning the policy is then a problem of repeatedly gathering samples with the current policy, minimizing the error between the discounted reward to the end of the episode as predicted by our current $Q(s^j,a_i)$ and the actual values gathered, and updating the policy with the resulting weights.
-This is fitted Q-iteration, a variant of generalized policy iteration \cite{Ernst2005,Sutton1998}.
+We then learn the optimal policy by repeatedly gathering samples with the current policy, minimizing the error between the discounted reward to the end of the episode as predicted by our current $Q(s^j,a)$ and the actual values gathered, and updating the policy with the resulting weights.
+%This is fitted Q-iteration, a variant of generalized policy iteration \cite{Ernst2005,Sutton1998}.
 
@@
 
-We use $L_2$-regularized regression to minimize the error.
-We run $15$ iterations of accumulating samples by running $350$ episodes, starting with a baseline policy which will be described in \autoref{sec:evaluation}, and cross-validating the regularization parameter at each iteration; samples are not thrown away between iterations.
+To prevent overfitting to the training data, we use $L_2$-regularized regression.
+We run $15$ iterations of accumulating samples by running $350$ episodes, starting with a baseline policy which will be described in \autoref{sec:evaluation}, and cross-validating the regularization parameter at each iteration.
+Samples are not thrown away between iterations.
 
-A meta-parameter of the approach is the discount $\gamma$.
-With $\gamma=0$, the value function is determined entirely by the immediate reward.
-Learning in this case can only result in completely greedy policies.
-
-With $\gamma=1$, the value function is determined by the expected rewards to the end of the episode, and so should be a close approximation to the final evaluation metric.
-However, the highest value for $\gamma$ is not necessarily best if the action-value function is not expressive enough to represent the actual state transition behavior of the world.
-We experiment with several values of $\gamma$, and find a mid-level value ($0.4$) to work best.
+With pre-computed detections on the PASCAL VOC 2007 dataset, the training procedure takes about $4$ hours on an $8$-core \emph{Xeon E5620} machine.
 
 \subsection{Feature representation}
-Our policy is at its base determined by a linear function of the features of the state: $\pi(s) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \theta_\pi^\top \phi(s,a_i)$.
-Since we want to be able to learn a dynamic policy, the observations $\mathbf{o}$ that are part of the state $s$ should play a role in determining the value of a potential action.
+Our policy is at its base determined by a linear function of the features of the state:
+\begin{align}
+\pi(s) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \theta_\pi^\top \phi(s,a_i).
+\end{align}
+
+%Since we want to be able to learn a dynamic policy, the observations $\mathbf{o}$ that are part of the state $s$ should play a role in determining the value of a potential action.
 
 We include the following quantities as features $\phi(s,a)$:
-\begin{description}
-\item[$P(C_a)$] The prior probability of the class that corresponds to the detector of action $a$
-\item[$P(C_0|\mathbf{o}) \ldots P(C_K|\mathbf{o})$] The probabilities of all classes, conditioned on the current set of observations.
-\item[$H(C_0|\mathbf{o}) \ldots H(C_K|\mathbf{o})$] The entropies of all classes, conditioned on the current set of observations.
-\end{description}
 
-Additionally, we include the mean and maximum entropies of all classes, the expected time of the action $c(a)$, and time features that represent the times until start and deadline, for a total of $F$ features.
+\begin{tabularx}{0.8\linewidth}{p{0.23\linewidth}p{0.69\linewidth}}
+$P(C_a)$ & The prior probability of the class that corresponds to the detector of action $a$ (omitted for the scene-context action).\\
+$P(C_0|\mathbf{o}) \ldots P(C_K|\mathbf{o})$ & The probabilities for all classes, conditioned on the current set of observations.\\
+$H(C_0|\mathbf{o}) \ldots H(C_K|\mathbf{o})$ & The entropies for all classes, conditioned on the current set of observations. \\
+\end{tabularx}
+
+Additionally, we include the mean and maximum entropy of class presence and time features that represent the times until start and deadline, for a total of $F = 1+|K|*2+6$ features.
 
@@
 There are two related limitations of MDPs when it comes to most systems of interesting complexity, however: the state has to be functionally approximated instead of exhaustively enumerated; and some aspects of the state are not observed, making the problem a Partially Observed MDP (POMDP), for which exact solution methods are intractable for all but rather small problems \cite{Roy2002}.
+Our initial solution to the problem of partial observability is to include features corresponding to our level of uncertainty into the feature representation, as in the technique of \emph{augmented} MDPs \cite{Kwok2004}.
 
-There isn't much to do about the necessity of approximating the state but design good features.
-Our initial solution to the partial observability problem is to include uncertainty features into the feature representation to \emph{augment} the MDP \cite{Kwok2004}.
+To formulate learning the policy as a single regression problem, we represent the features in block form, where $\phi(s,a)$ is a vector of size $F|\mathcal{A}|$, with all values set to $0$ except for the $F$-sized block corresponding to $a$.
 
-To formulate learning the policy as a single regression problem, we represent the features in block form, where $\phi(s,a_i)$ is a vector of size $F|\mathcal{A}|$, with all values set to $0$ except for the block corresponding to $a_i$.
-
-As an illustration, we visualize the learned weights on these features in \autoref{fig:weights}, reshaped such that each row shows the weights learned for an action, in order.
-The featurization for the $a_{gist}$ scene-context action, which concerns all classes, omits the first $P(C_a)$ feature.
+As an illustration, we visualize the learned weights on these features in \autoref{fig:weights}, reshaped such that each row shows the weights learned for an action, with the top row representing the scene context action and then next $20$ rows corresponding to the PASCAL VOC class detector actions.
 
@@
 Additionally, updating $P(C_i|\mathbf{o})$ presents choices regarding independence assumptions between the classes.
+We evaluate two approaches for updating probabilities: \emph{direct} and \emph{MRF}.
 
-We evaluate two approaches for updating probabilities: \emph{direct} and \emph{MRF}.
 In the \emph{direct} method, $P(C_i|\mathbf{o}) = score(C_i)$ if $\mathbf{o}$ includes the observations for class $C_i$ and $P(C_i|\mathbf{o}) = P(C_i)$ otherwise.
 This means that an observation of class $i$ does not influence the estimated probability of any class but $C_i$.
-$score(C_i)$ for $a_{{det}_i}$ is obtained by training a probabilistic classifier on the detections output.
-$score(C_i)$ for $a_{gist}$ is obtained by training probabilistic classifiers on the GIST feature, for all classes.
 
@@
 
-The graphical model structure is set as fully-connected, but some classes are overwhelmingly unlikely to co-occurr in our dataset.
-Accordingly, the graph edge weights are learned with $L_1$ regularization, which obtains the desired sparse structure \cite{Lee2006}.
+The graphical model structure is set as fully-connected, but some classes almost never co-occurr in our dataset.
+Accordingly, the edge weights are learned with $L_1$ regularization, which obtains a sparse structure \cite{Lee2006}.
 All parameters of the model are trained on fully-observed data, and Loopy Belief Propagation inference is implemented with an open-source graphical model package \cite{Jaimovich2010}.
-% As exact inference is generally intractable in this model, we use Loopy Belief Propagation; although it does not provide general convergence guarantees, it has been shown to work well empirically on similar tasks \cite{Desai2009}.
+
+An implementation detail: $score(C_i)$ for $a_{{det}_i}$ is obtained by training a probabilistic classifier on the list of detections, featurized by the top few confidence scores and the total number of detections.
+Similarly, $score(C_i)$ for $a_{gist}$ is obtained by training probabilistic classifiers on the GIST feature, for all classes.

### 2012-11-03 writeups/nips12/technical.tex
small change

@@
 
-Additionally, we include the mean and maximum entropy of class presence and time features that represent the times until start and deadline, for a total of $F = 1+|K|*2+6$ features.
+Additionally, we include the mean and maximum entropy of class presence and time features that represent the times until start and deadline, for a total of $F = 1+2K+6$ features.
 

### 2012-11-10 writeups/nips12/evaluation.tex
done with camera ready

@@
 Then there are instantiations of our method, as described in the previous section : \textbf{RL w/ Direct} inference and \textbf{RL w/ MRF} inference.
-In experiments, the two were not exceedingly different in performance, with the \textbf{MRF} model consistently outperforming \textbf{Direct}.
+As the \textbf{MRF} model consistently outperformed \textbf{Direct} by a small margin, we report results for that model only.
 
@@
 Visualizing the action trajectories of different policies.
-Action selection traces are plotted in orange over many episodes; the size of the blue circles correspond to the $\Delta ap$ obtained by the action.
+Action selection traces are plotted in orange over many episodes; the size of the blue circles correspond to the increase in AP obtained by the action.
 We see that the \textbf{Random} policy selects actions and obtains rewards randomly, while the \textbf{Oracle} policy obtains all rewards in the first few actions.
@@
 \begin{center}
-\begin{tabular}{|l|l|l|l|l|l|}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline
-Bounds & Random & Fixed Order & RL w/ MRF & w/ GIST         & Oracle \\ \hline
+Bounds & Random & Fixed Order & RL        & RL w/ GIST         & Oracle \\ \hline
 (0,20) & 0.250  & 0.342       & 0.378     & \textbf{0.382}  & 0.488 \\ 

### 2012-11-10 writeups/nips12/nips2012.tex
done with camera ready

@@
 Tobias Baumgartner \\
-Affiliation
+RWTH Aachen University
 \And
 Mario Fritz \\
-MPI Saarbr\"{u}cken
+MPI for Informatics 
 \And
@@
 Our method for \emph{timely} multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
-Toward this goal, we formulate a dynamic, \emph{closed-loop} policy that infers the contents of the image in order to decide which detector to deploy next.
+Toward this goal, we formulate a dynamic, closed-loop policy that infers the contents of the image in order to decide which detector to deploy next.
 In contrast to previous work, our method significantly diverges from the predominant greedy strategies, and is able to learn to take actions with deferred values.
 We evaluate our method with a novel \emph{timeliness} measure, computed as the area under an Average Precision vs. Time curve.
-Experiments are conducted on the eminent PASCAL VOC object detection dataset.
+Experiments are conducted on the PASCAL VOC object detection dataset.
 If execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
@@
 Here, we derive it for the novel detection AP vs. Time evaluation that we suggest is useful for evaluating efficiency in recognition.
-Although computation devoted to scheduling actions is less significant than the computation due to running the actions, an interesting future research direction is to explicitly consider this decision-making cost; the same goes for feature computation costs.
+Although computation devoted to scheduling actions is less significant than the computation due to running the actions, the next research direction is to explicitly consider this decision-making cost; the same goes for feature computation costs.
+Additionally, it is interesting to consider actions defined not just by object category but also by spatial region.
 The code for our method is available\footnote{\url{http://sergeykarayev.com/work/timely/}}.

### 2012-11-30 writeups/nips12/poster/poster.tex
nips poster draft

\documentclass[landscape]{article}

\usepackage{tboxen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage[tight]{subfigure}
\usepackage{color}
\usepackage{type1cm}
\usepackage{tabularx}
\usepackage{subfig}

% Custom variables

% How much length we want to add to the poster while editing.  Note
% that these are just integer variables.  There is probably a better
% way to do this...
\newcounter{width}
\newcounter{height}
\newcounter{extra-length}
% these are in cm
\setcounter{width}{110}
\setcounter{height}{68} % developing at 2/3 magnification for 40x65in poster
\setcounter{extra-length}{0} % for development

% Boolean variable: whether or not we want to show grid lines
\newif\ifusegrid
\usegridtrue
\usegridfalse

% You can define any rgb colors you want for the background.  The
% first two lines define a blue to cream fade.  See how they are used
% below.
\definecolor{bottomcolor}{rgb}{ 0.538, 0.663, .788}
\definecolor{topcolor}{rgb}{    0.538, 0.663, .788}
% Uncomment these next two lines if you want to have an all white background.
% TODO: temp dev setting
%\definecolor{topcolor}{rgb}{1,1,1}
%\definecolor{bottomcolor}{rgb}{1,1,1}

% Other counters that we will use below.
\newcounter{grid-top}
\newcounter{grid-right}
\newcounter{title-top}
\newcounter{title-left-margin}
\newcounter{title-width}
\newcounter{title-left}
\newcounter{title-box-width}

% ==============================================================================
% Set up paper sizes

\newcounter{total-height}
\setcounter{total-height}{\arabic{height} + \arabic{extra-length}}
\setlength{\paperwidth}{\arabic{width}cm}
\setlength{\paperheight}{\arabic{total-height}cm}
\setlength{\textwidth}{\paperwidth}
\setlength{\textheight}{\paperheight}

% These usually stay the same for tboxen
\setlength{\headheight}{0 cm}
\setlength{\headsep}{0 cm}
\setlength{\topmargin}{-2 cm} 
\setlength{\oddsidemargin}{-1in}

% From tboxen:
% this is often necessary for pdf and dvips to work
\ifx\pdfoutput\undefined 
% for dvi
\special{papersize=\arabic{width}cm,\arabic{height}cm}
\else 
% for pdf
\pdfpagewidth=\paperwidth 
\pdfpageheight=\paperheight 
\fi

% ==============================================================================
% POSTER STARTS HERE
\begin{document}
\begin{center}

  % ==============================================================================
  % Main body
  \begin{tikzpicture}

    % This defines your background box - entries are pretty self explanatory.
    % The colors ``topcolor'' and ``bottomcolor'' are defined above.
    \shade[top color = topcolor,
      bottom color = bottomcolor,
      rounded corners = 1cm, % The larger this is, the rounder your corners
      line width = 2mm, % The width of your border lines
      draw]
    (0,0) rectangle +(\textwidth-2cm,\textheight-1cm); 
    % This last line above just sets up the bounding box for the whole poster.  You don't want to change it.

    % ==============================================================================
    \ifusegrid
    % Draw grid guidelines if desired.
    \setcounter{grid-top}{\arabic{total-height}-1}
    \setcounter{grid-right}{\arabic{width}-2}
    \draw[style=help lines] (0,\arabic{extra-length}) grid (\arabic{grid-right},\arabic{grid-top});
    \setcounter{grid-top}{\arabic{height}-1}
    \foreach \x in {0,5,...,\arabic{grid-right}}
    \foreach \y in {0,5,...,\arabic{grid-top}}
    \draw (\x,\y) + (0,\arabic{extra-length}) node{\tiny \x,\y};
    \fi

    % ==============================================================================
    % Title box
    %
    % The following defaults make the title box span the whole top,
    % start 3cm from the top, and end 2 cm from both sides. I have
    % hard-coded the 2s and 3 below.  Play around with the trade-off
    % between changing these numbers and changing
    % ``title-left-margin'' if you are not happy with the defaults.
    \setcounter{title-left-margin}{0} % This specifies the additional padding to the right and left of the title.  Can be negative.
    \setcounter{title-top}{\arabic{total-height}-3} % Places the top of the title 3 cm from the top of the poster.
    \setcounter{title-width}{\arabic{width}-2*\arabic{title-left-margin} - 2*2 - 4} % Automatically calculates the width of the title based on the margin.
    \setcounter{title-left}{\arabic{title-left-margin} + 2} % Automatically places the title 2m from the left edge of the poster + the user specified margin.
    \setcounter{title-box-width}{\arabic{width} - 30}
    \path (\arabic{title-left},\arabic{title-top}) node(title) [style=tbox, text width=\arabic{title-width}cm] {
      \begin{center}

        % Three parboxes allow for images on both sides of the title
        % box with the title text in the middle.
        \parbox{10cm} {
        \includegraphics[width=10cm]{../../figures/berkeley_seal.pdf}
        }
        \parbox{\arabic{title-box-width}cm} {
          \centering
              {\Huge \bf{Timely Object Recognition} } \\
              \vspace{1cm}
              \begin{tabular}{cccc}
                {\huge Sergey Karayev$^1$, \hfill} & {\huge Tobias Baumgartner$^2$, \hfill} & {\huge Mario Fritz$^3$, \hfill} & {\huge Trevor Darrell$^1$}\\
                \multicolumn{4}{c}{\Large $^1$UC Berkeley, $^3$RWTH Aachen, $^3$MPI Informatics}
              \end{tabular}
        }
        \parbox{10cm} {
          % This is just an empty box to make the actual title centered.
          % Add another seal or image if you wish.
          \hspace{1cm}
        }

      \end{center}
    };

    % ==============================================================================
    % ABSTRACT
    \path (title.south west) ++(0cm,-2cm) + (-\arabic{title-left-margin}cm,0cm) node(introduction) [style=tbox,text width=30cm] {
    \begin{itemize}
      \item Our task is multi-class object detection in a setting where there is not enough time to evaluate all detectors.

      \item We use reinforcement learning to learn a \emph{dynamic} policy for selecting detectors and classifiers.

      \item We evaluate detection performance vs. time with the novel \emph{timeliness} measure, and test on the PASCAL VOC challenge.
    \end{itemize}

    }; \addcenteredtitle{introduction}{Abstract} 
    % The above line adds the title ``Introduction'' to the box named ``introduction''.

    % ==============================================================================
    % FIGURE 1 WITH EXPLANATION 
    \path (introduction.south west) ++(0cm,-2cm) node(coding) [style=tbox,text width=30cm] {
      \begin{center}
        \includegraphics[width=26cm]{../../figures/figure1_extended.pdf}
      \end{center}

      \begin{itemize}
        \item Potential actions $a \in \mathcal{A}$ are considered according to their predicted \emph{value}.
        \item The value $Q(s,a)$ depends on the \emph{belief state} of the system as well as the action considered.
        \item The selected action returns observations (list of detections, or evaluated feature).
        \item Observations update the belief state through an inference process.
        \item The final evaluation is the area of the AP vs. Time curve between the start time $T_s$ and end time $T_d$.
        \item VOCalues are learned with reinforcement learning, using a reward function derived from this evaluation.
      \end{itemize}

    }; \addcenteredtitle{coding}{Sequential Detection}

    % ==============================================================================
    % Learning the Policy
    \path (introduction.north east) ++(2cm,0cm) node(model) [style=tbox,text width=34 cm] {
      % \begin{center}
      %   \includegraphics[width=20cm]{../../figures/pomdp_annotated.pdf}
      % \end{center}
      We define our policy as taking an untaken action with maximum value.
      \begin{align*} \pi(s) = \arg\max_{a_i \in \mathcal{A} \setminus \mathcal{O}} Q(s,a_i) = \theta_\pi^\top \phi(s,a) \end{align*}
      The Q-function is linearly approximated.
      \\

      \begin{center}\textbf{Reward Function}\end{center}

      \parbox{20cm}{
      The final performance evaluation of area under the AP vs. Time curve between $T_s$ and $T_d$ is additive per action.
      We define the reward function as
      \begin{align*} R(s^j,a) = \Delta \text{ap} (t_T^j-\frac{1}{2}\Delta t) \end{align*}}
      \parbox{14cm}{
      \begin{center}
        \includegraphics[height=10cm]{../../figures/apvst_expl.pdf}
      \end{center}}
      \\

      \begin{center}\textbf{Reinforcement Learning}\end{center}
      To compute $Q^\pi(s^j,a) = \mathbb{E} [R \mid s, a, \pi)]$, where $R = \sum_{i=j}^J \gamma^{i-j} R(s^i,a^i)$ and $J$ is the index of the last action before deadline time $T_d$, we run Monte Carlo policy iteration.
      We evaluate full episodes of the detection task on several thousand images, with a decreasing $\epsilon$-greedy policy.
      Policy weights $\theta$ are updated with $L_2$ regularization.

      \paragraph{}
      We evaluate different values of the reward discount $\gamma$, which at $0$ induces a completely greedy policy, and at $1$ has full lookahead.
      We find $\gamma = 0.4$ to work best in cross-validation.
      \\

      \begin{center}\textbf{Feature Representation}\end{center}
      The features $\phi(s, a)$ are composed of\\

      {\small
      \begin{tabularx}{0.8\linewidth}{p{0.23\linewidth}p{0.69\linewidth}}
      $P(C_a)$ & The prior probability of presence of the class that corresponds to the detector of action $a$ (omitted for the scene-context action).\\

      $P(C_0|\mathbf{o}) \ldots P(C_K|\mathbf{o})$ & The presence probabilities for all classes, conditioned on the current set of observations.\\

      $H(C_0|\mathbf{o}) \ldots H(C_K|\mathbf{o})$ & The entropies for all classes, conditioned on the current set of observations. \\

      $t^j_T$ & The time until deadline, and four other time features.\\
      \end{tabularx}
      }\\\\

      \begin{center}\textbf{Updating the belief state}\end{center}
      Observations $\mathbf{o}$ of detector for class $k$ update $P(C_k|\mathbf{o})$ either \emph{directly} (using a probability estimated by a classifier trained on the detector output) or through an \emph{MRF}.
      The MRF is learned with $L_1$-regularization and inference is done with loopy belief propagation.

    }; \addcenteredtitle{model}{Learning the Policy}

    % ==============================================================================
    % RESULTS
    \path (model.north east) ++(2cm,0cm) node(results) [style=tbox,text width=30cm] {
    We evaluated on the PASCAL VOC 2007 detection task, with 20 Deformable Part Model detectors (one per class), and an additional
    scene context action (GIST feature).
    \\

    We compared against a random baseline, an optimal static ordering, and an oracle ordering.

    \parbox{12cm}{
    \textbf{Weights} Learning with a higher $\gamma$ results in policies more relient on the global scene feature, for example.}%
    \parbox{18cm}{\hfill
    \includegraphics[width=17cm]{../../figures/weights.pdf}}
    \\

    \parbox{18cm}{
    \includegraphics[width=17cm]{../../figures/trajectories.pdf}}%\hfill
    \parbox{12cm}{
    \textbf{Trajectories} Action selection traces are plotted in orange over many episodes; the size of the blue circles correspond to the increase in AP obtained by the action. Our policy does not stick a static order but selects actions dynamically to maximize the rewards obtained early on.}
    \\\\

    \parbox{18cm}{
    \textbf{Performance vs. Time}\\
    If execution is stopped when only half the detectors have been run, our method obtains 66\% better AP than a random ordering, and 14\% better performance than an intelligent baseline. On the timeliness measure, our method obtains at least 11\% better performance}
    \parbox{12cm}{\hfill
    \includegraphics[width=11cm]{../../figures/final1.png}}%\hfill
    \\

    \begin{center}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Bounds & Random & Fixed Order & RL        & RL w/ GIST         & Oracle \\ \hline
    (0,20) & 0.250  & 0.342       & 0.378     & \textbf{0.382}  & 0.488 \\ 
    (0,10) & 0.119  & 0.240       & 0.266     & \textbf{0.267}  & 0.464 \\ 
    (5,15) & 0.257  & 0.362       & 0.418     & \textbf{0.420}  & 0.530 \\ \hline
    \end{tabular}
    \end{center}

    }; \addcenteredtitle{results}{Results}

\end{tikzpicture}

\end{center}
\end{document}

### 2012-11-30 writeups/nips12/poster/poster.tex
mario's suggestions

@@
 \usegridtrue
-\usegridfalse
+%\usegridfalse
 
@@
     \setcounter{title-left-margin}{0} % This specifies the additional padding to the right and left of the title.  Can be negative.
-    \setcounter{title-top}{\arabic{total-height}-3} % Places the top of the title 3 cm from the top of the poster.
+    %% TODO: CAN GET 1CM AT TOP HERE  (when the number is -2)
+    \setcounter{title-top}{\arabic{total-height}-2} % Places the top of the title 3 cm from the top of the poster.
     \setcounter{title-width}{\arabic{width}-2*\arabic{title-left-margin} - 2*2 - 4} % Automatically calculates the width of the title based on the margin.
@@
         \parbox{10cm} {
-        \includegraphics[width=10cm]{../../figures/berkeley_seal.pdf}
+        \includegraphics[height=9cm]{../../figures/berkeley_seal.pdf}
         }
@@
               \begin{tabular}{cccc}
-                {\huge Sergey Karayev$^1$, \hfill} & {\huge Tobias Baumgartner$^2$, \hfill} & {\huge Mario Fritz$^3$, \hfill} & {\huge Trevor Darrell$^1$}\\
-                \multicolumn{4}{c}{\Large $^1$UC Berkeley, $^3$RWTH Aachen, $^3$MPI Informatics}
+                {\huge Sergey Karayev$^1$, \hfill} & {\huge Tobias Baumgartner$^2$, \hfill} & {\huge Mario Fritz$^3$, \hfill} & {\huge Trevor Darrell$^1$}\\\\
+                \multicolumn{4}{c}{\Large $^1$UC Berkeley, \hspace{2cm} $^2$RWTH Aachen, \hspace{2cm} $^3$MPI Informatics}
               \end{tabular}
@@
         \parbox{10cm} {
-          % This is just an empty box to make the actual title centered.
-          % Add another seal or image if you wish.
-          \hspace{1cm}
+          \includegraphics[width=10cm]{../../figures/MPI_logo.png}
         }
@@
 
-      \item We use reinforcement learning to learn a \emph{dynamic} policy for selecting detectors and classifiers.
+      \item We use reinforcement learning to learn a \emph{dynamic} policy for selecting detectors and classifiers, and learn to take actions that do not provide immediate reward.
 
@@
       \begin{center}
-        \includegraphics[width=26cm]{../../figures/figure1_extended.pdf}
+        \includegraphics[width=24cm]{../../figures/pomdp_annotated.pdf}
       \end{center}
@@
       \begin{itemize}
-        \item Potential actions $a \in \mathcal{A}$ are considered according to their predicted \emph{value}.
-        \item The value $Q(s,a)$ depends on the \emph{belief state} of the system as well as the action considered.
-        \item The selected action returns observations (list of detections, or evaluated feature).
+        \item An action $a \in \mathcal{A}$ can run detection for an object class $k$ in the whole image, or classify the scene.
+        \item Potential actions are considered according to their predicted \emph{value} $Q(s,a)$, which also depends on the \emph{belief state} $s$ of the system.
+        \item The selected action returns observations in the form of a list of detections, or simply an evaluated feature.
         \item Observations update the belief state through an inference process.
         \item The final evaluation is the area of the AP vs. Time curve between the start time $T_s$ and end time $T_d$.
-        \item VOCalues are learned with reinforcement learning, using a reward function derived from this evaluation.
       \end{itemize}
+
+      \begin{center}\line(1,0){350}\end{center}
+
+    \begin{center}\textbf{Policy Trajectories}\end{center}
+
+    \parbox{20cm}{
+    \includegraphics[width=19cm]{../../figures/trajectories.pdf}}%\hfill
+    \parbox{10cm}{
+    Action selection traces are plotted over many episodes; the size of the circles correspond to the increase in AP obtained by the action.
+Our policy selects actions dynamically to maximize the rewards obtained early on.}
 
@@
     \path (introduction.north east) ++(2cm,0cm) node(model) [style=tbox,text width=34 cm] {
-      % \begin{center}
-      %   \includegraphics[width=20cm]{../../figures/pomdp_annotated.pdf}
-      % \end{center}
+      \begin{center}
+        \includegraphics[width=30cm]{../../figures/figure1_extended_hor.pdf}
+      \end{center}
+
       We define our policy as taking an untaken action with maximum value.
       \begin{align*} \pi(s) = \arg\max_{a_i \in \mathcal{A} \setminus \mathcal{O}} Q(s,a_i) = \theta_\pi^\top \phi(s,a) \end{align*}
-      The Q-function is linearly approximated.
-      \\
 
-      \begin{center}\textbf{Reward Function}\end{center}
+      The value function
+      \begin{align*}Q^\pi(s^j,a) = \mathbb{E} [R \mid s, a, \pi)]\end{align*}
+      where $R = \sum_{i=j}^J \gamma^{i-j} R(s^i,a^i)$ and $J$ is the index of the last action before deadline time $T_d$.
 
       \parbox{20cm}{
-      The final performance evaluation of area under the AP vs. Time curve between $T_s$ and $T_d$ is additive per action.
+      \textbf{Reward Function:} The final performance evaluation of area under the AP vs. Time curve between $T_s$ and $T_d$ is additive per action.
       We define the reward function as
@@
       \begin{center}\textbf{Reinforcement Learning}\end{center}
-      To compute $Q^\pi(s^j,a) = \mathbb{E} [R \mid s, a, \pi)]$, where $R = \sum_{i=j}^J \gamma^{i-j} R(s^i,a^i)$ and $J$ is the index of the last action before deadline time $T_d$, we run Monte Carlo policy iteration.
+      To compute , we run Monte Carlo policy iteration.
       We evaluate full episodes of the detection task on several thousand images, with a decreasing $\epsilon$-greedy policy.
@@
       \\
+
+    }; \addcenteredtitle{model}{Learning to Detect on a Budget}
+
+    % ==============================================================================
+    % RESULTS
+    \path (model.north east) ++(2cm,0cm) node(results) [style=tbox,text width=30cm] {
+    We evaluated on the PASCAL VOC 2007 detection task, with 20 Deformable Part Model detectors (one per class), and an additional
+    scene context action (GIST feature).
+    \\
+
+    We compared against a random baseline, an optimal static ordering, and an oracle ordering.
 
@@
 
-    }; \addcenteredtitle{model}{Learning the Policy}
-
-    % ==============================================================================
-    % RESULTS
-    \path (model.north east) ++(2cm,0cm) node(results) [style=tbox,text width=30cm] {
-    We evaluated on the PASCAL VOC 2007 detection task, with 20 Deformable Part Model detectors (one per class), and an additional
-    scene context action (GIST feature).
-    \\
-
-    We compared against a random baseline, an optimal static ordering, and an oracle ordering.
-
     \parbox{12cm}{
@@
     \includegraphics[width=17cm]{../../figures/weights.pdf}}
-    \\
-
-    \parbox{18cm}{
-    \includegraphics[width=17cm]{../../figures/trajectories.pdf}}%\hfill
-    \parbox{12cm}{
-    \textbf{Trajectories} Action selection traces are plotted in orange over many episodes; the size of the blue circles correspond to the increase in AP obtained by the action.
-Our policy does not stick a static order but selects actions dynamically to maximize the rewards obtained early on.}
     \\\\

### 2012-12-01 writeups/nips12/poster/poster.tex
baller version

@@
 % Custom variables
+
+\newcommand{\argmax}[1]{\underset{#1}{\operatorname{arg}\operatorname{max}}\;}
 
@@
         \parbox{10cm} {
-        \includegraphics[height=9cm]{../../figures/berkeley_seal.pdf}
+        \includegraphics[height=8cm]{../../figures/berkeley_seal.pdf}
         }
@@
               \begin{tabular}{cccc}
-                {\huge Sergey Karayev$^1$, \hfill} & {\huge Tobias Baumgartner$^2$, \hfill} & {\huge Mario Fritz$^3$, \hfill} & {\huge Trevor Darrell$^1$}\\\\
-                \multicolumn{4}{c}{\Large $^1$UC Berkeley, \hspace{2cm} $^2$RWTH Aachen, \hspace{2cm} $^3$MPI Informatics}
+                {\Large Sergey Karayev$^1$, \hfill} & {\Large Tobias Baumgartner$^2$, \hfill} & {\Large Mario Fritz$^3$, \hfill} & {\Large Trevor Darrell$^1$}\\\\
+                \multicolumn{4}{c}{\large $^1$UC Berkeley, \hspace{2cm} $^2$RWTH Aachen, \hspace{2cm} $^3$MPI Informatics}
               \end{tabular}
@@
 
-    % ==============================================================================
-    % ABSTRACT
-    \path (title.south west) ++(0cm,-2cm) + (-\arabic{title-left-margin}cm,0cm) node(introduction) [style=tbox,text width=30cm] {
+    %%% MOTIVATION
+    \path (title.south west) ++(0cm,-2cm) + (-\arabic{title-left-margin}cm,0cm) node(motivation) [style=tbox,text width=28cm] {
+    \textbf{\textsc{Problem}}
     \begin{itemize}
-      \item Our task is multi-class object detection in a setting where there is not enough time to evaluate all detectors.
-
-      \item We use reinforcement learning to learn a \emph{dynamic} policy for selecting detectors and classifiers, and learn to take actions that do not provide immediate reward.
-
-      \item We evaluate detection performance vs. time with the novel \emph{timeliness} measure, and test on the PASCAL VOC challenge.
+      \item Want to detect objects of many classes in an image.
+      \item Detectors and classifiers already exist, but there is \textbf{not enough time to run all detectors}.
     \end{itemize}
 
-    }; \addcenteredtitle{introduction}{Abstract} 
-    % The above line adds the title ``Introduction'' to the box named ``introduction''.
-
-    % ==============================================================================
-    % FIGURE 1 WITH EXPLANATION 
-    \path (introduction.south west) ++(0cm,-2cm) node(coding) [style=tbox,text width=30cm] {
-      \begin{center}
-        \includegraphics[width=24cm]{../../figures/pomdp_annotated.pdf}
-      \end{center}
-
+    \textbf{\textsc{Approach}}
     \begin{itemize}
-        \item An action $a \in \mathcal{A}$ can run detection for an object class $k$ in the whole image, or classify the scene.
-        \item Potential actions are considered according to their predicted \emph{value} $Q(s,a)$, which also depends on the \emph{belief state} $s$ of the system.
-        \item The selected action returns observations in the form of a list of detections, or simply an evaluated feature.
-        \item Observations update the belief state through an inference process.
-        \item The final evaluation is the area of the AP vs. Time curve between the start time $T_s$ and end time $T_d$.
+      \item Formulate \textbf{timeliness} evaluation of detection performance vs. time.
+      \item Treat detectors and classifiers as ``black boxes''; use reinforcement learning to find a \textbf{dynamic} policy for deploying them.
     \end{itemize}
 
-      \begin{center}\line(1,0){350}\end{center}
+    \textbf{\textsc{Results}}
+    \begin{itemize}
+      \item Learn to take actions that do not provide immediate reward.
+      \item Wrapping per-class detectors in our system and setting a deadline\\\textbf{increases the multi-class Average Precision at deadline and before.}
+    \end{itemize}
+    }; \addcenteredtitle{motivation}{1. Motivation}
+
+    %%% MODEL & REINFORCEMENT LEARNING
+    \path (motivation.south west) ++(0cm,-2cm) node(implementation) [style=tbox,text width=28cm] {
+      \parbox{16cm}{
+      \textbf{\textsc{AP vs Time and the Reward}}
+      \begin{itemize}
+        \item The final performance evaluation is the area under the AP vs. Time curve between $T_s$ and $T_d$.
+        \item Because this is additive per action, we define \begin{align*} R(s^j,a) = \Delta \text{ap} (t_T^j-\frac{1}{2}\Delta t) \end{align*}
+      \end{itemize}
+      }
+      \parbox{12cm}{\hfill\includegraphics[width=11cm]{../../figures/apvst_expl.pdf}}
+      \\
+
+      \textbf{\textsc{Learning $\pi(s)$}} with fitted Q-iteration iteration.
+      \begin{itemize}
+        \item Gather samples under current $\pi$ by running detection episodes on several thousand images.
+        \item Update policy-defining weights $\theta$ with $L_1$ regularization
+        \item Gradually decrease $\epsilon$-greediness of policy.
+      \end{itemize}
+      \vspace{1cm}
+
+      \textbf{\textsc{Reward discount $\gamma$}}
+      \begin{itemize}
+      \item $\gamma=0$ induces a completely greedy policy, and at $\gamma=1$ is full lookahead.
+      \item $\gamma = 0.4$ performs best in cross-validation on the final evaluation.
+      \end{itemize}
+      \vspace{1cm}
+
+      \textbf{\textsc{The belief state}} posterior $P(C_k|\mathbf{o})$ is updated with observations $\mathbf{o}$ of detector for class $k$.
+      \begin{itemize}
+        \item \emph{Direct} method simply replaces the posterior of the corresponding class(es).
+        \item \emph{MRF} (pictured) method runs loopy BP in an MRF model, updating all posteriors.
+        \item MRF weights are learned with $L_1$-regularization.
+      \end{itemize}
+    }; \addcenteredtitle{implementation}{3. Implementation}
+
+    %%% FIGURE 1
+    \path (motivation.north east) ++(2cm,0cm) node(figure1) [style=tbox,text width=38cm] {
+      \begin{center}
+        \includegraphics[width=38cm]{../../figures/figure1_with_pomdp.pdf}
+      \end{center}
+      \begin{itemize}
+        \item Action $a \in \mathcal{A}$ can run detector of object class $k$ on whole image, or classify the scene.
+        \item The selected action returns observations $\mathbf{o}$: a list of detections, or an evaluated feature.
+        \item We define our policy as taking an untaken action with maximum value.
+\begin{align*} \pi(s) = \argmax{a_i \in \mathcal{A} \setminus \mathcal{O}} Q(s,a_i) = \theta_\pi^\top \phi(s,a) \end{align*}
+        \item Must learn an accurate approximation of the value function \begin{align*}Q^\pi(s^j,a) = \mathbb{E} [R \mid s, a, \pi)]\end{align*} where $R = \sum_{i=j}^J \gamma^{i-j} R(s^i,a^i)$ and $J$ is the index of the last action before deadline time $T_d$.
+      \end{itemize}
+    }; \addcenteredtitle{figure1}{2. Sequential Multi-class Detection}
+
+%%% FEATURES AND WEIGHTS
+    \path (figure1.south west) ++(0cm,-2cm) node(features) [style=tbox,text width=38cm] {
+      The features $\phi(s, a)$ reflect
+      \begin{itemize}
+        \item the probability that class $C$ is present in the image and its degree of certainty, for all classes.
+        \item time to $T_s$ and to $T_d$, and the expected time of the action.
+      \end{itemize}
+      \vspace{5mm}
+
+      \parbox{18cm}{\includegraphics[width=17cm]{../../figures/weights_greedy.pdf}\\\centering \small{\textbf{Greedy}}}\hfill%
+      \parbox{18cm}{\includegraphics[width=17cm]{../../figures/weights_rl.pdf}\\\centering \small{\textbf{Reinforcement Learning}}}\\
+      \begin{center}Learning with a higher $\gamma$ results in policies reliant on the global scene feature.\end{center}
+    }; \addcenteredtitle{features}{4. Feature Representation and Policy Weights}
+
+%%% RESULTS
+    \path (figure1.north east) ++(2cm,0cm) node(results) [style=tbox,text width=28cm] {
+      We evaluated on the PASCAL VOC 2007 detection task, with 20 Deformable Part Model detectors (one per class), and an additional
+      scene context action (GIST feature).
+      \\
+
+      We compared against a random baseline, an optimal static ordering, and an oracle ordering.
 
@@
 Our policy selects actions dynamically to maximize the rewards obtained early on.}
-
-    }; \addcenteredtitle{coding}{Sequential Detection}
-
-    % ==============================================================================
-    % Learning the Policy 
-    \path (introduction.north east) ++(2cm,0cm) node(model) [style=tbox,text width=34 cm] {
-      \begin{center}
-        \includegraphics[width=30cm]{../../figures/figure1_extended_hor.pdf}
-      \end{center}
-
-      We define our policy as taking an untaken action with maximum value.
-      \begin{align*} \pi(s) = \arg\max_{a_i \in \mathcal{A} \setminus \mathcal{O}} Q(s,a_i) = \theta_\pi^\top \phi(s,a) \end{align*}
-
-      The value function
-      \begin{align*}Q^\pi(s^j,a) = \mathbb{E} [R \mid s, a, \pi)]\end{align*}
-      where $R = \sum_{i=j}^J \gamma^{i-j} R(s^i,a^i)$ and $J$ is the index of the last action before deadline time $T_d$.
-
-      \parbox{20cm}{
-      \textbf{Reward Function:} The final performance evaluation of area under the AP vs. Time curve between $T_s$ and $T_d$ is additive per action.
-      We define the reward function as
-      \begin{align*} R(s^j,a) = \Delta \text{ap} (t_T^j-\frac{1}{2}\Delta t) \end{align*}}
-      \parbox{14cm}{
-      \begin{center}
-        \includegraphics[height=10cm]{../../figures/apvst_expl.pdf}
-      \end{center}}
-      \\
-
-      \begin{center}\textbf{Reinforcement Learning}\end{center}
-      To compute , we run Monte Carlo policy iteration.
-      We evaluate full episodes of the detection task on several thousand images, with a decreasing $\epsilon$-greedy policy.
-      Policy weights $\theta$ are updated with $L_2$ regularization.
-
-      \paragraph{}
-      We evaluate different values of the reward discount $\gamma$, which at $0$ induces a completely greedy policy, and at $1$ has full lookahead.
-      We find $\gamma = 0.4$ to work best in cross-validation.
-      \\
-
-    }; \addcenteredtitle{model}{Learning to Detect on a Budget}
-
-    % ==============================================================================
-    % RESULTS
-    \path (model.north east) ++(2cm,0cm) node(results) [style=tbox,text width=30cm] {
-    We evaluated on the PASCAL VOC 2007 detection task, with 20 Deformable Part Model detectors (one per class), and an additional
-    scene context action (GIST feature).
-    \\
-
-    We compared against a random baseline, an optimal static ordering, and an oracle ordering.
-
-    \begin{center}\textbf{Feature Representation}\end{center}
-      The features $\phi(s, a)$ are composed of\\
-
-      {\small
-      \begin{tabularx}{0.8\linewidth}{p{0.23\linewidth}p{0.69\linewidth}}
-      $P(C_a)$ & The prior probability of presence of the class that corresponds to the detector of action $a$ (omitted for the scene-context action).\\
-
-      $P(C_0|\mathbf{o}) \ldots P(C_K|\mathbf{o})$ & The presence probabilities for all classes, conditioned on the current set of observations.\\
-
-      $H(C_0|\mathbf{o}) \ldots H(C_K|\mathbf{o})$ & The entropies for all classes, conditioned on the current set of observations. \\
-
-      $t^j_T$ & The time until deadline, and four other time features.\\
-      \end{tabularx}
-      }\\\\
-
-      \begin{center}\textbf{Updating the belief state}\end{center}
-      Observations $\mathbf{o}$ of detector for class $k$ update $P(C_k|\mathbf{o})$ either \emph{directly} (using a probability estimated by a classifier trained on the detector output) or through an \emph{MRF}.
-      The MRF is learned with $L_1$-regularization and inference is done with loopy belief propagation.
-
-    \parbox{12cm}{
-    \textbf{Weights} Learning with a higher $\gamma$ results in policies more relient on the global scene feature, for example.}%
-    \parbox{18cm}{\hfill
-    \includegraphics[width=17cm]{../../figures/weights.pdf}}
-    \\\\
 
@@
       \end{center}
+    }; \addcenteredtitle{results}{5. Evaluation}
 
-    }; \addcenteredtitle{results}{Results}
+%%% Conclusion
+    \path (results.south west) ++(0cm,-2cm) node(conclusion) [style=tbox,text width=28cm] {
+      Conclusions drawn, future work.
+    }; \addcenteredtitle{conclusion}{6. Conclusion}
 
 \end{tikzpicture}
-
 \end{center}
